---
title: "FREESurfer CT"
author: "Daniela Cossio"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
   html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    classoption:
    - twocolumn
---

```{css, echo=FALSE}
TOC {
  color: #F6B2DB;
  font-family: Times;
  font-size: "16px"; 
  border-color: #F6B2DB;
}

h1.title {
  color: black ;
  font-family: Times;
  font-size: "72px";
  padding: "10px 0";
  background-color: #F6B2DB ;
  text-align: center;
}

h4.date {
  color: black ;
  font-family: Times;
  font-size: "34px";
  text-align: center;
}

h4.author {
  color: black;
  font-size: "34px";
  font-family: Times;
  text-align: center;
}


h1,h2, h3, h4, h5 ,h6 {
  text-align: center;
  font-family: Times;
  
}

body, p, h2{
  color: black; 
  font-family: Times;
}

hr {
  height:5px;
  border-width:0;
  background-color: black ;
}



```

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 100)
```

```{r adding libraries,echo=FALSE, results='hide',message=FALSE}
library(ggplot2)
#(plyr)
library(ppcor)
library(tidyverse)
# library(dplyr)
# library(tidyr)
library(stringr)
library(kableExtra)
# library(data.table)
# library(network)
# library(tidygraph)
# library(ggraph)
# library(igraph)
# library(networkD3)
# library(CINNA)
# library(umap)
# library(plotly)
#library(factoextra)
#library(lsr)
# library(car)
library(ggpubr)
#library(entropy)
#library(ds4psy)
# library(pROC)
#library(devtools)
#library(BRRR)
#library(stats)
#library(afex)
library(knitr)
library(janitor)
library(car)
library(ggiraph)
library(ggiraphExtra)
library(moonBook)
library(nationalparkcolors)
library(gridExtra)
library(markdown)
```

```{r, Functions, echo=FALSE, results='hide',message=FALSE}
# Here i have created a bunch of functions for things actions that i will be using repetitively.

ReadingCSVFunc <- function(pathname){
  
   #' @description: purpose of this is to read in CSVs and clean them up 
  #' @return: DF
  
  read.csv(paste0(working_dir, pathname), header=TRUE)

}

TableOutput <- function(df){
      knitr::kable(df, row.names=F) %>% kable_styling(bootstrap_options =  c("striped", "hover", "condensed"),position = "center") %>% scroll_box(width = "600px", height = "300px") 
    
  }


CleanDF <- function(DF,Variable){
  
  DF <- DF %>% select(-c("subject_id"))
  
  subinfo <- sub_info  %>% select(c("subject_id", "sex", "age_scan_years","repo_status",Variable))
  
  cleanedDF <- cbind(subinfo, DF) %>% drop_na(Variable) 
  
  cleanedDF$sex[cleanedDF$sex=="Male"] <- 1 
  cleanedDF$sex[cleanedDF$sex=="Female"] <- 0
  cleanedDF$sex <- as.numeric(cleanedDF$sex)
  
    return (cleanedDF)
}



```

```{r reading in our CSVs, echo=FALSE, results='hide',message=FALSE, warning=FALSE}

working_dir <- "/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/Cortical_thickness/Freesurfer/"
#working_dir <- "/Users/danielacossio/Library/CloudStorage/GoogleDrive-dcossio1@uci.edu/Other computers/My iMac/Chrastil_Lab/Projects/SNAG/Cortical_thickness/Freesurfer/" # Laptop path

sub_info <- ReadingCSVFunc("subject_info.csv") %>% filter(!(subject_id %in% c("309", "341")))

left_ct <- read.delim(paste0(working_dir,"DK_LH_parc_atlas.csv"),header=TRUE)
right_ct <- read.delim(paste0(working_dir,"DK_RH_parc_atlas.csv"),header=TRUE)
sub_cort <- read.delim(paste0(working_dir,"DK_seg_atlas.csv"),header=TRUE)


```

```{r, Clean up our column names, echo=FALSE, results='hide',message=FALSE, warning=FALSE}


for (i in 1:length(colnames(left_ct))){
  
  if (grepl("_thickness", colnames(left_ct[i]))){
    print(colnames(left_ct[i]))
  #   str_remove(left_ct_colnames[i],"_thickness")
   colnames(left_ct)[i] <- str_remove(colnames(left_ct[i]),"_thickness")
    
  }
  
}


all_rois <- cbind(sub_info, left_ct)


for (i in 1:length(colnames(right_ct))){
  
  if (grepl("_thickness", colnames(right_ct[i]))){
    print(colnames(right_ct[i]))
  #   str_remove(left_ct_colnames[i],"_thickness")
   colnames(right_ct)[i] <- str_remove(colnames(right_ct[i]),"_thickness")
    
  }
  
}


all_rois <- cbind(all_rois,right_ct)

colnames(sub_cort)[1] <- "subjects"

all_rois <- cbind(all_rois,sub_cort)

all_rois <- all_rois[,unique(colnames(all_rois))]


all_rois$sex[all_rois$sex=="Male"] <- 1 
  all_rois$sex[all_rois$sex=="Female"] <- 0
  all_rois$sex <- as.numeric(all_rois$sex)

```



# Overview and Hypothesis 
Using the DK atlas output 

Partial correlation with sex, age and intrcranial volume as covariates
bonferroni correction




```{r, Apriori lists, echo=FALSE, results='hide',message=FALSE, warning=FALSE}


# precentral, postcentral, superoir parietal, superior frontal, caudate and putamen 
lh_apriori <- c("lh_postcentral","lh_precentral","lh_superiorparietal","lh_superiorfrontal", "lh_cuneus","lh_medialorbitofrontal","lh_entorhinal","lh_parahippocampal","lh_precuneus","lh_lateraloccipital","lh_posteriorcingulate")

rh_apriori <- c("rh_postcentral","rh_precentral","rh_superiorparietal","rh_superiorfrontal", "rh_cuneus","rh_medialorbitofrontal","rh_entorhinal","rh_parahippocampal","rh_precuneus","rh_lateraloccipital","rh_posteriorcingulate")

sub_apriori <- c("Left.Caudate","Right.Caudate","Left.Putamen","Right.Putamen","Left.Hippocampus","Right.Hippocampus")
  
all_apriori <- c(lh_apriori,rh_apriori,sub_apriori)

```

aprioris are ```r print(all_apriori) ``` 

<hr>

# Degrees Traveled {.tabset .tabset-dropdown} 
## Average {.tabset .tabset-pills} 

### All {.tabset .tabset-pills} 

```{r, All DE Apriori Average,echo=FALSE, results='hide',message=FALSE, warning=FALSE}


df <- all_rois %>% filter(loop_de_avg_degree != "NA")

cor_results <-
  data.frame(matrix(nrow = 0, ncol = 7)) %>%   `colnames<-`(c("roi", "estimate", "p.value", "statistic", "n", "gp", "Method"))

pcorlist <- list()

for (ROI in all_apriori) {
  
  print(ROI)
  if(!is.na(sum(df[[ROI]])) == FALSE){

    pcorlist[[ROI]] <- NA

  }else{
  pcorlist[[ROI]] <-
    pcor.test(x = df[["loop_de_avg_degree"]], y = df[[ROI]], z = df[, c("age_scan_years","sex","EstimatedTotalIntraCranialVol")])
  temp <- cbind(ROI, pcorlist[[ROI]])
  cor_results <- rbind(cor_results, temp)
  }
}

cor_results$adj.pval <- p.adjust(cor_results$p.value, method = "bonferroni", n = length(cor_results$p.value))
cor_results <- arrange(cor_results,p.value)


```

```{r,echo=FALSE,message=FALSE}
TableOutput(cor_results)
```

<br>

<hr>

<br>

### Female {.tabset .tabset-pills}

```{r, Female DE Apriori Average,echo=FALSE, results='hide',message=FALSE, warning=FALSE}


df <- all_rois %>% filter(loop_de_avg_degree != "NA") %>% filter(sex==0)


cor_results <-
  data.frame(matrix(nrow = 0, ncol = 7)) %>%   `colnames<-`(c("roi", "estimate", "p.value", "statistic", "n", "gp", "Method"))

pcorlist <- list()

for (ROI in all_apriori) {
  
  print(ROI)
  if(!is.na(sum(df[[ROI]])) == FALSE){

    pcorlist[[ROI]] <- NA

  }else{
  pcorlist[[ROI]] <-
    pcor.test(x = df[["loop_de_avg_degree"]], y = df[[ROI]], z = df[, c("age_scan_years","EstimatedTotalIntraCranialVol")])
  temp <- cbind(ROI, pcorlist[[ROI]])
  cor_results <- rbind(cor_results, temp)
  }
}


cor_results$adj.pval <- p.adjust(cor_results$p.value, method = "bonferroni", n = length(cor_results$p.value))
cor_results <- arrange(cor_results,p.value)


```

```{r,echo=FALSE,message=FALSE}
TableOutput(cor_results)
```

<br>

<hr>

<br>

### Male {.tabset .tabset-pills}


```{r, Male DE Apriori Average,echo=FALSE, results='hide',message=FALSE, warning=FALSE}


df <- all_rois %>% filter(loop_de_avg_degree != "NA") %>% filter(sex==1)


cor_results <-
  data.frame(matrix(nrow = 0, ncol = 7)) %>%   `colnames<-`(c("roi", "estimate", "p.value", "statistic", "n", "gp", "Method"))

pcorlist <- list()

for (ROI in all_apriori) {
  

  if(!is.na(sum(df[[ROI]])) == FALSE){

    pcorlist[[ROI]] <- NA

  }else{
  pcorlist[[ROI]] <-
    pcor.test(x = df[["loop_de_avg_degree"]], y = df[[ROI]], z = df[, c("age_scan_years","EstimatedTotalIntraCranialVol")])
  temp <- cbind(ROI, pcorlist[[ROI]])
  cor_results <- rbind(cor_results, temp)
  }
}


cor_results$adj.pval <- p.adjust(cor_results$p.value, method = "bonferroni", n = length(cor_results$p.value))
cor_results <- arrange(cor_results,p.value)


```

```{r,echo=FALSE,message=FALSE}
TableOutput(cor_results)
```



```{r, rh_cuneus, echo=FALSE, results='hide',message=FALSE, warning=FALSE}

fit.1 <- lm(loop_de_avg_degree ~ age_scan_years + EstimatedTotalIntraCranialVol , data=df)

df$residual1 <- residuals(fit.1)

fit.2 <- lm(rh_cuneus ~ age_scan_years +EstimatedTotalIntraCranialVol, data=df)
df$residual2 <- residuals(fit.2)

ggplot(df, aes(x=residual2, y=residual1)) +
   geom_point(color="#1E4273", size=8) +
   stat_smooth(method="lm",se=FALSE, color="#1E4273")+
  stat_cor(label.x.npc = 0.5, size=8) +
  labs(
    x = "loop_de_avg_degree",
    y = "rh_cuneus") +
  theme(legend.position = "right",  
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.ticks.y=element_blank(),
        axis.ticks.x=element_blank(),
        panel.background =element_blank(),
        axis.line = element_line(colour = "black"))

```

<br>

<hr>

<br>


# Angular Error  {.tabset .tabset-dropdown} 
## Average {.tabset .tabset-pills} 

### All {.tabset .tabset-pills} 

```{r, All AE Apriori Average,echo=FALSE, results='hide',message=FALSE, warning=FALSE}


df <- all_rois %>% filter(loop_ae_avg_degree != "NA")

cor_results <-
  data.frame(matrix(nrow = 0, ncol = 7)) %>%   `colnames<-`(c("roi", "estimate", "p.value", "statistic", "n", "gp", "Method"))

pcorlist <- list()

for (ROI in all_apriori) {
  
  if(!is.na(sum(df[[ROI]])) == FALSE){

    pcorlist[[ROI]] <- NA

  }else{
  pcorlist[[ROI]] <-
    pcor.test(x = df[["loop_ae_avg_degree"]], y = df[[ROI]], z = df[, c("age_scan_years","sex","EstimatedTotalIntraCranialVol")])
  temp <- cbind(ROI, pcorlist[[ROI]])
  cor_results <- rbind(cor_results, temp)
  }
}

cor_results$adj.pval <- p.adjust(cor_results$p.value, method = "bonferroni", n = length(cor_results$p.value))
cor_results <- arrange(cor_results,p.value)


```

```{r,echo=FALSE,message=FALSE}
TableOutput(cor_results)
```


```{r, lh_superiorparietal, echo=FALSE, results='hide',message=FALSE, warning=FALSE}

fit.1 <- lm(loop_ae_avg_degree ~ sex + age_scan_years + EstimatedTotalIntraCranialVol , data=df)

df$residual1 <- residuals(fit.1)

fit.2 <- lm(lh_superiorparietal ~ sex + age_scan_years +EstimatedTotalIntraCranialVol, data=df)
df$residual2 <- residuals(fit.2)

ggplot(df, aes(x=residual2, y=residual1)) +
   geom_point(color="#243D25", size=8) +
   stat_smooth(method="lm",se=FALSE, color="#243D25")+
  stat_cor(label.x.npc = 0.5, size=8) +
  labs(
    x = "loop_ae_avg_degree",
    y = "lh_superiorparietal") +
  theme(legend.position = "center",  
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        panel.background =element_blank(),
        axis.ticks.y=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line = element_line(colour = "black"))

```
```{r, rh_superiorparietal, echo=FALSE, results='hide',message=FALSE, warning=FALSE}

fit.1 <- lm(loop_ae_avg_degree ~ sex + age_scan_years + EstimatedTotalIntraCranialVol , data=df)

df$residual1 <- residuals(fit.1)

fit.2 <- lm(rh_superiorparietal ~ sex + age_scan_years +EstimatedTotalIntraCranialVol, data=df)
df$residual2 <- residuals(fit.2)

ggplot(df, aes(x=residual2, y=residual1)) +
   geom_point(color="#243D25") +
   stat_smooth(method="lm",se=FALSE, color="#243D25")+
  stat_cor(label.x.npc = 0.5) +
  labs(
    x = "loop_ae_avg_degree",
    y = "rh_superiorparietal") +
  theme(legend.position = "right",  
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
         axis.ticks.y=element_blank(),
        axis.ticks.x=element_blank(),
        panel.background =element_blank(),
        axis.line = element_line(colour = "black"))

```


<br>

<hr>

<br>

### Female {.tabset .tabset-pills}

```{r, Female AE Apriori Average,echo=FALSE, results='hide',message=FALSE, warning=FALSE}


df <- all_rois %>% filter(loop_ae_avg_degree != "NA") %>% filter(sex==0)


cor_results <-
  data.frame(matrix(nrow = 0, ncol = 7)) %>%   `colnames<-`(c("roi", "estimate", "p.value", "statistic", "n", "gp", "Method"))

pcorlist <- list()

for (ROI in all_apriori) {
  
  if(!is.na(sum(df[[ROI]])) == FALSE){

    pcorlist[[ROI]] <- NA

  }else{
  pcorlist[[ROI]] <-
    pcor.test(x = df[["loop_ae_avg_degree"]], y = df[[ROI]], z = df[, c("age_scan_years","EstimatedTotalIntraCranialVol")])
  temp <- cbind(ROI, pcorlist[[ROI]])
  cor_results <- rbind(cor_results, temp)
  }
}


cor_results$adj.pval <- p.adjust(cor_results$p.value, method = "bonferroni", n = length(cor_results$p.value))
cor_results <- arrange(cor_results,p.value)

```

```{r,echo=FALSE,message=FALSE}
TableOutput(cor_results)
```

```{r, lh_postcentral, echo=FALSE, results='hide',message=FALSE, warning=FALSE}

fit.1 <- lm(loop_ae_avg_degree ~ age_scan_years + EstimatedTotalIntraCranialVol , data=df)

df$residual1 <- residuals(fit.1)

fit.2 <- lm(lh_postcentral ~ age_scan_years +EstimatedTotalIntraCranialVol, data=df)
df$residual2 <- residuals(fit.2)

ggplot(df, aes(x=residual2, y=residual1)) +
   geom_point(color="#F8B2AC",size=8) +
   stat_smooth(method="lm",se=FALSE, color="#F8B2AC")+
  stat_cor(label.x.npc = 0.5,size=8) +
  labs(
    x = "loop_ae_avg_degree",
    y = "lh_postcentral") +
  theme(legend.position = "right",  
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        panel.background =element_blank(),
         axis.ticks.y=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line = element_line(colour = "black"))

```

```{r, , echo=FALSE, results='hide',message=FALSE, warning=FALSE}


ggplot(df, aes(x=loop_ae_avg_degree, y=lh_postcentral)) +
   geom_point(color="#F8B2AC") +
   stat_smooth(method="lm",se=FALSE, color="#F8B2AC")+
  stat_cor(label.x.npc = 0.5) +
  labs(
    x = "loop_ae_avg_degree",
    y = "lh_postcentral") +
  theme(legend.position = "right",  
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        panel.background =element_blank(),
        axis.line = element_line(colour = "black"))

```

<br>

<hr>

<br>

### Male {.tabset .tabset-pills}

```{r, male AE Apriori Average,echo=FALSE, results='hide',message=FALSE, warning=FALSE}


df <- all_rois %>% filter(loop_ae_avg_degree != "NA") %>% filter(sex==1)


cor_results <-
  data.frame(matrix(nrow = 0, ncol = 7)) %>%   `colnames<-`(c("roi", "estimate", "p.value", "statistic", "n", "gp", "Method"))

pcorlist <- list()

for (ROI in all_apriori) {
  
  print(ROI)
  if(!is.na(sum(df[[ROI]])) == FALSE){

    pcorlist[[ROI]] <- NA

  }else{
  pcorlist[[ROI]] <-
    pcor.test(x = df[["loop_ae_avg_degree"]], y = df[[ROI]], z = df[, c("age_scan_years","EstimatedTotalIntraCranialVol")])
  temp <- cbind(ROI, pcorlist[[ROI]])
  cor_results <- rbind(cor_results, temp)
  }
}


cor_results$adj.pval <- p.adjust(cor_results$p.value, method = "bonferroni", n = length(cor_results$p.value))
cor_results <- arrange(cor_results,p.value)

```

```{r,echo=FALSE,message=FALSE}
TableOutput(cor_results)
```




## rad3 {.tabset .tabset-pills} 

### All {.tabset .tabset-pills} 
### Female {.tabset .tabset-pills}
### Male {.tabset .tabset-pills}