---
title: "Young MLINDIV Path Efficiency"
author: "Daniela Cossio"
date: "2/8/2023"
output: html_document
---

```{r adding libraries,echo=FALSE, results='hide',message=FALSE}
library(ggplot2)
#(plyr)
library(tidyverse)
# library(dplyr)
# library(tidyr)
library(stringr)
# library(data.table)
# library(network)
# library(tidygraph)
# library(ggraph)
# library(igraph)
# library(networkD3)
# library(CINNA)
# library(umap)
# library(plotly)
#library(factoextra)
#library(lsr)
# library(car)
library(ggpubr)
#library(entropy)
#library(ds4psy)
# library(pROC)
#library(devtools)
#library(BRRR)
#library(stats)
#library(afex)
library(knitr)
```


```{r Global Variables, ,echo=FALSE, results='hide',message=FALSE}
all_trial_path <- "/Users/danielacossio/Library/CloudStorage/GoogleDrive-dcossio1@uci.edu/My Drive/White matter tract/young-MLINDIV/DSI/Path_eff/Alltrials_PathEff/"
correct_trial_path <- "/Users/danielacossio/Library/CloudStorage/GoogleDrive-dcossio1@uci.edu/My Drive/White matter tract/young-MLINDIV/DSI/Path_eff/AccTrials_PathEff/"
rows2grab <- c("Tract Name", "number of tracts","mean length(mm)","diameter(mm)", "volume(mm^3)")
```

# Overview 
This is the analysis of white matter dsi studio connectometry for young maze path efficiency 

# <span style="color: darkblue;">Methods </span> 
##### **Participants** 
* Total number of scans = 
  * Total scans used in analysis=  
  
        
##### **Scan parameters** 
* Locations from UCSB and UCI

##### **QSIprep** 
* Version used: 
* The following parameters were used
  * dwi_denoise_window **5** 
  * hmc_model **3dSHORE** 
  * hmc-transform **Rigid** 
  * shoreline_iters **2**

### **DSI Studio**
*Version and tags used 
  * **chen-2022-01-26**

##### **Correlational connectometry**

###### **Parameters** 
* T-threshold =  vary by analysis
* Length = 25
* Permutation = 10,000
* pruning 4
* non normalized QA

#### **Analyses and Final sample sizes ** 

##### **Exclusions** 
* 347 was excluded due to low quality out liar in DSI 

##### Path Efficiency {.tabset} 
###### All subjects 
N= 79

T threshold  

* QA = 4  
* MD = 3.7  
* RD = 4.4  
* AD = 3.7  

###### Men 
N= 39  

T threshold  

* QA = 3.2 
* MD = 3.3  
* RD = 3.7  
* AD = 2.6  

###### Women
N= 40  

T threshold  

* QA = 4.1 
* MD = 2.9  
* RD = 2.4  
* AD = 3.4  


<!---------------------------------------Results---------------------------------->

# <span style="color: darkorange;"> Results with All trial path efficiency  </span>  

<!---------------------------------------QA PAth Efficiency --------------------------------->
## QA {.tabset}

```{r QA variables ,echo=FALSE, results='hide',message=FALSE}
# All subjects
QA_patheff_all_neg <- read.delim(paste0(all_trial_path,'QA/all_subs/QA_PE_all_neg.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame() %>% na.omit()

# MEN
QA_patheff_male_neg <- read.delim(paste0(all_trial_path,'QA/male/QA_PE_male_neg.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame()%>% na.omit()


# Women 
QA_patheff_female_neg <- read.delim(paste0(all_trial_path,'QA/female/QA_PE_fem_neg.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame() %>% na.omit()

```
### Summary of results 
DSI studio analyses revealed that there are significant negative associations between tracts with QA and Path efficiency. In this case, lower path efficiency is considered better performance. Lower PE scores are associated with higher QA values suggesting that better white matter integrity is associated with better PE performance. This finding was found when analyzing all subjects with sex and age as covariates and when splitting men and women.  

### All subjects
#### <span style="color: hotpink;"> Positive Corrs (FDR = 1.000000) </span> 
No significant tracts  

####  <span class="text-center" style="color: Teal;"> Neg Corrs (FDR = 0.004717)</span> 
```{r, echo=FALSE}
knitr::kable(QA_patheff_all_neg, row.names=F)
```

### Men
#### <span style="color: hotpink;"> Positive Corrs (FDR = 1.000000) </span> 
No significant tracts  

####  <span class="text-center" style="color: Teal;"> Neg Corrs (FDR = 0.008850)</span> 
```{r, echo=FALSE}
knitr::kable(QA_patheff_male_neg, row.names=F)
```


### Women
#### <span style="color: hotpink;"> Positive Corrs (FDR = 1.000000) </span> 
No significant tracts

####  <span class="text-center" style="color: Teal;"> Neg Corrs (FDR = 0.003205)</span> 
```{r, echo=FALSE}
knitr::kable(QA_patheff_female_neg, row.names=F)
```


## MD {.tabset}
```{r MD variables ,echo=FALSE, results='hide',message=FALSE}
# All subjects
MD_patheff_all_pos <- read.delim(paste0(all_trial_path,'MD/all_subs/MD_PE_all_pos.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame() %>% na.omit()

# MEN
MD_patheff_male_pos <- read.delim(paste0(all_trial_path,'MD/male/MD_PE_male.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame()%>% na.omit()


# Women 
MD_patheff_female_pos <- read.delim(paste0(all_trial_path,'MD/female/MD_PE_fem_pos.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame() %>% na.omit()

```

### Summary of results 
DSI studio analyses revealed that there are significant positive associations between tracts with MD and Path efficiency. Increased MD is a signal of impaired white matter integrity and increased diffusion levels.  In this case, lower path efficiency is considered better performance. Lower PE scores are associated with lower MD values suggesting that better white matter integrity is associated with better PE performance. This finding was found when analyzing all subjects with sex and age as covariates and when splitting men and women.  


### All subjects
#### <span style="color: hotpink;"> Positive Corrs (FDR = 0.000559) </span>  

```{r, echo=FALSE}
knitr::kable(MD_patheff_all_pos, row.names=F)
```  

####  <span class="text-center" style="color: Teal;"> Neg Corrs (FDR = 1.000000)</span> 
No Significant Tracts  

### Men
#### <span style="color: hotpink;"> Positive Corrs (FDR = 0.007752) </span> 
```{r, echo=FALSE}
knitr::kable(MD_patheff_male_pos, row.names=F)
```
####  <span class="text-center" style="color: Teal;"> Neg Corrs (FDR = 1.000000)</span> 
No Significant Tracts  

### Women 
#### <span style="color: hotpink;"> Positive Corrs (FDR = 0.002268) </span> 
```{r, echo=FALSE}
knitr::kable(MD_patheff_female_pos, row.names=F)
```
####  <span class="text-center" style="color: Teal;"> Neg Corrs (FDR = 1.000000)</span> 
No Significant Tracts  

## AD {.tabset}
```{r AD variables ,echo=FALSE, results='hide',message=FALSE}
# All subjects
AD_patheff_all_pos <- read.delim(paste0(all_trial_path,'AD/all_subs/AD_PE_all_pos.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame() %>% na.omit()

# MEN
AD_patheff_male_pos <- read.delim(paste0(all_trial_path,'AD/male/AD_PE_male_pos.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame()%>% na.omit()


# Women 
AD_patheff_female_pos <- read.delim(paste0(all_trial_path,'AD/female/AD_PE_fem_pos.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame() %>% na.omit()

```

### Summary of results 
DSI studio analyses revealed that there are significant positive associations between tracts with MD and Path efficiency. AD is a measure of water diffusion along an axon and can be non-specifically associated with axonal density.  In this case, lower path efficiency is considered better performance. Lower PE scores are associated with lower AD values suggesting that  better PE scores are associated with decreased AD. This finding was found when analyzing all subjects with sex and age as covariates and when splitting men and women.  

### All subjects
#### <span style="color: hotpink;"> Positive Corrs (FDR = 0.007407) </span> 
```{r, echo=FALSE}
knitr::kable(AD_patheff_all_pos, row.names=F)
```
####  <span class="text-center" style="color: Teal;"> Neg Corrs (FDR = 1.000000)</span> 
No Significant Tracts  

### Men
#### <span style="color: hotpink;"> Positive Corrs (FDR = 0.010753) </span> 
```{r, echo=FALSE}
knitr::kable(AD_patheff_male_pos, row.names=F)
```
####  <span class="text-center" style="color: Teal;"> Neg Corrs (FDR = 1.000000)</span> 
No Significant Tracts  

### Women 
#### <span style="color: hotpink;"> Positive Corrs (FDR = 0.000498) </span> 
```{r, echo=FALSE}
knitr::kable(AD_patheff_female_pos, row.names=F)
```
####  <span class="text-center" style="color: Teal;"> Neg Corrs (FDR = 1.000000)</span> 
No Significant Tracts  

## RD {.tabset}
```{r RD variables ,echo=FALSE, results='hide',message=FALSE}
# All subjects
RD_patheff_all_pos <- read.delim(paste0(all_trial_path,'RD/all_subs/RD_PE_all_pos.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame() %>% na.omit()

# MEN
RD_patheff_male_pos <- read.delim(paste0(all_trial_path,'RD/male/RD_PE_male_pos.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame()%>% na.omit()


# Women 
RD_patheff_female_pos <- read.delim(paste0(all_trial_path,'RD/female/RD_PE_fem_pos.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame() %>% na.omit()

```
### Summary of results 
DSI studio analyses revealed that there are significant positive associations between tracts with RDand Path efficiency. RD is a measure of water diffusion away from an axon.  In this case, lower path efficiency is considered better performance. Lower PE scores are associated with lower RD values suggesting that  better PE scores are associated decreased RD. This finding was found when analyzing all subjects with sex and age as covariates and when splitting men and women.  

### All subjects
#### <span style="color: hotpink;"> Positive Corrs (FDR = 0.010000) </span> 
```{r, echo=FALSE}
knitr::kable(RD_patheff_all_pos, row.names=F)
```
####  <span class="text-center" style="color: Teal;"> Neg Corrs (FDR = 1.000000)</span> 
No Significant Tracts  

### Men
#### <span style="color: hotpink;"> Positive Corrs (FDR = 0.012195) </span> 
```{r, echo=FALSE}
knitr::kable(RD_patheff_male_pos, row.names=F)
```
####  <span class="text-center" style="color: Teal;"> Neg Corrs (FDR = 1.000000)</span> 
No Significant Tracts  

### Women 
#### <span style="color: hotpink;"> Positive Corrs (FDR = 0.006757) </span> 
```{r, echo=FALSE}
knitr::kable(RD_patheff_female_pos, row.names=F)
```
####  <span class="text-center" style="color: Teal;"> Neg Corrs (FDR = 1.000000)</span> 
No Significant Tracts  

<!---------------------------------------END --------------------------------->

# <span style="color: darkorange;"> Results with only correct trial path efficiency  </span>  

<!---------------------------------------QA correct trial PAth Efficiency --------------------------------->
## QA {.tabset}

```{r correct PE QA variables ,echo=FALSE, results='hide',message=FALSE}
# All subjects

# MEN
QA_CorrPE_male_pos <- read.delim(paste0(correct_trial_path,'QA/male/QA_acctrialPE_male_pos.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame()%>% na.omit()

QA_CorrPE_male_neg <- read.delim(paste0(correct_trial_path,'QA/male/QA_acctrialPE_male_neg.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame()%>% na.omit()


# Women 
QA_CorrPE_female_neg <- read.delim(paste0(correct_trial_path,'QA/female/QA_acctrialPE_fem_neg.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame() %>% na.omit()

```
### Summary of results 

### Men
#### <span style="color: hotpink;"> Positive Corrs (FDR = 0.009276) </span> 
```{r, echo=FALSE}
knitr::kable(QA_CorrPE_male_pos, row.names=F)
```

####  <span class="text-center" style="color: Teal;"> Neg Corrs (FDR = 0.008850)</span> 
```{r, echo=FALSE}
knitr::kable(QA_CorrPE_male_neg, row.names=F)
```

### Women
####  <span class="text-center" style="color: Teal;"> Neg Corrs (FDR = 0.003650)</span> 
```{r, echo=FALSE}
knitr::kable(QA_CorrPE_female_neg, row.names=F)
```


## MD {.tabset}

### Summary of results 
No significant correlations across any groups 


## AD {.tabset}
```{r correct trials AD variables ,echo=FALSE, results='hide',message=FALSE}
# MEN
AD_CorrPE_male_neg <- read.delim(paste0(correct_trial_path,'AD/male/AD_acctrialPE_male_neg.csv'), header=FALSE, sep="\t") %>%  filter(V1 %in% rows2grab) %>% t() %>% `colnames<-`(rows2grab) %>% `[`(-c(1),) %>% as.data.frame()%>% na.omit()

```

### Summary of results 
Only males had significant negative correlations between AD and PE score 

### Men
#### <span style="color: hotpink;"> Positive Corrs (FDR = 1.000000) </span> 
No Significant Tracts  

####  <span class="text-center" style="color: Teal;"> Neg Corrs (FDR = 0.005882)</span> 
```{r, echo=FALSE}
knitr::kable(AD_CorrPE_male_neg, row.names=F)
```

## RD {.tabset}

### Summary of results 
No significant correlations across any groups 

<!---------------------------------------END --------------------------------->
# <span style="color: darkorange;"> END  </span>  
