---
title: "Tractometry Analysis"
date: "2023-04-07"
output:
   html_document: 
     toc: yes
     toc_float: yes
     toc_depth: 2
     theme: flatly
     code_folding: hide

---
```{css, echo=FALSE}

h1, h2 {
  text-align: center;
  font-weight: bold;
}
```

```{r adding libraries, echo=FALSE, message=FALSE, results='hide'}
library(ggplot2)
#(plyr)
library(tidyverse)
# library(dplyr)
# library(tidyr)
library(stringr)
library(kableExtra)
# library(data.table)
# library(network)
# library(tidygraph)
# library(ggraph)
# library(igraph)
# library(networkD3)
# library(CINNA)
# library(umap)
# library(plotly)
#library(factoextra)
#library(lsr)
# library(car)
library(ggpubr)
#library(entropy)
#library(ds4psy)
# library(pROC)
#library(devtools)
#library(BRRR)
#library(stats)
#library(afex)
library(knitr)
library(janitor)
# library(car)
# library(ggiraph)
# library(ggiraphExtra)
# library(moonBook)
library(nationalparkcolors)
library(ggprism)

```

```{r warning=FALSE, message=FALSE, echo = FALSE}
# WE'll need to make several lists ahead of time in order to get the if statements together 

subjects <- read.csv("/Users/danielacossio/Library/CloudStorage/GoogleDrive-dcossio1@uci.edu/My Drive/White matter tract/MidlifeWM_DSI2023/DSI/maze/maze_subinfo.csv") %>% select(subject_id) %>% `colnames<-`(c("V1"))

subInfo <- read.csv("/Users/danielacossio/Library/CloudStorage/GoogleDrive-dcossio1@uci.edu/My Drive/White matter tract/MidlifeWM_DSI2023/DSI/maze/maze_subinfo.csv") %>% select(sex,age_scan_years, repo_status)

subInfo$sex <- replace(subInfo$sex, subInfo$sex==0, "female")
subInfo$sex <- replace(subInfo$sex, subInfo$sex==1, "male")

npc_everglades <- park_palette("Everglades")
npc_channel <- park_palette("ChannelIslands")
npc_saguaro <- park_palette("Saguaro")

figpath <- "/Users/danielacossio/Library/CloudStorage/GoogleDrive-dcossio1@uci.edu/My Drive/White matter tract/MidlifeWM_DSI2023/DSI/tractometry/"
```

```{r Reading in the results for all subjects in maze, echo=FALSE, message=FALSE, results='hide'}

working_dir <- "/Users/danielacossio/Library/CloudStorage/GoogleDrive-dcossio1@uci.edu/My Drive/White matter tract/MidlifeWM_DSI2023/DSI/maze/tractometry"

master_tractometryDF <- data.frame(matrix(ncol = 0, nrow = 105))
databases <- c("ad","rd","qa","md")
ROI_folders <- list.dirs(working_dir, recursive = FALSE) # finding the main folders for ROI
for (ROI_folder in ROI_folders) {
  print(ROI_folder)

  for (db in 1:length(databases)){
    print(db)
    
    metric <- list.files(ROI_folder, pattern = paste0("*.",databases[db],".*txt"))
    
    for (m in metric){
      print(m)
      
      if (databases[db] == "qa"){
        
        roi_col <- substring(m, 19) %>% str_sub(end = -5) 
      
          tempdf<-
            read.table(paste0(ROI_folder, "/", m), sep = "\t") %>% filter(!str_detect(V1, c("mean_qa_post_norm"))) %>% select(V2) %>% `colnames<-`(paste0(databases[db],"_",roi_col)) 
          
           master_tractometryDF <- cbind(master_tractometryDF, tempdf)
          
} else {
        roi_col <- substring(m, 19) %>% str_sub(end = -5) 
      
          tempdf<-
            read.table(paste0(ROI_folder, "/", m), sep = "\t") %>% select(V2) %>% `colnames<-`(paste0(databases[db],"_",roi_col))
          
          master_tractometryDF <- cbind(master_tractometryDF, tempdf)
    }
  }
  }
}

rows <- read.table(paste0(ROI_folder, "/", m), sep = "\t") %>% select(V1) %>% filter(!str_detect(V1, c("mean_md")))
rows <- rbind(rows,subjects)

master_tractometryDF <- cbind(master_tractometryDF,rows) 
master_tractometryDF <- master_tractometryDF[ ,c(17,1:16)]

```

# <span style="color: green;"> QA </span>{.tabset}

## <span style="color: darkblue; font-size:25px; font-family:Arial;">  Summary </span>

<br><br><br><br><br><br><br>

```{r,  QA Values for,echo=FALSE, message=FALSE, results='hide'}
# Lets compare set up our QA data frame 
QAdf <- master_tractometryDF %>% select(V1,qa_Cingulum_L,qa_Cingulum_R,qa_Fornix_L,qa_Fornix_R) %>% filter(V1 %in% as.character(subjects$V1)) %>% mutate(sex = subInfo$sex)

m_QA <- QAdf %>% filter(sex=="male") 

f_QA <- QAdf %>% filter(sex=="female") 
```

## <span style="color: darkblue; font-size:25px; font-family:Arial;">  Men </span>

<center>
<span class="text-center" style="color: black; font-size:18px; font-family:Arial;"> **Distribution of data** </span>

</center>

```{r, male normality  Normality, echo=FALSE, message=FALSE, results='asis'}
# male left cingulum failed normality 0.02

male_cing_L_norm <- shapiro.test(m_QA$qa_Cingulum_L) #

male_cing_R_norm <- shapiro.test(m_QA$qa_Cingulum_R)

male_fornix_L_norm <- shapiro.test(m_QA$qa_Fornix_L)

male_fornix_R_norm <- shapiro.test(m_QA$qa_Fornix_R)
  
male_cing_norm_vals <-
  cbind(male_cing_L_norm[["p.value"]],
        male_cing_R_norm[["p.value"]],
        male_fornix_L_norm[["p.value"]],
        male_fornix_R_norm[["p.value"]]) %>% `colnames<-`(c("Left cingulum", "Right cingulum", "Left Fornix", "Right Fornix")) %>% `row.names<-`(c("Males"))

```

<span class="text-center" style="color: black; font-size:14px; font-family:Arial;">

The normality of the QA values was assessed using the shapiro-wilks test of normality. QA values from males was not normally        distributed in the area **left cingulum** (p = `r male_cing_norm_vals[1,1]`) but normally distributed in the **right cingulum** (p=`r male_cing_norm_vals[1,2]`), **Left fornix** (p=`r male_cing_norm_vals[1,3]`), and **Right Fornix** (p = `r male_cing_norm_vals[1,4]`).

<br>

**Table 1.p values from normality tests using shapiro-wilks.** </span>

```{r male table of normality , echo=FALSE, message=FALSE}
knitr::kable(male_cing_norm_vals)%>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "500px", height = "100px")
```

<br><br><br>

<center>
<span class="text-center" style="color: black; font-size:18px; font-family:Arial;"> **Descriptive stats** </span>
<br>
</center>

```{r Descriptitve stats for males }

m_QA_cing_L_summary <- summary(m_QA$qa_Cingulum_L)
m_QA_cing_R_summary <- summary(m_QA$qa_Cingulum_R)

m_QA_fornix_R_summary <- summary(m_QA$qa_Fornix_R) 
m_QA_fornix_L_summary <- summary(m_QA$qa_Fornix_L) 

QA_male_summary <- rbind(m_QA_cing_L_summary, m_QA_cing_R_summary,m_QA_fornix_L_summary,m_QA_fornix_R_summary) %>% `row.names<-`(c("Left cingulum", "Right cingulum", "Left Fornix", "Right Fornix")) %>% as.data.frame()
```

```{r male descriptive stats, echo=FALSE, message=FALSE}
knitr::kable(QA_male_summary)%>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "575px", height = "200px")
```

<br><br><br><br><br><br>

## <span style="color: darkblue; font-size:25px; font-family:Arial; text-align:center"> Women </span>

<center>
<span class="text-center" style="color: black; font-size:18px; font-family:Arial;"> **Distribution of data** </span>
</center>

<br>
```{r female Normality, echo=FALSE, message=FALSE}
#female left cingulum  # normal 0.8221
female_cing_L_norm <- shapiro.test(f_QA$qa_Cingulum_L)

#female left cingulum  # normal 0.8221
female_cing_R_norm <- shapiro.test(f_QA$qa_Cingulum_R)

female_fornix_L_norm <- shapiro.test(f_QA$qa_Fornix_L)

female_fornix_R_norm <- shapiro.test(f_QA$qa_Fornix_R)

female_norm_vals <-
  cbind(female_cing_L_norm[["p.value"]],
        female_cing_R_norm[["p.value"]],
        female_fornix_L_norm[["p.value"]],
        female_fornix_R_norm[["p.value"]]) %>% `colnames<-`(c("Left cingulum", "Right cingulum", "Left Fornix", "Right Fornix")) %>% `row.names<-`(c("Females"))
```

<span class="text-center" style="color: black; font-size:14px; font-family:Arial;">

The normality of the QA values was assessed using the  shapiro-wilks test of normality. QA values from females was normally distributed  in the **left cingulum** (p = `r female_norm_vals[1,1]`) and **right cingulum** (p=`r female_norm_vals[1,2]`), **Left Fornix** (p= `r female_norm_vals[1,3]`), **Right Fornix** (p= `r female_norm_vals[1,4]`)

<br>

**Table 1. P values from normality tests using shapiro-wilks.** </span>

```{r female table of normality , echo=FALSE, message=FALSE}
knitr::kable(female_norm_vals)%>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "500px", height = "100px")
```

<br><br><br>

<center>
<span class="text-center" style="color: black; font-size:18px; font-family:Arial;"> **Descriptive stats** </span>
</center>

```{r Female Descriptive stats,echo=FALSE, message=FALSE, results='hide'}

f_QA_cing_L_summary <- summary(f_QA$qa_Cingulum_L)
f_QA_cing_R_summary <- summary(f_QA$qa_Cingulum_R)

f_QA_fornix_L_summary <- summary(f_QA$qa_Fornix_L)
f_QA_fornix_R_summary <- summary(f_QA$qa_Fornix_R) 

QA_female_summary <- rbind(f_QA_cing_L_summary, f_QA_cing_R_summary,f_QA_fornix_L_summary,f_QA_fornix_R_summary) %>% `row.names<-`(c("Left cingulum", "Right cingulum", "Left Fornix", "Right Fornix")) %>% as.data.frame()
```

<br>

```{r female descriptive stats, echo=FALSE, message=FALSE}
knitr::kable(QA_female_summary)%>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "575px", height = "200px")
```

<br><br><br><br><br><br>

## <span style="color: darkblue; font-size:25px; font-family:Arial; text-align:center"> T Tests </span>

<br>
<center>
<span style="color: black; font-size:18px; font-family:Arial; text-align:center"> **P values from t tests** </span>
</center>

```{r ttest,echo=FALSE, message=FALSE, results='hide'}
QA_Cing_L <- wilcox.test(m_QA$qa_Cingulum_L,f_QA$qa_Cingulum_L)
QA_Cing_R <- wilcox.test(m_QA$qa_Cingulum_R,f_QA$qa_Cingulum_R)
QA_fornix_L <- t.test(m_QA$qa_Fornix_L,f_QA$qa_Fornix_R) 
QA_fornix_R <- wilcox.test(m_QA$qa_Fornix_R,f_QA$qa_Fornix_R) 

QA_pvalues <-
  cbind(QA_Cing_L[["p.value"]],
        QA_Cing_R[["p.value"]],
        QA_fornix_L[["p.value"]],
        QA_fornix_R[["p.value"]]) %>% `colnames<-`(c("Left cingulum", "Right cingulum", "Left Fornix", "Right Fornix")) %>% as.data.frame()

```

```{r T tests, echo=FALSE, message=FALSE}
knitr::kable(QA_pvalues, row.names = FALSE)%>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "575px", height = "100px")
```

<br><br><br><br><br><br>

<center>
<span style="color: black; font-size:18px; font-family:Arial; text-align:center"> **Figures** </span>
</center>
<br>

```{r QA Cingulum L, dev='png', fig.show='hide'}

  QA_L_Cing <- QAdf %>%
    ggplot(aes(x=sex, y= qa_Cingulum_L, group=sex)) +
      geom_boxplot(width=0.5 ,fill= c("#E45A5A", "#80792B")) +
      scale_y_binned(n.breaks=10, nice.breaks = TRUE) +
      labs(x= "Sex", y= " QA", title ="Left Cingulum" ) +
      theme(axis.title.x = element_text(vjust=- 4, size = 16),
            axis.title.y = element_text(vjust=8, size = 16), 
            axis.text.x = element_text(size = 12),
            axis.text.y = element_text(size = 12),
            panel.background =element_blank(),
            axis.line = element_line(colour = "black"),  
            plot.margin = margin(1, 2, 1, 1.5, "cm"), 
            plot.title = element_text(hjust = 0.5, vjust = 2, size = 16, face="bold"))

print(QA_L_Cing)
```

<center>
![**Figure 1. QA Values for Left Cingulum**](`r knitr::fig_chunk('QA Cingulum L', 'png')`)
</center>

<br><br>

```{r QA Cingulum R, dev='png', fig.show='hide'}
   
QA_R_Cing <- QAdf %>%
    ggplot(aes(x=sex, y= qa_Cingulum_R)) +
      geom_boxplot(width=0.5 ,fill= c("#E45A5A", "#80792B")) +
      scale_y_binned(n.breaks=10, nice.breaks = TRUE) +
      labs(x= "Sex", y= " QA", title ="Right Cingulum" ) +
      theme(axis.title.x = element_text(vjust=- 4, size = 16),
            axis.title.y = element_text(vjust=8, size = 16), 
            axis.text.x = element_text(size = 12),
            axis.text.y = element_text(size = 12),
            panel.background =element_blank(),
            axis.line = element_line(colour = "black"),  
            plot.margin = margin(1, 2, 1, 1.5, "cm"), 
            plot.title = element_text(hjust = 0.5, vjust = 2, size = 16, face="bold"))

print(QA_R_Cing)
```

<center>
![**Figure 2. QA Values for Right Cingulum**](`r knitr::fig_chunk('QA Cingulum R', 'png')`)
</center>

<br><br>

```{r QA Fornix L, dev='png', fig.show='hide'}

df_p_val <- data.frame(
  group1 = "female",
  group2 = "male",
  label = "*",
  y.position = 0.32
)


pdf(file = paste0(figpath,"corr_QA_FornixL.pdf"),width=10, height=8)  

QA_L_fornix <- QAdf %>% ggplot(aes(x=sex, y= qa_Fornix_L)) +
      geom_boxplot(width=0.5 ,fill= c("#E45A5A", "#80792B")) +
      scale_y_binned(n.breaks=10, nice.breaks = TRUE) +
      labs(x= "Sex", y= " QA" ) +
      theme(axis.title.x = element_blank(),
            axis.title.y = element_blank(), 
            axis.text.x = element_blank(),
            axis.text.y = element_text(size = 25),
            panel.background =element_blank(),
            axis.line = element_line(colour = "black"),  
            plot.margin = margin(3, 2, 3, 2, "cm")) +
  add_pvalue(df_p_val,
                     xmin = "group1",
                     xmax = "group2",
                     label = "label",
                     y.position = "y.position",# bracket
                     bracket.size = 1,
                    label.size = 10,
                      tip.length = c(0.05,0.05 )) +
  scale_y_continuous(n.breaks = 4)
  
print(QA_L_fornix)

 dev.off() 


```

<center>
![**Figure 2. QA Values for Right Cingulum**](`r knitr::fig_chunk('QA Fornix L', 'png')`)
</center>

<br><br>

```{r QA Fornix R, dev='png', fig.show='hide'}
   
QA_R_fornix <- QAdf %>%
    ggplot(aes(x=sex, y= qa_Fornix_R)) +
      geom_boxplot(width=0.5 ,fill= c("#E45A5A", "#80792B")) +
      scale_y_binned(n.breaks=10, nice.breaks = TRUE) +
      labs(x= "Sex", y= " QA", title ="Right Fornix" ) +
      theme(axis.title.x = element_text(vjust=- 4, size = 16),
            axis.title.y = element_text(vjust=8, size = 16), 
            axis.text.x = element_text(size = 12),
            axis.text.y = element_text(size = 12),
            panel.background =element_blank(),
            axis.line = element_line(colour = "black"),  
            plot.margin = margin(1, 2, 1, 1.5, "cm"), 
            plot.title = element_text(hjust = 0.5, vjust = 2, size = 16, face="bold"))

print(QA_R_fornix)
```

<center>

![**Figure 4. QA Values for Right Fornix**](`r knitr::fig_chunk('QA Fornix R', 'png')`)

</center>

<br><br><br><br><br><br>

# <span style="color: green;"> MD </span>{.tabset}

## <span style="color: darkblue; font-size:25px; font-family:Arial;">  Summary </span>

<br><br><br><br><br><br>

```{r,  MD Values for,echo=FALSE, message=FALSE, results='hide'}
# Lets compare set up our QA data frame 
MDdf <- master_tractometryDF %>% select(V1,md_Cingulum_L,md_Cingulum_R,md_Fornix_L,md_Fornix_R) %>% filter(V1 %in% as.character(subjects$V1)) %>% mutate(sex = subInfo$sex)

m_MD <- MDdf %>% filter(sex=="male") 

f_MD <- MDdf %>% filter(sex=="female") 
```

## <span style="color: darkblue; font-size:25px; font-family:Arial;">  Men </span>

<center>
<span class="text-center" style="color: black; font-size:18px; font-family:Arial;"> **Distribution of data** </span>

</center>
```{r, md male normality  Normality, echo=FALSE, message=FALSE, results='asis'}
# male left cingulum failed normality 0.02

MD_male_cing_L_norm <- shapiro.test(m_MD$md_Cingulum_L) #normal

MD_male_cing_R_norm <- shapiro.test(m_MD$md_Cingulum_R) #normal

MD_male_fornix_L_norm <- shapiro.test(m_MD$md_Fornix_L) # not normal but very barely 

MD_male_fornix_R_norm <- shapiro.test(m_MD$md_Fornix_R) #normal
  
MD_male_cing_norm_vals <-
  cbind(MD_male_cing_L_norm[["p.value"]],
        MD_male_cing_R_norm[["p.value"]],
        MD_male_fornix_L_norm[["p.value"]],
        MD_male_fornix_R_norm[["p.value"]]) %>% `colnames<-`(c("Left cingulum", "Right cingulum", "Left Fornix", "Right Fornix")) %>% `row.names<-`(c("Males"))

```

<span class="text-center" style="color: black; font-size:14px; font-family:Arial;">

The normality of the MD values was assessed using the shapiro-wilks test of normality. MD values from males was normally distributed for **left cingulum** (p = `r MD_male_cing_norm_vals[1,1]`) but normally distributed in the **right cingulum** (p=`r MD_male_cing_norm_vals[1,2]`), **Left fornix** (p=`r MD_male_cing_norm_vals[1,3]`), and **Right Fornix** (p = `r MD_male_cing_norm_vals[1,4]`).

<br>

**Table 1.p values from normality tests using shapiro-wilks.** </span>

```{r MD male table of normality , echo=FALSE, message=FALSE}
knitr::kable(MD_male_cing_norm_vals)%>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "500px", height = "100px")
```

<br><br><br>

<center>
<span class="text-center" style="color: black; font-size:18px; font-family:Arial;"> **Descriptive stats** </span>
<br>
</center>

```{r  MD Descriptitve stats for males }

m_MD_cing_L_summary <- summary(m_MD$md_Cingulum_L)
m_MD_cing_R_summary <- summary(m_MD$md_Cingulum_R)

m_MD_fornix_R_summary <- summary(m_MD$md_Fornix_R) 
m_MD_fornix_L_summary <- summary(m_MD$md_Fornix_L) 

MD_male_summary <- rbind(m_MD_cing_L_summary, m_MD_cing_R_summary,m_MD_fornix_L_summary,m_MD_fornix_R_summary) %>% `row.names<-`(c("Left cingulum", "Right cingulum", "Left Fornix", "Right Fornix")) %>% as.data.frame()
```

```{r MD male descriptive stats, echo=FALSE, message=FALSE}
knitr::kable(MD_male_summary)%>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "575px", height = "200px")
```

<br><br><br><br><br><br>

## <span style="color: darkblue; font-size:25px; font-family:Arial;">  Women </span>

<center>
<span class="text-center" style="color: black; font-size:18px; font-family:Arial;"> **Distribution of data** </span>
</center>

<br>
```{r  MD female Normality, echo=FALSE, message=FALSE}
#female left cingulum  # normal 
MD_female_cing_L_norm <- shapiro.test(f_MD$md_Cingulum_L)

#female left cingulum  # normal 
MD_female_cing_R_norm <- shapiro.test(f_MD$md_Cingulum_R)

MD_female_fornix_L_norm <- shapiro.test(f_MD$md_Fornix_L)

MD_female_fornix_R_norm <- shapiro.test(f_MD$md_Fornix_R)

MD_female_norm_vals <-
  cbind(MD_female_cing_L_norm[["p.value"]],
        MD_female_cing_R_norm[["p.value"]],
        MD_female_fornix_L_norm[["p.value"]],
        MD_female_fornix_R_norm[["p.value"]]) %>% `colnames<-`(c("Left cingulum", "Right cingulum", "Left Fornix", "Right Fornix")) %>% `row.names<-`(c("Females"))
```

<span class="text-center" style="color: black; font-size:14px; font-family:Arial;">

The normality of the MD values was assessed using the  shapiro-wilks test of normality. MD values from females was normally distributed  in the **left cingulum** (p = `r MD_female_norm_vals[1,1]`) and **right cingulum** (p=`r MD_female_norm_vals[1,2]`), **Left Fornix** (p= `r MD_female_norm_vals[1,3]`), **Right Fornix** (p= `r MD_female_norm_vals[1,4]`)

<br>

**Table 1.p values from normality tests using shapiro-wilks.** </span>

```{r MD Female table of normality , echo=FALSE, message=FALSE}
knitr::kable(MD_female_norm_vals)%>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "500px", height = "100px")
```

<br><br><br>

<center>
<span class="text-center" style="color: black; font-size:18px; font-family:Arial;"> **Descriptive stats** </span>
<br>
</center>

```{r  MD Descriptitve stats for females }

f_MD_cing_L_summary <- summary(f_MD$md_Cingulum_L)
f_MD_cing_R_summary <- summary(f_MD$md_Cingulum_R)

f_MD_fornix_R_summary <- summary(f_MD$md_Fornix_R) 
f_MD_fornix_L_summary <- summary(f_MD$md_Fornix_L) 

MD_female_summary <-
  rbind(
    f_MD_cing_L_summary,
    f_MD_cing_R_summary,
    f_MD_fornix_R_summary,
    f_MD_fornix_L_summary
  ) %>% `row.names<-`(c("Left cingulum", "Right cingulum", "Left Fornix", "Right Fornix")) %>% as.data.frame()
```

```{r MD female descriptive stats, echo=FALSE, message=FALSE}
knitr::kable(MD_female_summary)%>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "575px", height = "200px")
```




<br><br><br><br><br><br>

## <span style="color: darkblue; font-size:25px; font-family:Arial;">  T Test </span>

<center>
<span style="color: black; font-size:18px; font-family:Arial; text-align:center"> **P values from t tests** </span>
</center>

```{r  MD ttest,echo=FALSE, message=FALSE, results='hide'}
MD_Cing_L <- t.test(m_MD$md_Cingulum_L,f_MD$md_Cingulum_L)
MD_Cing_R <- t.test(m_MD$md_Cingulum_R,f_MD$md_Cingulum_R)
MD_fornix_L <- t.test(m_MD$md_Fornix_L,f_MD$md_Fornix_R) 
MD_fornix_R <- t.test(m_MD$md_Fornix_R,f_MD$md_Fornix_R) 

MD_pvalues <-
  cbind(MD_Cing_L[["p.value"]],
        MD_Cing_R[["p.value"]],
        MD_fornix_L[["p.value"]],
        MD_fornix_R[["p.value"]]) %>% `colnames<-`(c("Left cingulum", "Right cingulum", "Left Fornix", "Right Fornix")) %>% as.data.frame()

```

```{r  MD T tests, echo=FALSE, message=FALSE}
knitr::kable(MD_pvalues, row.names = FALSE)%>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "575px", height = "100px")
```

<br><br>
<center>
<span style="color: black; font-size:18px; font-family:Arial; text-align:center"> **Figures** </span>
</center>
<br>

```{r MD Cingulum L, dev='png', fig.show='hide'}

  MD_L_Cing <- MDdf %>%
    ggplot(aes(x=sex, y= md_Cingulum_L, group=sex)) +
      geom_boxplot(width=0.5 ,fill= c("#E45A5A", "#80792B")) +
      scale_y_binned(n.breaks=10, nice.breaks = TRUE) +
      labs(x= "Sex", y= " MD", title ="Left Cingulum" ) +
      theme(axis.title.x = element_text(vjust=- 4, size = 16),
            axis.title.y = element_text(vjust=8, size = 16), 
            axis.text.x = element_text(size = 12),
            axis.text.y = element_text(size = 12),
            panel.background =element_blank(),
            axis.line = element_line(colour = "black"),  
            plot.margin = margin(1, 2, 1, 1.5, "cm"), 
            plot.title = element_text(hjust = 0.5, vjust = 2, size = 16, face="bold"))

print(MD_L_Cing)
```

<center>
![**Figure 1. MD Values for Left Cingulum**](`r knitr::fig_chunk('MD Cingulum L', 'png')`)
</center>

<br><br>


```{r MD Cingulum R, dev='png', fig.show='hide'}

  MD_R_Cing <- MDdf %>%
    ggplot(aes(x=sex, y= md_Cingulum_R, group=sex)) +
      geom_boxplot(width=0.5 ,fill= c("#E45A5A", "#80792B")) +
      scale_y_binned(n.breaks=10, nice.breaks = TRUE) +
      labs(x= "Sex", y= " MD", title ="Right Cingulum" ) +
      theme(axis.title.x = element_text(vjust=- 4, size = 16),
            axis.title.y = element_text(vjust=8, size = 16), 
            axis.text.x = element_text(size = 12),
            axis.text.y = element_text(size = 12),
            panel.background =element_blank(),
            axis.line = element_line(colour = "black"),  
            plot.margin = margin(1, 2, 1, 1.5, "cm"), 
            plot.title = element_text(hjust = 0.5, vjust = 2, size = 16, face="bold"))

print(MD_R_Cing)
```

<center>
![**Figure 2. MD Values for Right Cingulum**](`r knitr::fig_chunk('MD Cingulum R', 'png')`)
</center>

<br><br>

```{r MD Fornix L, dev='png', fig.show='hide'}

MD_p_val <- data.frame(
  group1 = "female",
  group2 = "male",
  label = "*",
  y.position = 1.4
)


pdf(file = paste0(figpath,"corr_MD_FornixL.pdf"), width = 10, height=8) 
  MD_L_Fornix <- MDdf %>%
    ggplot(aes(x=sex, y= md_Fornix_L)) +
      geom_boxplot(width=0.5 ,fill= c("#E45A5A", "#80792B")) +
      scale_y_binned(n.breaks=10, nice.breaks = TRUE) +
      labs(x= "Sex", y= " MD" ) +
      theme(axis.title.x = element_blank(),
            axis.title.y = element_blank(), 
            axis.text.x = element_blank(),
            axis.text.y = element_text(size = 25),
            panel.background =element_blank(),
            axis.line = element_line(colour = "black"),  
            plot.margin = margin(3, 2, 3, 2, "cm")) +
    ylim(min(MDdf$md_Fornix_L),1.5) #+
  #scale_y_continuous(n.breaks = 4) 

print(MD_L_Fornix)

dev.off

```

<center>
![**Figure 3. MD Values for Left Fornix **](`r knitr::fig_chunk('MD Fornix L', 'png')`)
</center>

<br><br>

```{r MD Fornix R, dev='png', fig.show='hide'}

  MD_R_Fornix <- MDdf %>%
    ggplot(aes(x=sex, y= md_Fornix_R, group=sex)) +
      geom_boxplot(width=0.5 ,fill= c("#E45A5A", "#80792B")) +
      scale_y_binned(n.breaks=10, nice.breaks = TRUE) +
      labs(x= "Sex", y= " MD", title ="Right Fornix" ) +
      theme(axis.title.x = element_text(vjust=- 4, size = 16),
            axis.title.y = element_text(vjust=8, size = 16), 
            axis.text.x = element_text(size = 12),
            axis.text.y = element_text(size = 12),
            panel.background =element_blank(),
            axis.line = element_line(colour = "black"),  
            plot.margin = margin(1, 2, 1, 1.5, "cm"), 
            plot.title = element_text(hjust = 0.5, vjust = 2, size = 16, face="bold"))

print(MD_R_Fornix)
```

<center>
![**Figure 4. MD Values for Right Fornix **](`r knitr::fig_chunk('MD Fornix R', 'png')`)
</center>

<br><br><br><br><br><br>

# <span style="color: green;"> AD </span>{.tabset}

## <span style="color: darkblue; font-size:25px; font-family:Arial;">  Summary </span>

<br><br><br><br><br><br>

```{r,  AD Values for,echo=FALSE, message=FALSE, results='hide'}
# Lets compare set up our MD data frame 
ADdf <- master_tractometryDF %>% select(V1,ad_Cingulum_L,ad_Cingulum_R,ad_Fornix_L,ad_Fornix_R) %>% filter(V1 %in% as.character(subjects$V1)) %>% mutate(sex = subInfo$sex)

m_AD <- ADdf %>% filter(sex=="male") 

f_AD <- ADdf %>% filter(sex=="female") 
```

## <span style="color: darkblue; font-size:25px; font-family:Arial;">  Men </span>

<center>
<span class="text-center" style="color: black; font-size:18px; font-family:Arial;"> **Distribution of data** </span>

```{r, ad male normality  Normality, echo=FALSE, message=FALSE, results='asis'}

AD_male_cing_L_norm <- shapiro.test(m_AD$ad_Cingulum_L) #normal

AD_male_cing_R_norm <- shapiro.test(m_AD$ad_Cingulum_R) #normal

AD_male_fornix_L_norm <- shapiro.test(m_AD$ad_Fornix_L) # not normal but very barely 

AD_male_fornix_R_norm <- shapiro.test(m_AD$ad_Fornix_R) #normal
  
AD_male_cing_norm_vals <-
  cbind(AD_male_cing_L_norm[["p.value"]],
        AD_male_cing_R_norm[["p.value"]],
        AD_male_fornix_L_norm[["p.value"]],
        AD_male_fornix_R_norm[["p.value"]]) %>% `colnames<-`(c("Left cingulum", "Right cingulum", "Left Fornix", "Right Fornix")) %>% `row.names<-`(c("Males"))

```

<span style="color: black; font-size:14px; font-family:Arial;">

The normality of the AD values was assessed using the shapiro-wilks test of normality. AD values from males was normally distributed for **left cingulum** (p = `r AD_male_cing_norm_vals[1,1]`), **right cingulum** (p=`r AD_male_cing_norm_vals[1,2]`), **Left fornix** (p=`r AD_male_cing_norm_vals[1,3]`), and **Right Fornix** (p = `r AD_male_cing_norm_vals[1,4]`).

<br>

**Table 1.p values from normality tests using shapiro-wilks.** </span>

```{r AD male table of normality , echo=FALSE, message=FALSE}
knitr::kable(AD_male_cing_norm_vals)%>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "500px", height = "100px")
```

<br><br><br>

<center>
<span class="text-center" style="color: black; font-size:18px; font-family:Arial;"> **Descriptive stats** </span>
<br>
</center>

```{r  AD Descriptitve stats for males }

m_AD_cing_L_summary <- summary(m_AD$ad_Cingulum_L)
m_AD_cing_R_summary <- summary(m_AD$ad_Cingulum_R)

m_AD_fornix_R_summary <- summary(m_AD$ad_Fornix_R) 
m_AD_fornix_L_summary <- summary(m_AD$ad_Fornix_L) 

AD_male_summary <- rbind(m_AD_cing_L_summary, m_AD_cing_R_summary,m_AD_fornix_L_summary,m_AD_fornix_R_summary) %>% `row.names<-`(c("Left cingulum", "Right cingulum", "Left Fornix", "Right Fornix")) %>% as.data.frame()
```

```{r AD male descriptive stats, echo=FALSE, message=FALSE}
knitr::kable(AD_male_summary)%>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "575px", height = "200px")
```

<br><br><br><br><br><br>

## <span style="color: darkblue; font-size:25px; font-family:Arial;">  Women </span>

<center>
<span class="text-center" style="color: black; font-size:18px; font-family:Arial;"> **Distribution of data** </span>

```{r, ad female normality  Normality, echo=FALSE, message=FALSE, results='asis'}

AD_female_cing_L_norm <- shapiro.test(f_AD$ad_Cingulum_L) #normal

AD_female_cing_R_norm <- shapiro.test(f_AD$ad_Cingulum_R) #normal

AD_female_fornix_L_norm <- shapiro.test(f_AD$ad_Fornix_L) # not normal but very barely 

AD_female_fornix_R_norm <- shapiro.test(f_AD$ad_Fornix_R) #normal
  
AD_female_cing_norm_vals <-
  cbind(AD_female_cing_L_norm[["p.value"]],
        AD_female_cing_R_norm[["p.value"]],
        AD_female_fornix_L_norm[["p.value"]],
        AD_female_fornix_R_norm[["p.value"]]) %>% `colnames<-`(c("Left cingulum", "Right cingulum", "Left Fornix", "Right Fornix")) %>% `row.names<-`(c("Males"))

```

<span style="color: black; font-size:14px; font-family:Arial;">

The normality of the AD values was assessed using the shapiro-wilks test of normality. AD values from females was normally distributed for **left cingulum** (p = `r AD_female_cing_norm_vals[1,1]`), **right cingulum** (p=`r AD_female_cing_norm_vals[1,2]`), **Left fornix** (p=`r AD_female_cing_norm_vals[1,3]`), and **Right Fornix** (p = `r AD_female_cing_norm_vals[1,4]`).

<br>

**Table 1.p values from normality tests using shapiro-wilks.** </span>

```{r AD female table of normality , echo=FALSE, message=FALSE}
knitr::kable(AD_female_cing_norm_vals)%>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "500px", height = "100px")
```

<br><br><br>

<center>
<span class="text-center" style="color: black; font-size:18px; font-family:Arial;"> **Descriptive stats** </span>
<br>
</center>

```{r  AD Descriptitve stats for females }

f_AD_cing_L_summary <- summary(f_AD$ad_Cingulum_L)
f_AD_cing_R_summary <- summary(f_AD$ad_Cingulum_R)

f_AD_fornix_R_summary <- summary(f_AD$ad_Fornix_R) 
f_AD_fornix_L_summary <- summary(f_AD$ad_Fornix_L) 

AD_female_summary <- rbind(f_AD_cing_L_summary, f_AD_cing_R_summary,f_AD_fornix_L_summary,f_AD_fornix_R_summary) %>% `row.names<-`(c("Left cingulum", "Right cingulum", "Left Fornix", "Right Fornix")) %>% as.data.frame()
```

```{r AD female descriptive stats, echo=FALSE, message=FALSE}
knitr::kable(AD_female_summary)%>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "575px", height = "200px")
```

<br><br><br><br><br><br>

## <span style="color: darkblue; font-size:25px; font-family:Arial;">  T Test </span>

<center>
<span style="color: black; font-size:18px; font-family:Arial; text-align:center"> **P values from t tests** </span>
</center>

```{r  AD ttest,echo=FALSE, message=FALSE, results='hide'}

AD_Cing_L <- t.test(m_AD$ad_Cingulum_L,f_AD$ad_Cingulum_L)
AD_Cing_R <- t.test(m_AD$ad_Cingulum_R,f_AD$ad_Cingulum_R)
AD_fornix_L <- t.test(m_AD$ad_Fornix_L,f_AD$ad_Fornix_R) 
AD_fornix_R <- t.test(m_AD$ad_Fornix_R,f_AD$ad_Fornix_R) 

AD_pvalues <-
  cbind(AD_Cing_L[["p.value"]],
        AD_Cing_R[["p.value"]],
        AD_fornix_L[["p.value"]],
        AD_fornix_R[["p.value"]]) %>% `colnames<-`(c("Left cingulum", "Right cingulum", "Left Fornix", "Right Fornix")) %>% as.data.frame()

```

```{r  AD T tests, echo=FALSE, message=FALSE}
knitr::kable(AD_pvalues, row.names = FALSE)%>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "575px", height = "100px")
```

<br><br><br><br><br><br>

# <span style="color: green;"> RD </span>{.tabset}

## <span style="color: darkblue; font-size:25px; font-family:Arial;">  Summary </span>

```{r,  RD Values for,echo=FALSE, message=FALSE, results='hide'}
# Lets compare set up our MD data frame 
RDdf <- master_tractometryDF %>% select(V1,rd_Cingulum_L,rd_Cingulum_R,rd_Fornix_L,rd_Fornix_R) %>% filter(V1 %in% as.character(subjects$V1)) %>% mutate(sex = subInfo$sex)

m_RD <- RDdf %>% filter(sex=="male") 

f_RD <- RDdf %>% filter(sex=="female") 
```

## <span style="color: darkblue; font-size:25px; font-family:Arial;">  Men </span>
## <span style="color: darkblue; font-size:25px; font-family:Arial;">  Women </span>
## <span style="color: darkblue; font-size:25px; font-family:Arial;">  T Test </span>

