---
title: "DSP Analysis and summary 2025"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
   html_document:
    toc: true
    toc_float: true
    toc_depth: 6
    theme: flatly
editor_options: 
  chunk_output_type: inline
---
<!-- Reading in my libraries -->
```{r adding libraries,echo=FALSE, results='hide',message=FALSE}
library(ggplot2)
#(plyr)
library(tidyverse)
# library(dplyr)
# library(tidyr)
library(stringr)
library(kableExtra)
# library(data.table)
# library(network)
# library(tidygraph)
# library(ggraph)
# library(igraph)
# library(networkD3)
# library(CINNA)
# library(umap)
# library(plotly)
#library(factoextra)
#library(lsr)
# library(car)
library(ggpubr)
#library(entropy)
#library(ds4psy)
# library(pROC)
#library(devtools)
#library(BRRR)
#library(stats)
#library(afex)
library(knitr)
library(janitor)
library(car)
library(ggiraph)
library(ggiraphExtra)
library(moonBook)
library(nationalparkcolors)
library(gridExtra)
library(markdown)
library(psych)
library(ppcor)
library(mediation)
```


<!-- below is code for generating the markdown html. just basic aesthetics -->

```{css, echo=FALSE}
TOC {
  color: #F6B2DB;
  font-family: Arial;
  font-size: "16px"; 
  border-color: #F6B2DB;
}

h1.title {
  color: black ;
  font-family: Arial;
  font-size: "72px";
  padding: "10px 0";
  background-color: #F6B2DB ;
  text-align: center;
}

h4.date {
  color: black ;
  font-family: Arial;
  font-size: "34px";
  text-align: center;
}

h4.author {
  color: black;
  font-size: "34px";
  font-family: Arial;
  text-align: center;
}


h1,h2, h3, h4, h5 ,h6 {
  text-align: center;
  font-family: Arial;
  
}

body, p, h2{
  color: black; 
  font-family: Arial;
}

hr {
  height:5px;
  border-width:0;
  background-color: black ;
}



```

<!-- Below is a bunch of functions that reduce the code throughout the script -->
```{r functions, echo=FALSE, results='hide',message=FALSE}

ReadingCSVFunc <- function(pathname){
  
  read.delim(paste0(working_dir, pathname), header=FALSE,sep = "\t")
  
   #README
  #Purpose: to read in the CSVs that I extract from the correlational tractography from DSI studio.  
  #Inputs: You simply need to include the path to the CSV from the working directory. We set our working dir above so you just need the rest of the path.
  
}

CleanInput <- function(DF){
  #README
  # The purpose of this function is to take the CSV that I extract from the correlational tractography and that has already been read into the script and made into a dataframe. It is then cleaned to create a clean output that grabs the following rows: "Tract Name", "number of tracts","mean length(mm)", "total volume(mm^3)"), and then re organizes the information for each subject into one dataframe. There's an if statement because some CSVs only have one significant tract and it needs a slightly different code to reorganize that. 
  
  #INPUT: Should take in a DF that was created when you read in the CSV from the correlational tract analysis. The output of the ReadingCSVFunc

 DF <- DF %>% remove_empty("cols") 
  
  if(length(DF) < 3){
    DF <- DF %>% 
            filter(V1 %in% rows2grab) %>% 
              t() %>% 
                `colnames<-`(rows2grab) %>% 
                  as.data.frame() %>% 
                    `[`(-c(1),)
    
  } else{
    
    DF <- DF %>% 
      filter(V1 %in% rows2grab) %>% 
        t() %>% 
            `colnames<-`(rows2grab) %>% 
                `[`(-c(1),) %>% 
                    as.data.frame() 
  }
 
          
  return(DF)
  
}


Extract_raw_values <- function(DF,Metric) {
  # Purpose of this function is to clean the data without me having to copy and paste everything later. 
  
  # Data = raw unclean dataframe we want to clean up 
  # Metric will be either MD or QA
  # sex is either male or female
 
  
  # Let's read in our data frame 
  
  # grab  ROIcolumn names 
  colNames <- DF  %>% remove_empty("cols") %>%
  filter(V1 == "Tract Name") %>% t() %>% `[`(-1) 
  
  
  subinfo <- sub_info  %>% select(c("subject_id", "sex", "age_scan_years", "maze_accuracy_pct")) 
 
  # Let's grab our values 
  if (Metric == "MD"){
    Values <- DF %>% remove_empty("cols") %>% 
     filter(str_detect(V1, c("mean_md"))) %>%
   `colnames<-`(c("Subjects",colNames)) 
  }
  else{
    Values <- DF %>%
     remove_empty("cols") %>%
      filter(str_detect(V1, c("mean_qa"))) %>% 
  `colnames<-`(c("Subjects",colNames)) %>% filter(!str_detect(Subjects, c("sub-369"))) 

  }
  
  # now let's put this together 
  ConvToNum <-  apply(Values[,2:length(Values)],2, as.numeric)
  Values[,2:length(Values)] <- ConvToNum
  
  cleanedDF <- cbind(subinfo,Values) %>% na.omit() %>% select(-c("Subjects"))
  
  return (cleanedDF)
}


TableOutput <- function(df){
  knitr::kable(df, row.names=F) %>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "800px", height = "300px") 
}

```


# Overview of experiment and analyses

This is the complete analysis of the DSP task using white matter and bevaior and hormones. 

<br><br><br>

<hr>

# Methods {.tabset .tabset-pills} 

## **Participants** 

  * Total number of scans = 120 (males and females)  
  
  * Total scans used in analysis= 69  
  * Excluded subs 329 and 372 from analyses due to bad behavior data and Subject 347 and 424 failed quality 
  control check in DSI
  
    * All subjects = 69 <br>
    * Men = 24 <br>
    * Women = 45 <br>
    * Pre = 18 <br>
    * Peri = 14 <br>
    * Post = 13 <br>

<br><br>
<hr> 


  
## **Scan parameters** 

  * Locations from UCSB and UCI
  
<br><br>

<hr> 


## **QSIprep** 

  * Version used: 0.16.0RC3

  * The following parameters were used
    * dwi_denoise_window **5** 
    * hmc_model **3dSHORE** 
    * hmc-transform **Rigid** 
    * shoreline_iters **2**
<br><br>

<hr> 

## **DSI Studio**

  * Version and tags used via singularity container: **chen-2024-05-03**
  
  * **Parameters** 
    * T-threshold = 2.5
    * Length = 25
    * Permutation = 4,000
    * pruning 4
    * QA
    * Covariates: sex, age, and FNAME

<hr>


## **Hormones and behavior**

I am doing a mediation analysis to understand the relation ship between white matter, hormones, and performance on the dual solution paradigm.

From shuying's data, DSP is associated with estradial. Increased solution index is associated with increased solution index.

MD is negatively associated with Solution Index such that increased MD in the fornix is associated with less shortcuts. Essentially lower white matter integrity in fornix is associated with lower performance.

Hypothesis for mediation is that greater estradiol is driving the relationship in which greater integrity in the fornix for greater solution index. 


X= Mean diffusivity in fornix  
Y= greater SI on DSP task  
M= Estradiol  
<br>
<hr>
<br>

**Subject Numbers for DSP analyses**

Shuyings numbers are as follows:  
Women: 47  
MEn:29  
Total:76

Daniela's

Women: 47   
Men: 27  
Total: 74  

These are the subject I excluded but she included:  
352  
372  
388  

These were excluded later from hippocampal analyses so i just excluded their behavior here as well. Adding these in gives me 77 which is still not the correct number of subjects. I'm not sure which one is the extra. For now I'll add them back in but it shouldn't affect much. 


# Reading in and prepping our data {.tabset .tabset-fade}

<!-- Setting the path to our extracted diffusion data and grabbing our subject info -->
```{r reading in our CSVs, results='hide',message=FALSE}
working_dir <- "/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/DSI/DSP"

rows2grab <- c("Tract Name", "number of tracts","mean length(mm)","diameter(mm)", "volume(mm^3)")

behavior_sub_info <- read.csv("/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/sub_info_sheets/SNAG_Behavior.csv") # This is a sheet that has all of the subjects with at least one usable behavior task (Loop, maze, dsp)

DSP_DSI_DF <- read.csv("/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/sub_info_sheets/SNAG_DSP_scans.csv") %>% filter(!is.na(subject_id)) # This is from the main subject sheet and includes all subjects that have a dsp score AND should have a scan with them

path2tractometry <- ("/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/DSI/Tractometry/output")

sub_info <- read.csv("/Users/danielacossio/Documents/Chrastil_Lab/Projects/subject_info.csv")

# List of all subject directories
tractometry_subfiles <- list.dirs("/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/DSI/Tractometry/output", full.names = FALSE,recursive = FALSE)

data_dsp <- behavior_sub_info %>% filter(dsp_useable == "Yes") %>% filter(subject_id < 500) # dataframe with all subjects that have usable DSP
f_data_dsp <- data_dsp %>% filter(sex == "Female")
m_data_dsp<- data_dsp %>% filter(sex=="Male") # Men only


#This is going through and reading in the output from dsi studio and then combining it into one dataframe and then combining that with our data frame that contains our subject data. 

# create an empty dataframe to loop into
fornix_output_df <-  data.frame(matrix(ncol = 5, nrow = 0)) %>% `colnames<-`(c("subjects","QA_L_fornix","QA_R_fornix","MD_L_fornix","MD_R_fornix"))

# creating a loop to go into each sub dir. read in each txt file and extract the 
for(file in 1:length((tractometry_subfiles))){

  
  # creating an empty single row dataframe
  empty_loop_df <- data.frame(matrix(ncol = 5, nrow = 1))  %>% `colnames<-`(c("subjects","QA_L_fornix","QA_R_fornix","MD_L_fornix","MD_R_fornix"))
  
  # inputting the subject id
  empty_loop_df$subjects <- str_remove(tractometry_subfiles[file],"sub-")
  
  
  # Let's do a quick folder check to make sure it's not empty 
  
  
  if(file.size(paste0(path2tractometry,"/",tractometry_subfiles[file])) < 96) next
  
  #grabbing all the left and right variables 
  
  if (file.exists(paste0(path2tractometry,"/",tractometry_subfiles[file],"/",tractometry_subfiles[file],"_space-T1w_desc-preproc_dwi.ProjectionBasalGanglia_FornixL.stat.txt")) == FALSE) {
    L_fornix <- data.frame(matrix(ncol = 2, nrow = 2))
  } else{
    L_fornix <- read_delim(paste0(path2tractometry,"/",tractometry_subfiles[file],"/",tractometry_subfiles[file],"_space-T1w_desc-preproc_dwi.ProjectionBasalGanglia_FornixL.stat.txt"),col_names = FALSE) %>% filter(X1 %in% c("qa","md"))
  }
  
  
  if (file.exists(paste0(path2tractometry,"/",tractometry_subfiles[file],"/",tractometry_subfiles[file],"_space-T1w_desc-preproc_dwi.ProjectionBasalGanglia_FornixR.stat.txt")) == FALSE) {
    R_fornix <- data.frame(matrix(ncol = 2, nrow = 2))
  }else{
  
  R_fornix <- read_delim(paste0(path2tractometry,"/",tractometry_subfiles[file],"/",tractometry_subfiles[file],"_space-T1w_desc-preproc_dwi.ProjectionBasalGanglia_FornixR.stat.txt"),col_names = FALSE) %>% filter(X1 %in% c("qa","md"))
  }
  
  # Putting them into out dataframe
  #Grab all QA values
  empty_loop_df$QA_L_fornix <- L_fornix$X2[1] # row 1 is QA
  empty_loop_df$QA_R_fornix <- R_fornix$X2[1]
    
    
  empty_loop_df$MD_L_fornix <- L_fornix$X2[2] # row 2 is MD
  empty_loop_df$MD_R_fornix <- R_fornix$X2[2]
  
  fornix_output_df <- rbind(fornix_output_df,empty_loop_df)
}


# now we have to grab the information from sub info and combine but we need to make sure we're grabbing all the correct subjects from each dataframe. Something to note is that this final fornix data frame is based off of scans and includes some people who do not have a DSP score. There's probably a way to simplify the code below.

altered_sub_info <- DSP_DSI_DF %>% filter(subject_id %in% c(fornix_output_df$subjects)) 

fornix_output_df <- fornix_output_df %>%  filter(subjects %in% c(DSP_DSI_DF$subject_id))


clean_DF <- cbind(altered_sub_info,fornix_output_df)

clean_DF$QA_Whole_Fornix <- rowMeans(clean_DF[,c("QA_L_fornix","QA_R_fornix")])

clean_DF$MD_Whole_Fornix <- rowMeans(clean_DF[,c("MD_L_fornix","MD_R_fornix")])


all_women_clean_df <- clean_DF %>% filter(sex=="Female")

```

Below is a list of important variables:    
* working_dir  
* rows2grab  
* behavior_sub_info  
* DSP_DSI_DF  
* path2tractometry  
* sub_info  
* tractometry_subfiles  
* clean_DF  
* data_dsp  

<br><br>

<hr>

# Behavior and Hormones {.tabset .tabset-pills}

## Step 1: Normality check and visualization of data 

### DSP distribution & Normality (behav only) {.tabset}

Here I am plotting the data for all dsp(regardless of scan). There are a total of 74 subjects here. Shuying had about 76 subjects and i noted the discrpenacy above. You can see there is a right hand skew on this data and it does not pass normality test (p-value = 9.242e-05)

```{r}
ggplot(data_dsp, aes(x=dsp_si_true_pct)) +
   geom_bar(width = 0.1)
shapiro.test(data_dsp$dsp_si_true_pct)
```


<br>
<br>

The table below summarizes all of the columns. Each row indicates a column location.
```{r}
TableOutput(describe(data_dsp))
```

<br>
<br>

So can we then try and normalize the data?

Here let's normalize using log transform. Log transform does change the skew but also some numbers (0) are now labeled as inf. Meaning we should do something to make those turn into an acutal number  perhaps 0.0001?

```{r}
ggplot(data_dsp, aes(x=log(dsp_si_true_pct))) +
   geom_bar(width = 0.1)

#I think things need to be changed from 0 to 0. 001
shapiro.test(log(data_dsp$dsp_si_true_pct)) # this comes out as Na but shuyings did not so idk why that's happening.
```

<br>

LEt's try a square root transform 

The square root transform normalizes it a bit more but it still failed normality test. 
```{r}

ggplot(data_dsp, aes(x=sqrt(dsp_si_true_pct))) +
   geom_bar(width = 0.1)

shapiro.test(sqrt(data_dsp$dsp_si_true_pct)) # 

```

<br>

#### Females DSP Distribution & normality (behav only)

Now here i want to look at the skews for males and females separately. There's a bit of a skew and it does not pass normality (p-value = 0.001114)

```{r}
ggplot(f_data_dsp, aes(x=dsp_si_true_pct)) +
   geom_bar(width = 0.1)
shapiro.test(f_data_dsp$dsp_si_true_pct)
```

```{r}
df_dsp_norm <- f_data_dsp %>% 
  mutate_at(scale, .vars = vars(estradiol_spatial_pg_ml,
                                fsh_spatial_miu_ml,
                                dsp_si_true_pct))
```

LEt's look at a transformation of all womens data

log transform: again NA for normality test but does appear to fix it a bit
```{r}

ggplot(f_data_dsp, aes(x=log(dsp_si_true_pct))) +
   geom_bar(width = 0.1)

#I think things need to be changed from 0 to 0. 001
shapiro.test(log(f_data_dsp$dsp_si_true_pct)) # this comes out as Na but shuyings did not so idk why that's happening.


```

Square Transform: again still skewefd and fails normality. 

```{r}

ggplot(f_data_dsp, aes(x=sqrt(dsp_si_true_pct))) +
   geom_bar(width = 0.1)


shapiro.test(sqrt(f_data_dsp$dsp_si_true_pct)) #


```

<br>
<br>

#### Males DSP Distribution & normality (behav only)

Now let's look at males. Here there is a bit of a skew and it failes normality (p-value = 0.02375)

```{r}
ggplot(m_data_dsp, aes(x=dsp_si_true_pct)) +
   geom_bar(width = 0.1)
shapiro.test(m_data_dsp$dsp_si_true_pct)
```


<br>
<br>

#### Estradiol distribution & normality

Here let's look at estradial skews for all women who have a dsp score. It does not pass normality 4.352e-07
```{r}
ggplot(f_data_dsp, aes(x=estradiol_spatial_pg_ml)) +
   geom_bar(width = 10)
shapiro.test(f_data_dsp$estradiol_spatial_pg_ml)

```

Can we tranform Estradial . This still fails normality but just barely p-value = 0.03153
```{r}

ggplot(f_data_dsp, aes(x=log(estradiol_spatial_pg_ml))) +
   geom_freqpoly(width = 10)
shapiro.test(log(f_data_dsp$estradiol_spatial_pg_ml))
```

Square root?This still fails normality but just barely p-value = 0.002019
```{r}

ggplot(f_data_dsp, aes(x=sqrt(estradiol_spatial_pg_ml))) +
   geom_freqpoly(width = 10)
shapiro.test(sqrt(f_data_dsp$estradiol_spatial_pg_ml))
```

<br>

#### FSH distribution & normality

FSh also has a skew and fails normality p-value = 0.0008676

```{r}

ggplot(f_data_dsp, aes(x=fsh_spatial_miu_ml)) +
   geom_bar(width = 10)
shapiro.test(f_data_dsp$fsh_spatial_miu_ml)
```
<br> 

Can we tranform FSH . This still fails normality p-value = 0.0008156
```{r}

ggplot(f_data_dsp, aes(x=log(fsh_spatial_miu_ml))) +
   geom_freqpoly(width = 10)
shapiro.test(log(f_data_dsp$fsh_spatial_miu_ml))
```

Square root?This still fails normality p-value = 0.003438.
```{r}

ggplot(f_data_dsp, aes(x=sqrt(fsh_spatial_miu_ml))) +
   geom_freqpoly(width = 10)
shapiro.test(sqrt(f_data_dsp$fsh_spatial_miu_ml))
```


No good way to normalize this data so far. I will probably leave it as is. 

<br>
<br>

#### DSP+Scan Distribution  

So just like above, this data set is also right skewed and fails normality 0.005673

```{r}
ggplot(clean_DF, aes(x=clean_DF$dsp_si_true_pct)) +
   geom_bar(width = 0.1)
shapiro.test(clean_DF$dsp_si_true_pct)
```

<br>

Again, for women there is a skew but barely fails normality p=0.02
```{r}
ggplot(all_women_clean_df, aes(x=dsp_si_true_pct)) +
   geom_bar(width = 0.1)

shapiro.test(all_women_clean_df$dsp_si_true_pct)
```

So let's try transforming this

Log transform all subjects. This visually looks much less skewed but also has some infinate numbers so we can check normality. Might need to change the inf to 0?
```{r}

ggplot(clean_DF, aes(x=log(clean_DF$dsp_si_true_pct))) +
   geom_bar(width = 0.1)
shapiro.test(log(clean_DF$dsp_si_true_pct))

```

Just to check, sqrt. Fails normality because of the 0s P = 0.001583

```{r}

ggplot(clean_DF, aes(x=sqrt(clean_DF$dsp_si_true_pct))) +
   geom_bar(width = 0.1)
shapiro.test(sqrt(clean_DF$dsp_si_true_pct))

```


LEt's look at the females

Log transform all subjects. This visually looks much less skewed but also has some infinate numbers so we can check normality. Might need to change the inf to 0?
```{r}

ggplot(all_women_clean_df, aes(x=log(all_women_clean_df$dsp_si_true_pct))) +
   geom_bar(width = 0.1)
shapiro.test(log(all_women_clean_df$dsp_si_true_pct))

```

Just to check, sqrt. Fails normality because of the 0s P = 0.002123

```{r}

ggplot(all_women_clean_df, aes(x=sqrt(all_women_clean_df$dsp_si_true_pct))) +
   geom_bar(width = 0.1)
shapiro.test(sqrt(all_women_clean_df$dsp_si_true_pct))

```

<br>
<hr>
<br>

## Step 2: Prepare the mediation by grabbing our final df. Removing any rows that are NA 

<!-- Creating a dataframe for just the estradiaol people -->
```{r}
mediation_estradiol_DF <-
  clean_DF %>% dplyr::select(
    subject_id,
    sex,
    age_spatial_years,
    repo_status,
    dsp_si_true_pct,
    estradiol_scan_pg_ml,
    estradiol_spatial_pg_ml,
    progesterone_scan_ng_ml,
    testosterone_scan_ng_dl,
    fsh_scan_miu_ml,
    QA_L_fornix,
    QA_R_fornix,
    MD_L_fornix,
    MD_R_fornix,
    MD_Whole_Fornix,
    QA_Whole_Fornix
  ) %>% filter(!is.na(dsp_si_true_pct)) %>% filter(!is.na(estradiol_spatial_pg_ml)) %>% filter(sex == "Female")
```

<!-- Creating a dataframe for just the Testosterone people -->

```{r}
mediation_test_DF <-
  clean_DF %>% dplyr::select(
    subject_id,
    sex,
    age_spatial_years,
    repo_status,
    dsp_si_true_pct,
    estradiol_scan_pg_ml,
    progesterone_scan_ng_ml,
    testosterone_scan_ng_dl,
    fsh_scan_miu_ml,
    QA_L_fornix,
    QA_R_fornix,
    MD_L_fornix,
    MD_R_fornix
  ) %>% filter(!is.na(dsp_si_true_pct)) %>% filter(!is.na(testosterone_scan_ng_dl)) %>% filter(sex == "Female")

```

<!-- Creating a dataframe for just the FSH people -->

```{r}
mediation_FSH_DF <-
  clean_DF %>% dplyr::select(
    subject_id,
    sex,
    age_spatial_years,
    repo_status,
    dsp_si_true_pct,
    estradiol_scan_pg_ml,
    progesterone_scan_ng_ml,
    testosterone_scan_ng_dl,
    fsh_scan_miu_ml,
    fsh_spatial_miu_ml,
    QA_L_fornix,
    QA_R_fornix,
    MD_L_fornix,
    MD_R_fornix,
    MD_Whole_Fornix,
    QA_Whole_Fornix
  ) %>% filter(!is.na(dsp_si_true_pct)) %>% filter(!is.na(fsh_scan_miu_ml)) %>% filter(sex == "Female")
```



<br><br>

<hr>

# Can we replicate shuyings findings? {.tabset .tabset-pills}

## Estradiol

Below is the code that recreates shuyings results in her dissertation. 
"For the DSP task, women with higher estradiol levels took more shortcuts, such that higher estradiol levels were positively associated with solution index (rs(45) = 0.42, p = 0.002)". She used a one-tail spearman correlation because dsp and estradiol fail normality tests. Additionally she removed two subjects due to outliars. 

Below are the results without removing outliars
our results p=0.001601
N=47
```{r, warning=FALSE}

# this one uses spatial hormones
cor.test(f_data_dsp$estradiol_spatial_pg_ml,
         f_data_dsp$dsp_si_true_pct,
         conf.level = 0.95,
         alternative = "greater",
         method = "spearman")

#This one uses scan hormones
cor.test(f_data_dsp$estradiol_scan_pg_ml,
         f_data_dsp$dsp_si_true_pct,
         conf.level = 0.95,
         alternative = "greater",
         method = "spearman")
```


She also did a partial cor to control for age. here it is still significant even when controlling for age. p-value=0.02876795

```{r, warning=FALSE}
pcor.test(f_data_dsp$estradiol_spatial_pg_ml,
          f_data_dsp$dsp_si_true_pct,
          f_data_dsp$age_spatial_years, 
          method = "spearman") #p-value=0.02876795

```
          
          
Here it is if we remove outliars p= 0.0035. REplicates shuyings code and results. 

```{r, warning=FALSE}
f_data_dsp_outlier_e <- f_data_dsp  %>%  filter(!subject_id %in% c(
    "415", "355"))

cor.test(f_data_dsp_outlier_e$estradiol_spatial_pg_ml,
         f_data_dsp_outlier_e$dsp_si_true_pct,
         alternative = "greater",
         conf.level = 0.95,
         method = "spearman") #p-value:0.003529


```



### FSH

Here, its another one tailed correlation test. Pvalue 0.02903
```{r, warning=FALSE}
fsh <- f_data_dsp %>% filter(is.na(fsh_spatial_miu_ml) != TRUE)

cor.test(fsh$fsh_spatial_miu_ml,
         fsh$dsp_si_true_pct,
         conf.level = 0.95,
          alternative = "less",
         method = "spearman") # Pvalue 0.02903
```

This is a partial correlation that controls for spatial age and is not significant: Pvalue 0.414744. This replicates some of shuyins code but not what was in the script.
```{r}
pcor.test(fsh$fsh_spatial_miu_ml,
          fsh$dsp_si_true_pct,
          fsh$age_spatial_years, 
          method = "spearman")  # Pvalue 0.414744
```


Below is the code that replicated shuyings script for controlling for age.P#0.05638. It' a correlation with the residuals. 
```{r}

x <- fsh$fsh_spatial_miu_ml
y <- fsh$dsp_si_true_pct
z <- fsh$age_spatial_years
cor.test(lm(x ~ z)$residuals,
         lm(y ~ z)$residuals,
         alternative = "less",
         conf.level = 0.95,
         method = "spearman") #0.05638
```



<br>

## Hormone comparison

### estradiol

Average Scan Estradiol `r mean(all_women_clean_df$estradiol_scan_pg_ml)`

Average Spatial Estradiol `r mean(all_women_clean_df$estradiol_spatial_pg_ml)`
```{r}
hormones_df <- all_women_clean_df %>% dplyr::select(c("subject_id","estradiol_scan_pg_ml","estradiol_spatial_pg_ml","progesterone_scan_ng_ml","progesterone_spatial_ng_ml","fsh_scan_miu_ml","fsh_spatial_miu_ml")) #Creating a df that contains just the hormones so i can visualize them side by side.
```

Density plots of the scan and spatial estradiol. 
<!-- Theres probably a better way to compare them  -->
```{r}

ggplot(data=all_women_clean_df, aes(x=estradiol_scan_pg_ml)) +
  geom_density()

ggplot(data=all_women_clean_df, aes(x=estradiol_spatial_pg_ml)) +
  geom_density()

```

### FSH

Average Scan FSH `r mean(all_women_clean_df$fsh_scan_miu_ml)`

Average Spatial FSH `r mean(all_women_clean_df$fsh_spatial_miu_ml)`

Density plots of the scan and spatial FSH. They're basically identical tho so i'll need to check these. 

```{r}

ggplot(data=all_women_clean_df, aes(x=fsh_scan_miu_ml)) +
  geom_density()

ggplot(data=all_women_clean_df, aes(x=fsh_spatial_miu_ml)) +
  geom_density()


```

<br><br>

<hr>


<br><br>

<hr>

# Mediation {.tabset .tabset-fade}

## Estradiol

X <- White Matter
Y <- DSP SI
M <- Hormones /FSH

Step 1 of mediation is to complete the first correlation in which X= fornix and Y = DSP. WE need to regress our x and y. p= 

```{r}
model.1 <- lm(dsp_si_true_pct ~  MD_Whole_Fornix , mediation_estradiol_DF) 
summary(model.1)
```

```{r}
model.1.Left <- lm(dsp_si_true_pct ~  MD_L_fornix , mediation_estradiol_DF) 
summary(model.1.Left)
```

```{r}
model.1.R <- lm(dsp_si_true_pct ~  MD_R_fornix , mediation_estradiol_DF) 
summary(model.1.R)
```

Step 2 of mediation is to complete the next correlation in which M= hormones and X = Fornix. p=0.9646 So here the MD  and estradiol are not significant. Stopping here. 

```{r}
model.2 <- lm(estradiol_spatial_pg_ml  ~ MD_Whole_Fornix , mediation_estradiol_DF)
summary(model.2)
```






## FSH

X <- White Matter
Y <- DSP SI
M <- Hormones /FSH



Step 1 of mediation is to complete the first correlation in which X= MD whole fornix and Y = DSP. WE need to regress our x and y, 

```{r}
model.1 <- lm(dsp_si_true_pct ~ MD_Whole_Fornix , mediation_FSH_DF) 
summary(model.1)
```

Step 2 of mediation is to complete the next correlation in which M= hormones and Y = DSP. p=0.6713 This is where it gets a bit challenging here. because this doesn't replicate with shuyings thing. Probably because this is two-tailed and hers is one tailed. WE might be able to move forward with this tbh. 

```{r}
model.2 <- lm(fsh_spatial_miu_ml ~ MD_Whole_Fornix , mediation_FSH_DF)
summary(model.2)
```




# Summarized Results

- There's really no difference between scan and spatial hormones. FSH is the exact same between spatial and scan. Estradiol is a bit different between them but shouldn't be too much of a difference. Changes a bit of the significance but not overall relationships. 

- I can replicate shuyings one tailed analysies but i don't know if i can do an actual mediation analysis. When i do a linear regression, nothing is significant. 

- 
CANNOT REPLICATE THIS WITH NEW TRACTOMETRY VERSION: For estradiol, solution index is associated with MD. Shuyings results show that estradiol is associated with more shortcuts but estradiol is not associated with MD based on our linear regression here. So white matter contributes to SI performance, and so does estradiol but estradiol does not impact white matter. Therefore they may be influencing SI performance through different mechanisms. 

-similar for FSH. We know that MD and SI are associated. We know FSH and SI are associated. The problem is that MD and FSh are not associated. Therefore they are influencing performance via different mechanisms. 



# Correlational tractography results 