---
title: "DSP_SI"
author: "Daniela Cossio"
date: "10/9/2023"
output:
   html_document:
    toc: true
    toc_float: true
    toc_depth: 6
    theme: flatly
editor_options: 
  chunk_output_type: inline
---

```{r adding libraries,echo=FALSE, results='hide',message=FALSE}
library(ggplot2)
#(plyr)
library(tidyverse)
# library(dplyr)
# library(tidyr)
library(stringr)
library(kableExtra)
# library(data.table)
# library(network)
# library(tidygraph)
# library(ggraph)
# library(igraph)
# library(networkD3)
# library(CINNA)
# library(umap)
# library(plotly)
#library(factoextra)
#library(lsr)
# library(car)
library(ggpubr)
#library(entropy)
#library(ds4psy)
# library(pROC)
#library(devtools)
#library(BRRR)
#library(stats)
#library(afex)
library(knitr)
library(janitor)
library(car)
library(ggiraph)
library(ggiraphExtra)
library(moonBook)
library(nationalparkcolors)
library(gridExtra)
library(markdown)
```


```{css, echo=FALSE}
TOC {
  color: #F6B2DB;
  font-family: Arial;
  font-size: "16px"; 
  border-color: #F6B2DB;
}

h1.title {
  color: black ;
  font-family: Arial;
  font-size: "72px";
  padding: "10px 0";
  background-color: #F6B2DB ;
  text-align: center;
}

h4.date {
  color: black ;
  font-family: Arial;
  font-size: "34px";
  text-align: center;
}

h4.author {
  color: black;
  font-size: "34px";
  font-family: Arial;
  text-align: center;
}


h1,h2, h3, h4, h5 ,h6 {
  text-align: center;
  font-family: Arial;
  
}

body, p, h2{
  color: black; 
  font-family: Arial;
}

hr {
  height:5px;
  border-width:0;
  background-color: black ;
}



```

```{r reading in our CSVs, echo=FALSE, results='hide',message=FALSE}
working_dir <- "/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/DSI_rerun_data/DSP/"

rows2grab <- c("Tract Name", "number of tracts","mean length(mm)","diameter(mm)", "volume(mm^3)")

sub_info <- read.csv("/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/DSI_rerun_data/subject_info.csv")
```

```{r functions, echo=FALSE, results='hide',message=FALSE}

ReadingCSVFunc <- function(pathname){
  
  read.delim(paste0(working_dir, pathname), header=FALSE,sep = "\t")
  
}

CleanInput <- function(DF){
  

  DF <- DF %>% 
      remove_empty("cols") %>% 
        filter(V1 %in% rows2grab) %>% 
          t() %>% 
            `colnames<-`(rows2grab) %>% 
                `[`(-c(1),) %>% 
                    as.data.frame()
  return(DF)
}


Extract_raw_values <- function(DF,Metric) {
  # Purpose of this function is to clean the data without me having to copy and paste everything later. 
  
  # Data = raw unclean dataframe we want to clean up 
  # Metric will be either MD or QA
  # sex is either male or female
 
  
  # Let's read in our data frame 
  
  # grab  ROIcolumn names 
  colNames <- DF  %>% remove_empty("cols") %>%
  filter(V1 == "Tract Name") %>% t() %>% `[`(-1) 
  
  
  subinfo <- sub_info  %>% select(c("subject_id", "sex", "age_scan_years", "maze_accuracy_pct")) 
 
  # Let's grab our values 
  if (Metric == "MD"){
    Values <- DF %>% remove_empty("cols") %>% 
     filter(str_detect(V1, c("mean_md"))) %>%
   `colnames<-`(c("Subjects",colNames)) 
  }
  else{
    Values <- DF %>%
     remove_empty("cols") %>%
      filter(str_detect(V1, c("mean_qa"))) %>% 
  `colnames<-`(c("Subjects",colNames)) %>% filter(!str_detect(Subjects, c("sub-369"))) 

  }
  
  # now let's put this together 
  ConvToNum <-  apply(Values[,2:length(Values)],2, as.numeric)
  Values[,2:length(Values)] <- ConvToNum
  
  cleanedDF <- cbind(subinfo,Values) %>% na.omit() %>% select(-c("Subjects"))
  
  return (cleanedDF)
}


TableOutput <- function(df){
  knitr::kable(df, row.names=F) %>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "600px", height = "300px") 
}

```

# Overview 
This is the analysis of white matter dsi studio connectometry for DSP

<br><br><br>

<hr>

# Methods {.tabset .tabset-pills} 

## **Participants** 

  * Total number of scans = 120 (males and females)  
  
  * Total scans used in analysis= 72  
  * Excluded subs 329 and 372 from analyses due to bad behavior data and Subject 347 failed quality 
  control check in DSI
  
    * All subjects = 72 <br>
    * Men = 27 <br>
    * Women = 45 <br>
    * Pre = 18 <br>
    * Peri = 14 <br>
    * Post = 13 <br>

<br><br>
<hr> 


  
## **Scan parameters** 

  * Locations from UCSB and UCI
  
<br><br>

<hr> 


## **QSIprep** 

  * Version used: 0.16.0RC3

  * The following parameters were used
    * dwi_denoise_window **5** 
    * hmc_model **3dSHORE** 
    * hmc-transform **Rigid** 
    * shoreline_iters **2**
<br><br>

<hr> 

## **DSI Studio**

  * Version and tags used via singularity container: **chen-2022-07-31**
  
  * **Parameters** 
    * T-threshold = 2.5
    * Length = 25
    * Permutation = 4,000
    * pruning 4
    * non normalized QA
    * Covariates: sex, age, and FNAME

<hr>

<br><br><br><br><br>

# **Solution index results**  


## QA {.tabset .tabset-pills}

### All subjects

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.186047)</strong> </span>

<br><br><br><br>


<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.024621)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("QA/all.DSP.SI.neg.csv")))
```


<hr>

<br><br><br><br>


### Females

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.031429)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("QA/female.dsp.si.pos.csv")))
```

<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.000398)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("QA/female.dsp.si.neg.csv")))
```


<hr>

<br><br><br><br>

### Males

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.001014)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("QA/males.DSP.QA.pos.csv")))
```

<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.000601)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("QA/males.DSP.QA.neg.csv")))
```


<hr>

<br><br><br><br>

### Pre


<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.000099)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("QA/pre.DSP.pos.csv")))
```

<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.001429)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("QA/pre.DSP.neg.csv")))
```


<hr>

<br><br><br><br>



### Peri



<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.002134)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("QA/peri.DSP.SI.neg.csv")))
```


<hr>

<br><br><br><br>

### Post


<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.011455)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("QA/post.DSP.SI.pos.csv")))
```

<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.007131)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("QA/post.DSP.SI.neg.csv")))
```


<hr>

<br><br><br><br>



## MD {.tabset .tabset-pills}
### All subjects

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.085551)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("MD/MD_DSP_si_true_all_pos.csv")))
```

<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.011940)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("MD/MD_DSP_si_true_all_neg.csv")))
```


<hr>

<br><br><br><br>

### Females


<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.011636)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("MD/MD_DSP_si_true_fem_neg.csv")))
```


<hr>

<br><br><br><br>

### Males

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.056582)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("MD/MD_DSP_si_true_male_pos.csv")))
```

<hr>

<br><br><br><br>

### pre

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.005970)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("MD/MD_DSP_si_true_pre_neg.csv")))
```


<hr>

<br><br><br><br>

### peri

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.045612)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("MD/MD_DSP_si_true_peri_pos.csv")))
```


<hr>

<br><br><br><br>

### post

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.011787)</strong> </span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("MD/MD_DSP_si_true_post_neg.csv")))
```


<hr>

<br><br><br><br>
