---
title: "SNAG Loop"
author: "Daniela Cossio"
date: "10/21/2023"
output:
   html_document:
    toc: true
    toc_float: true
    toc_depth: 6
    theme: flatly
editor_options: 
  chunk_output_type: inline
---

```{css, echo=FALSE}
h1, h2, h3, h4, h5 ,h6 {
  text-align: center;
  font-family: Times;
  
}

h1, h2 {
background-color: LavenderBlush;
  font-weight: bold;
}

body, p {
  color: black; 
  font-family: Times;
}


```

```{r adding libraries,echo=FALSE, results='hide',message=FALSE}
library(ggplot2)
#(plyr)
library(tidyverse)
# library(dplyr)
# library(tidyr)
library(stringr)
library(kableExtra)
# library(data.table)
# library(network)
# library(tidygraph)
# library(ggraph)
# library(igraph)
# library(networkD3)
# library(CINNA)
# library(umap)
# library(plotly)
#library(factoextra)
#library(lsr)
# library(car)
library(ggpubr)
#library(entropy)
#library(ds4psy)
# library(pROC)
#library(devtools)
#library(BRRR)
#library(stats)
#library(afex)
library(knitr)
library(janitor)
library(car)
library(ggiraph)
library(ggiraphExtra)
library(moonBook)
library(nationalparkcolors)
library(gridExtra)
library(markdown)
```

```{r reading in our CSVs, echo=FALSE, results='hide',message=FALSE}
working_dir <- "/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/DSI_rerun_data/"

 #working_dir <- "/Users/danielacossio/Library/CloudStorage/GoogleDrive-dcossio1@uci.edu/Other computers/My iMac/Chrastil_Lab/Projects/SNAG/DSI_rerun_data/" # Laptop path

rows2grab <- c("Tract Name", "number of tracts","mean length(mm)","diameter(mm)", "volume(mm^3)")


# sub_info <- read.csv("/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/DSI_rerun_data/subject_info.csv")

sub_info <- read.csv(paste0(working_dir,"subject_info.csv"))
```

```{r functions, echo=FALSE, results='hide',message=FALSE}

ReadingCSVFunc <- function(pathname){
  
  read.delim(paste0(working_dir, pathname), header=FALSE,sep = "\t")
  
}

CleanInput <- function(DF){
  

  DF <- DF %>% remove_empty("cols") 
  
  if(length(DF) < 3){
    DF <- DF %>% 
            filter(V1 %in% rows2grab) %>% 
              t() %>% 
                `colnames<-`(rows2grab) %>% 
                  as.data.frame() %>% 
                    `[`(-c(1),) 
    
  } else{
    
    DF <- DF %>% 
      filter(V1 %in% rows2grab) %>% 
        t() %>% 
            `colnames<-`(rows2grab) %>% 
                `[`(-c(1),) %>% 
                    as.data.frame() %>% 
                      arrange(`Tract Name`)
  }
 
          
  return(DF)
}


Extract_raw_values <- function(DF,Metric) {
  # Purpose of this function is to clean the data without me having to copy and paste everything later. 
  
  # Data = raw unclean dataframe we want to clean up 
  # Metric will be either MD or QA
  # sex is either male or female
 
  
  # Let's read in our data frame 
  
     colNames <- DF  %>% remove_empty("cols") %>%
  filter(V1 == "Tract Name") %>% t() %>% `[`(-1) 
  
  
  # grab  ROIcolumn names 
 
  
  subinfo <- sub_info  %>% select(c("subject_id", "sex", "age_scan_years", "maze_accuracy_pct", "REPO")) 
 
  # Let's grab our values 
  if (Metric == "MD"){
    Values <- DF %>% remove_empty("cols") %>% 
     filter(str_detect(V1, c("mean_md"))) %>%
   `colnames<-`(c("Subjects",colNames)) %>% filter(!str_detect(Subjects, c("sub-369"))) 
  }
  else{
    Values <- DF %>%
     remove_empty("cols") %>%
      filter(str_detect(V1, c("mean_qa"))) %>% 
  `colnames<-`(c("Subjects",colNames)) %>% filter(!str_detect(Subjects, c("sub-369"))) 

  }
  
  # now let's put this together 
  if (length(Values) < 3) {
    Values[,2] <- as.numeric(Values[,2])
  }else{
  ConvToNum <-  apply(Values[,2:length(Values)],2, as.numeric)
  Values[,2:length(Values)] <- ConvToNum
  }
  
  cleanedDF <- cbind(subinfo,Values) %>% na.omit() %>% select(-c("Subjects"))
  
  return (cleanedDF)
}


TableOutput <- function(df, style, width, height, caption){
 
  if (style == "classic"){
      knitr::kable(df, row.names=F) %>% kable_classic(full_width = F, html_font = "Cambria")
  } else {
      knitr::kable(df, row.names=F) %>% kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% scroll_box(width = paste0(width,"px"), height = paste0(height,"px")) 
    
  }

}

```
# Overview 
This is the analysis of white matter dsi studio connectometry for Maze and Loop 

# <span style="color: darkblue;">Methods </span>  {.tabset .tabset-pills} 

## **Participants** 

  * Total number of scans = 120 (males and females)  
  
  * Total scans used in analysis= 118  
  * Excluded subs 329 and 372 from analyses due to bad behavior data and Subject 347 failed quality 
  control check in DSI
   * Several subjects removed because they did not have rad3 score  
<br><br><br><br><br>

## **Loop**

Average 

  * All subjects = 43 
  * Men = 18
  * Women = 25
  * Stage
  * Pre = 11
  * Peri = 7 
  * Post = 17
  
rad3

  * All subjects = 39 
  * Men = 15
  * Women = 24
  * Stage
  * Pre = 10
  * Peri = 7 
  * Post = 7
<br><br><br><br><br>
 
  
## **Scan parameters** 

  * Locations from UCSB and UCI
<br><br><br><br><br>

## **QSIprep** 

  * Version used: 0.16.0RC3

  * The following parameters were used
    * dwi_denoise_window **5** 
    * hmc_model **3dSHORE** 
    * hmc-transform **Rigid** 
    * shoreline_iters **2**
<br><br><br><br><br>

## **DSI Studio**

  * Version and tags used via singularity container: **chen-2022-07-31**
  
  * **Parameters** 
    * T-threshold = 2.5
    * Length = 25
    * Permutation = 4,000
    * pruning 4
    * non normalized QA

<br><br><br><br><br>


## **Connectronomy analysis methods write up**
<br>

A diffusion spectrum imaging scheme was used, and a total of 128 diffusion sampling were acquired.  
The maximum b-value was 4990 s/mm². The in-plane resolution was 1.8 mm. The slice thickness wasc1.8 mm. The accuracy of b-table orientation was examined by comparing fiber orientations with those of a population-averaged template (Yeh et al. Neuroimage, 2018). The b-table was flipped by 
The diffusion data were reconstructed in the MNI space using q-space diffeomorphic reconstruction
(Yeh et al., Neuroimage, 58(1):91-9, 2011) to obtain the spin distribution function (Yeh et al., IEEE TMI, ;29(9):1626-35, 2010).  A diffusion sampling length ratio of 1.25 was used. The output resolution in diffeomorphic reconstruction was 1.8 mm isotropic. The tensor metrics were calculated using DWI with b-value lower than 1750 s/mm². The quantitative anisotropy was extracted as the local connectome fingerprint (LCF, Yeh et al. PLoS Comput Biol 12(11): e1005203) and used in the connectometry analysis.</p>
<br>

Diffusion MRI connectometry (Yeh et al. NeuroImage 125 (2016): 162-171) was used to derive the correlational tractography that has QA, MD, AD, and RD correlated with Maze Accuracy and path efficiency. A nonparametric Spearman partial correlation was used to derive the correlation, and the effect of sex, age_scan_years, and repo_status was removed using a multiple regression model. The total number of subjects varied on analysis (See Analyses and Final sample sizes above). A T-score threshold of 2.5 was assigned and tracked using a deterministic fiber tracking algorithm (Yeh et al. PLoS ONE 8(11): e80713, 2013) to obtain correlational tractography. A seeding region was placed at whole brain (39,49,29) .
<br>

 The tracks were filtered by topology-informed pruning (Yeh et al. Neurotherapeutics, 16(1), 52-58, 2019) with 4 iteration(s). A length threshold of 25 voxel distance was used to select tracks. To estimate the false discovery rate, a total of 4000 randomized permutations were applied to the group label to obtain the null distribution of the track length.</p>

<br><br><br><br><br><br>

# <span style="color: darkorange;"> Results </span>    

## <span style="color: darkorange;"> **Position Error** </span>  {.tabset .tabset-dropdown} 

### Rad3 {.tabset .tabset-pills}
#### Summary
Increased QA in many tracts outside of the limbic area are associated with a lower position error. Many regions involved in motor functions and movements showed negative associations with PE. Better white matter integrity in these regions corresponded to lower position error. In females, QA is negatively associated with tracts involved in motor/sensory input, corpus callosum body/taptum and the cingulum frontal-parietal  bundle. The corpus callosum forceps (major and minor), and congulum frontal parahippocampal appear to be positively associated with performance, greater QA values are associated with greater PE. suggesting that, reliance on the regions may lead to inefficient path integration.

in all subjects, MD is negatively associated with PE in limbic regions. Lower MD (better WM) is associated with higher MD. Suggesting that perhaps midlife adults are not relying on limbic regions to successfully navigate. In women, this relationship is maintained. Males display an opposite relationship with lower MD (better wm) being asscoaicted with lower PE (better performance ). Suggesting that in males, better WM in limbic regions is necessary for better path integration. 

#### QA {.tabset .tabset-pills}
##### All subject
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.000407)</strong> </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/fname_cov/all.loopPE.rad3.neg.csv")), "classic", 500, 200)
```

<br>

<p style="text-align:center ; font-size: 24px" > <strong> No FNAME </strong> </p>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.000760)</strong> </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/rad3pe.all.qa.neg.csv")), "classic", 500, 200)
```
<br><br><br>

##### Females

<!------ fname --------->  
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.033223)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/fname_cov/females.loopPE.rad3.pos.csv")), "classic", 500, 200)
```


<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.014408)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/fname_cov/females.loopPE.rad3.neg.csv")), "classic", 500, 200)
```

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong> No FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.005420)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/rad3pe.fem.qa.pos.csv")), "classic", 500, 200)
```


<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.029793)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/rad3pe.fem.qa.neg.csv")), "classic", 500, 200)
```


##### Males

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.039893)</strong> </span>
```{r,echo=FALSE,message=FALSE}

TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/fname_cov/males.loopPE.rad3.neg.csv")), "classic", 500, 200)
```

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong> No FNAME </strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.184615)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/rad3pe.male.qa.pos.csv")), "classic", 500, 200)
```
<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.040864)</strong> </span>
```{r,echo=FALSE,message=FALSE}

TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/rad3pe.male.qa.neg.csv")), "classic", 500, 200)
```


##### pre

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.088051)</strong> </span>
```{r,echo=FALSE,message=FALSE}

TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/fname_cov/pre.loopPE.rad3.neg.csv")), "classic", 500, 200)
```

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong> No FNAME </strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.068586)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/rad3pe.pre.qa.pos.csv")), "classic", 500, 200)
```
<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.020932)</strong> </span>
```{r,echo=FALSE,message=FALSE}

TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/rad3pe.pre.qa.neg.csv")), "classic", 500, 200)
```

<br><br>

##### Peri

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = )</strong> </span>
```{r,echo=FALSE,message=FALSE}

# TableOutput(CleanInput(ReadingCSVFunc("")), "classic", 500, 200)
```

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong> No FNAME </strong> </p>
<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR =  0.048013)</strong> </span>
```{r,echo=FALSE,message=FALSE}

TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/rad3pe.peri.qa.neg.csv")), "classic", 500, 200)
```

<br><br>

##### post

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = )</strong> </span>
```{r,echo=FALSE,message=FALSE}

# TableOutput(CleanInput(ReadingCSVFunc("")), "classic", 500, 200)
```

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong> No FNAME </strong> </p>

No significant results
<br><br>

#### MD {.tabset .tabset-pills}
##### All subject

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.086273)</strong> </span>
```{r,echo=FALSE,message=FALSE}
rad3PE_neg_MD_all <- CleanInput(ReadingCSVFunc("Loop/MD/fname/MD_loop_pe_rad3_all_neg.csv"))

TableOutput(rad3PE_neg_MD_all, "classic", 500, 200, "Table 1.Tracts with MD negatively associated with loop PE")
```

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong>Previous run</strong> </p>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.000616)</strong> </span>
```{r,echo=FALSE,message=FALSE}
rad3PE_neg_MD_all1 <- CleanInput(ReadingCSVFunc("Loop/MD/nofname/MD_loopRad3_all_neg.csv"))

TableOutput(rad3PE_neg_MD_all1, "classic", 500, 200, "Table 1.Tracts with MD negatively associated with loop PE")
```


##### Females
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.000221)</strong> </span>
```{r,echo=FALSE,message=FALSE}
rad3PE_neg_MD_fem <- CleanInput(ReadingCSVFunc("Loop/MD/fname/MD_loop_pe_rad3_fem_neg.csv"))

TableOutput(rad3PE_neg_MD_fem, "classic", 500, 200, "Table 1.Tracts with MD negatively associated with loop PE")
```

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong>Previous run</strong> </p>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.000443)</strong> </span>
```{r,echo=FALSE,message=FALSE}
rad3PE_neg_MD_fem1 <- CleanInput(ReadingCSVFunc("Loop/MD/nofname/MD_loopRad3_female_neg.csv"))

TableOutput(rad3PE_neg_MD_fem1, "classic", 500, 200, "Table 1.Tracts with MD negatively associated with loop PE")
```



##### Males
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.101287)</strong> </span>
```{r,echo=FALSE,message=FALSE}
rad3PE_pos_MD_male <- CleanInput(ReadingCSVFunc("Loop/MD/fname/MD_loop_pe_rad3_male_pos.csv"))

TableOutput(rad3PE_pos_MD_male, "classic", 500, 200, "Table 1.Tracts with MD positively associated with loop PE")
```


<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong>Previous run</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.058621)</strong> </span>
```{r,echo=FALSE,message=FALSE}
rad3PE_pos_MD_male1 <- CleanInput(ReadingCSVFunc("/Loop/MD/nofname/MD_loopRad3_male_pos.csv"))

TableOutput(rad3PE_pos_MD_male1, "classic", 500, 200, "Table 1.Tracts with MD positively associated with loop PE")
```

### Average {.tabset .tabset-pills}

#### QA {.tabset .tabset-pills}
##### All subject
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.002682)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/fname_cov/all.loopPE.average.neg.csv")), "classic", 500, 200)
```

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong>No FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.015957)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/avgpe.all.qa.pos.csv")), "classic", 500, 200)
```


<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.067564)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/avgpe.all.qa.neg.csv")), "classic", 500, 200)
```

##### Females
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR =  0.001412)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/fname_cov/female.loopPE.average.pos.csv")), "classic", 500, 200)
```


<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.003136)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/fname_cov/female.loopPE.average.neg.csv")), "classic", 500, 200)
```

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong>No FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR =  0.002551)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/avgpe.fem.qa.pos.csv")), "classic", 500, 200)
```


<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.001030)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/avgpe.fem.qa.neg.csv")), "classic", 500, 200)
```

<br><br><br>

##### Males
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.015386)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/fname_cov/males.loopPE.average.neg.csv")), "classic", 500, 200)
```

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong>No FNAME</strong> </p>
<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.017570)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/avgpe.male.qa.neg.csv")), "classic", 500, 200)
```

<br><br><br>


##### Pre
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.051982)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/fname_cov/pre.LoopPE.ave.neg.csv")), "classic", 500, 200)
```

<br><br>

<p style="text-align:center ; font-size: 24px" > <strong>No FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR =  0.163683)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/avgpe.pre.qa.pos.csv")), "classic", 500, 200)
```

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.037464)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/avgpe.pre.qa.neg.csv")), "classic", 500, 200)
```

<br><br><br>

##### Peri
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<br><br>

<p style="text-align:center ; font-size: 24px" > <strong>No FNAME</strong> </p>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.034684)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/avgpe.peri.qa.neg.csv")), "classic", 500, 200)
```

<br><br><br>

##### post
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>
did not run 
<br><br>

<p style="text-align:center ; font-size: 24px" > <strong>No FNAME</strong> </p>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.145591)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/PE/noFNAME/avgpe.post.qa.neg.csv")), "classic", 500, 200)
```

<br><br><br>



#### MD{.tabset .tabset-pills}
##### All subject
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong>Previous run</strong> </p>
##### Females
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong>Previous run</strong> </p>
##### Males
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong>Previous run</strong> </p>

## <span style="color: darkorange;"> **Degrees Traveled** </span>  {.tabset .tabset-dropdown} 
### Rad3 {.tabset .tabset-pills}
#### summary
#### QA {.tabset .tabset-pills}
##### All subject

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.000183)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/DE/fname/all.loopDE.rad3.pos.csv")), "classic", 500, 200)
```

<br><br>

<p style="text-align:center ; font-size: 24px" > <strong> No FNAME </strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR =  0.000549)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/DE/nofname/rad3de.all.qa.pos.csv")), "classic", 500, 200)
```

<br><br><br>

##### Females
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR =  0.000076)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("/Loop/QA/DE/fname/female.loopDE.rad3.pos.csv")), "classic", 500, 200)
```

<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.062500)</strong> </span>
```{r,echo=FALSE,message=FALSE}

TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/DE/fname/female.loopDE.rad3.neg.csv")), "classic", 500, 200)
```

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong> No FNAME</strong> </p>


<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR =  0.000189)</strong> </span>
```{r,echo=FALSE,message=FALSE}

TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/DE/nofname/rad3de.fem.qa.pos.csv")), "classic", 500, 200)
```

<br><br><br>


##### Males
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR =  0.178310)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("/Loop/QA/DE/fname/males.loopDE.rad3.pos.csv")), "classic", 500, 200)
```

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong> No FNAME </strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR =  0.082808)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/DE/nofname/rad3de.male.qa.pos.csv")), "classic", 500, 200)
```

<br><br><br>


##### Pre
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

no significant results
<br>

<p style="text-align:center ; font-size: 24px" > <strong> No FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR =  0.077631)</strong> </span>
```{r,echo=FALSE,message=FALSE}

TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/DE/nofname/rad3de.pre.qa.pos.csv")), "classic", 500, 200)
```


<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.007108)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/DE/nofname/rad3de.pre.qa.neg.csv")), "classic", 500, 200)
```

<br><br><br>

##### Peri
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>
did not run

<p style="text-align:center ; font-size: 24px" > <strong> No FNAME</strong> </p>


<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.068688)</strong> </span>
```{r,echo=FALSE,message=FALSE}

TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/DE/nofname/rad3de.peri.qa.neg.csv")), "classic", 500, 200)
```

<br><br><br>


##### Post

No significant results

<br><br><br>

#### MD {.tabset .tabset-pills}
##### All subject
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR =  0.042231)</strong> </span>
```{r,echo=FALSE,message=FALSE}
rad3DE_pos_MD_all <- CleanInput(ReadingCSVFunc("/Loop/MD/fname/MD_loop_DE_rad3_all_pos.csv"))

TableOutput(rad3DE_pos_MD_all, "classic", 500, 200, "Table 1.Tracts with MD positively associated with loop Degrees Traveled")
```

<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong>Previous run</strong> </p>
<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR =  0.029053)</strong> </span>
```{r,echo=FALSE,message=FALSE}
rad3DE_pos_MD_all1 <- CleanInput(ReadingCSVFunc("Loop/MD/nofname/MD_loopRad3_all_neg.csv"))

TableOutput(rad3DE_pos_MD_all1, "classic", 500, 200, "Table 1.Tracts with MD positively associated with loop Degrees Traveled")
```

##### Females
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>
<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR =  0.100772)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/MD/fname/MD_loop_De_rad3_fem_pos.csv")), "classic", 500, 200, "Table 1.Tracts with MD positively associated with loop Degrees Traveled")
```

<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.023033)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/MD/fname/MD_loop_De_rad3_fem_neg.csv")), "classic", 500, 200, "Table 1.Tracts with MD negatively associated with loop PE")
```
<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong>Previous run</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR =  0.023865)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/MD/nofname/MD_loopRad3_female_neg.csv")), "classic", 500, 200, "Table 1.Tracts with QA positively associated with loop Degrees Traveled")
```

<br>


##### Males
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

No results
<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong>Previous run</strong> </p>

No results

<br><br><br><br><br><br>

s


### average


## <span style="color: darkorange;"> **Angular Error** </span>  {.tabset .tabset-dropdown}
### Rad3 {.tabset .tabset-pills}
#### QA {.tabset .tabset-pills}
##### all subs

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.000188)</strong> </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/AE/fname/all.loopAE.rad3.neg.csv")), "classic", 500, 200," Table 1.Tracts with QA negatively associated with loop AE rad3 ")
```

<br>

<p style="text-align:center ; font-size: 24px" > <strong>Previous run</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.000675)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/AE/nofname/QA_loopAErad3_all_pos.csv")), "classic", 500, 200, "Table 1.Tracts with QA positively associated with loop AE rad3")
```

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.004296)</strong> </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/AE/nofname/QA_loopAErad3_all_neg.csv")), "classic", 500, 200," Table 1.Tracts with QA negatively associated with loop AE rad3 ")
```




<br><br><br>


##### males
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.026294)</strong> </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/AE/fname/male.loopAE.rad3.neg.csv")), "classic", 500, 200," Table 1.Tracts with QA negatively associated with loop AE rad3 ")
```

<br>
<br>

<p style="text-align:center ; font-size: 24px" > <strong>Previous run</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.012481)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/AE/nofname/QA_loopAErad3_male_pos.csv")), "classic", 500, 200, "Table 1.Tracts with QA positively associated with loop AE rad3")
```

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.024096)</strong> </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/AE/nofname/QA_loopAErad3_male_neg.csv")), "classic", 500, 200," Table 1.Tracts with QA negatively associated with loop AE rad3 ")
```

##### females
<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.077778)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/AE/fname/female.loopAE.rad3.pos.csv")), "classic", 500, 200, "Table 1.Tracts with QA positively associated with loop AE rad3")
```

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.006016)</strong> </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/AE/fname/female.loopAE.rad3.neg.csv")), "classic", 500, 200," Table 1.Tracts with QA negatively associated with loop AE rad3 ")
```

<p style="text-align:center ; font-size: 24px" > <strong>Previous run</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.015385)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/AE/nofname/QA_loopAErad3_female_pos.csv")), "classic", 500, 200, "Table 1.Tracts with QA positively associated with loop AE rad3")
```

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"> <strong>Negative  (FDR = 0.001027)</strong> </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("Loop/QA/AE/nofname/QA_loopAErad3_female_neg.csv")), "classic", 500, 200," Table 1.Tracts with QA negatively associated with loop AE rad3 ")
```
#### MD {.tabset .tabset-pills}
##### all subs
##### males
##### females

### Average {.tabset .tabset-pills}
#### QA {.tabset .tabset-pills}
##### all subs
##### males
##### females



#### MD {.tabset .tabset-pills}
##### all subs
##### males
##### females