---
title: "SNAG maze DSI results"
author: "Daniela Cossio"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
    html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    classoption:
    - twocolumn
---

<!-- below is code for generating the markdown html. just basic aesthetics -->
```{css, echo=FALSE}
TOC {
  color: #F6B2DB;
  font-family: Times;
  font-size: "16px"; 
  border-color: #F6B2DB;
}

h1 {
  color: black ;
  font-family: Times;
  font-size: "72px";
  padding: "10px 0";
  text-align: center;
}

h4.date {
  color: black ;
  font-family: Times;
  font-size: "34px";
  text-align: center;
}

h4.author {
  color: black;
  font-size: "34px";
  font-family: Times;
  text-align: center;
}


h2, h3, h4, h5 ,h6 {
  text-align: center;
  font-family: Times;
  
}

body, p{
  color: black; 
  font-family: Times;
}

hr {
  height:5px;
  border-width:0;
  background-color: black ;
}



```

<!-- More  basic Aesthetics -->

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 100)
```

<!-- Loading in libraries  -->
```{r adding libraries,echo=FALSE, results='hide',message=FALSE}
library(ggplot2)
#(plyr)
library(tidyverse)
# library(dplyr)
# library(tidyr)
library(stringr)
library(kableExtra)
# library(data.table)
# library(network)
# library(tidygraph)
# library(ggraph)
# library(igraph)
# library(networkD3)
# library(CINNA)
# library(umap)
# library(plotly)
#library(factoextra)
#library(lsr)
# library(car)
library(ggpubr)
#library(entropy)
#library(ds4psy)
# library(pROC)
#library(devtools)
#library(BRRR)
#library(stats)
#library(afex)
library(knitr)
library(janitor)
library(car)
library(ggiraph)
library(ggiraphExtra)
library(moonBook)
library(nationalparkcolors)
library(gridExtra)
library(markdown)
library(psych)
library(Rmisc)
```

<!-- Reading in the paths and the CSV that contains all of the subject info -->
```{r reading in our CSVs, echo=FALSE, results='hide',message=FALSE}
#working_dir <-"/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/DSI/Maze/"

working_dir <- "/Users/danielacossio/Desktop/MAZE/" #laptop

rows2grab <- c("Tract Name", "number of tracts","mean length(mm)", "total volume(mm^3)")


sub_info <- read.csv(paste0(working_dir,"MazeDSI.csv")) # this is a csv that contains all of the important subject information.
```

<!-- Below is a bunch of functions that reduce the code throughout the script -->
```{r functions, echo=FALSE, results='hide',message=FALSE}



ReadingCSVFunc <- function(pathname){
  #README 
  #Purpose of this code is to read in the CSVs that I extract from the correlational tractography from DSI studio. You simply need to include the path to the CSV from the working directory. We set our working dir above so you just need the rest of the path. 
  read.delim(paste0(working_dir, pathname), header=FALSE,sep = "\t")
}

CleanInput <- function(DF){
  
#README
  # The purpose of this function is to take the CSV that I extract from the correlational tractography and that has already been read into the script and made into a dataframe. It is then cleaned to create a clean output that grabs the following rows: "Tract Name", "number of tracts","mean length(mm)", "total volume(mm^3)"), and then re organizes the information for each subject into one dataframe. There's an if statement because some CSVs only have one significant tract and it needs a slightly different code to reorganize that. 
  
  DF <- DF %>% remove_empty("cols") 
  
  if(length(DF) < 3){
    DF <- DF %>% 
            filter(V1 %in% rows2grab) %>% 
              t() %>% 
                `colnames<-`(rows2grab) %>% 
                  as.data.frame() %>% 
                    `[`(-c(1),)
    
  } else{
    
    DF <- DF %>% 
      filter(V1 %in% rows2grab) %>% 
        t() %>% 
            `colnames<-`(rows2grab) %>% 
                `[`(-c(1),) %>% 
                    as.data.frame() 
  }
 
          
  return(DF)
}




TableOutput <- function(df){
  #Purpose of this is to create a clean table that can be shown on the html. Most of this is aesthetics but it's a lot so i created a function to reduce the clutter later. 
  # The DF that is input is a clean data frame of the correlational tractography. At this point it has gone through the ReadingCSVFunc, and CleanInput
      knitr::kable(df, row.names=F) %>% kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% scroll_box(width = "600px", height = "300px")
    
  }


# Extract_raw_values <- function(DF,Metric) {
#   # Purpose of this function is to clean the data without me having to copy and paste everything later. As well as extract 
#   
#   # Data = raw unclean dataframe we want to clean up 
#   # Metric will be either MD or QA
#   # sex is either male or female
#  
#   
#   # Let's read in our data frame 
#   
#      colNames <- DF  %>% remove_empty("cols") %>%
#   filter(V1 == "Tract Name") %>% t() %>% `[`(-1) 
#   
#   
#   # grab  ROIcolumn names 
#  
#   
#   subinfo <- sub_info  %>% select(c("subject_id", "sex", "age_scan_years", "loop_pe_rad3_m", "loop_de_rad3_degree","REPO")) 
#  
#   # Let's grab our values 
#   if (Metric == "MD"){
#     Values <- DF %>% remove_empty("cols") %>% 
#      filter(str_detect(V1, c("mean_md"))) %>%
#    `colnames<-`(c("Subjects",colNames)) %>% filter(!str_detect(Subjects, c("sub-369"))) 
#   }
#   else{
#     Values <- DF %>%
#      remove_empty("cols") %>%
#       filter(str_detect(V1, c("mean_qa"))) %>% 
#   `colnames<-`(c("Subjects",colNames)) %>% filter(!str_detect(Subjects, c("sub-369"))) 
# 
#   }
#   
#   # now let's put this together 
#   if (length(Values) < 3) {
#     Values[,2] <- as.numeric(Values[,2])
#   }else{
#   ConvToNum <-  apply(Values[,2:length(Values)],2, as.numeric)
#   Values[,2:length(Values)] <- ConvToNum
#   }
#   
#   cleanedDF <- cbind(subinfo,Values) %>% na.omit() %>% select(-c("Subjects"))
#   
#   return (cleanedDF)
# }


# TableOutput <- function(df, style, width, height, caption){
#  
#   if (style == "classic"){
#       knitr::kable(df, row.names=F) %>% kable_classic(full_width = F, html_font = "Cambria")
#   } else {
#       knitr::kable(df, row.names=F) %>% kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% scroll_box(width = paste0(width,"px"), height = paste0(height,"px")) 
#     
#   }
# 
# }


```

<hr> 
<br>

# Overview 
This is the analysis of white matter dsi studio connectometry for Maze and Loop 

<br>

<hr> 

# <span style="color: darkblue;">Methods </span>  {.tabset .tabset-pills} 

## **Participants** 

  * Total number of scans = 120 (males and females)  
  
  * Total scans used in analysis= 118  
  * Excluded subs 329 and 372 from analyses due to bad behavior data and Subject 347 failed quality control check in DSI
  

<br><br><br>

<hr>

## **Maze Accuracy and Path Efficiency**

  * All subjects = 80
  * Men = 21
  * Women = 59
  * Stage
  * Pre = 23
  * Peri = 20 
  * Post = 16
  
We had 82 last time so i excluded 2 more people from this analysis. one from low quality and then one bc of health issues. 347 and 424
  
<br><br><br><br><br>
 
 <hr>
  
## **Scan parameters** 

  * Locations from UCSB and UCI
  
<br><br><br><br><br>

<hr>

## **QSIprep** 

  * Version used: 0.16.0RC3

  * The following parameters were used
    * dwi_denoise_window **5** 
    * hmc_model **3dSHORE** 
    * hmc-transform **Rigid** 
    * shoreline_iters **2**
<br><br><br><br><br>

<hr>


## **DSI Studio**

  * Version and tags used via singularity container: **chen-2024-05-22**
  
  * **Parameters** 
    * T-threshold = 2.5
    * Length = 25
    * Permutation = 4,000
    * pruning 4

<br><br><br><br><br>

<hr>

## **Connectronomy analysis methods write up**
<br>

A diffusion spectrum imaging scheme was used, and a total of 128 diffusion sampling were acquired.  
The maximum b-value was 4990 s/mm². The in-plane resolution was 1.8 mm. The slice thickness wasc1.8 mm. The accuracy of b-table orientation was examined by comparing fiber orientations with those of a population-averaged template (Yeh et al. Neuroimage, 2018). The b-table was flipped by 
The diffusion data were reconstructed in the MNI space using q-space diffeomorphic reconstruction
(Yeh et al., Neuroimage, 58(1):91-9, 2011) to obtain the spin distribution function (Yeh et al., IEEE TMI, ;29(9):1626-35, 2010).  A diffusion sampling length ratio of 1.25 was used. The output resolution in diffeomorphic reconstruction was 1.8 mm isotropic. The tensor metrics were calculated using DWI with b-value lower than 1750 s/mm². The quantitative anisotropy was extracted as the local connectome fingerprint (LCF, Yeh et al. PLoS Comput Biol 12(11): e1005203) and used in the connectometry analysis.</p>
<br>

Diffusion MRI connectometry (Yeh et al. NeuroImage 125 (2016): 162-171) was used to derive the correlational tractography that has QA, MD, AD, and RD correlated with Maze Accuracy and path efficiency. A nonparametric Spearman partial correlation was used to derive the correlation, and the effect of sex, age_scan_years, and repo_status was removed using a multiple regression model. The total number of subjects varied on analysis (See Analyses and Final sample sizes above). A T-score threshold of 2.5 was assigned and tracked using a deterministic fiber tracking algorithm (Yeh et al. PLoS ONE 8(11): e80713, 2013) to obtain correlational tractography. A seeding region was placed at whole brain (39,49,29) .
<br>

 The tracks were filtered by topology-informed pruning (Yeh et al. Neurotherapeutics, 16(1), 52-58, 2019) with 4 iteration(s). A length threshold of 25 voxel distance was used to select tracks. To estimate the false discovery rate, a total of 4000 randomized permutations were applied to the group label to obtain the null distribution of the track length.</p>

<br><br><br><br><br><br>

<hr>

# **Results** {.tabset .tabset-pills} 

### Behavior
No sex differences between males and females when using wilconox test since normality failed. Do i try and normalize data points?
```{r,echo=FALSE, results='hide',message=FALSE}
# Sex differences Ttest
sub_info$SEX[sub_info$SEX==1]<-c("Male")
sub_info$SEX[sub_info$SEX==0]<-c("Female")
sub_info$SEX <- as.factor(sub_info$SEX)

shapiro.test(female_subs$maze_accuracy_pct) # not normal 
shapiro.test(male_subs$maze_accuracy_pct) #Not normal 

SexTest <- wilcox.test(female_subs$maze_accuracy_pct,male_subs$maze_accuracy_pct)
SexTest


sub_info %>% ggplot(aes(x = SEX, y = maze_accuracy_pct, fill=SEX)) +
  geom_boxplot(width=0.5,fatten = 1) +
  geom_point(shape=16, position=position_jitter(0.1)) +
  scale_fill_manual(values=c("#7d4c5a", "#6c6c6e"))+
  scale_y_continuous(breaks = seq(0, 1, by = 0.2)) +
   xlab("Sex")+
   ylab("Wayfinding Success") +
  theme(axis.title.x = element_text(vjust=- 4, size = 16),
         axis.title.y = element_text(vjust=8, size = 16),
         axis.text.x = element_text(size = 12),
         axis.text.y = element_text(size = 12),
         panel.background =element_blank(),
         axis.line = element_line(colour = "black"),
         plot.margin = margin(1, 2, 1, 1.5, "cm"),
         plot.title = element_text(hjust = 0.5, vjust = 2, size = 16, face="bold" )
 )

# scale_color_manual(values=c("#4e363e", "#6c6c6e"))+

```

```{r,echo=FALSE, results='hide',message=FALSE}
# Menopause differences Ttest

sub_info$REPO[sub_info$REPO==0]<-c("Male")
sub_info$REPO[sub_info$REPO==1]<-c("Pre")
sub_info$REPO[sub_info$REPO==2]<-c("Peri")
sub_info$REPO[sub_info$REPO==3]<-c("Post")

group_by(sub_info, REPO) %>%
+     summarise(
+         count = n(),
+         mean = mean(maze_accuracy_pct, na.rm = TRUE),
+         sd = sd(maze_accuracy_pct, na.rm = TRUE))


MenopauseTest <- aov(maze_accuracy_pct~REPO,sub_info)
summary(MenopauseTest)
#Siginifcant effect of REPO on performance 

ggboxplot(sub_info, x = "REPO", y = "maze_accuracy_pct", 
          color = "REPO",
          order = c("Male", "Pre", "Peri", "Post"),
          ylab = "Wayfinding Success", xlab = "Group")


sub_info %>% ggplot(aes(x = REPO, y = maze_accuracy_pct, fill=REPO)) +
  geom_boxplot(width=0.5,fatten = 1) +
  geom_point(shape=16, position=position_jitter(0.1)) +
  scale_fill_manual(values=c("#6c6c6e","#7d4c5a", "#CD8A9B","#806d71"))+
  scale_y_continuous(breaks = seq(0, 1, by = 0.2)) +
   xlab("Sex")+
   ylab("Wayfinding Success") +
  theme(axis.title.x = element_text(vjust=- 4, size = 16),
         axis.title.y = element_text(vjust=8, size = 16),
         axis.text.x = element_text(size = 12),
         axis.text.y = element_text(size = 12),
         panel.background =element_blank(),
         axis.line = element_line(colour = "black"),
         plot.margin = margin(1, 2, 1, 1.5, "cm"),
         plot.title = element_text(hjust = 0.5, vjust = 2, size = 16, face="bold" )
 )

```

<br>
Need to see if things are different from chance
```{r, Chance }

df_maze_fem <- sub_info %>% filter(SEX == "Female")
t.test(df_maze_fem$maze_accuracy_pct, mu=.1111, alternative="greater", conf.level=0.95)

mean(df_maze_fem$maze_accuracy_pct)
sd(df_maze_fem$maze_accuracy_pct)
CI(df_maze_fem$maze_accuracy_pct, ci = 0.95)

#Cohen's d: (mean - mu)/sd
(mean(df_maze_fem$maze_accuracy_pct) - .1111)/sd(df_maze_fem$maze_accuracy_pct)

cohen.d.ci((mean(df_maze_fem$maze_accuracy_pct) - .1111)/sd(df_maze_fem$maze_accuracy_pct),
            n1=59, alpha = 0.05)
```

```{r}
df_maze_male <- sub_info %>% filter(SEX == "Male")
t.test(df_maze_male$maze_accuracy_pct, mu=.1111, alternative="greater", conf.level=0.95)

mean(df_maze_male$maze_accuracy_pct)
sd(df_maze_male$maze_accuracy_pct)
CI(df_maze_male$maze_accuracy_pct, ci = 0.95)

#Cohen's d: (mean - mu)/sd
(mean(df_maze_male$maze_accuracy_pct) - .1111)/sd(df_maze_male$maze_accuracy_pct)

cohen.d.ci((mean(df_maze_male$maze_accuracy_pct) - .1111)/sd(df_maze_male$maze_accuracy_pct),
            n1=21, alpha = 0.05)
```


```{r}
df_maze_pre <- sub_info %>% filter(REPO == 1)
t.test(df_maze_pre$maze_accuracy_pct, mu=.1111, alternative="greater", conf.level=0.95)

mean(df_maze_pre$maze_accuracy_pct)
sd(df_maze_pre$maze_accuracy_pct)
CI(df_maze_pre$maze_accuracy_pct, ci = 0.95)

#Cohen's d: (mean - mu)/sd
(mean(df_maze_pre$maze_accuracy_pct) - .1111)/sd(df_maze_pre$maze_accuracy_pct)

cohen.d.ci((mean(df_maze_pre$maze_accuracy_pct) - .1111)/sd(df_maze_pre$maze_accuracy_pct),
            n1=59, alpha = 0.05)
```


```{r}
df_maze_peri <- sub_info %>% filter(REPO == 2)
t.test(df_maze_peri$maze_accuracy_pct, mu=.1111, alternative="greater", conf.level=0.95)

mean(df_maze_peri$maze_accuracy_pct)
sd(df_maze_peri$maze_accuracy_pct)
CI(df_maze_peri$maze_accuracy_pct, ci = 0.95)

#Cohen's d: (mean - mu)/sd
(mean(df_maze_peri$maze_accuracy_pct) - .1111)/sd(df_maze_peri$maze_accuracy_pct)

cohen.d.ci((mean(df_maze_peri$maze_accuracy_pct) - .1111)/sd(df_maze_peri$maze_accuracy_pct),
            n1=59, alpha = 0.05)
```



```{r}
df_maze_post <- sub_info %>% filter(REPO == 2)
t.test(df_maze_post$maze_accuracy_pct, mu=.1111, alternative="greater", conf.level=0.95)

mean(df_maze_post$maze_accuracy_pct)
sd(df_maze_post$maze_accuracy_pct)
CI(df_maze_post$maze_accuracy_pct, ci = 0.95)

#Cohen's d: (mean - mu)/sd
(mean(df_maze_post$maze_accuracy_pct) - .1111)/sd(df_maze_post$maze_accuracy_pct)

cohen.d.ci((mean(df_maze_post$maze_accuracy_pct) - .1111)/sd(df_maze_post$maze_accuracy_pct),
            n1=59, alpha = 0.05)
```






This is a visualization of the accuracy performance for the subjects that i have scans for. One creates a bar graph split by sex and the other is a ranked order

<!-- ```{r, echo=FALSE, results='hide',message=FALSE} -->

<!-- # Let's just scatter plot performance -->

<!-- pdf(file = paste0(working_dir,"/figures/behavior_maze_acc_barPlot.pdf"),width=12, height=8) -->
<!--  ggplot(sub_info, aes(x=SEX,y=maze_accuracy_pct, fill=factor(SEX))) + -->
<!--    geom_boxplot() +geom_point(size=4, color = "black") +    labs(x ="sex", y = "Maze Accuracy") + scale_fill_manual(values = c("#E2929D","#502E23")) -->
<!--  dev.off() -->

<!--  pdf(file = paste0(working_dir,"/figures/behavior_maze_acc_rank.pdf"),width=12, height=8) -->
<!-- test <- sub_info$maze_accuracy_pct %>% sort() %>% as.data.frame() %>% mutate(rank=1:80) -->
<!--  ggplot(test, aes(x=rank,y=.)) + geom_point(size=4, color = "black") -->
<!--  dev.off() -->

<!-- ``` -->



<!-- <hr> -->


## Summary 

Broadly, QA is positively associated with maze accuracy

<!-- The code below is to display the FDR values for the analyses into two columns -->

::::::{style="display: flex;"}

:::{.column width="50%"}
**QA FDRs when controlling for FNAME**     
All: **(<span style="color: LightSeaGreen;"> - </span>) 0.001980**       
Female: **(<span style="color: LightSeaGreen;"> - </span>) 0.003378**  
Male: **(<span style="color: LightSeaGreen;"> - </span>) 0.000774**  
Pre : **(<span style="color: MediumOrchid;"> + </span>) 0.006250** | **(<span style="color: LightSeaGreen;"> - </span>) 0.030870**  
Peri: **(<span style="color: MediumOrchid;"> + </span>) 0.004310** 
Post: **(<span style="color: MediumOrchid;"> + </span>) 0.000628** | **(<span style="color: LightSeaGreen;"> - </span>) 0.002725** 
::: 
  
:::{ .column width="50%"}
  **QA FDRs when NOT controlling for FNAME**  
  All: **(<span style="color: LightSeaGreen;"> - </span>) 0.002320**    
  Female:**(<span style="color: LightSeaGreen;"> - </span>) 0.003378**      
  Male:  **(<span style="color: LightSeaGreen;"> - </span>) 0.000216**    
  Pre : **(<span style="color: LightSeaGreen;"> - </span>) XXXXX**      
  Peri: **(<span style="color: MediumOrchid;"> + </span>) XXXXX**    
  Post: **(<span style="color: LightSeaGreen;"> - </span>) XXXXX** | **(<span style="color: MediumOrchid;"> + </span>) XXXXX**
:::
::::::

<hr>

::::::{style="display: flex;"}

:::{.column width="50%"}
**MD FDRs when controlling for FNAME**     
All: 1.000      
Female: 1.000  
Male: **(<span style="color: MediumOrchid;"> + </span>) 0.004082** | **(<span style="color: LightSeaGreen;"> - </span>) 0.250000**        
Pre : **(<span style="color: LightSeaGreen;"> - </span>) 0.002024**    
Peri: **(<span style="color: MediumOrchid;"> + </span>) 0.166667**          
Post: **(<span style="color: LightSeaGreen;"> - </span>) 0.012987**  
::: 
  
:::{ .column width="50%"}
  **MD FDRs when NOT controlling for FNAME**  
  All: 1.000  
  Female: 1.000     
  Male:  **(<span style="color: MediumOrchid;"> + </span>) 0.003333** | **(<span style="color: LightSeaGreen;"> - </span>) 0.020000**  
  Pre : **(<span style="color: LightSeaGreen;"> - </span>) 0.002128**      
  Peri: 1.000  
  Post: 1.000
:::
::::::


<br><br><br>

<hr>

## QA {.tabset .tabset-pills}

### All subjects 

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span> Increased QA is associated with **Decreased ACC** (FDR = 0.001980) </span>

<!-- This code below repeats and is just a way for me to read in the CSV, Clean it up, and then create an aesthetic table for the html -->

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("FNAME/QA/all/QA_FNAME_all.csv")))
```

<br>

<p style="text-align:center ; font-size: 24px" > <strong> No FNAME Control </p>

<span> Increased QA is associated with **Decreased ACC** (FDR = 0.002320)</span>
```{r,echo=FALSE,message=FALSE}
 TableOutput(CleanInput(ReadingCSVFunc("NO_FNAME/QA/All/QA_NOFNAME_all.csv")))
```


<br><br><br>

<hr>

### Females

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span> Increased QA is associated with **decreased ACC** FDR= 0.003378</span>

```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("FNAME/QA/female/QA_FNAME_female.csv")))

```

<br><br>

<p style="text-align:center ; font-size: 24px" > <strong> No Control for FNAME </strong> </p>
<br>

<span> Increased QA is associated with **decreased ACC** FDR= 0.005495 </span>
```{r,echo=FALSE,message=FALSE}
 TableOutput(CleanInput(ReadingCSVFunc("NO_FNAME/QA/female/QA_NOFNAME_female_2.csv")))
```

<br><br><br>

<hr>

### Males 

N=21

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>
<br>

<span> Increased QA associated with **Decreased ACC** FDR= 0.000774</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("FNAME/QA/male/QA_FNAME_male.csv")))

```
<br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong>No FNAME control</strong> </p>
<br>
<span> Increased QA is associated with **decreased ACC** FDR= 0.000216 </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("NO_FNAME/QA/male/QA_NOFNAME_male.csv")))

```


<br><br><br>

<hr>

### Pre

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>
<br>

<span> Increasing QA is associated with **Increased Acc** FDR= 0.006250  </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("FNAME/QA/pre/QA_FNAME_pre.inc.csv")))

```
<br>

<span> Increasing QA is associated with **Decreased Acc**  (FDR = 0.030870) </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("FNAME/QA/pre/QA_FNAME_pre.dec.csv")))

```
<br><br>

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>
<br>

<span> Increasing QA is associated with **Increased Acc** FDR= 0.005952  </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("NO_FNAME/QA/pre/QA_NOFNAME_pre_inc.csv")))

```
<br>

<span> Increasing QA is associated with **Decreased Acc** FDR= 0.076101  </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("NO_FNAME/QA/pre/QA_NOFNAME_pre_dec.csv")))
```

<hr>


### Peri

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>
<br>

<span> Increased QA associated with **Increased ACC** FDR=0.004310 </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("FNAME/QA/peri/QA_FNAME_peri.csv")))

```
<br>
<br>

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>
<br><br>

<span> Increased QA associated with **Increased ACC** FDR=0.004202 </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("NO_FNAME/QA/peri/QA_NOFNAME_peri.csv")))

```
<br>

<hr>


### Post

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>
<br>

<span> Increased QA is associated with **Increased ACC** FDR=0.000628  </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("FNAME/QA/post/QA_FNAME_post.inc.csv")))

```
<br>

<span> Increased QA is associated with **Decreased ACC** FDR=0.002725 </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("FNAME/QA/post/QA_FNAME_post.dec.csv")))

```

<br><br>

<p style="text-align:center ; font-size: 24px" > <strong>No Control for FNAME</strong> </p>
<br>

<span> Increased QA is associated with **Increased ACC** FDR=0.000751  </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("NO_FNAME/QA/post/QA_NOFNAME_post_inc.csv")))
```
<br>

<span> Increased QA is associated with **Decreased ACC** FDR=0.001650 </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("NO_FNAME/QA/post/QA_NOFNAME_post_dec.csv")))

```

<br>

<hr>

## MD {.tabset .tabset-pills}

### All subject

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

No significant tracts

<br>

<p style="text-align:center ; font-size: 24px" > <strong>No Control for FNAME</strong> </p>

No significant tracts

<br>

<hr>

### Females

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

No significant tracts

<br>

<p style="text-align:center ; font-size: 24px" > <strong>No Control for FNAME</strong> </p>

No significant tracts

<br>

<hr>

### Males

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span> Increased MD is associated with **Increased ACC** FDR=0.004082  </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("FNAME/MD/male/MD_FNAME_male_inc.csv")))
```

<br>

<p style="text-align:center ; font-size: 24px" > <strong>No control for FNAME</strong> </p>

<span> Increased MD is associated with **Increased ACC** FDR=0.003333  </span>


```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("NO_FNAME/MD/male/MD_NOFNAME_male.inc.csv")))
```

<br>

<span> Increased MD is associated with **Decreased ACC** FDR=0.020000  </span>


```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("NO_FNAME/MD/male/MD_NOFNAME_male.dec.csv")))
```

<hr>

### Pre

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span> Increased MD is associated with **Decreased ACC** FDR=0.002024  </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("FNAME/MD/pre/MD_FNAME_pre.csv")))
```

<br>

<p style="text-align:center ; font-size: 24px" > <strong>No FNAME Control</strong> </p>


<span> Increased MD is associated with **Decreased ACC** FDR=0.002024  </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("NO_FNAME/MD/pre/MD_NOFNAME_pre.csv")))
```

<br>

<hr>

### Peri

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span> Increased MD is associated with **Increased ACC** FDR=0.166667  </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("FNAME/MD/peri/MD_FNAME_peri.csv")))
```

<br><br>

<p style="text-align:center ; font-size: 24px" > <strong>No FNAME Control</strong> </p>

no significant TRacts
<br>

<hr>



### Post

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span> Increased MD is associated with **Decreased ACC** FDR=0.012987 </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("FNAME/MD/post/MD_FNAME_post.csv")))
```

<br>

<p style="text-align:center ; font-size: 24px" > <strong>No FNAME Control</strong> </p>

no significant TRacts

<br>
