---
title: "SNAG maze DSI results"
author: "Daniela Cossio"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
    html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    classoption:
    - twocolumn
---

<!-- below is code for generating the markdown html. just basic aesthetics -->
```{css, echo=FALSE}
TOC {
  color: #F6B2DB;
  font-family: Times;
  font-size: "16px"; 
  border-color: #F6B2DB;
}

h1 {
  color: black ;
  font-family: Times;
  font-size: "72px";
  padding: "10px 0";
  text-align: center;
}

h4.date {
  color: black ;
  font-family: Times;
  font-size: "34px";
  text-align: center;
}

h4.author {
  color: black;
  font-size: "34px";
  font-family: Times;
  text-align: center;
}


h2, h3, h4, h5 ,h6 {
  text-align: center;
  font-family: Times;
  
}

body, p{
  color: black; 
  font-family: Times;
}

hr {
  height:5px;
  border-width:0;
  background-color: black ;
}



```

<!-- More  basic Aesthetics -->

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 100)
```

<!-- Loading in libraries  -->
```{r adding libraries,echo=FALSE, results='hide',message=FALSE}
library(ggplot2)
#(plyr)
library(tidyverse)
# library(dplyr)
# library(tidyr)
library(stringr)
library(kableExtra)
# library(data.table)
# library(network)
# library(tidygraph)
# library(ggraph)
# library(igraph)
# library(networkD3)
# library(CINNA)
# library(umap)
# library(plotly)
#library(factoextra)
#library(lsr)
# library(car)
library(ggpubr)
#library(entropy)
#library(ds4psy)
# library(pROC)
#library(devtools)
#library(BRRR)
#library(stats)
#library(afex)
library(knitr)
library(janitor)
library(car)
library(ggiraph)
library(ggiraphExtra)
library(moonBook)
library(nationalparkcolors)
library(gridExtra)
library(markdown)
library(psych)
library(Rmisc)
library(ppcor)

```

<!-- Reading in the paths and the CSV that contains all of the subject info -->
```{r reading in our CSVs, echo=FALSE, results='hide',message=FALSE}
working_dir <-"/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/DSI/Maze/"

#working_dir <- "/Users/danielacossio/Desktop/MAZE/" #laptop

rows2grab <- c("Tract Name", "number of tracts","mean length(mm)", "total volume(mm^3)")


sub_info <- read.csv(paste0(working_dir,"MazeDSI.csv")) # this is a csv that contains all of the important subject information.
```

<!-- Below is a bunch of functions that reduce the code throughout the script -->
```{r functions, echo=FALSE, results='hide',message=FALSE}



ReadingCSVFunc <- function(pathname){
  #README 
  #Purpose of this code is to read in the CSVs that I extract from the correlational tractography from DSI studio. You simply need to include the path to the CSV from the working directory. We set our working dir above so you just need the rest of the path. 
  read.delim(paste0(working_dir, pathname), header=FALSE,sep = "\t")
}

CleanInput <- function(DF){
  
#README
  # The purpose of this function is to take the CSV that I extract from the correlational tractography and that has already been read into the script and made into a dataframe. It is then cleaned to create a clean output that grabs the following rows: "Tract Name", "number of tracts","mean length(mm)", "total volume(mm^3)"), and then re organizes the information for each subject into one dataframe. There's an if statement because some CSVs only have one significant tract and it needs a slightly different code to reorganize that. 
  
  DF <- DF %>% remove_empty("cols") 
  
  if(length(DF) < 3){
    DF <- DF %>% 
            filter(V1 %in% rows2grab) %>% 
              t() %>% 
                `colnames<-`(rows2grab) %>% 
                  as.data.frame() %>% 
                    `[`(-c(1),)
    
  } else{
    
    DF <- DF %>% 
      filter(V1 %in% rows2grab) %>% 
        t() %>% 
            `colnames<-`(rows2grab) %>% 
                `[`(-c(1),) %>% 
                    as.data.frame() 
  }
 
          
  return(DF)
}




TableOutput <- function(df){
  #Purpose of this is to create a clean table that can be shown on the html. Most of this is aesthetics but it's a lot so i created a function to reduce the clutter later. 
  # The DF that is input is a clean data frame of the correlational tractography. At this point it has gone through the ReadingCSVFunc, and CleanInput
      knitr::kable(df, row.names=F) %>% kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% scroll_box(width = "600px", height = "300px")
    
  }


# Extract_raw_values <- function(DF,Metric) {
#   # Purpose of this function is to clean the data without me having to copy and paste everything later. As well as extract 
#   
#   # Data = raw unclean dataframe we want to clean up 
#   # Metric will be either MD or QA
#   # sex is either male or female
#  
#   
#   # Let's read in our data frame 
#   
#      colNames <- DF  %>% remove_empty("cols") %>%
#   filter(V1 == "Tract Name") %>% t() %>% `[`(-1) 
#   
#   
#   # grab  ROIcolumn names 
#  
#   
#   subinfo <- sub_info  %>% select(c("subject_id", "sex", "age_scan_years", "loop_pe_rad3_m", "loop_de_rad3_degree","REPO")) 
#  
#   # Let's grab our values 
#   if (Metric == "MD"){
#     Values <- DF %>% remove_empty("cols") %>% 
#      filter(str_detect(V1, c("mean_md"))) %>%
#    `colnames<-`(c("Subjects",colNames)) %>% filter(!str_detect(Subjects, c("sub-369"))) 
#   }
#   else{
#     Values <- DF %>%
#      remove_empty("cols") %>%
#       filter(str_detect(V1, c("mean_qa"))) %>% 
#   `colnames<-`(c("Subjects",colNames)) %>% filter(!str_detect(Subjects, c("sub-369"))) 
# 
#   }
#   
#   # now let's put this together 
#   if (length(Values) < 3) {
#     Values[,2] <- as.numeric(Values[,2])
#   }else{
#   ConvToNum <-  apply(Values[,2:length(Values)],2, as.numeric)
#   Values[,2:length(Values)] <- ConvToNum
#   }
#   
#   cleanedDF <- cbind(subinfo,Values) %>% na.omit() %>% select(-c("Subjects"))
#   
#   return (cleanedDF)
# }


# TableOutput <- function(df, style, width, height, caption){
#  
#   if (style == "classic"){
#       knitr::kable(df, row.names=F) %>% kable_classic(full_width = F, html_font = "Cambria")
#   } else {
#       knitr::kable(df, row.names=F) %>% kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% scroll_box(width = paste0(width,"px"), height = paste0(height,"px")) 
#     
#   }
# 
# }


```

<hr> 
<br>

# Overview 
This is the analysis of white matter dsi studio connectometry for Maze

<br>

<hr> 

# <span style="color: darkblue;">Methods </span>  {.tabset .tabset-pills} 

## **Participants** 

  * Total number of scans = 120 (males and females)  
  
  * Total scans used in analysis= 118  
  * Excluded subs 329 and 372 from analyses due to bad behavior data and Subject 347 failed quality control check in DSI
  

<br><br><br>

<hr>

## **Maze Accuracy and Path Efficiency**

  * All subjects = 80
  * Men = 21
  * Women = 59
  * Stage
  * Pre = 23
  * Peri = 20 
  * Post = 16
  
We had 82 last time so i excluded 2 more people from this analysis. one from low quality and then one bc of health issues. 347 and 424
  
<br><br><br><br><br>
 
 <hr>
  
## **Scan parameters** 

  * Locations from UCSB and UCI
  
<br><br><br><br><br>

<hr>

## **QSIprep** 

  * Version used: 0.16.0RC3

  * The following parameters were used
    * dwi_denoise_window **5** 
    * hmc_model **3dSHORE** 
    * hmc-transform **Rigid** 
    * shoreline_iters **2**
<br><br><br><br><br>

<hr>


## **DSI Studio**

  * Version and tags used via singularity container: **chen-2024-05-22**
  
  * **Parameters** 
    * T-threshold = 2.5
    * Length = 25
    * Permutation = 4,000
    * pruning 4

<br><br><br><br><br>

<hr>

## **Connectronomy analysis methods write up**
<br>

A diffusion spectrum imaging scheme was used, and a total of 128 diffusion sampling were acquired.  
The maximum b-value was 4990 s/mm². The in-plane resolution was 1.8 mm. The slice thickness wasc1.8 mm. The accuracy of b-table orientation was examined by comparing fiber orientations with those of a population-averaged template (Yeh et al. Neuroimage, 2018). The b-table was flipped by 
The diffusion data were reconstructed in the MNI space using q-space diffeomorphic reconstruction
(Yeh et al., Neuroimage, 58(1):91-9, 2011) to obtain the spin distribution function (Yeh et al., IEEE TMI, ;29(9):1626-35, 2010).  A diffusion sampling length ratio of 1.25 was used. The output resolution in diffeomorphic reconstruction was 1.8 mm isotropic. The tensor metrics were calculated using DWI with b-value lower than 1750 s/mm². The quantitative anisotropy was extracted as the local connectome fingerprint (LCF, Yeh et al. PLoS Comput Biol 12(11): e1005203) and used in the connectometry analysis.</p>
<br>

Diffusion MRI connectometry (Yeh et al. NeuroImage 125 (2016): 162-171) was used to derive the correlational tractography that has QA, MD, AD, and RD correlated with Maze Accuracy and path efficiency. A nonparametric Spearman partial correlation was used to derive the correlation, and the effect of sex, age_scan_years, and repo_status was removed using a multiple regression model. The total number of subjects varied on analysis (See Analyses and Final sample sizes above). A T-score threshold of 2.5 was assigned and tracked using a deterministic fiber tracking algorithm (Yeh et al. PLoS ONE 8(11): e80713, 2013) to obtain correlational tractography. A seeding region was placed at whole brain (39,49,29) .
<br>

 The tracks were filtered by topology-informed pruning (Yeh et al. Neurotherapeutics, 16(1), 52-58, 2019) with 4 iteration(s). A length threshold of 25 voxel distance was used to select tracks. To estimate the false discovery rate, a total of 4000 randomized permutations were applied to the group label to obtain the null distribution of the track length.</p>

<br><br><br><br><br><br>

<hr>

# **Results** {.tabset .tabset-pills} 

```{r, creating and changing variables}

sub_info$SEX[sub_info$SEX==1]<-c("Male")
sub_info$SEX[sub_info$SEX==0]<-c("Female")
sub_info$SEX <- as.factor(sub_info$SEX)
sub_info$REPO[sub_info$REPO==0]<-c("Male")
sub_info$REPO[sub_info$REPO==1]<-c("Pre")
sub_info$REPO[sub_info$REPO==2]<-c("Peri")
sub_info$REPO[sub_info$REPO==3]<-c("Post")

#Creating group DF
df_maze_fem <- sub_info %>% filter(SEX == "Female")
df_maze_male <- sub_info %>% filter(SEX == "Male")
df_maze_pre <- sub_info %>% filter(REPO == "Pre")
df_maze_peri <- sub_info %>% filter(REPO == "Peri")
df_maze_post <- sub_info %>% filter(REPO == "Post")

```

### Behavior

#### Maze 

LEt's look at the performance distribution and normality

Womens performance is also not normal p-value = 6.529e-10
```{r}
ggplot(df_maze_fem, aes(x=maze_accuracy_pct)) +
   geom_bar(width = 0.1)
shapiro.test(df_maze_fem$maze_accuracy_pct)
```

Males performance is also not normal p-value = 3.491e-06
```{r}
ggplot(df_maze_male, aes(x=maze_accuracy_pct)) +
   geom_bar(width = 0.1)
shapiro.test(df_maze_male$maze_accuracy_pct)
```



No sex differences between males and females when using wilconox test since normality failed. Do i try and normalize data points?
```{r,echo=FALSE, results='hide',message=FALSE}
# Sex differences Ttest


sub_info %>% ggplot(aes(x = SEX, y = maze_accuracy_pct, fill=SEX)) +
  geom_boxplot(width=0.5,fatten = 1) +
  geom_point(shape=16, position=position_jitter(0.1)) +
  scale_fill_manual(values=c("#7d4c5a", "#6c6c6e"))+
  scale_y_continuous(breaks = seq(0, 1, by = 0.2)) +
   xlab("Sex")+
   ylab("Wayfinding Success") +
  theme(axis.title.x = element_text(vjust=- 4, size = 16),
         axis.title.y = element_text(vjust=8, size = 16),
         axis.text.x = element_text(size = 12),
         axis.text.y = element_text(size = 12),
         panel.background =element_blank(),
         axis.line = element_line(colour = "black"),
         plot.margin = margin(1, 2, 1, 1.5, "cm"),
         plot.title = element_text(hjust = 0.5, vjust = 2, size = 16, face="bold" )
 )

# scale_color_manual(values=c("#4e363e", "#6c6c6e"))+

```

```{r, summary stats}
group_by(sub_info, REPO) %>% dplyr::summarise(count = n(), mean = mean(maze_accuracy_pct, na.rm = TRUE), sd = sd(maze_accuracy_pct, na.rm = TRUE))

```

Needed to do the one way  anova between all groups

```{r,echo=FALSE, results='hide',message=FALSE, one way anova}
# Menopause differences Ttest
MenopauseTest <- aov(maze_accuracy_pct~REPO,sub_info)
summary(MenopauseTest)

# BElow is shuyings code
# options(contrasts=c("contr.sum", "contr.poly"))
# interaction_acc <- aov(AvgAccuracy~Group*Sex, data = df_maze)
# Anova(interaction_acc, type="III")

test1 <- kruskal.test(maze_accuracy_pct~REPO,sub_info)
```

```{r, group boxplot}


sub_info %>% ggplot(aes(x = factor(REPO, levels=c("Male", "Pre", "Peri", "Post")), y = maze_accuracy_pct, fill= REPO)) +
  geom_boxplot(width=0.5,fatten = 1, show.legend = FALSE) +
  geom_point(shape=16, position=position_jitter(0.1)) +
  scale_fill_manual(values=c("#6c6c6e","#7d4c5a", "#CD8A9B","#806d71"))+
  scale_y_continuous(breaks = seq(0, 1, by = 0.2)) +
   xlab("Sex")+
   ylab("Wayfinding Success") +
  theme(axis.title.x = element_text(vjust=- 4, size = 16),
         axis.title.y = element_text(vjust=8, size = 16),
         axis.text.x = element_text(size = 12),
         axis.text.y = element_text(size = 12),
         panel.background =element_blank(),
         axis.line = element_line(colour = "black"),
         plot.margin = margin(1, 2, 1, 1.5, "cm"),
         plot.title = element_text(hjust = 0.5, vjust = 2, size = 16, face="bold" )
 )

# ggboxplot(sub_info, x = "REPO", y = "maze_accuracy_pct", 
#           color = "REPO",
#           order = c("Male", "Pre", "Peri", "Post"),
#           ylab = "Wayfinding Success", xlab = "Group")
```

<br>
Need to see if things are different from chance
Women only
```{r, df_maze_fem  }

t.test(df_maze_fem$maze_accuracy_pct, mu=.1111, alternative="greater", conf.level=0.95)
mean(df_maze_fem$maze_accuracy_pct)
sd(df_maze_fem$maze_accuracy_pct)
CI(df_maze_fem$maze_accuracy_pct, ci = 0.95)

#Cohen's d: (mean - mu)/sd
(mean(df_maze_fem$maze_accuracy_pct) - .1111)/sd(df_maze_fem$maze_accuracy_pct)

cohen.d.ci((mean(df_maze_fem$maze_accuracy_pct) - .1111)/sd(df_maze_fem$maze_accuracy_pct),
            n1=59, alpha = 0.05)
```
Males chance
```{r, df_maze_male}

t.test(df_maze_male$maze_accuracy_pct, mu=.1111, alternative="greater", conf.level=0.95)

mean(df_maze_male$maze_accuracy_pct)
sd(df_maze_male$maze_accuracy_pct)
CI(df_maze_male$maze_accuracy_pct, ci = 0.95)

#Cohen's d: (mean - mu)/sd
(mean(df_maze_male$maze_accuracy_pct) - .1111)/sd(df_maze_male$maze_accuracy_pct)

cohen.d.ci((mean(df_maze_male$maze_accuracy_pct) - .1111)/sd(df_maze_male$maze_accuracy_pct),
            n1=21, alpha = 0.05)
```

Pre menopausal women chance
```{r,df_maze_pre}

t.test(df_maze_pre$maze_accuracy_pct, mu=.1111, alternative="greater", conf.level=0.95)

mean(df_maze_pre$maze_accuracy_pct)
sd(df_maze_pre$maze_accuracy_pct)
CI(df_maze_pre$maze_accuracy_pct, ci = 0.95)

#Cohen's d: (mean - mu)/sd
(mean(df_maze_pre$maze_accuracy_pct) - .1111)/sd(df_maze_pre$maze_accuracy_pct)

cohen.d.ci((mean(df_maze_pre$maze_accuracy_pct) - .1111)/sd(df_maze_pre$maze_accuracy_pct),
            n1=59, alpha = 0.05)
```

Peri menopausal
```{r, df_maze_peri}

t.test(df_maze_peri$maze_accuracy_pct, mu=.1111, alternative="greater", conf.level=0.95)

mean(df_maze_peri$maze_accuracy_pct)
sd(df_maze_peri$maze_accuracy_pct)
CI(df_maze_peri$maze_accuracy_pct, ci = 0.95)

#Cohen's d: (mean - mu)/sd
(mean(df_maze_peri$maze_accuracy_pct) - .1111)/sd(df_maze_peri$maze_accuracy_pct)

cohen.d.ci((mean(df_maze_peri$maze_accuracy_pct) - .1111)/sd(df_maze_peri$maze_accuracy_pct),
            n1=59, alpha = 0.05)
```



```{r, df_maze_post}

t.test(df_maze_post$maze_accuracy_pct, mu=.1111, alternative="greater", conf.level=0.95)

mean(df_maze_post$maze_accuracy_pct)
sd(df_maze_post$maze_accuracy_pct)
CI(df_maze_post$maze_accuracy_pct, ci = 0.95)

#Cohen's d: (mean - mu)/sd
(mean(df_maze_post$maze_accuracy_pct) - .1111)/sd(df_maze_post$maze_accuracy_pct)

cohen.d.ci((mean(df_maze_post$maze_accuracy_pct) - .1111)/sd(df_maze_post$maze_accuracy_pct),
            n1=59, alpha = 0.05)
```






This is a visualization of the accuracy performance for the subjects that i have scans for. One creates a bar graph split by sex and the other is a ranked order

<!-- ```{r, echo=FALSE, results='hide',message=FALSE} -->

<!-- # Let's just scatter plot performance -->

<!-- pdf(file = paste0(working_dir,"/figures/behavior_maze_acc_barPlot.pdf"),width=12, height=8) -->
<!--  ggplot(sub_info, aes(x=SEX,y=maze_accuracy_pct, fill=factor(SEX))) + -->
<!--    geom_boxplot() +geom_point(size=4, color = "black") +    labs(x ="sex", y = "Maze Accuracy") + scale_fill_manual(values = c("#E2929D","#502E23")) -->
<!--  dev.off() -->

<!--  pdf(file = paste0(working_dir,"/figures/behavior_maze_acc_rank.pdf"),width=12, height=8) -->
<!-- test <- sub_info$maze_accuracy_pct %>% sort() %>% as.data.frame() %>% mutate(rank=1:80) -->
<!--  ggplot(test, aes(x=rank,y=.)) + geom_point(size=4, color = "black") -->
<!--  dev.off() -->

<!-- ``` -->



<!-- <hr> -->

#### FNAME GRoup comparisons

First we are doing a one- way anova between all groups 
```{r,echo=FALSE, results='hide',message=FALSE}

group_by(sub_info, REPO) %>% dplyr::summarise(count = n(), mean = mean(FNAME, na.rm = TRUE), sd = sd(FNAME, na.rm = TRUE))
```

```{r, Check group compairsions between FNAME}
FNAMEMenopauseTest <- aov(FNAME~REPO,sub_info)
summary(FNAMEMenopauseTest)
#There is a Siginifcant effect of REPO on performance 
```

```{r, have to do follow up post hoc tests}
TukeyHSD(FNAMEMenopauseTest)
#Peri menopause and males differ in FNAME performance. Not even sure what that means 
```


```{r, FNAME plot}
sub_info %>% ggplot(aes(x = factor(REPO, levels=c("Male", "Pre", "Peri", "Post")), y = FNAME, fill= REPO)) +
  geom_boxplot(width=0.5,fatten = 1, show.legend = FALSE) +
  geom_point(shape=16, position=position_jitter(0.1)) +
  scale_fill_manual(values=c("#6c6c6e","#7d4c5a", "#CD8A9B","#806d71"))+
   xlab("Sex")+
   ylab("FNAME") +
  scale_y_continuous(breaks = seq(0, 100, by = 20)) +
  theme(axis.title.x = element_text(vjust=- 4, size = 16),
         axis.title.y = element_text(vjust=8, size = 16),
         axis.text.x = element_text(size = 12),
         axis.text.y = element_text(size = 12),
         panel.background =element_blank(),
         axis.line = element_line(colour = "black"),
         plot.margin = margin(1, 2, 1, 1.5, "cm"),
         plot.title = element_text(hjust = 0.5, vjust = 2, size = 16, face="bold" )
 )


```


### Hormones and behavior correlations

I am going to rerun correlation analyses between hormones and maze accuracy. I am basing this off of what shuying has previosly done. Below i will highlight what i plan to do. 

1) Split all groups into separate data frames. should already be done above
2)Check normality of the groups for hormones
3) if normal, use partial pearson correlation to control for age if not normal use spearman 
4) shuying had a priori predictions here so we will use a one tailed analysis for estradiol and FSH
5) progesterone and testosterone would not have any strong a priori so they are two-tailed for women
6) for males, testosterone is one tailed in positive direction
7) Do i do one controlling for age and one not controlling for age?? 

#### Estradiol 


Here let's look at estradiol skews for all women who have a dsp score. It does not pass normality 1.151e-08
```{r}
ggplot(df_maze_fem, aes(x=estradiol_spatial_pg_ml)) +
   geom_bar(width = 10)
shapiro.test(df_maze_fem$estradiol_spatial_pg_ml)
```



Correlation between maze and estradiol for scan and spatial. No significant association.

Why use cor test vs cor ?

Cor test is a correlation for paired samples. paired samples are those that are from the same group but different time points. unapiared would be two different groups.
```{r, warning=FALSE}

# this one uses spatial hormones
cor.test(df_maze_fem$estradiol_spatial_pg_ml,
         df_maze_fem$maze_accuracy_pct,
         conf.level = 0.95,
         alternative = "greater",
         method = "spearman")

#This one uses scan hormones
cor.test(df_maze_fem$estradiol_scan_pg_ml,
         df_maze_fem$maze_accuracy_pct,
         conf.level = 0.95,
         alternative = "greater",
         method = "spearman")
```

Partial correlation between estradiol spatial and performance while controlling for age. no significant association 
```{r, warning=FALSE}
pcor.test(df_maze_fem$estradiol_spatial_pg_ml,
          df_maze_fem$maze_accuracy_pct,
          df_maze_fem$age_spatial_years, 
          method = "spearman")
```



#### Progesterone

Here let's look at progesterone skews for all women who have a dsp score. It does not pass normality 1.912e-12
```{r}
ggplot(df_maze_fem, aes(x=progesterone_spatial_ng_ml)) +
   geom_bar(width = 1)
shapiro.test(df_maze_fem$progesterone_spatial_ng_ml)
```



Correlation between maze and progesterone for scan and spatial. No significant association p-value = 0.3366
```{r, warning=FALSE}

# this one uses spatial hormones
cor.test(df_maze_fem$progesterone_spatial_ng_ml,
         df_maze_fem$maze_accuracy_pct,
         conf.level = 0.95,
         alternative = "greater",
         method = "spearman")

#This one uses scan hormones
cor.test(df_maze_fem$progesterone_scan_ng_ml,
         df_maze_fem$maze_accuracy_pct,
         conf.level = 0.95,
         alternative = "greater",
         method = "spearman")
```

Partial correlation between progesterone spatial and performance while controlling for age. no significant association 
```{r, warning=FALSE}
pcor.test(df_maze_fem$progesterone_spatial_ng_ml,
          df_maze_fem$maze_accuracy_pct,
          df_maze_fem$age_spatial_years, 
          method = "spearman") 
```



#### FSH
Here let's look at FSH skews for all women who have a dsp score. It does not pass normality 1.193e-06
```{r}
ggplot(df_maze_fem, aes(x=fsh_spatial_miu_ml)) +
   geom_bar(width = 1)
shapiro.test(df_maze_fem$fsh_spatial_miu_ml)
```



Correlation between maze and progesterone for scan and spatial. No significant association p-value =  0.7945
```{r, warning=FALSE}

# this one uses spatial hormones
cor.test(df_maze_fem$fsh_spatial_miu_ml,
         df_maze_fem$maze_accuracy_pct,
         conf.level = 0.95,
         alternative = "greater",
         method = "spearman")

#This one uses scan hormones
cor.test(df_maze_fem$fsh_scan_miu_ml,
         df_maze_fem$maze_accuracy_pct,
         conf.level = 0.95,
         alternative = "greater",
         method = "spearman")
```

Partial correlation between FSH spatial and performance while controlling for age. no significant association 
```{r, warning=FALSE}
pcor.test(df_maze_fem$fsh_spatial_miu_ml,
          df_maze_fem$maze_accuracy_pct,
          df_maze_fem$age_spatial_years, 
          method = "spearman") 
```

#### Testosterone (males and females)

##### women
Here let's look at Testosterone skews for all women who have a dsp score. It does not pass normality p-value = 1.93e-05
```{r}
ggplot(df_maze_fem, aes(x=testosterone_spatial_ng_dl)) +
   geom_bar(width = 1)
shapiro.test(df_maze_fem$testosterone_spatial_ng_dl)
```



Correlation between maze and Testosterone for scan and spatial. No significant association p-value =  0.9101
```{r, warning=FALSE}

# this one uses spatial hormones
cor.test(df_maze_fem$testosterone_spatial_ng_dl,
         df_maze_fem$maze_accuracy_pct,
         conf.level = 0.95,
         alternative = "greater",
         method = "spearman")

#This one uses scan hormones
cor.test(df_maze_fem$testosterone_scan_ng_dl,
         df_maze_fem$maze_accuracy_pct,
         conf.level = 0.95,
         alternative = "greater",
         method = "spearman")
```

Partial correlation between Testosterone spatial and performance while controlling for age. no significant association  0.3174194
```{r, warning=FALSE}
pcor.test(df_maze_fem$testosterone_scan_ng_dl,
          df_maze_fem$maze_accuracy_pct,
          df_maze_fem$age_spatial_years, 
          method = "spearman") 
```

##### Men

Here let's look at Testosterone skews for all men who have a maze score. it passes p-value = 0.1295
```{r}
ggplot(df_maze_male, aes(x=testosterone_spatial_ng_dl)) +
   geom_bar(width = 1)
shapiro.test(df_maze_male$testosterone_spatial_ng_dl)
```



Correlation between maze and Testosterone for scan and spatial. No significant association p-value =  0.4246
```{r, warning=FALSE}

# this one uses spatial hormones
cor.test(df_maze_male$testosterone_spatial_ng_dl,
         df_maze_male$maze_accuracy_pct,
         conf.level = 0.95,
         alternative = "greater",
         method = "spearman")

#This one uses scan hormones
cor.test(df_maze_male$testosterone_scan_ng_dl,
         df_maze_male$maze_accuracy_pct,
         conf.level = 0.95,
         alternative = "greater",
         method = "spearman")
```

Partial correlation between Testosterone spatial and performance while controlling for age. no significant association  0.8558466
```{r, warning=FALSE}
pcor.test(df_maze_male$testosterone_scan_ng_dl,
          df_maze_male$maze_accuracy_pct,
          df_maze_male$age_spatial_years, 
          method = "spearman") 
```