---
title: "SNAG maze DSI results"
author: "Daniela Cossio"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
    html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    classoption:
    - twocolumn
---

```{css, echo=FALSE}
TOC {
  color: #F6B2DB;
  font-family: Times;
  font-size: "16px"; 
  border-color: #F6B2DB;
}

h1 {
  color: black ;
  font-family: Times;
  font-size: "72px";
  padding: "10px 0";
  text-align: center;
}

h4.date {
  color: black ;
  font-family: Times;
  font-size: "34px";
  text-align: center;
}

h4.author {
  color: black;
  font-size: "34px";
  font-family: Times;
  text-align: center;
}


h2, h3, h4, h5 ,h6 {
  text-align: center;
  font-family: Times;
  
}

body, p{
  color: black; 
  font-family: Times;
}

hr {
  height:5px;
  border-width:0;
  background-color: black ;
}



```

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 100)
```

```{r adding libraries,echo=FALSE, results='hide',message=FALSE}
library(ggplot2)
#(plyr)
library(tidyverse)
# library(dplyr)
# library(tidyr)
library(stringr)
library(kableExtra)
# library(data.table)
# library(network)
# library(tidygraph)
# library(ggraph)
# library(igraph)
# library(networkD3)
# library(CINNA)
# library(umap)
# library(plotly)
#library(factoextra)
#library(lsr)
# library(car)
library(ggpubr)
#library(entropy)
#library(ds4psy)
# library(pROC)
#library(devtools)
#library(BRRR)
#library(stats)
#library(afex)
library(knitr)
library(janitor)
library(car)
library(ggiraph)
library(ggiraphExtra)
library(moonBook)
library(nationalparkcolors)
library(gridExtra)
library(markdown)
```

```{r reading in our CSVs, echo=FALSE, results='hide',message=FALSE}
working_dir <-"/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/DSI_rerun_data/"

# PE_working_dir <- "/Users/danielacossio/Library/CloudStorage/GoogleDrive-dcossio1@uci.edu/My Drive/White matter tract/MidlifeWM_DSI2023/DSI/maze/Path_eff/"

rows2grab <- c("Tract Name", "number of tracts","mean length(mm)","diameter(mm)", "volume(mm^3)")


sub_info <- read.csv(paste0(working_dir,"subject_info.csv"))
```

```{r functions, echo=FALSE, results='hide',message=FALSE}

ReadingCSVFunc <- function(pathname){
  
  read.delim(paste0(working_dir, pathname), header=FALSE,sep = "\t")
  
}

CleanInput <- function(DF){
  

  DF <- DF %>% remove_empty("cols") 
  
  if(length(DF) < 3){
    DF <- DF %>% 
            filter(V1 %in% rows2grab) %>% 
              t() %>% 
                `colnames<-`(rows2grab) %>% 
                  as.data.frame() %>% 
                    `[`(-c(1),)
    
  } else{
    
    DF <- DF %>% 
      filter(V1 %in% rows2grab) %>% 
        t() %>% 
            `colnames<-`(rows2grab) %>% 
                `[`(-c(1),) %>% 
                    as.data.frame() 
  }
 
          
  return(DF)
}


Extract_raw_values <- function(DF,Metric) {
  # Purpose of this function is to clean the data without me having to copy and paste everything later. 
  
  # Data = raw unclean dataframe we want to clean up 
  # Metric will be either MD or QA
  # sex is either male or female
 
  
  # Let's read in our data frame 
  
     colNames <- DF  %>% remove_empty("cols") %>%
  filter(V1 == "Tract Name") %>% t() %>% `[`(-1) 
  
  
  # grab  ROIcolumn names 
 
  
  subinfo <- sub_info  %>% select(c("subject_id", "sex", "age_scan_years", "loop_pe_rad3_m", "loop_de_rad3_degree","REPO")) 
 
  # Let's grab our values 
  if (Metric == "MD"){
    Values <- DF %>% remove_empty("cols") %>% 
     filter(str_detect(V1, c("mean_md"))) %>%
   `colnames<-`(c("Subjects",colNames)) %>% filter(!str_detect(Subjects, c("sub-369"))) 
  }
  else{
    Values <- DF %>%
     remove_empty("cols") %>%
      filter(str_detect(V1, c("mean_qa"))) %>% 
  `colnames<-`(c("Subjects",colNames)) %>% filter(!str_detect(Subjects, c("sub-369"))) 

  }
  
  # now let's put this together 
  if (length(Values) < 3) {
    Values[,2] <- as.numeric(Values[,2])
  }else{
  ConvToNum <-  apply(Values[,2:length(Values)],2, as.numeric)
  Values[,2:length(Values)] <- ConvToNum
  }
  
  cleanedDF <- cbind(subinfo,Values) %>% na.omit() %>% select(-c("Subjects"))
  
  return (cleanedDF)
}


TableOutput <- function(df){
      knitr::kable(df, row.names=F) %>% kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% scroll_box(width = "600px", height = "300px")
    
  }


# TableOutput <- function(df, style, width, height, caption){
#  
#   if (style == "classic"){
#       knitr::kable(df, row.names=F) %>% kable_classic(full_width = F, html_font = "Cambria")
#   } else {
#       knitr::kable(df, row.names=F) %>% kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% scroll_box(width = paste0(width,"px"), height = paste0(height,"px")) 
#     
#   }
# 
# }


```

<hr> 
<br>

# Overview 
This is the analysis of white matter dsi studio connectometry for Maze and Loop 

<br>

<hr> 

# <span style="color: darkblue;">Methods </span>  {.tabset .tabset-pills} 

## **Participants** 

  * Total number of scans = 120 (males and females)  
  
  * Total scans used in analysis= 118  
  * Excluded subs 329 and 372 from analyses due to bad behavior data and Subject 347 failed quality 
  control check in DSI
  

<br><br><br>

<hr>

## **Maze Accuracy and Path Efficiency**

  * All subjects = 82
  * Men = 22
  * Women = 60
  * Stage
  * Pre = 23
  * Peri = 20 
  * Post = 17
  
<br><br><br><br><br>
 
 <hr>
  
## **Scan parameters** 

  * Locations from UCSB and UCI
  
<br><br><br><br><br>

<hr>

## **QSIprep** 

  * Version used: 0.16.0RC3

  * The following parameters were used
    * dwi_denoise_window **5** 
    * hmc_model **3dSHORE** 
    * hmc-transform **Rigid** 
    * shoreline_iters **2**
<br><br><br><br><br>

<hr>


## **DSI Studio**

  * Version and tags used via singularity container: **chen-2022-07-31**
  
  * **Parameters** 
    * T-threshold = 2.5
    * Length = 25
    * Permutation = 4,000
    * pruning 4
    * non normalized QA

<br><br><br><br><br>

<hr>

## **Connectronomy analysis methods write up**
<br>

A diffusion spectrum imaging scheme was used, and a total of 128 diffusion sampling were acquired.  
The maximum b-value was 4990 s/mm². The in-plane resolution was 1.8 mm. The slice thickness wasc1.8 mm. The accuracy of b-table orientation was examined by comparing fiber orientations with those of a population-averaged template (Yeh et al. Neuroimage, 2018). The b-table was flipped by 
The diffusion data were reconstructed in the MNI space using q-space diffeomorphic reconstruction
(Yeh et al., Neuroimage, 58(1):91-9, 2011) to obtain the spin distribution function (Yeh et al., IEEE TMI, ;29(9):1626-35, 2010).  A diffusion sampling length ratio of 1.25 was used. The output resolution in diffeomorphic reconstruction was 1.8 mm isotropic. The tensor metrics were calculated using DWI with b-value lower than 1750 s/mm². The quantitative anisotropy was extracted as the local connectome fingerprint (LCF, Yeh et al. PLoS Comput Biol 12(11): e1005203) and used in the connectometry analysis.</p>
<br>

Diffusion MRI connectometry (Yeh et al. NeuroImage 125 (2016): 162-171) was used to derive the correlational tractography that has QA, MD, AD, and RD correlated with Maze Accuracy and path efficiency. A nonparametric Spearman partial correlation was used to derive the correlation, and the effect of sex, age_scan_years, and repo_status was removed using a multiple regression model. The total number of subjects varied on analysis (See Analyses and Final sample sizes above). A T-score threshold of 2.5 was assigned and tracked using a deterministic fiber tracking algorithm (Yeh et al. PLoS ONE 8(11): e80713, 2013) to obtain correlational tractography. A seeding region was placed at whole brain (39,49,29) .
<br>

 The tracks were filtered by topology-informed pruning (Yeh et al. Neurotherapeutics, 16(1), 52-58, 2019) with 4 iteration(s). A length threshold of 25 voxel distance was used to select tracks. To estimate the false discovery rate, a total of 4000 randomized permutations were applied to the group label to obtain the null distribution of the track length.</p>

<br><br><br><br><br><br>

<hr>

# **Results** {.tabset .tabset-pills} 

<!-- ### Behavior -->





<!-- <hr> -->


## Summary 

Broadly, QA is positively associated with maze accuracy

::::::{style="display: flex;"}

:::{.column width="50%"}
**QA FDRs when controlling for FNAME**     
All: **(<span style="color: MediumOrchid;"> + </span>) 0.000381**     
Female: **(<span style="color: MediumOrchid;"> + </span>) 0.000571**  
Male: (<span style="color: LightSeaGreen;"> - </span>) 0.055556 | **(<span style="color: MediumOrchid;"> + </span>) 0.000042**     
Pre : **(<span style="color: LightSeaGreen;"> - </span>) 0.023256** | **(<span style="color: MediumOrchid;"> + </span>) 0.000501**     
Peri: **(<span style="color: LightSeaGreen;"> - </span>) 0.002994** | **(<span style="color: MediumOrchid;"> + </span>) 0.000219**      
Post: **(<span style="color: LightSeaGreen;"> - </span>) 0.003425** | **(<span style="color: MediumOrchid;"> + </span>) 0.003762** 
::: 
  
:::{ .column width="50%"}
  **MD FDRs when controlling for FNAME**  
  All: (<span style="color: MediumOrchid;"> + </span>) 0.066199   
  Female: (<span style="color: LightSeaGreen;"> - </span>) 0.107527     
  Male:  **(<span style="color: MediumOrchid;"> + </span>) 0.009051**    
  Pre : **(<span style="color: LightSeaGreen;"> - </span>) 0.000315**      
  Peri: **(<span style="color: MediumOrchid;"> + </span>) 0.014418**    
  Post: **(<span style="color: LightSeaGreen;"> - </span>) 0.017658** | **(<span style="color: MediumOrchid;"> + </span>) 0.009454**
:::
::::::

<br><br><br>

<hr>

## QA {.tabset .tabset-pills}

### All subjects 

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.00381)</strong> </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/fname_covariate/QA_positive_mazeacc_all_fname.csv")))
```

<br>

<p style="text-align:center ; font-size: 24px" > <strong>previous run results</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.000282)</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/noFNAME/all_maze_accuracy_pct.t2.length25.pos.csv")))
```


<br><br><br>

<hr>

### Females

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positively FDR= 0.000571</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/fname_covariate/female.mazelearningacc.pos.csv")))

```

<br>

<p style="text-align:center ; font-size: 24px" > <strong>previous run results</strong> </p>
<br><br>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positively FDR= 0.000327</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/noFNAME/females_maze_accuracy_pos.csv")))

```

<br><br><br>

<hr>

### Males 

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>
<br><br>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"><strong> Positively FDR= 0.000042</strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/fname_covariate/male.mazelearning.acc.pos.csv")))

```
<br><br><br><br>

<p style="text-align:center ; font-size: 24px" > <strong>previous run results</strong> </p>
<br><br>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"><strong> Positive (FDR = 0.000131)</strong> </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/noFNAME/male.maze_accuracy_pct.t2.length25.pos_corr.csv")))

```

<br><br><br><br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"><strong>Negative (FDR = 0.001658)</strong> </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/noFNAME/male.maze_accuracy_pct.t2.length25.neg_corr.csv")))

```

<br><br><br>

<hr>

### Pre

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>
<br><br>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"><strong> Positively FDR=0.000501 </strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/fname_covariate/pre.mazelearningacc.pos.csv")))

```
<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"><strong>Negative (FDR = 0.023256)</strong> </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/fname_covariate/pre.mazelearningacc.neg.csv")))

```

<p style="text-align:center ; font-size: 24px" > <strong>previous run results</strong> </p>
<br><br>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"><strong> Positively FDR=0.002547 </strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/noFNAME/maze.QA.pre.pos.csv")))

```
<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"><strong>Negative (FDR = 0.021739)</strong> </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/noFNAME/maze.QA.pre.neg.csv")))

```

<hr>


### Peri

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>
<br>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"><strong> Positively FDR=0.000219 </strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/fname_covariate/peri.mazelearning.acc.pos.csv")))

```
<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"><strong>Negative (FDR = 0.002994)</strong> </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/fname_covariate/peri.mazelearning.acc.neg.csv")))

```

<br>

<p style="text-align:center ; font-size: 24px" > <strong>previous run results</strong> </p>
<br><br>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"><strong> Positively FDR=0.000286 </strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/noFNAME/qa.peri.pos.csv")))

```
<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"><strong>Negative (FDR = 0.049774)</strong> </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/noFNAME/qa.peri.neg.csv")))

```

<hr>


### Post

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>
<br>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"><strong> Positively FDR=0.003425 </strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/fname_covariate/peri.mazelearning.acc.pos.csv")))

```
<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"><strong>Negative (FDR = 0.003762)</strong> </span>
```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/fname_covariate/peri.mazelearning.acc.neg.csv")))

```

<br>

<p style="text-align:center ; font-size: 24px" > <strong>previous run results</strong> </p>
<br><br>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"><strong> Positively FDR=0.006613 </strong> </span>
```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/QA/noFNAME/mAZE.QA.post.pos.csv")))

```
<br>



## MD {.tabset .tabset-pills}

### All subject

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.066199)</strong> </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/MD/FNAME/maze.MD.all.pos.csv")))
```

<br>

<p style="text-align:center ; font-size: 24px" > <strong>previous run results</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.018490)</strong> </span>


```{r,echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/MD/noFNAME/newversion/maze.MD.all.pos.csv")))
```

<br>

<hr>

### Females

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"><strong>Negative (FDR = 0.107527)</strong> </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/MD/FNAME/maze.MD.female.neg.csv")))
```

<br>

<p style="text-align:center ; font-size: 24px" > <strong>previous run results</strong> </p>

No Significant Results 

### Males

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.009051)</strong> </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/MD/FNAME/maze.MD.male.pos.csv")))
```

<br>

<p style="text-align:center ; font-size: 24px" > <strong>previous run results</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.018970)</strong> </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/MD/noFNAME/newversion/maze.MD.males.pos.csv")))
```

<hr>

### Pre

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"><strong>Negative (FDR = 0.000315)</strong> </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/MD/FNAME/maze.MD.pre.neg.csv")))
```

<br>

<p style="text-align:center ; font-size: 24px" > <strong>previous run results</strong> </p>


<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"><strong>Negative (FDR = 0.000313)</strong> </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/MD/noFNAME/newversion/maze.MD.pre.neg.csv")))
```



### Peri

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.014418)</strong> </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/MD/FNAME/maze.MD.peri.pos.csv")))
```

<br>

<p style="text-align:center ; font-size: 24px" > <strong>previous run results</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = .000309)</strong> </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/MD/noFNAME/newversion/maze.MD.peri.pos.csv")))
```

<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"><strong>Negative (FDR = 0.014286)</strong> </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/MD/noFNAME/newversion/maze.MD.peri.neg.csv")))
```



### Post

<p style="text-align:center ; font-size: 24px" > <strong>Control for FNAME</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.009454)</strong> </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/MD/FNAME/maze.MD.post.pos.csv")))
```

<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"><strong>Negative (FDR = 0.017658)</strong> </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/MD/FNAME/maze.MD.post.neg.csv")))
```

<br><br>
<p style="text-align:center ; font-size: 24px" > <strong>previous run results</strong> </p>

<span style="color: MediumOrchid;font-size: 18px;background-color: Snow"> <strong>Positive (FDR = 0.000615)</strong> </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/MD/noFNAME/newversion/maze.MD.post.pos.csv")))
```

<br>

<span style="color: LightSeaGreen;font-size: 18px;background-color: Snow"><strong>Negative (FDR = 0.017321)</strong> </span>

```{r, echo=FALSE,message=FALSE}
TableOutput(CleanInput(ReadingCSVFunc("maze_acc/MD/noFNAME/MD_post_neg.csv")))
```

