---
title: "Mediation Analysis"
author: "Daniela Cossio"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
    html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    classoption:
    - twocolumn
---

```{r adding libraries,echo=FALSE, results='hide',message=FALSE}
library(ggplot2)
#(plyr)
library(tidyverse)
# library(dplyr)
# library(tidyr)
library(stringr)
library(kableExtra)
# library(data.table)
# library(network)
# library(tidygraph)
# library(ggraph)
# library(igraph)
# library(networkD3)
# library(CINNA)
# library(umap)
# library(plotly)
#library(factoextra)
#library(lsr)
# library(car)
library(ggpubr)
#library(entropy)
#library(ds4psy)
# library(pROC)
#library(devtools)
#library(BRRR)
#library(stats)
#library(afex)
library(knitr)
library(janitor)
library(car)
library(ggiraph)
library(ggiraphExtra)
library(moonBook)
library(nationalparkcolors)
library(gridExtra)
library(markdown)
library(psych)
```



```{css, echo=FALSE}
TOC {
  color: #F6B2DB;
  font-family: Arial;
  font-size: "16px"; 
  border-color: #F6B2DB;
}

h1.title {
  color: black ;
  font-family: Arial;
  font-size: "72px";
  padding: "10px 0";
  background-color: #F6B2DB ;
  text-align: center;
}

h4.date {
  color: black ;
  font-family: Arial;
  font-size: "34px";
  text-align: center;
}

h4.author {
  color: black;
  font-size: "34px";
  font-family: Arial;
  text-align: center;
}


h1,h2, h3, h4, h5 ,h6 {
  text-align: center;
  font-family: Arial;
  
}

body, p, h2{
  color: black; 
  font-family: Arial;
}

hr {
  height:5px;
  border-width:0;
  background-color: black ;
}



```



```{r functions, echo=FALSE, results='hide',message=FALSE}

ReadingCSVFunc <- function(pathname){
  
  read.delim(paste0(working_dir, pathname), header=FALSE,sep = "\t")
  
}

CleanInput <- function(DF){
  

  DF <- DF %>% 
      remove_empty("cols") %>% 
        filter(V1 %in% rows2grab) %>% 
          t() %>% 
            `colnames<-`(rows2grab) %>% 
                `[`(-c(1),) %>% 
                    as.data.frame()
  return(DF)
}


Extract_raw_values <- function(DF,Metric) {
  # Purpose of this function is to clean the data without me having to copy and paste everything later. 
  
  # Data = raw unclean dataframe we want to clean up 
  # Metric will be either MD or QA
  # sex is either male or female
 
  
  # Let's read in our data frame 
  
  # grab  ROIcolumn names 
  colNames <- DF  %>% remove_empty("cols") %>%
  filter(V1 == "Tract Name") %>% t() %>% `[`(-1) 
  
  
  subinfo <- sub_info  %>% select(c("subject_id", "sex", "age_scan_years", "maze_accuracy_pct")) 
 
  # Let's grab our values 
  if (Metric == "MD"){
    Values <- DF %>% remove_empty("cols") %>% 
     filter(str_detect(V1, c("mean_md"))) %>%
   `colnames<-`(c("Subjects",colNames)) 
  }
  else{
    Values <- DF %>%
     remove_empty("cols") %>%
      filter(str_detect(V1, c("mean_qa"))) %>% 
  `colnames<-`(c("Subjects",colNames)) %>% filter(!str_detect(Subjects, c("sub-369"))) 

  }
  
  # now let's put this together 
  ConvToNum <-  apply(Values[,2:length(Values)],2, as.numeric)
  Values[,2:length(Values)] <- ConvToNum
  
  cleanedDF <- cbind(subinfo,Values) %>% na.omit() %>% select(-c("Subjects"))
  
  return (cleanedDF)
}


TableOutput <- function(df){
  knitr::kable(df, row.names=F) %>% 
  kable_styling(bootstrap_options =  c("striped", "hover", "condensed")) %>% 
  scroll_box(width = "800px", height = "300px") 
}



```

# Reading in and prepping our data 

```{r reading in our CSVs, echo=FALSE, results='hide',message=FALSE}
working_dir <- "/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/DSI_rerun_data/DSP/"

rows2grab <- c("Tract Name", "number of tracts","mean length(mm)","diameter(mm)", "volume(mm^3)")

All_sub_info <- read.csv("/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/sub_info_sheets/SNAG_Behavior.csv") # This is a sheet that has all of the subjects with at least one usable behavior task (Loop, maze, dsp)

DSP_DSI_DF <- read.csv("/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/sub_info_sheets/SNAG_DSP_scans.csv") %>% filter(!is.na(subject_id)) # This is from the main subject sheet and includes all subjects that have a dsp score AND should have a scan with them
```

Complete Subject Database

```{r}
TableOutput(All_sub_info)

```


# Methods and approach

# Thought process
I am doing a mediation analysis to understand the relation ship between white matter, hormones, and performance on the dual solution paradigm.

From shuying's data, DSP is associated with estradial. Increased solution index is associated with increased solution index.

MD is negatively associated with Solution Index such that increased MD in the fornix is associated with less shortcuts. Essentially lower white matter integrity in fornix is associated with lower performance.

Hypothesis for mediation is that greater estradiol is driving the relationship in which greater integrity in the fornix for greater solution index. 


X= Mean diffusivity in fornix  
Y= greater SI on DSP task  
M= Estradiol  


## Data Cleaning and organizing

### Step 1: read in the raw data

```{r,message=FALSE}

# This is a data frame which cotains a folder for each subject with 2 text files 
path2data <- ("/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/mediation_test_data/data_from_Midlife_20230103")

# List of all subject directories
subfiles <- list.dirs("/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/mediation_test_data/data_from_Midlife_20230103", full.names = FALSE,recursive = FALSE) # all of the data extracted from dsi 

# create an empty dataframe to loop into
fornix_output_df <-  data.frame(matrix(ncol = 5, nrow = 0)) %>% `colnames<-`(c("subjects","QA_L_fornix","QA_R_fornix","MD_L_fornix","MD_R_fornix"))

# creating a loop to go into each sub dir. read in each txt file and extract the 
for(file in 1:length((subfiles))){

  
  # creating an empty single row dataframe
  empty_loop_df <- data.frame(matrix(ncol = 5, nrow = 1))  %>% `colnames<-`(c("subjects","QA_L_fornix","QA_R_fornix","MD_L_fornix","MD_R_fornix"))
  
  # inputting the subject id
  empty_loop_df$subjects <- str_remove(subfiles[file],"sub-")
  
  
  # Let's do a quick folder check to make sure it's not empty 
  
  
  if(file.size(paste0(path2data,"/",subfiles[file])) < 128) next
  
  #grabbing all the left and right variables 
  L_fornix <- read_delim(paste0(path2data,"/",subfiles[file],"/",subfiles[file],"_space-T1w_desc-preproc_dwi.ProjectionBasalGanglia_FornixL.stat.txt"),col_names = FALSE) %>% filter(X1 %in% c("qa","md"))
  
  R_fornix <- read_delim(paste0(path2data,"/",subfiles[file],"/",subfiles[file],"_space-T1w_desc-preproc_dwi.ProjectionBasalGanglia_FornixR.stat.txt"),col_names = FALSE) %>% filter(X1 %in% c("qa","md"))
  
  # Putting them into out dataframe
  #Grab all QA values
  empty_loop_df$QA_L_fornix <- L_fornix$X2[1] # row 1 is QA
  empty_loop_df$QA_R_fornix <- R_fornix$X2[1]
    
    
  empty_loop_df$MD_L_fornix <- L_fornix$X2[2] # row 2 is MD
  empty_loop_df$MD_R_fornix <- R_fornix$X2[2]
  
  fornix_output_df <- rbind(fornix_output_df,empty_loop_df)
}


# now we have to grab the information from sub info and combine but we need to make sure we're grabbing all the correct subjects from each dataframe

altered_sub_info <- DSP_DSI_DF %>% filter(subject_id %in% c(fornix_output_df$subjects)) 

fornix_output_df <- fornix_output_df %>%  filter(subjects %in% c(DSP_DSI_DF$subject_id))


clean_DF <- cbind(altered_sub_info,fornix_output_df)

clean_DF$QA_Whole_Fornix <- rowMeans(clean_DF[,c("QA_L_fornix","QA_R_fornix")])

clean_DF$MD_Whole_Fornix <- rowMeans(clean_DF[,c("MD_L_fornix","MD_R_fornix")])
```


Step 2: Normality check and visualization of data


WE can see that the DSP values are not normally distributed when looking at all the subject and when looking at just women only.

Here I am plotting the data for all dsp. There are a total of 74 

```{r}
data_dsp <- All_sub_info %>% filter(dsp_useable == "Yes") %>% filter(subject_id < 500) # dataframe with all subjects that have usable DSP

ggplot(data_dsp, aes(x=dsp_si_true_pct)) +
   geom_bar(width = 0.1)
shapiro.test(data_dsp$dsp_si_true_pct)


TableOutput(describe(data_dsp))
```

```{r}
#check visualization and normality of all dsp data not just the scans ones

data_dsp <- All_sub_info %>% filter(dsp_useable == "Yes") 

f_data_dsp <- data_dsp %>% filter(sex == "Female") # Women only
  
m_data_dsp<- data_dsp %>% filter(sex=="Male") # Men only
  



ggplot(f_data_dsp, aes(x=dsp_si_true_pct)) +
   geom_bar(width = 0.1)
shapiro.test(f_data_dsp$dsp_si_true_pct)


ggplot(m_data_dsp, aes(x=dsp_si_true_pct)) +
   geom_bar(width = 0.1)
shapiro.test(m_data_dsp$dsp_si_true_pct)


shapiro.test(f_data_dsp$estradiol_scan_pg_ml)
shapiro.test(f_data_dsp$fsh_spatial_miu_ml)



```

```{r}

ggplot(f_data_dsp, aes(x=log(f_data_dsp$dsp_si_true_pct))) +
   geom_bar(width = 0.1)
shapiro.test(log(f_data_dsp$dsp_si_true_pct))

ggplot(f_data_dsp, aes(x=sqrt(f_data_dsp$dsp_si_true_pct))) +
   geom_bar(width = 0.1)
shapiro.test(sqrt(f_data_dsp$dsp_si_true_pct))



ggplot(f_data_dsp, aes(x=log(f_data_dsp$estradiol_scan_pg_ml))) +
   geom_freqpoly(width = 0.1)
shapiro.test(log(f_data_dsp$estradiol_scan_pg_ml))

ggplot(f_data_dsp, aes(x=sqrt(f_data_dsp$estradiol_scan_pg_ml))) +
   geom_freqpoly(width = 0.1)
shapiro.test(sqrt(f_data_dsp$estradiol_scan_pg_ml))



shapiro.test(log(f_data_dsp$fsh_spatial_miu_ml))


shapiro.test(sqrt(f_data_dsp$fsh_spatial_miu_ml))


```




```{r}
all_women_df <- sub_info %>% filter(sex.1==0)

ggplot(all_women_df, aes(x=dsp_si_true_pct)) +
   geom_bar(width = 0.1)

shapiro.test(all_women_df$dsp_si_true_pct)



# Let's try a transformation



```

```{r}

all_women_clean_df <- clean_DF %>% filter(sex.1==0)

ggplot(all_women_clean_df, aes(x=dsp_si_true_pct)) +
   geom_bar(width = 0.1)

shapiro.test(all_women_clean_df$dsp_si_true_pct)

```

step 2.5: Can we replicate shuyings findings?

```{r}

cor.test(all_women_df$estradiol_scan_pg_ml,
         all_women_df$dsp_si_true_pct,
         conf.level = 0.95,
         method = "spearman")
```

```{r}
hist(log(all_women_df$dsp_si_true_pct))

shapiro.test(sqrt(all_women_df$dsp_si_true_pct))
```


Step 3: Prepare the mediation by grabbing our final df. Removing any rows that are NA 

```{r}
mediation_estradiol_DF <- clean_DF %>% select(subject_id,sex.1,age_spatial_years,REPO,dsp_si_true_pct,estradiol_scan_pg_ml,progesterone_scan_ng_ml,testosterone_scan_ng_dl,fsh_scan_miu_ml,QA_L_fornix,QA_R_fornix,MD_L_fornix,MD_R_fornix, MD_Whole_Fornix, QA_Whole_Fornix) %>% filter(!is.na(dsp_si_true_pct )) %>% filter(!is.na(estradiol_scan_pg_ml)) %>% filter(sex.1 == 0)
```

```{r}
mediation_test_DF <- clean_DF %>% select(subject_id,sex.1,age_spatial_years,REPO,dsp_si_true_pct,estradiol_scan_pg_ml,progesterone_scan_ng_ml,testosterone_scan_ng_dl,fsh_scan_miu_ml,QA_L_fornix,QA_R_fornix,MD_L_fornix,MD_R_fornix) %>% filter(!is.na(dsp_si_true_pct )) %>% filter(!is.na(testosterone_scan_ng_dl)) %>% filter(sex.1 == 0)
```

```{r}
mediation_FSH_DF <- clean_DF %>% select(subject_id,sex.1,age_spatial_years,REPO,dsp_si_true_pct,estradiol_scan_pg_ml,progesterone_scan_ng_ml,testosterone_scan_ng_dl,fsh_scan_miu_ml,QA_L_fornix,QA_R_fornix,MD_L_fornix,MD_R_fornix) %>% filter(!is.na(dsp_si_true_pct )) %>% filter(!is.na(fsh_scan_miu_ml)) %>% filter(sex.1 == 0)
```



## Mediation

## Estradiol
Step 1 of mediation is to complete the first correlation in which X= L_fornix and Y = DSP

```{r}
model.1 <- lm(MD_Whole_Fornix ~ dsp_si_true_pct, mediation_estradiol_DF)
summary(model.1)
```

Step 2 of mediation is to complete the next correlation in which X= hormones and Y = DSP

```{r}
model.2 <- lm(estradiol_scan_pg_ml ~ dsp_si_true_pct, mediation_estradiol_DF)
summary(model.2)
```


```{r}
model.2 <- lm(estradiol_scan_pg_ml ~ MD_Whole_Fornix, mediation_estradiol_DF)
summary(model.2)
```




# Summarized Results

