---
title: "Young_MidlifeSexDiff"
purpose: "This is to analyze sex differences in behavior both in the young participants. This uses parts of viasakhs and kates code"   #
input: Trial.csv and participant.csv and participant info               
output: Figures and analysis for various variables                    
Notes:  
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
#(plyr)
library(tidyverse)
# library(dplyr)
# library(tidyr)
library(stringr)
# library(data.table)
# library(network)
# library(tidygraph)
# library(ggraph)
# library(igraph)
# library(networkD3)
# library(CINNA)
# library(umap)
# library(plotly)
library(factoextra)
library(lsr)
# library(car)
library(ggpubr)
library(entropy)
#library(ds4psy)
# library(pROC)
library(devtools)
library(BRRR)
library(stats)
library(afex)
library(mediation)

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
workdir<- "/Users/danielacossio/Desktop/MLINDIV_analysisDC/MidlifeDesktopBehavior"
setwd(workdir)
```


```{r reading in midlife files }
#infosheet with age/sex
subjInfo<-read.csv ("/Users/danielacossio/Desktop/MLINDIV_analysisDC/MidlifeDesktopBehavior/BehaviorAnalysisScripts/MAZE_data_old.csv")  %>% dplyr::select(Subject.ID,Sex,Age.Spatial..years.,) %>% `colnames<-` (c("Subject","sex","age")) %>% arrange(.$Subject)

#preprocessed trial data 
trialDF<-read.csv ("/Users/danielacossio/Desktop/MLINDIV_analysisDC/MidlifeDesktopBehavior/BehaviorAnalysisScripts/MLINDIV_trial_master.csv") %>% filter(Subject %in% c(as.character(subjInfo$Subject))) 

#preprocessed participant data 
participantDF<-read.csv ("/Users/danielacossio/Desktop/MLINDIV_analysisDC/MidlifeDesktopBehavior/BehaviorAnalysisScripts/MLINDIV_participant_master.csv") %>%  filter(Subject %in% c(as.character(subjInfo$Subject)))

# Combining sex and age columns to trial and participant sheet 
mid_master_trial <- inner_join(subjInfo, trialDF, by="Subject") 
mid_master_trial$age <- as.factor("midlife")
mid_master_trial$sex <- as.factor(mid_master_trial$sex)

mid_master_participant <- inner_join(subjInfo, participantDF, by="Subject") 
mid_master_participant$age <- as.factor("midlife")
mid_master_participant$sex <- as.factor(mid_master_participant$sex)

```

```{r reading in young participants}
#repeating what i did for midlife to the young group.
yngsubjInfo<-read.csv("/Volumes/GoogleDrive/My Drive/MLINDIV_SNAG_preprocessing/young_SNAG/young_snag_participantinfo.csv")  %>% dplyr::select(subject_id,sex,age_spatial_years) %>% `colnames<-` (c("Subject","sex","age"))

yngtrialDF<-read.csv ("/Volumes/GoogleDrive/My Drive/MLINDIV_SNAG_preprocessing/young_SNAG/young_trial_master (1).csv") %>% filter(Subject %in% c(as.character(yngsubjInfo$Subject))) 

yngparticipantDF <-read.csv("/Volumes/GoogleDrive/My Drive/MLINDIV_SNAG_preprocessing/young_SNAG/young_participant_master (1).csv") %>% filter(Subject %in% c(as.character(yngsubjInfo$Subject))) 


yng_master_trial <- inner_join(yngsubjInfo, yngtrialDF, by="Subject") 
yng_master_trial$age <- as.factor("young")
yng_master_trial$sex <- as.factor(yng_master_trial$sex)

yng_master_participant <- inner_join(yngsubjInfo, yngparticipantDF, by="Subject") 
yng_master_participant$age <-as.factor("young")
yng_master_participant$sex <-as.factor(yng_master_participant$sex)
```

```{r prepping variables for later use}

locs <- c('A', 'B', 'C', 'D', 'E', 'F', 'G', 'H', 'I', 'J', 'K', 'L', 'M', 'N', 'O', 'P', 'Q', 'R', 'S', 'T', 'U', 'V', 'W', 'X', "Y", "Z")
objs_orientations<- c('A4', 'I2', 'K4', 'L2', 'N3', 'O2', 'P2', 'Y2', 'W4')
objects<-c('A', 'I', 'K', 'L', 'N', 'O', 'P', 'Y', 'W')
hallways <- c('B', 'C', 'D', 'E', 'F', 'G', 'H', 'J', 'M', 'Q', 'R', 'S', 'T', 'U', "V", 'X', "Z")

#A=guitar
#I=snowman
#L=spaceship
#K=lamp post
#N=chicken
#O=trophy
#P=chair
#Y=umbrella
#W=cuckoo clock

#ttest output colnames for data later 
#colttest <-  c("estimate","statistic", "p.value", "parameter"," conf.low"," conf.high"," method","alternative")
```

```{r prepping dataframes for later use}

mid_female_analysis<-mid_master_participant %>% filter(sex == "Female") %>% dplyr::select(Subject,sex,age) %>% as.data.frame()      #creating master analysis data-frame to store all final exploration variable outputs into 

mid_male_analysis<-mid_master_participant %>% filter(sex == "Male") %>% dplyr::select(Subject,sex,age) %>% as.data.frame() 
  
yng_female_analysis<-yng_master_participant %>% filter(sex == "Female") %>% dplyr::select(Subject,sex,age) %>% as.data.frame()

yng_male_analysis<-yng_master_participant %>% filter(sex == "Male") %>% dplyr::select(Subject,sex,age) %>% as.data.frame()  #same thing for young

```

```{r Little bit of preprocessing on the explore trials }

mid_explor <- mid_master_trial %>% filter(is.na(accuracy) == TRUE)

#creating empty dataframe to store contents of for loop into 
mid_expl_df<- data.frame(matrix(nrow = nrow(mid_explor)))

for (i in 1:nrow(mid_explor)){
  e_string_orient<-as.list(strsplit(mid_explor$e_paths[i],split=" ")) 
  e_string<-as.list(strsplit(mid_explor$paths[i],split=" ")) 
  F3_index<-which(sapply(e_string_orient[[1]], FUN=function(X) "F3" %in% X))+1  
  e_string[[1]][F3_index]<-"N" #replacing with N
  V2_index<-which(sapply(e_string_orient[[1]], FUN=function(X) "V2" %in% X))+1
  e_string[[1]][V2_index]<-"Y" #replacing with Y
  e_string<-paste(e_string[[1]], collapse = " ") 
  mid_expl_df[i,1]<-e_string 
}

mid_expl_df$Subject<-mid_explor$Subject
mid_expl_df <- mid_expl_df %>% rename(paths = matrix.nrow...nrow.mid_explor..) 

mid_expl_df <- inner_join(mid_master_participant,mid_expl_df) 
```

```{r explore trial young preprocessing }
yng_explor <- yng_master_trial %>% filter(is.na(accuracy) == TRUE)
yng_expl_df<- data.frame(matrix(nrow = nrow(yng_explor)))

for (i in 1:nrow(yng_explor)){
  e_string_orient<-as.list(strsplit(yng_explor$e_paths[i],split=" ")) 
  e_string<-as.list(strsplit(yng_explor$paths[i],split=" ")) 
  F3_index<-which(sapply(e_string_orient[[1]], FUN=function(X) "F3" %in% X))+1  
  e_string[[1]][F3_index]<-"N" #replacing with N
  V2_index<-which(sapply(e_string_orient[[1]], FUN=function(X) "V2" %in% X))+1
  e_string[[1]][V2_index]<-"Y" #replacing with Y
  e_string<-paste(e_string[[1]], collapse = " ") 
  yng_expl_df[i,1]<-e_string 
}

yng_expl_df$Subject<-yng_explor$Subject
yng_expl_df <- yng_expl_df %>% rename(paths = matrix.nrow...nrow.yng_explor..) 
yng_expl_df <- inner_join(yng_master_participant,yng_expl_df) 

```

Distance Summary of results: No sex differences in men and women during midlife:
Only midlife male displaye a normal distribution. A two factor anova revealed that  
Theres no significant differece between men and women at any age when seeing an anova that there was an effect of sex (0.009454) and an effect of age( 0.000496 ) but no interaction. 
```{r Distance analysis using ANOVA }

yng_male_analysis$Dist <-
  yng_master_participant %>% filter(sex == "Male") %>% pull(em_path_dist_trav)
yng_female_analysis$Dist <-
  yng_master_participant %>% filter(sex == "Female") %>% pull(em_path_dist_trav)
dist <- rbind(yng_male_analysis, yng_female_analysis)

#Midlife
mid_female_analysis$Dist <-
  mid_master_participant %>% filter(sex == "Female") %>% pull(em_path_dist_trav)
dist <- rbind(dist, mid_female_analysis)
#male
mid_male_analysis$Dist <-
  mid_master_participant %>% filter(sex == "Male") %>% pull(em_path_dist_trav)
dist <- rbind(dist, mid_male_analysis)


# Checking data distribution and normality 

shapiro.test(yng_male_analysis$Dist)  # p-value = 0.04028
shapiro.test(yng_female_analysis$Dist) # p-value = 0.03625
shapiro.test(mid_female_analysis$Dist) # p-value = 0.01943
shapiro.test(mid_male_analysis$Dist) #p-value = 0.1104


dist_aov <-  aov(formula=Dist ~ sex * age, dist)
summary(dist_aov)
###########Plot distribution#####
# Plotting the distribution
# ym <- ggplot(yng_male_analysis, aes(x=Dist)) + 
#   geom_histogram(bins=10)
# yf <- ggplot(yng_female_analysis, aes(x=Dist)) + 
#   geom_histogram(bins=10)
# 
# mm <- ggplot(mid_male_analysis,aes(x=Dist))+ 
#   geom_histogram(bins=10)
# mf <- ggplot(mid_female_analysis, aes(x=Dist))+ 
#   geom_histogram(bins=10)
# 
# distance_distr <- ggarrange(ym,yf,mm,mf,
#                        labels = c("Young Male", "Young Female", "Midlife Male","Midlife Female"),
#                        font.label = list(size = 12, color = "red"),
#                        vjust = 1.5,
#                        ncol=2, nrow = 3)
# annotate_figure(distance_distr,
#                 top = text_grob("Visualizing mpg", color = "red", face = "bold", size = 14))


```

```{Using Log to }

```

Same as distance 
Only midlife male displayed a normal distribution. A two factor anova revealed that  
#Theres no significant differece between men and women at any age when seeing an anova that there was an effect of sex (0.009454) and an effect of age( 0.000496 ) but no interaction. 
```{r SPEED }
yng_male_analysis$speed <-yng_master_participant %>% filter(sex == "Male") %>% dplyr::select(em_path_dist_trav) %>% .$em_path_dist_trav/480
yng_female_analysis$speed<- yng_master_participant %>% filter(sex == "Female") %>% dplyr::select(em_path_dist_trav) %>% .$em_path_dist_trav/480
Speed <- rbind(yng_female_analysis,  yng_male_analysis)

#Midlife
mid_female_analysis$speed<-mid_master_participant%>% filter(sex == "Female") %>% dplyr::select(em_path_dist_trav) %>% .$em_path_dist_trav/480
Speed <- rbind(Speed, mid_female_analysis)
#male
mid_male_analysis$speed<-mid_master_participant%>% filter(sex == "Male") %>% dplyr::select(em_path_dist_trav) %>% .$em_path_dist_trav/480
Speed <- rbind( Speed,  mid_male_analysis) %>% dplyr::select(!(Dist))

#Normality test to assess whether samples are normally distributed 
# Midlife
shapiro.test(mid_female_analysis$speed) #p=0.019
shapiro.test(mid_male_analysis$speed)# p =.1104
#young
shapiro.test(yng_female_analysis$speed) #p= 0.03
shapiro.test(yng_male_analysis$speed)# p = 0,.04 

#
speed_aov <-  aov(formula=speed ~ sex * age,Speed)
summary(speed_aov)

########## Plotting the distribution #########
# ym <- ggplot(yng_male_analysis, aes(x=speed)) + 
#   geom_histogram(bins=10)
# yf <- ggplot(yng_female_analysis, aes(x=speed)) + 
#   geom_histogram(bins=10)
# 
# mm <- ggplot(mid_male_analysis,aes(x=speed))+ 
#   geom_histogram(bins=10)
# mf <- ggplot(mid_female_analysis, aes(x=speed))+ 
#   geom_histogram(bins=10)
# 
# multi_plot <- ggarrange(ym,yf,mm,mf,
#                        labels = c("Young Male", "Young Female", "Midlife Male","Midlife Female"),
#                        font.label = list(size = 12, color = "red"),
#                        vjust = 3,
#                        ncol=2, nrow = 2)
# annotate_figure(multi_plot,
#                 top = text_grob("Speed data distribution", color = "red", face = "bold", size = 14))

```

```{r midlife explore object processing }

mid_big_explore<-as.data.frame(str_split_fixed(mid_expl_df$paths," ",nrow(mid_expl_df)))
mid_big_explore <- mid_big_explore %>% mutate(subject = mid_expl_df$Subject) 
mid_big_explore <-mid_big_explore[,c(ncol(mid_big_explore), 1:(ncol(mid_big_explore)-1))] 

row_labels<-c(1:nrow(mid_big_explore))
mid_big_explore<- split( mid_big_explore , f = row_labels)

#for loop to find consecutive location repeats, and remove them 
for (i in 1:length(mid_big_explore)){
  mid_big_explore[[i]]<-t(mid_big_explore[[i]])
  mid_big_explore[[i]][mid_big_explore[[i]] == ""] <- NA 
  repeat_logical<-t(c(NA, mid_big_explore[[i]]) == c(mid_big_explore[[i]], NA))[1:length(mid_big_explore[[i]])]
  repeats<- grep("TRUE",repeat_logical)
  mid_big_explore[[i]][repeats,1]<-"repeats"  
  mid_big_explore[[i]]<-t(mid_big_explore[[i]])
  mid_big_explore[[i]]<-as.data.frame(mid_big_explore[[i]]) 
}

mid_big_explore<-unsplit(mid_big_explore,row_labels)#merging all chunks back into single dataframe 
mid_big_explore[is.na(mid_big_explore)]<-"none" #replacing all NAs with string, otherwise for loop below won't work 
mid_big_explore <-  mid_big_explore %>% mutate(sex = mid_expl_df$sex) %>% mutate(age = mid_expl_df$age)

mid_big_explore <-mid_big_explore[,c(1,176,177,2:175)]

#for loop to determine location counts 
mid_big_explore_counts <- data.frame(matrix(ncol = 0, nrow = nrow(mid_big_explore)))#creating dataframe to store counts into  

for (i in locs){
  mid_big_explore_counts$subject <- mid_big_explore$subject
  d <- as.data.frame(apply(mid_big_explore,1,function(x) sum(x==i))) # not sure what this function is 
  names(d) <- i
  mid_big_explore_counts <- cbind(d, mid_big_explore_counts)
}

mid_big_explore_counts <- mid_big_explore_counts %>% mutate(sex=mid_expl_df$sex) %>% mutate(age =mid_expl_df$age)


```

```{r Young explore object processing }
#location visits
yng_big_explore<-as.data.frame(str_split_fixed(yng_expl_df$paths," ",nrow(yng_expl_df)))
yng_big_explore <- yng_big_explore %>% mutate(subject = yng_expl_df$Subject) 
yng_big_explore <-yng_big_explore[,c(ncol(yng_big_explore), 1:(ncol(yng_big_explore)-1))] 

row_labels<-c(1:nrow(yng_big_explore))
yng_big_explore<- split( yng_big_explore , f = row_labels)

#for loop to find consecutive location repeats, and remove them 
for (i in 1:length(yng_big_explore)){
  yng_big_explore[[i]]<-t(yng_big_explore[[i]])
  yng_big_explore[[i]][yng_big_explore[[i]] == ""] <- NA 
  repeat_logical<-t(c(NA, yng_big_explore[[i]]) == c(yng_big_explore[[i]], NA))[1:length(yng_big_explore[[i]])]
  repeats<- grep("TRUE",repeat_logical)
  yng_big_explore[[i]][repeats,1]<-"repeats"  
  yng_big_explore[[i]]<-t(yng_big_explore[[i]])
  yng_big_explore[[i]]<-as.data.frame(yng_big_explore[[i]]) 
}

yng_big_explore<-unsplit(yng_big_explore,row_labels)#merging all chunks back into single dataframe 
yng_big_explore[is.na(yng_big_explore)]<-"none" #replacing all NAs with string, otherwise for loop below won't work 
yng_big_explore <-  yng_big_explore %>% mutate(sex = yng_expl_df$sex)%>% mutate(age = yng_expl_df$age)

yng_big_explore <-yng_big_explore[,c(1,102,103,3:101)]

#for loop to determine location counts 
yng_big_explore_counts <- data.frame(matrix(ncol = 0, nrow = nrow(yng_big_explore)))#creating dataframe to store counts into  

for (i in locs){
  yng_big_explore_counts$subject <- yng_big_explore$subject
  d <- as.data.frame(apply(yng_big_explore,1,function(x) sum(x==i))) # not sure what this function is
  names(d) <- i
  yng_big_explore_counts <- cbind(d, yng_big_explore_counts)
}

yng_big_explore_counts <- yng_big_explore_counts %>% mutate(sex=yng_expl_df$sex) %>% mutate(age =yng_expl_df$age)


```

# All data was normal and there was only an effect of age 
```{r object visits }
#midlife 
mid_male_obj_visits <- mid_big_explore_counts %>% filter(sex=="Male") %>%   transmute(subject,sex,age, A, I, L, K, N, O, P, Y, W)
cols_sum<-c(4:length(mid_male_obj_visits))
mid_male_obj_visits$total= rowSums(mid_male_obj_visits[,cols_sum])
mObj_ave <-aggregate(mid_male_obj_visits$total, list(mid_male_obj_visits$subject), FUN=mean)
mid_male_analysis$TotalObjVisits <- mObj_ave$x

#females
mid_female_obj_visits <- mid_big_explore_counts %>% filter(sex=="Female") %>%   transmute(subject,sex,age, A, I, L, K, N, O, P, Y, W)
cols_sum<-c(4:length(mid_female_obj_visits))
mid_female_obj_visits$total= rowSums(mid_female_obj_visits[,cols_sum])
fObj_ave <- aggregate(mid_female_obj_visits$total, list(mid_female_obj_visits$subject), FUN=mean)
mid_female_analysis$TotalObjVisits<-fObj_ave$x

ObjVisits <- rbind(mid_female_analysis,mid_male_analysis)

# GRabbing the young group

yng_male_obj_visits <- yng_big_explore_counts %>% filter(sex=="Male") %>%   transmute(subject,sex,age, A, I, L, K, N, O, P, Y, W)
cols_sum<-c(4:length(yng_male_obj_visits))
yng_male_obj_visits$total= rowSums(yng_male_obj_visits[,cols_sum])
yng_mObj_ave <-aggregate(yng_male_obj_visits$total, list(yng_male_obj_visits$subject), FUN=mean)
yng_male_analysis$TotalObjVisits <- yng_mObj_ave$x

ObjVisits <- rbind(ObjVisits,yng_male_analysis)
#females
yng_female_obj_visits <- yng_big_explore_counts %>% filter(sex=="Female") %>%   transmute(subject,sex,age, A, I, L, K, N, O, P, Y, W)
cols_sum<-c(4:length(yng_female_obj_visits))
yng_female_obj_visits$total= rowSums(yng_female_obj_visits[,cols_sum])
fObj_ave <- aggregate(yng_female_obj_visits$total, list(yng_female_obj_visits$subject), FUN=mean)
yng_female_analysis$TotalObjVisits<-fObj_ave$x

ObjVisits <- rbind(ObjVisits,yng_female_analysis) %>% dplyr::select(!(Dist)) %>% dplyr::select(!(speed))

# Data distribution and nromality 
shapiro.test(mid_male_analysis$TotalObjVisits) #normal 
shapiro.test(mid_female_analysis$TotalObjVisits) # normal
shapiro.test(yng_male_analysis$TotalObjVisits) #normal 
shapiro.test(yng_female_analysis$TotalObjVisits) # normal 

Obj_aov <- aov(formula=TotalObjVisits ~ sex * age ,ObjVisits)
summary(Obj_aov)

########## plots#########
# ym <- ggplot(yng_male_analysis, aes(x=TotalObjVisits)) + 
#   geom_histogram(bins=10)
# yf <- ggplot(yng_female_analysis, aes(x=TotalObjVisits)) + 
#   geom_histogram(bins=10)
# 
# mm <- ggplot(mid_male_analysis,aes(x=TotalObjVisits))+ 
#   geom_histogram(bins=10)
# mf <- ggplot(mid_female_analysis, aes(x=TotalObjVisits))+ 
#   geom_histogram(bins=10)
# 
# obj_distr <- ggarrange(ym,yf,mm,mf,
#                        labels = c("Young Male", "Young Female", "Midlife Male","Midlife Female"),
#                        font.label = list(size = 12, color = "red"),
#                        vjust = 3,
#                        ncol=2, nrow = 2)
# annotate_figure(obj_distr,
#                 top = text_grob("Total object data distribution", color = "red", face = "bold", size = 14))
# #does the plot have a common legend)

```

A normality test was run on each group. All groupd were normally distributed. no sex effects. 
```{r Hallway visits}
#midlife male
mid_male_hall_visits <- mid_big_explore_counts %>% filter(sex =="Male") %>% transmute(subject,sex,age, B, C, D, E, `F`, G, H, J, M, Q, R, S, `T`, U, V, X, Z)
cols_sum<-c(4:length(mid_male_hall_visits))
mid_male_hall_visits$total<-rowSums(mid_male_hall_visits[,cols_sum])#finding total hallway counts for each subject for each session 
mid_male_hall_visits_mean<-aggregate(mid_male_hall_visits$total, list(mid_male_hall_visits$subject), FUN=mean)
mid_male_analysis$TotalHallwayVisits<-mid_male_hall_visits_mean$x 

# midlife female
mid_female_hall_visits <- mid_big_explore_counts %>% filter(sex =="Female") %>%   transmute(subject,sex,age, B, C, D, E, `F`, G, H, J, M, Q, R, S, `T`, U, V, X, Z)
cols_sum<-c(4:length(mid_female_hall_visits))
mid_female_hall_visits$total<-rowSums(mid_female_hall_visits[,cols_sum])#finding total hallway counts for each subject for each session 
mid_female_hall_visits_mean<-aggregate(mid_female_hall_visits$total, list(mid_female_hall_visits$subject), FUN=mean)
mid_female_analysis$TotalHallwayVisits<-mid_female_hall_visits_mean$x 

halls <- rbind(mid_female_analysis,mid_male_analysis)

#Young male

yng_male_hall_visits <- yng_big_explore_counts %>% filter(sex =="Male") %>%   transmute(subject,sex,age, B, C, D, E, `F`, G, H, J, M, Q, R, S, `T`, U, V, X, Z)
cols_sum<-c(4:length(yng_male_hall_visits))
yng_male_hall_visits$total<-rowSums(yng_male_hall_visits[,cols_sum])#finding total hallway counts for each subject for each session 
yng_male_hall_visits_mean<-aggregate(yng_male_hall_visits$total, list(yng_male_hall_visits$subject), FUN=mean)
yng_male_analysis$TotalHallwayVisits<-yng_male_hall_visits_mean$x 

halls <- rbind(halls,yng_male_analysis)

# ynglife female
yng_female_hall_visits <- yng_big_explore_counts %>% filter(sex =="Female") %>%   transmute(subject,sex,age, B, C, D, E, `F`, G, H, J, M, Q, R, S, `T`, U, V, X, Z)
cols_sum<-c(4:length(yng_female_hall_visits))
yng_female_hall_visits$total<-rowSums(yng_female_hall_visits[,cols_sum])#finding total hallway counts for each subject for each session 
yng_female_hall_visits_mean<-aggregate(yng_female_hall_visits$total, list(yng_female_hall_visits$subject), FUN=mean)
yng_female_analysis$TotalHallwayVisits<-yng_female_hall_visits_mean$x 

halls <- rbind(halls,yng_female_analysis) %>% dplyr::select(Subject,sex,age,TotalHallwayVisits)

#normality distribution

shapiro.test(yng_male_analysis$TotalHallwayVisits) 
shapiro.test(yng_female_analysis$TotalHallwayVisits)
shapiro.test(mid_male_analysis$TotalHallwayVisits) 
shapiro.test(mid_female_analysis$TotalHallwayVisits)

hallvis_aov<- aov(formula=TotalHallwayVisits ~ sex*age ,halls)
summary(hallvis_aov)
######## plot ##############

ym <- ggplot(yng_male_analysis, aes(x=TotalHallwayVisits)) + 
  geom_histogram(bins=10)
yf <- ggplot(yng_female_analysis, aes(x=TotalHallwayVisits)) + 
  geom_histogram(bins=10)

mm <- ggplot(mid_male_analysis,aes(x=TotalHallwayVisits))+ 
  geom_histogram(bins=10)
mf <- ggplot(mid_female_analysis, aes(x=TotalHallwayVisits))+ 
  geom_histogram(bins=10)

hall_distr <- ggarrange(ym,yf,mm,mf,
                       labels = c("Young Male", "Young Female", "Midlife Male","Midlife Female"),
                       font.label = list(size = 12, color = "red"),
                       vjust = 3,
                       ncol=2, nrow = 2)
annotate_figure(hall_distr,
                top = text_grob("Total Hall data distribution", color = "red", face = "bold", size = 14))
#does the plot have a common legend)

```

 All groups were normally distributed. No sex or age effects 
```{r Turns Made }
#young MAle and Female

yng_female_analysis$turns <- yng_master_participant %>% filter(sex == "Female") %>% pull(em_turns_count)
yng_male_analysis$turns <- yng_master_participant %>% filter(sex == "Male") %>% pull(em_turns_count)

Turns <- rbind(yng_female_analysis,yng_male_analysis )
# MIDLIFE
mid_male_analysis$turns <- mid_master_participant%>% filter(sex == "Male") %>% pull(em_turns_count)
Turns <- rbind(Turns,mid_male_analysis)

mid_female_analysis$turns <- mid_master_participant%>% filter(sex == "Female") %>% pull(em_turns_count)
Turns <- rbind(Turns,mid_female_analysis) %>% dplyr::select(Subject,sex,age,turns)
#Normality test to assess whether samples are normally distributed 
shapiro.test(yng_female_analysis$turns)
shapiro.test(yng_male_analysis$turns)
shapiro.test(mid_female_analysis$turns)
shapiro.test(mid_male_analysis$turns)

# analysis
turns_aov<- aov(formula=turns ~ sex*age ,Turns)
summary(turns_aov)

########plots ##########
# ym <- ggplot(yng_male_analysis, aes(x=turns)) + 
#   geom_histogram(bins=10)
# yf <- ggplot(yng_female_analysis, aes(x=turns)) + 
#   geom_histogram(bins=10)
# 
# mm <- ggplot(mid_male_analysis,aes(x=turns))+ 
#   geom_histogram(bins=10)
# mf <- ggplot(mid_female_analysis, aes(x=turns))+ 
#   geom_histogram(bins=10)
# 
# turns_distr <- ggarrange(ym,yf,mm,mf,
#                        labels = c("Young Male", "Young Female", "Midlife Male","Midlife Female"),
#                        font.label = list(size = 12, color = "red"),
#                        vjust = 3,
#                        ncol=2, nrow = 2)
# annotate_figure(turns_distr,
#                 top = text_grob("Total turns data distribution", color = "red", face = "bold", size = 14))
#does the plot have a common legend)


```

The data was not normally distributed for group: Midlife males(p-value = 0.04288), Midlife Females (p-value = 0.002284), Young males (p-value = 0.01312). Age effect (4.18e-0). A trend towards an interaction (0.0590) and sex effect (0.0807)
```{r Pause Duration}
# Young 
yng_female_analysis$pauses <- yng_master_participant %>% filter(sex == "Female") %>% pull(em_average_RT)
yng_male_analysis$pauses <- yng_master_participant %>% filter(sex == "Male") %>% pull(em_average_RT)

Pauses <- rbind(yng_female_analysis,yng_male_analysis)

#Midlife
mid_male_analysis$pauses <- mid_master_participant%>% filter(sex == "Male") %>% pull(em_average_RT)
Pauses <- rbind(Pauses,mid_male_analysis)

mid_female_analysis$pauses <- mid_master_participant%>% filter(sex == "Female") %>% pull(em_average_RT)
Pauses <- rbind(Pauses,mid_female_analysis) %>% dplyr::select(Subject,sex,age,pauses)

#Normality test and Distribution of data 
shapiro.test(yng_female_analysis$pauses)
shapiro.test(yng_male_analysis$pauses)
shapiro.test(mid_female_analysis$pauses)
shapiro.test(mid_male_analysis$pauses)

pauses_aov<- aov(formula=pauses ~ sex*age ,Pauses)
summary(pauses_aov)

# Post Hoc
# pairwise.t.test(Pauses$pauses, dist$group, p.adj="bonferroni")
# 
# TukeyHSD(pauses_aov)


#########plots #########
# ym <- ggplot(yng_male_analysis, aes(x=pauses)) + 
#   geom_histogram(bins=10)
# yf <- ggplot(yng_female_analysis, aes(x=pauses)) + 
#   geom_histogram(bins=10)
# 
# mm <- ggplot(mid_male_analysis,aes(x=pauses))+ 
#   geom_histogram(bins=10)
# mf <- ggplot(mid_female_analysis, aes(x=pauses))+ 
#   geom_histogram(bins=10)
# 
# pauses_distr <- ggarrange(ym,yf,mm,mf,
#                        labels = c("Young Male", "Young Female", "Midlife Male","Midlife Female"),
#                        font.label = list(size = 12, color = "red"),
#                        vjust = 3,
#                        ncol=2, nrow = 2)
# annotate_figure(pauses_distr,
#                 top = text_grob("Total turns data distribution", color = "red", face = "bold", size = 14))

```

Only midlife females failed normality (0.0232). A two factor anova showed an effect of age (4.06e-06) and sex (0.00213) but no interaction. 
```{r Evenness Of Exploration Objects}
## Young Males#####
yngM_spreadObjs <-
  yng_male_obj_visits %>% gather("location", "count", 4:12) %>%
  pivot_wider(
    id_cols = c("subject", "sex", "age"),
    names_from = location,
    values_from = count,
    values_fn = sum
  )
yngM_spreadObjs <-
  yngM_spreadObjs %>% mutate(std = apply(yngM_spreadObjs[4:12], 1, sd))
yngM_flip_objs <-
  yngM_spreadObjs %>% gather("location", "count", 4:12) %>% pivot_wider(
    id_cols = location,
    names_from = subject,
    values_from = count,
    values_fn = sum
  )
yngM_totalvisits <-
  as.data.frame(apply(yngM_spreadObjs[4:12], 2, sum)) %>% mutate(sd = apply(yngM_spreadObjs[4:12], 2, sd)) %>% mutate(location = yngM_flip_objs$location)

yng_male_analysis$evenness <- yngM_spreadObjs$std

### Young Females#####
yngF_spreadObjs <-
  yng_female_obj_visits %>% gather("location", "count", 4:12) %>%
  pivot_wider(
    id_cols = c("subject", "sex", "age"),
    names_from = location,
    values_from = count,
    values_fn = sum
  )
yngF_spreadObjs <-
  yngF_spreadObjs %>% mutate(std = apply(yngF_spreadObjs[4:12], 1, sd))

yngF_flip_objs <-
  yngF_spreadObjs %>% gather("location", "count", 4:12) %>% pivot_wider(
    id_cols = location,
    names_from = subject,
    values_from = count,
    values_fn = sum
  )

# will have to rename and re do this part below 10/12/2022
yngF_totalvisits <-
  as.data.frame(apply(yngF_spreadObjs[4:12], 2, sum)) %>% mutate(sd = apply(yngF_spreadObjs[4:12], 2, sd)) %>% mutate(location = yngF_flip_objs$location)

yng_female_analysis$evenness <- yngF_spreadObjs$std

#Binding the yng male and female evenness spread into one data frame for cleaner analysis 
Spread <- rbind(yng_male_analysis,yng_female_analysis)

### Midlife Males #####
midM_spreadObjs <-
  mid_male_obj_visits %>% gather("location", "count", 4:12) %>%
  pivot_wider(
    id_cols = c("subject", "sex", "age"),
    names_from = location,
    values_from = count,
    values_fn = sum
  )
midM_spreadObjs <-
  midM_spreadObjs %>% mutate(std = apply(midM_spreadObjs[4:12], 1, sd))
midM_flip_objs <-
  midM_spreadObjs %>% gather("location", "count", 4:12) %>% pivot_wider(
    id_cols = location,
    names_from = subject,
    values_from = count,
    values_fn = sum
  )
midM_totalvisits <-
  as.data.frame(apply(midM_spreadObjs[4:12], 2, sum)) %>% mutate(sd = apply(midM_spreadObjs[4:12], 2, sd)) %>% mutate(location = midM_flip_objs$location)

mid_male_analysis$evenness <- midM_spreadObjs$std

Spread <- rbind(Spread,mid_male_analysis)

#### Female Females #####
midF_spreadObjs <-
  mid_female_obj_visits %>% gather("location", "count", 4:12) %>%
  pivot_wider(
    id_cols = c("subject", "sex", "age"),
    names_from = location,
    values_from = count,
    values_fn = sum
  )
midF_spreadObjs <-
  midF_spreadObjs %>% mutate(std = apply(midF_spreadObjs[4:12], 1, sd))

midF_flip_objs <-
  midF_spreadObjs %>% gather("location", "count", 4:12) %>% pivot_wider(
    id_cols = location,
    names_from = subject,
    values_from = count,
    values_fn = sum
  )

# will have to rename and re do this part below 10/12/2022
midF_totalvisits <-
  as.data.frame(apply(midF_spreadObjs[4:12], 2, sum)) %>% mutate(sd = apply(midF_spreadObjs[4:12], 2, sd)) %>% mutate(location = midF_flip_objs$location)

mid_female_analysis$evenness <- midF_spreadObjs$std

#Binding the mid male and female evenness spread into one data frame for cleaner analysis 
Spread <- rbind(Spread,mid_female_analysis) %>% dplyr::select(Subject,sex,age,evenness)

#### Data Distribution and normality check ####
shapiro.test(yng_female_analysis$evenness)
shapiro.test(yng_male_analysis$evenness)
shapiro.test(mid_female_analysis$evenness)
shapiro.test(mid_male_analysis$evenness)


### Analysis ####
obj_evenness_aov<- aov(formula=evenness ~ sex*age ,Spread)
summary(obj_evenness_aov)

########plot #######
# ym <- ggplot(yng_male_analysis, aes(x=evenness)) + 
#   geom_histogram(bins=10)
# yf <- ggplot(yng_female_analysis, aes(x=evenness)) + 
#   geom_histogram(bins=10)
# 
# mm <- ggplot(mid_male_analysis,aes(x=evenness))+ 
#   geom_histogram(bins=10)
# mf <- ggplot(mid_female_analysis, aes(x=evenness))+ 
#   geom_histogram(bins=10)
# 
# pauses_distr <- ggarrange(ym,yf,mm,mf,
#                        labels = c("Young Male", "Young Female", "Midlife Male","Midlife Female"),
#                        font.label = list(size = 12, color = "red"),
#                        vjust = 3,
#                        ncol=2, nrow = 2)
# annotate_figure(pauses_distr,
#                 top = text_grob("Total evenness data distribution", color = "red", face = "bold", size = 14))


```

# midlife male and females failed normality (P= 0.0002499,0.009405, respectively). There was an effect of age (4.06e-06) and sex (0.00213) but no interaction. 
```{r Eveness of Exploration (Hallways)}
## Young Males#####
yngM_spreadHalls <-
  yng_male_hall_visits %>% gather("location", "count", 4:12) %>%
  pivot_wider(
    id_cols = c("subject", "sex", "age"),
    names_from = location,
    values_from = count,
    values_fn = sum
  )
yngM_spreadHalls <-
  yngM_spreadHalls %>% mutate(std = apply(yngM_spreadHalls[4:12], 1, sd))
yngM_flip_halls <-
  yngM_spreadHalls %>% gather("location", "count", 4:12) %>% pivot_wider(
    id_cols = location,
    names_from = subject,
    values_from = count,
    values_fn = sum
  )
yngM_totalhallvis <-
  as.data.frame(apply(yngM_spreadHalls[4:12], 2, sum)) %>% mutate(sd = apply(yngM_spreadHalls[4:12], 2, sd)) %>% mutate(location = yngM_flip_halls$location)

yng_male_analysis$HallEvenness <- yngM_spreadHalls$std

### Young Females#####
yngF_spreadHalls <-
  yng_female_hall_visits %>% gather("location", "count", 4:12) %>%
  pivot_wider(
    id_cols = c("subject", "sex", "age"),
    names_from = location,
    values_from = count,
    values_fn = sum
  )
yngF_spreadHalls <-
  yngF_spreadHalls %>% mutate(std = apply(yngF_spreadHalls[4:12], 1, sd))

yngF_flip_halls <-
  yngF_spreadHalls %>% gather("location", "count", 4:12) %>% pivot_wider(
    id_cols = location,
    names_from = subject,
    values_from = count,
    values_fn = sum
  )

# will have to rename and re do this part below 10/12/2022
yngF_totalhallvis <-
  as.data.frame(apply(yngF_spreadHalls[4:12], 2, sum)) %>% mutate(sd = apply(yngF_spreadHalls[4:12], 2, sd)) %>% mutate(location = yngF_flip_halls$location)

yng_female_analysis$HallEvenness <- yngF_spreadHalls$std

#Binding the yng male and female evenness spread into one data frame for cleaner analysis 
Hallspread <- rbind(yng_male_analysis,yng_female_analysis)

### Midlife Males #####
midM_spreadHalls <-
  mid_male_hall_visits %>% gather("location", "count", 4:12) %>%
  pivot_wider(
    id_cols = c("subject", "sex", "age"),
    names_from = location,
    values_from = count,
    values_fn = sum
  )
midM_spreadHalls <-
  midM_spreadHalls %>% mutate(std = apply(midM_spreadHalls[4:12], 1, sd))
midM_flip_halls <-
  midM_spreadHalls %>% gather("location", "count", 4:12) %>% pivot_wider(
    id_cols = location,
    names_from = subject,
    values_from = count,
    values_fn = sum
  )
midM_totalhallvis <-
  as.data.frame(apply(midM_spreadHalls[4:12], 2, sum)) %>% mutate(sd = apply(midM_spreadHalls[4:12], 2, sd)) %>% mutate(location = midM_flip_halls$location)

mid_male_analysis$HallEvenness <- midM_spreadHalls$std

Hallspread <- rbind(Hallspread,mid_male_analysis)

#### Female Females #####
midF_spreadHalls <-
  mid_female_hall_visits %>% gather("location", "count", 4:12) %>%
  pivot_wider(
    id_cols = c("subject", "sex", "age"),
    names_from = location,
    values_from = count,
    values_fn = sum
  )
midF_spreadHalls <-
  midF_spreadHalls %>% mutate(std = apply(midF_spreadHalls[4:12], 1, sd))
midF_flip_halls <-
  midF_spreadHalls %>% gather("location", "count", 4:12) %>% pivot_wider(
    id_cols = location,
    names_from = subject,
    values_from = count,
    values_fn = sum
  )
midF_totalhallvis <-
  as.data.frame(apply(midF_spreadHalls[4:12], 2, sum)) %>% mutate(sd = apply(midF_spreadHalls[4:12], 2, sd)) %>% mutate(location = midF_flip_halls$location)

mid_female_analysis$HallEvenness <- midF_spreadHalls$std

#Binding the mid male and female evenness spread into one data frame for cleaner analysis 
Hallspread <- rbind(Hallspread,mid_female_analysis) %>% dplyr::select(Subject,sex,age,HallEvenness)

#### Data Distribution and normality check ####
shapiro.test(yng_female_analysis$HallEvenness)
shapiro.test(yng_male_analysis$HallEvenness)
shapiro.test(mid_female_analysis$HallEvenness)
shapiro.test(mid_male_analysis$HallEvenness)


### Analysis ####
Hallevenness_aov<- aov(formula=evenness ~ sex*age ,Spread)
summary(Hallevenness_aov)


#######plot ######
# ym <- ggplot(yng_male_analysis, aes(x=HallEvenness)) + 
#   geom_histogram(bins=10)
# yf <- ggplot(yng_female_analysis, aes(x=HallEvenness)) + 
#   geom_histogram(bins=10)
# 
# mm <- ggplot(mid_male_analysis,aes(x=HallEvenness))+ 
#   geom_histogram(bins=10)
# mf <- ggplot(mid_female_analysis, aes(x=HallEvenness))+ 
#   geom_histogram(bins=10)
# 
# pauses_distr <- ggarrange(ym,yf,mm,mf,
#                        labels = c("Young Male", "Young Female", "Midlife Male","Midlife Female"),
#                        font.label = list(size = 12, color = "red"),
#                        vjust = 3,
#                        ncol=2, nrow = 2)
# annotate_figure(pauses_distr,
#                 top = text_grob("Total Hall evenness data distribution", color = "red", face = "bold", size = 14))
```

Midlife female and young female failed normality tests. Two factor anova revelead an effect of sex(0.03406) and age( 0.00247) but no interaction
```{r BUTTON PRESS MOVES}
#### Young Males ###
yngM_button_press<- yng_explor %>% filter(Procedure == "ExploreProc")  %>% filter(sex == "Male") 
yngM_button_press<-yngM_button_press %>% transmute(Subject,sex,age, nodesturns_count)
yngM_button_press_mean<-aggregate(yngM_button_press$nodesturns_count, list(yngM_button_press$Subject), FUN=mean) #calculating mean number of button presses

yng_male_analysis$ButtonPress<-yngM_button_press_mean$x 

### Young Females ####
yngF_button_press<- yng_explor %>% filter(Procedure == "ExploreProc")  %>% filter(sex == "Female") 
yngF_button_press<-yngF_button_press %>% transmute(Subject,sex,age, nodesturns_count)
yngF_button_press_mean<-aggregate(yngF_button_press$nodesturns_count, list(yngF_button_press$Subject), FUN=mean) #calculating mean number of button presses

yng_female_analysis$ButtonPress<-yngF_button_press_mean$x 

BP <- rbind(yng_female_analysis, yng_male_analysis)
#### Midlife Males ###
midM_button_press<- mid_explor %>% filter(Procedure == "ExploreProc")  %>% filter(sex == "Male") 
midM_button_press<-midM_button_press %>% transmute(Subject,sex,age,nodesturns_count)
midM_button_press_mean<-aggregate(midM_button_press$nodesturns_count, list(midM_button_press$Subject), FUN=mean) #calculating mean number of button presses

mid_male_analysis$ButtonPress<-midM_button_press_mean$x 

BP <- rbind(BP, mid_male_analysis)
### Midlife Females ####
midF_button_press<- mid_explor %>% filter(Procedure == "ExploreProc")  %>% filter(sex == "Female") 
midF_button_press<-midF_button_press %>% transmute(Subject,sex,age, nodesturns_count)
midF_button_press_mean<-aggregate(midF_button_press$nodesturns_count, list(midF_button_press$Subject), FUN=mean) #calculating mean number of button presses

mid_female_analysis$ButtonPress<-midF_button_press_mean$x 

BP <- rbind(BP, mid_female_analysis)%>% dplyr::select(Subject,sex,age,ButtonPress)

shapiro.test(yng_female_analysis$ButtonPress)
shapiro.test(yng_male_analysis$ButtonPress)
shapiro.test(mid_female_analysis$ButtonPress)
shapiro.test(mid_male_analysis$ButtonPress)

BP_aov<- aov(formula=ButtonPress ~ sex*age ,BP)
summary(BP_aov)
 

```

```{r Midlife path roaming entropy processing}
#Path Roaming Entropy 
mid_exp_paths<-as.data.frame(mid_big_explore[,c("subject", "sex", "age")]) #building empty dataframe which we will populate with output from for loop below (part 1)
mid_exp_paths$paths<-rep("TBC",nrow(mid_exp_paths)) #adding TBCs for now, this will be replaced with output from for loop below 

#For loop to condense path trajectories from midlife_big_explore into single sequence, and remove "repeats" and "none"
for (i in 1:nrow(mid_big_explore)){
  cols<-4:length(mid_big_explore) #indexing columns to condense into single sequence 
  mid_exp_paths[i,4]<-paste(mid_big_explore[i,cols], collapse = '') #combining all characters into single sequence 
  mid_exp_paths[i,4]<-gsub('[repeatsnone]', '', mid_exp_paths[i,4])#removing strings "repeats" and "none" from sequence
}

#Combining each subject's exploration trajectories across both sessions into one exploration trajectory 
mid_exp_paths<- mid_exp_paths %>% group_by(subject) %>% mutate(newcol=paste(paths, collapse = '')) #combining trajectories for each subject
mid_exp_paths<- mid_exp_paths %>% filter (row_number() %% 2 !=0) #deletes even rows, which are duplicates with regards to combined trajectories 
names(mid_exp_paths)[names(mid_exp_paths) == 'newcol'] <- 'CombinedPaths' #renaming column 
mid_exp_paths<-as.data.frame(mid_exp_paths) #converting to df so that for loop below works 

#For loop to calculate path roaming entropies 
for (i in 1:nrow(mid_exp_paths)){
  y<-strsplit(mid_exp_paths[i,5],split = "")
  y_counts_table<-table(y)
  y_counts_vals<-as.numeric(y_counts_table)
  y_entropy<-entropy(y_counts_vals,method = c("ML")) #calculate Shannon's Entropy 
  mid_exp_paths$entropy[i]<-y_entropy
} 

mid_female_analysis$entropy <- mid_exp_paths %>% filter(sex=="Female") %>% .[,c("entropy")]
mid_male_analysis$entropy <- mid_exp_paths %>% filter(sex=="Male") %>% .[,c("entropy")]

```

```{r young path roaming entropy processing}
#Path Roaming Entropy 
yng_exp_paths<-as.data.frame(yng_big_explore[,c("subject", "sex", "age")]) #building empty dataframe which we will populate with output from for loop below (part 1)
yng_exp_paths$paths<-rep("TBC",nrow(yng_exp_paths)) #adding TBCs for now, this will be replaced with output from for loop below 

#For loop to condense path trajectories from ynglife_big_explore into single sequence, and remove "repeats" and "none"
for (i in 1:nrow(yng_big_explore)){
  cols<-4:length(yng_big_explore) #indexing columns to condense into single sequence 
  yng_exp_paths[i,4]<-paste(yng_big_explore[i,cols], collapse = '') #combining all characters into single sequence 
  yng_exp_paths[i,4]<-gsub('[repeatsnone]', '', yng_exp_paths[i,4])#removing strings "repeats" and "none" from sequence
}

#Combining each subject's exploration trajectories across both sessions into one exploration trajectory 
yng_exp_paths<- yng_exp_paths %>% group_by(subject) %>% mutate(newcol=paste(paths, collapse = '')) #combining trajectories for each subject
yng_exp_paths<- yng_exp_paths %>% filter (row_number() %% 2 !=0) #deletes even rows, which are duplicates with regards to combined trajectories 
names(yng_exp_paths)[names(yng_exp_paths) == 'newcol'] <- 'CombinedPaths' #renaming column 
yng_exp_paths<-as.data.frame(yng_exp_paths) #converting to df so that for loop below works 

#For loop to calculate path roaming entropies 
for (i in 1:nrow(yng_exp_paths)){
  y<-strsplit(yng_exp_paths[i,5],split = "")
  y_counts_table<-table(y)
  y_counts_vals<-as.numeric(y_counts_table)
  y_entropy<-entropy(y_counts_vals,method = c("ML")) #calculate Shannon's Entropy 
  yng_exp_paths$entropy[i]<-y_entropy
} 

yng_female_analysis$entropy <- yng_exp_paths %>% filter(sex=="Female") %>% .[,c("entropy")]
yng_male_analysis$entropy <- yng_exp_paths %>% filter(sex=="Male") %>% .[,c("entropy")]

Entropy <- rbind(mid_exp_paths,yng_exp_paths) %>% dplyr::select(subject,sex,age,entropy)

```

A normality test was run on each group. The data was not normally distributed for any group: Midlife males(p-value = 0.00695), Midlife Females (p-value = 1e-05), Young males (p-value =  0.01314), and young females (p-value = 0.05319). A two factor anova revealed an effect of sex (0.000274) and an effect of age (< 2e-16)
```{r Entropy Analysis}
#normality
shapiro.test(yng_female_analysis$entropy)
shapiro.test(yng_male_analysis$entropy)
shapiro.test(mid_female_analysis$entropy)
shapiro.test(mid_male_analysis$entropy)

entropy_aov<- aov(formula=entropy ~ sex*age ,Entropy)
summary(entropy_aov)
```

A normality test was run on each group. The data was not normally distributed for most groups: Midlife males(p-value = 0.01381), Midlife Females (p-value = 0.000541), Young males (p-value =  0.0001843), and young females (p-value = 0.3501). A two factor anova revealed an effect of sex (0.00455) and an effect of age (< 2e-16)
```{r Longest Hallway}
#Longest Hallway Sequence 
#For loop to identify longest hallway sequence 
for (i in 1:nrow(mid_exp_paths)){
  z<-strsplit(mid_exp_paths[i,5],split = "")
  logical<-as.vector(sapply(z, `%in%`, objects)) #finding if each visited location is an object or not in binary form (true=object, false=hallway)
  mid_exp_paths$hallwayseq[i]<-with(rle(logical),max(lengths))#finding longest sequence of hallway visits that is not interrupted by an object visit; note that max seq is bound to be hallway as you can't have long sequences of obj visits ('Trues')  
}

mid_female_analysis$hallwayseq <- mid_exp_paths %>% filter(sex=="Female") %>% .[,c("hallwayseq")]
mid_male_analysis$hallwayseq <- mid_exp_paths %>% filter(sex=="Male") %>% .[,c("hallwayseq")]

## young 
for (i in 1:nrow(yng_exp_paths)){
  z<-strsplit(yng_exp_paths[i,5],split = "")
  logical<-as.vector(sapply(z, `%in%`, objects)) 
  yng_exp_paths$hallwayseq[i]<-with(rle(logical),max(lengths))
}

yng_female_analysis$hallwayseq <- yng_exp_paths %>% filter(sex=="Female") %>% .[,c("hallwayseq")]
yng_male_analysis$hallwayseq <- yng_exp_paths %>% filter(sex=="Male") %>% .[,c("hallwayseq")]

shapiro.test(yng_female_analysis$hallwayseq)
shapiro.test(yng_male_analysis$hallwayseq)
shapiro.test(mid_female_analysis$hallwayseq)
shapiro.test(mid_male_analysis$hallwayseq)


longesthall <- rbind(mid_exp_paths,yng_exp_paths) %>% dplyr::select(subject,sex,age,hallwayseq)

longesthall_aov<- aov(formula=hallwayseq ~ sex*age,longesthall)
summary(longesthall_aov)


```

A normality test was run on each group. The data was not normally distributed for any group: Midlife males(p-value = 3.011e-05), Midlife Females (p-value = 3.273e-10), Young males (p-value = 0.005024), and young females (p-value = 0.0191). A two factor anova revealed a sex and age interaction (6.83e-05 ).  post hox non parametric ttests revealed a sex difference in young (p=2.591e-06) but not midlife (0.1046)
```{r Performance on wayfinding : accuracy}
# young subs 
yng_female_analysis$accuracy <-yng_master_participant %>% filter(sex == "Female") %>% dplyr::pull(tm_accuracy) 

yng_male_analysis$accuracy <-yng_master_participant %>% filter(sex == "Male") %>% dplyr::pull(tm_accuracy)

AccDF <- rbind(yng_male_analysis, yng_female_analysis)

acc_aov <-  aov(formula= accuracy ~ sex * age, AccDF)
summary(acc_aov)

# post hoc non parametric tests
# #Wilcoxon Test midlife 
ttst(AccDF[AccDF$sex == 'Male' & AccDF$age == "midlife", c("tm_accuracy")],AccDF[AccDF$sex == 'Female' & AccDF$age == "midlife", c("tm_accuracy")])
#young wilcox ttest 
wilcox.test(AccDF[AccDF$sex == 'Male' & AccDF$age == "young", c("tm_accuracy")],AccDF[AccDF$sex == 'Female' & AccDF$age == "young", c("tm_accuracy")])


```

```{r Mediation Analysis }
mediation_df <- rbind(mid_female_analysis,mid_male_analysis)
mediation_df <- rbind(mediation_df,yng_female_analysis)
mediation_df <- rbind(mediation_df,yng_male_analysis)

#Step 1- Finding Total Effect (relationship between independent variable & dependent variable)
# there's a weird return with the vairable names 
fit.totaleffect<-lm(accuracy ~ age+sex, mediation_df)
summary(fit.totaleffect)

#Pause Duration As Mediator Analysis
# does  age regression on pauses
pause_fit.dv<-lm(pauses ~ age, mediation_df) # here the dv being mediated is relationship between age and pauses 
summary(pause_fit.dv)
# does  sex regression on pauses. no 
pause_fit.mediator<-lm(pauses ~ sex, mediation_df) # sex is the mediator
summary(pause_fit.mediator)
# no mediation


#Object Visits As Mediator Analysis  
obj_fit.mediator<-lm(TotalObjVisits ~ sex, mediation_df)
summary(obj_fit.mediator)

obj_fit.dv<-lm(TotalObjVisits ~ age, mediation_df)
summary(obj_fit.dv)
# no mediation



```


```{r Plots for distance }
yng_distance <- yng_master_participant %>% dplyr::select(Subject,sex,age) %>% as.data.frame() %>% mutate(Dist = yng_master_participant$em_path_dist_trav)
mid_distance <- mid_master_participant %>% dplyr::select(Subject,sex,age) %>% as.data.frame() %>% mutate(Dist = mid_master_participant$em_path_dist_trav)

dist <- rbind(yng_distance,mid_distance)

#this was just to create a better grouping


sam_size <- dist%>%dplyr::group_by(group)%>% dplyr::summarize(num=n())


pdf("Distance Traveled in young and midlife split by gender.pdf")
dist %>%
  left_join(sam_size) %>%
  mutate(myaxis=paste0(group,"\n", "n=", num)) %>%
  ggplot( aes(x=myaxis, y=Dist, fill=group)) +
  geom_violin() +
  geom_boxplot(width=0.2, color="grey", alpha=0.2) +
  geom_jitter(position = position_jitter(seed = 1, width = 0.1)) +
  scale_colour_brewer(cbPalette) +
  stat_summary(fun="mean",size =0.2, color="red" )+
  theme(legend.position="none", plot.title = element_text(size=14)) +
  ggtitle("Distance in young and midlife split by gender") +
  xlab("") +
  ylab("Distance traveled")
dev.off()

```

```{r Plot for object visits }
yng_obj <- rbind(yng_female_analysis,yng_male_analysis) %>% 
  dplyr::select(Subject,TotalObjVisits) %>% 
  arrange() %>% 
  mutate(sex= yng_master_participant$sex)%>% 
  mutate(age= yng_master_participant$age)

mid_obj <- rbind(mid_female_analysis,mid_male_analysis) %>% 
  dplyr::select(Subject,TotalObjVisits) %>% 
  arrange() %>% 
  mutate(sex= mid_master_participant$sex)%>% 
  mutate(age= mid_master_participant$age)

ObjVisits <- rbind(yng_obj,mid_obj)


sam_size <- ObjVisits%>%dplyr::group_by(group)%>% dplyr::summarize(num=n())


pdf("Distance Traveled in young and midlife split by gender.pdf")
ObjVisits %>%
  left_join(sam_size) %>%
  mutate(myaxis=paste0(group,"\n", "n=", num)) %>%
  ggplot( aes(x=myaxis, y=TotalObjVisits, fill=group)) +
  #geom_violin() +
    geom_boxplot(width=0.2, color="grey", alpha=0.2) +
    geom_jitter(position = position_jitter(seed = 1, width = 0.1)) +
    scale_colour_brewer(cbPalette) +
    stat_summary(fun="mean",size =0.2, color="red" )+
    theme(legend.position="none", plot.title = element_text(size=14)) +
    ggtitle("Object Visits in young and midlife split by gender") +
    theme(plot.title = element_text(hjust = 0.5))+
  xlab("") +
  ylab("Object Visits")
dev.off()

# LEts just do women 
pdf("Distance Traveled in young and midlife Women.pdf")
ObjVisits %>%
  left_join(sam_size) %>% 
  filter(sex == "Female") %>% 
  mutate(myaxis=paste0(group,"\n", "n=", num)) %>%
  ggplot( aes(x=myaxis, y=TotalObjVisits, fill=group)) +
  #geom_violin() +
    geom_boxplot(width=0.2, color="grey", alpha=0.2) +
    geom_jitter(position = position_jitter(seed = 1, width = 0.1)) +
    scale_colour_brewer(cbPalette) +
    stat_summary(fun="mean",size =0.2, color="red" )+
    theme(legend.position="none", plot.title = element_text(size=14)) +
    ggtitle("Object Visits in young and midlife women") +
    theme(plot.title = element_text(hjust = 0.5))+
    xlab("") +
    ylab("Total bject Visits")
dev.off()


#Lets do men
pdf("Distance Traveled in young and midlife Men.pdf")
ObjVisits %>%
  left_join(sam_size) %>% 
  filter(sex == "Male") %>% 
  mutate(myaxis=paste0(group,"\n", "n=", num)) %>%
  ggplot( aes(x=myaxis, y=TotalObjVisits, fill=group)) +
  #geom_violin() +
    geom_boxplot(width=0.2, color="grey", alpha=0.2) +
    geom_jitter(position = position_jitter(seed = 1, width = 0.1)) +
    scale_colour_brewer(cbPalette) +
    stat_summary(fun="mean",size =0.2, color="red" )+
    theme(legend.position="none", plot.title = element_text(size=14)) +
    ggtitle("Object Visits in young and midlife women") +
    theme(plot.title = element_text(hjust = 0.5))+
    xlab("") +
    ylab("Total Object Visits")
dev.off()





```








Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
