---
title: "Young_MidlifeSexDiff"
purpose: "This is to analyze sex differences in behavior both in the toung participants. This uses parts of viasakhs and kates code"   #
input: Trial.csv and participant.csv and participant info               
output: Figures and analysis for various variables                    
Notes:  
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
#(plyr)
library(tidyverse)
# library(dplyr)
# library(tidyr)
library(stringr)
# library(data.table)
# library(network)
# library(tidygraph)
# library(ggraph)
# library(igraph)
# library(networkD3)
# library(CINNA)
# library(umap)
# library(plotly)
library(factoextra)
library(lsr)
# library(car)
# library(ggpubr)
# library(entropy)
# library(ds4psy)
# library(pROC)
library(devtools)
library(BRRR)
library(afex)

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
workdir<- "/Users/danielacossio/Desktop/MLINDIV_analysisDC/MidlifeDesktopBehavior"
setwd(workdir)
```

```{r reading in midlife }
#infosheet with age/sex
subjInfo<-read.csv ("/Users/danielacossio/Desktop/MLINDIV_analysisDC/MidlifeDesktopBehavior/BehaviorAnalysisScripts/MAZE_data_old.csv")  %>% select(Subject.ID,Sex,Age.Scan..years.,) %>% `colnames<-` (c("Subject","sex","age")) %>% arrange(.$Subject)

#preprocessed data 
trialDF<-read.csv ("/Users/danielacossio/Desktop/MLINDIV_analysisDC/MidlifeDesktopBehavior/BehaviorAnalysisScripts/MLINDIV_trial_master.csv") %>% filter(Subject %in% c(as.character(subjInfo$Subject))) 

participantDF<-read.csv ("/Users/danielacossio/Desktop/MLINDIV_analysisDC/MidlifeDesktopBehavior/BehaviorAnalysisScripts/MLINDIV_participant_master.csv") %>%  filter(Subject %in% c(as.character(subjInfo$Subject)))

mid_master_trial <- inner_join(subjInfo, trialDF, by="Subject") 
mid_master_participant <- inner_join(subjInfo, participantDF, by="Subject") 

```

```{r reading in young participants}
yngsubjInfo<-read.csv("/Volumes/GoogleDrive/My Drive/MLINDIV_SNAG_preprocessing/young_SNAG/young_snag_participantinfo.csv")  %>% select(subject_id,sex,age_spatial_years) %>% `colnames<-` (c("Subject","sex","age"))

yngtrialDF<-read.csv ("/Volumes/GoogleDrive/My Drive/MLINDIV_SNAG_preprocessing/young_SNAG/young_trial_master (1).csv") %>% filter(Subject %in% c(as.character(yngsubjInfo$Subject))) 

yngparticipantDF <-read.csv("/Volumes/GoogleDrive/My Drive/MLINDIV_SNAG_preprocessing/young_SNAG/young_participant_master (1).csv") %>% filter(Subject %in% c(as.character(yngsubjInfo$Subject))) 


yng_master_trial <- inner_join(yngsubjInfo, yngtrialDF, by="Subject") 
yng_master_participant <- inner_join(yngsubjInfo, yngparticipantDF, by="Subject") 

```

```{r prepping variables for later use}

locs <- c('A', 'B', 'C', 'D', 'E', 'F', 'G', 'H', 'I', 'J', 'K', 'L', 'M', 'N', 'O', 'P', 'Q', 'R', 'S', 'T', 'U', 'V', 'W', 'X', "Y", "Z")
objs_orientations<- c('A4', 'I2', 'K4', 'L2', 'N3', 'O2', 'P2', 'Y2', 'W4')
objects<-c('A', 'I', 'K', 'L', 'N', 'O', 'P', 'Y', 'W')
hallways <- c('B', 'C', 'D', 'E', 'F', 'G', 'H', 'J', 'M', 'Q', 'R', 'S', 'T', 'U', "V", 'X', "Z")

#A=guitar
#I=snowman
#L=spaceship
#K=lamp post
#N=chicken
#O=trophy
#P=chair
#Y=umbrella
#W=cuckoo clock

#ttest output colnames for data later 
#colttest <-  c("estimate","statistic", "p.value", "parameter"," conf.low"," conf.high"," method","alternative")
```

```{r prepping datafranes for later use}

mid_female_analysis<-mid_master_participant %>% filter(sex == "Female") %>% select(Subject) %>% as.data.frame() #creating master analysis data-frame to store all final exploration variable outputs into 
mid_male_analysis<-mid_master_participant %>% filter(sex == "Male") %>% select(Subject) %>% as.data.frame()
  
yng_female_analysis<-yng_master_participant %>% filter(sex == "Female") %>% select(Subject) %>% as.data.frame() 
yng_male_analysis<-yng_master_participant %>% filter(sex == "Male") %>% select(Subject) %>% as.data.frame() #same thing for young

```


```{r GRabbing the exploration trials for both groups }

mid_explor <- mid_master_trial %>% filter(is.na(accuracy) == TRUE)
yng_explor <- yng_master_trial %>% filter(is.na(accuracy) == TRUE)

```

```{r Little bit of preprocessing on the explore trials }

#creating empty dataframe to store contents of for loop into 
# midlife 

mid_expl_df<- data.frame(matrix(nrow = nrow(mid_explor)))

for (i in 1:nrow(mid_explor)){
  e_string_orient<-as.list(strsplit(mid_explor$e_paths[i],split=" ")) 
  e_string<-as.list(strsplit(mid_explor$paths[i],split=" ")) 
  F3_index<-which(sapply(e_string_orient[[1]], FUN=function(X) "F3" %in% X))+1  
  e_string[[1]][F3_index]<-"N" #replacing with N
  V2_index<-which(sapply(e_string_orient[[1]], FUN=function(X) "V2" %in% X))+1
  e_string[[1]][V2_index]<-"Y" #replacing with Y
  e_string<-paste(e_string[[1]], collapse = " ") 
  mid_expl_df[i,1]<-e_string 
}

mid_expl_df$Subject<-mid_explor$Subject
mid_expl_df <- mid_expl_df %>% rename(paths = matrix.nrow...nrow.mid_explor..) 

mid_explr_Subinfo <- inner_join(mid_master_participant,mid_expl_df)
```

```{r explore trial young preprocessing }

yng_expl_df<- data.frame(matrix(nrow = nrow(yng_explor)))

for (i in 1:nrow(yng_explor)){
  e_string_orient<-as.list(strsplit(yng_explor$e_paths[i],split=" ")) 
  e_string<-as.list(strsplit(yng_explor$paths[i],split=" ")) 
  F3_index<-which(sapply(e_string_orient[[1]], FUN=function(X) "F3" %in% X))+1  
  e_string[[1]][F3_index]<-"N" #replacing with N
  V2_index<-which(sapply(e_string_orient[[1]], FUN=function(X) "V2" %in% X))+1
  e_string[[1]][V2_index]<-"Y" #replacing with Y
  e_string<-paste(e_string[[1]], collapse = " ") 
  yng_expl_df[i,1]<-e_string 
}

yng_expl_df$Subject<-yng_explor$Subject
yng_expl_df <- yng_expl_df %>% rename(paths = matrix.nrow...nrow.yng_explor..) 

yng_explr_Subinfo <- inner_join(yng_master_participant,yng_expl_df)

```


Distance Summary of results: No sex differences in men and women during midlife:

There's no significant difference between men and women at the young age but there was at the midlife age. Women traveled significantly less than men did. Nho significant difference between midlife men andage men 
```{r Distance }

#Let's look at the young men first 
 yng_male_analysis$Dist<- yng_master_participant %>% filter(sex == "Male") %>% pull(em_path_dist_trav)
shapiro.test(yng_male_analysis$Dist)  #not normal 
# young female 
 yng_female_analysis$Dist<- yng_master_participant %>% filter(sex == "Female") %>% pull(em_path_dist_trav)
shapiro.test(yng_female_analysis$Dist) # not normal 

# Lets do the young 
wilcox.test(yng_female_analysis$Dist,yng_male_analysis$Dist) #no difference 

# LEts do Midlife 
mid_female_analysis$Dist<-mid_master_participant%>% filter(sex == "Female") %>% pull(em_path_dist_trav)
#male
mid_male_analysis$Dist<-mid_master_participant%>% filter(sex == "Male") %>% pull(em_path_dist_trav)


#Normality test to assess whether samples are normally distributed  # females is not normal
shapiro.test(mid_male_analysis$Dist)
shapiro.test(mid_female_analysis$Dist)
wilcox.test(mid_female_analysis$Dist,mid_male_analysis$Dist) #0.03 


# young female vs young midlife
wilcox.test(mid_female_analysis$Dist,yng_female_analysis$Dist) # significant pvalue = 0.001139 

#midlife women =217.6289
#yng=244.3077

# young men vs midlife men 
wilcox.test(mid_male_analysis$Dist,yng_male_analysis$Dist) #not significantly different 
# young men =248.3646
#midlife men = 233.9728

```

```{r Distance analysis using non normal anova NOT WORKING RN }
yng_distance <- yng_master_participant %>% select(Subject,sex,age) %>% as.data.frame() %>% mutate(Dist = yng_master_participant$em_path_dist_trav)
mid_distance <- mid_master_participant %>% select(Subject,sex,age) %>% as.data.frame() %>% mutate(Dist = mid_master_participant$em_path_dist_trav)

dist <- rbind(yng_distance,mid_distance)

#this was just to quickly convert to binary
for (gender in 1:nrow(dist)){
   if (dist$sex[gender] == "Female") {
      dist$sex[gender] = 0
     } else {
      dist$sex[gender] = 1
    }
 }


# this was just to quickly convert to binary
  for (group in 1:nrow(dist)){
    if (dist$age[group] < 25) {
      dist$group[group] <- "young"
      } else {
         dist$group[group] <- "midlife"
      }
  }
 

a <-  aov(formula=Dist ~ group + age + sex,dist)
summary(a)

dist %>% 
  aov_ez(id = 'group', dv = 'Dist', within = 'group' , covariate = list('age', 'sex'))

# the hypothesis were assuming are that men and women

# i think maybe taking z score 
```

```{r SPEED Skipped for now }

```

```{r midlife explore object processing }
mid_big_explore<-as.data.frame(str_split_fixed(mid_expl_df$paths," ",nrow(mid_expl_df)))
mid_big_explore <- mid_big_explore %>% mutate(subject = mid_expl_df$Subject) 
mid_big_explore <-mid_big_explore[,c(ncol(mid_big_explore), 1:(ncol(mid_big_explore)-1))] 

row_labels<-c(1:nrow(mid_big_explore))
mid_big_explore<- split( mid_big_explore , f = row_labels)

#for loop to find consecutive location repeats, and remove them 
for (i in 1:length(mid_big_explore)){
  mid_big_explore[[i]]<-t(mid_big_explore[[i]])
  mid_big_explore[[i]][mid_big_explore[[i]] == ""] <- NA 
  repeat_logical<-t(c(NA, mid_big_explore[[i]]) == c(mid_big_explore[[i]], NA))[1:length(mid_big_explore[[i]])]
  repeats<- grep("TRUE",repeat_logical)
  mid_big_explore[[i]][repeats,1]<-"repeats"  
  mid_big_explore[[i]]<-t(mid_big_explore[[i]])
  mid_big_explore[[i]]<-as.data.frame(mid_big_explore[[i]]) 
}

mid_big_explore<-unsplit(mid_big_explore,row_labels)#merging all chunks back into single dataframe 
mid_big_explore[is.na(mid_big_explore)]<-"none" #replacing all NAs with string, otherwise for loop below won't work 
mid_big_explore <-  mid_big_explore %>% mutate(sex = mid_explr_Subinfo$sex)

#for loop to determine location counts 
mid_big_explore_counts <- data.frame(matrix(ncol = 0, nrow = nrow(mid_big_explore)))#creating dataframe to store counts into  

for (i in locs){
  mid_big_explore_counts$subject <- mid_big_explore$subject
  d <- as.data.frame(apply(mid_big_explore,1,function(x) sum(x==i))) # not sure what this function is 
  names(d) <- i
  mid_big_explore_counts <- cbind(d, mid_big_explore_counts)
}

mid_big_explore_counts <- mid_big_explore_counts %>% mutate(sex=mid_explr_Subinfo$sex)


```

```{r explore object processing }
yng_big_explore<-as.data.frame(str_split_fixed(yng_expl_df$paths," ",nrow(yng_expl_df)))
yng_big_explore <- yng_big_explore %>% mutate(subject = yng_expl_df$Subject) 
yng_big_explore <-yng_big_explore[,c(ncol(yng_big_explore), 1:(ncol(yng_big_explore)-1))] 

row_labels<-c(1:nrow(yng_big_explore))
yng_big_explore<- split( yng_big_explore , f = row_labels)

#for loop to find consecutive location repeats, and remove them 
for (i in 1:length(yng_big_explore)){
  yng_big_explore[[i]]<-t(yng_big_explore[[i]])
  yng_big_explore[[i]][yng_big_explore[[i]] == ""] <- NA 
  repeat_logical<-t(c(NA, yng_big_explore[[i]]) == c(yng_big_explore[[i]], NA))[1:length(yng_big_explore[[i]])]
  repeats<- grep("TRUE",repeat_logical)
  yng_big_explore[[i]][repeats,1]<-"repeats"  
  yng_big_explore[[i]]<-t(yng_big_explore[[i]])
  yng_big_explore[[i]]<-as.data.frame(yng_big_explore[[i]]) 
}

yng_big_explore<-unsplit(yng_big_explore,row_labels)#merging all chunks back into single dataframe 
yng_big_explore[is.na(yng_big_explore)]<-"none" #replacing all NAs with string, otherwise for loop below won't work 
yng_big_explore <-  yng_big_explore %>% mutate(sex = yng_explr_Subinfo$sex)

#for loop to determine location counts 
yng_big_explore_counts <- data.frame(matrix(ncol = 0, nrow = nrow(yng_big_explore)))#creating dataframe to store counts into  

for (i in locs){
  yng_big_explore_counts$subject <- yng_big_explore$subject
  d <- as.data.frame(apply(yng_big_explore,1,function(x) sum(x==i))) # not sure what this function is 
  names(d) <- i
  yng_big_explore_counts <- cbind(d, yng_big_explore_counts)
}

yng_big_explore_counts <- yng_big_explore_counts %>% mutate(sex=yng_explr_Subinfo$sex)


```


Object Visits Summary: There are sex differences in the young group in that men visited object significantly more than women. There are no sex differences between men and women during midlife. ACross groups Men and women in the age group visited significantly more objects than their younger counter parts. 
```{r object visits }

#midlife 
male_obj_visits <- mid_big_explore_counts %>% filter(sex=="Male") %>%   transmute(subject,sex, A, I, L, K, N, O, P, Y, W)
cols_sum<-c(3:length(male_obj_visits))
male_obj_visits$total= rowSums(male_obj_visits[,cols_sum])
mObj_ave <-aggregate(male_obj_visits$total, list(male_obj_visits$subject), FUN=mean)
mid_male_analysis$TotalObjVisits <- mObj_ave$x
#females
female_obj_visits <- mid_big_explore_counts %>% filter(sex=="Female") %>%   transmute(subject,sex, A, I, L, K, N, O, P, Y, W)
cols_sum<-c(3:length(female_obj_visits))
female_obj_visits$total= rowSums(female_obj_visits[,cols_sum])
fObj_ave <- aggregate(female_obj_visits$total, list(female_obj_visits$subject), FUN=mean)
mid_female_analysis$TotalObjVisits<-fObj_ave$x
#Object Visits- Normality test to assess whether samples are normally distributed
shapiro.test(mid_male_analysis$TotalObjVisits) #normal 
shapiro.test(mid_female_analysis$TotalObjVisits) # normal
#Object Visits - T-Test  # no differe

# GRabbing the young group

male_obj_visits <- yng_big_explore_counts %>% filter(sex=="Male") %>%   transmute(subject,sex, A, I, L, K, N, O, P, Y, W)
cols_sum<-c(3:length(male_obj_visits))
male_obj_visits$total= rowSums(male_obj_visits[,cols_sum])
mObj_ave <-aggregate(male_obj_visits$total, list(male_obj_visits$subject), FUN=mean)
yng_male_analysis$TotalObjVisits <- mObj_ave$x
#females
female_obj_visits <- yng_big_explore_counts %>% filter(sex=="Female") %>%   transmute(subject,sex, A, I, L, K, N, O, P, Y, W)
cols_sum<-c(3:length(female_obj_visits))
female_obj_visits$total= rowSums(female_obj_visits[,cols_sum])
fObj_ave <- aggregate(female_obj_visits$total, list(female_obj_visits$subject), FUN=mean)
yng_female_analysis$TotalObjVisits<-fObj_ave$x

shapiro.test(yng_male_analysis$TotalObjVisits) #normal 
shapiro.test(yng_female_analysis$TotalObjVisits) # normal 



#Instead of a ttest we're going to do an ANOVA

yng_distance <- yng_master_participant %>% select(Subject,sex,age) %>% as.data.frame() %>% mutate(Dist = yng_master_participant$em_path_dist_trav)
mid_distance <- mid_master_participant %>% select(Subject,sex,age) %>% as.data.frame() %>% mutate(Dist = mid_master_participant$em_path_dist_trav)

dist <- rbind(yng_distance,mid_distance)

dist %>% 
  aov_car(formula= Dist~)



# lets do some analysis 

# young female vs young male # signicant difference
# pvalue=  0.02034 d=0.59377
# mean yng=male 9.75
#young =9.15
wilcox.test(yng_female_analysis$TotalObjVisits,yng_male_analysis$TotalObjVisits)
cohensD(yng_female_analysis$TotalObjVisits,yng_male_analysis$TotalObjVisits)

# midlife group 
#non sig  p=0.08762 d=0.4
wilcox.test(mid_female_analysis$TotalObjVisits,mid_male_analysis$TotalObjVisits)
cohensD(mid_female_analysis$TotalObjVisits,mid_male_analysis$TotalObjVisits)

# what about young vs midlife 
# females p-value = 8.953e-10
# midlife =12.45
#young =9.15
wilcox.test(mid_female_analysis$TotalObjVisits,yng_female_analysis$TotalObjVisits)
cohensD(mid_female_analysis$TotalObjVisits,yng_female_analysis$TotalObjVisits)

# males
#p=1.562e-06
# mean yng=9.75
#mid = 13.43478
wilcox.test(mid_male_analysis$TotalObjVisits,yng_male_analysis$TotalObjVisits)
cohensD(mid_male_analysis$TotalObjVisits,yng_male_analysis$TotalObjVisits)
mean(yng_male_analysis$TotalObjVisits)


```

```{r Plots for distance }
yng_distance <- yng_master_participant %>% select(Subject,sex,age) %>% as.data.frame() %>% mutate(Dist = yng_master_participant$em_path_dist_trav)
mid_distance <- mid_master_participant %>% select(Subject,sex,age) %>% as.data.frame() %>% mutate(Dist = mid_master_participant$em_path_dist_trav)

dist <- rbind(yng_distance,mid_distance)

#this was just to create a better grouping
 for (group in 1:nrow(dist)){
   if (dist$age[group] < 25 && dist$sex[group] == "Female" ) {
     dist$group[group] <- "young_female"
     }
   if (dist$age[group] > 35 && dist$sex[group] == "Female" ) {
     dist$group[group] <- "mid_female"
     }
   if (dist$age[group] > 35 && dist$sex[group] == "Male" ) {
     dist$group[group] <- "mid_male"
   }
   if (dist$age[group] < 25 && dist$sex[group] == "Male" ) {
     dist$group[group] <- "young_male"
   }
  }

sam_size <- dist%>%dplyr::group_by(group)%>% dplyr::summarize(num=n())


pdf("Distance Traveled in young and midlife split by gender.pdf")
dist %>%
  left_join(sam_size) %>%
  mutate(myaxis=paste0(group,"\n", "n=", num)) %>%
  ggplot( aes(x=myaxis, y=Dist, fill=group)) +
  #geom_violin() +
  geom_boxplot(width=0.2, color="grey", alpha=0.2) +
  geom_jitter(position = position_jitter(seed = 1, width = 0.1)) +
  scale_colour_brewer(cbPalette) +
  stat_summary(fun="mean",size =0.2, color="red" )+
  theme(legend.position="none", plot.title = element_text(size=14)) +
  ggtitle("Distance in young and midlife split by gender") +
  xlab("") +
  ylab("Distance traveled")
dev.off()

```

```{r Plot for object visits }
yng_obj <- rbind(yng_female_analysis,yng_male_analysis) %>% 
  select(Subject,TotalObjVisits) %>% 
  arrange() %>% 
  mutate(sex= yng_master_participant$sex)%>% 
  mutate(age= yng_master_participant$age)

mid_obj <- rbind(mid_female_analysis,mid_male_analysis) %>% 
  select(Subject,TotalObjVisits) %>% 
  arrange() %>% 
  mutate(sex= mid_master_participant$sex)%>% 
  mutate(age= mid_master_participant$age)

ObjVisits <- rbind(yng_obj,mid_obj)

#this was just to create a better grouping
 for (group in 1:nrow(ObjVisits)){
   if (ObjVisits$age[group] < 25 && ObjVisits$sex[group] == "Female" ) {
     ObjVisits$group[group] <- "young_female"
     }
   if (ObjVisits$age[group] > 35 && ObjVisits$sex[group] == "Female" ) {
     ObjVisits$group[group] <- "mid_female"
     }
   if (ObjVisits$age[group] > 35 && ObjVisits$sex[group] == "Male" ) {
     ObjVisits$group[group] <- "mid_male"
   }
   if (ObjVisits$age[group] < 25 && ObjVisits$sex[group] == "Male" ) {
     ObjVisits$group[group] <- "young_male"
   }
  }

sam_size <- ObjVisits%>%dplyr::group_by(group)%>% dplyr::summarize(num=n())


pdf("Distance Traveled in young and midlife split by gender.pdf")
ObjVisits %>%
  left_join(sam_size) %>%
  mutate(myaxis=paste0(group,"\n", "n=", num)) %>%
  ggplot( aes(x=myaxis, y=TotalObjVisits, fill=group)) +
  #geom_violin() +
    geom_boxplot(width=0.2, color="grey", alpha=0.2) +
    geom_jitter(position = position_jitter(seed = 1, width = 0.1)) +
    scale_colour_brewer(cbPalette) +
    stat_summary(fun="mean",size =0.2, color="red" )+
    theme(legend.position="none", plot.title = element_text(size=14)) +
    ggtitle("Object Visits in young and midlife split by gender") +
    theme(plot.title = element_text(hjust = 0.5))+
  xlab("") +
  ylab("Object Visits")
dev.off()

# LEts just do women 
pdf("Distance Traveled in young and midlife Women.pdf")
ObjVisits %>%
  left_join(sam_size) %>% 
  filter(sex == "Female") %>% 
  mutate(myaxis=paste0(group,"\n", "n=", num)) %>%
  ggplot( aes(x=myaxis, y=TotalObjVisits, fill=group)) +
  #geom_violin() +
    geom_boxplot(width=0.2, color="grey", alpha=0.2) +
    geom_jitter(position = position_jitter(seed = 1, width = 0.1)) +
    scale_colour_brewer(cbPalette) +
    stat_summary(fun="mean",size =0.2, color="red" )+
    theme(legend.position="none", plot.title = element_text(size=14)) +
    ggtitle("Object Visits in young and midlife women") +
    theme(plot.title = element_text(hjust = 0.5))+
    xlab("") +
    ylab("Total bject Visits")
dev.off()


#Lets do men
pdf("Distance Traveled in young and midlife Men.pdf")
ObjVisits %>%
  left_join(sam_size) %>% 
  filter(sex == "Male") %>% 
  mutate(myaxis=paste0(group,"\n", "n=", num)) %>%
  ggplot( aes(x=myaxis, y=TotalObjVisits, fill=group)) +
  #geom_violin() +
    geom_boxplot(width=0.2, color="grey", alpha=0.2) +
    geom_jitter(position = position_jitter(seed = 1, width = 0.1)) +
    scale_colour_brewer(cbPalette) +
    stat_summary(fun="mean",size =0.2, color="red" )+
    theme(legend.position="none", plot.title = element_text(size=14)) +
    ggtitle("Object Visits in young and midlife women") +
    theme(plot.title = element_text(hjust = 0.5))+
    xlab("") +
    ylab("Total Object Visits")
dev.off()





```








Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
