---
title: "Creating Figures for VR output BY Daniela Cossio"
output: html_notebook
---

```{r}
########################################################################
##       Figure: For creating figures for midlife VR output           ##  
##       data input :                                                 ##
##                                                                    ##
##                                                                    ##
########################################################################
```

```{r setup, include=FALSE, echo=FALSE}

# setting our workdir

require("knitr")
opts_knit$set(root.dir = "/Users/danielacossio/Desktop/MLINDIV_analysisDC/VRPilot/DSP/outputs")

getwd()

```

```{r}

# uploading your data that you want to visualize 

df <- read.csv(paste0(workdir,"/","DSPParticipant.csv"))

```
 

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
