---
title: "Manuscript DSP Code"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
   html_document: 
     toc: yes
     toc_float: yes
editor_options: 
  chunk_output_type: inline
---

<!-- Reading in my libraries -->
```{r adding libraries,echo=FALSE, results='hide',message=FALSE}
library(ggplot2)
library(tidyverse)
library(stringr)
library(kableExtra)
library(markdown)
library(psych)
library(ppcor)
library(mediation)
library(knitr)
library(janitor)
#library(car)
#library(ggiraph)
#library(ggiraphExtra)
library(moonBook)
#library(nationalparkcolors)
#library(gridExtra)
# library(dplyr)
# library(tidyr)
# library(data.table)
# library(network)
# library(tidygraph)
# library(ggraph)
# library(igraph)
# library(networkD3)
# library(CINNA)
# library(umap)
# library(plotly)
#library(factoextra)
#library(lsr)
#library(ggpubr)
#library(entropy)
#library(ds4psy)
# library(pROC)
#library(devtools)
#library(BRRR)
#library(stats)
#library(afex)

#library(FSA)
```

<!-- below is code for generating the markdown html. just basic aesthetics -->

```{css, echo=FALSE}
TOC {
  color: #F6B2DB;
  font-family: Arial;
  font-size: "16px"; 
  border-color: #F6B2DB;
}

h1.title {
  color: black ;
  font-family: Arial;
  font-size: "72px";
  padding: "10px 0";
  background-color: #F6B2DB ;
  text-align: center;
}

h4.date {
  color: black ;
  font-family: Arial;
  font-size: "34px";
  text-align: center;
}

h4.author {
  color: black;
  font-size: "34px";
  font-family: Arial;
  text-align: center;
}


h1,h2, h3, h4, h5 ,h6 {
  text-align: center;
  font-family: Arial;
  
}

body, p, h2{
  color: black; 
  font-family: Arial;
}

hr {
  height:5px;
  border-width:0;
  background-color: black ;
}



```


# Overview of experiment and analyses {.tabset .tabset-fade}

This is the complete analysis of the DSP task using white matter and bevaior and hormones. 

<br><br><br>

<hr>

# Methods {.tabset .tabset-pills} 

## **Participants** 
### Midlife 
  * Total number of scans = 120 (males and females)  
  
  * Total scans used in analysis= 69  
  * Excluded subs 329 and 372 from analyses due to bad behavior data and Subject 347 and 424 failed quality 
  control check in DSI
  
    * All subjects = 69 <br>
    * Men = 24 <br>
    * Women = 45 <br>
    * Pre = 18 <br>
    * Peri = 14 <br>
    * Post = 13 <br>

<br><br>

### Young 
  * total subject with DSP = 27
  * Total scans used in analysis= 25  
  * Excluded subs 380 and 384 due to low quality outliar 
  
    * All subjects = 27 <br>
    * Men =  <br>
    * Women =  <br>
 
    
    
<hr> 


  
## **Scan parameters** 

  * Locations from UCSB and UCI
  
<br><br>

<hr> 


## **QSIprep** 

  * Version used: 0.16.0RC3

  * The following parameters were used
    * dwi_denoise_window **5** 
    * hmc_model **3dSHORE** 
    * hmc-transform **Rigid** 
    * shoreline_iters **2**
<br><br>

<hr> 

## **DSI Studio**

  * Version and tags used via singularity container: **chen-2024-05-03**
  
  * **Parameters** 
    * T-threshold = 2.5
    * Length = 25
    * Permutation = 4,000
    * pruning 4
    * QA
    * Covariates: sex, age, and FNAME

<hr>


## **Hormones and behavior**

I am doing a mediation analysis to understand the relation ship between white matter, hormones, and performance on the dual solution paradigm.

From shuying's data, DSP is associated with estradial. Increased solution index is associated with increased solution index.

MD is negatively associated with Solution Index such that increased MD in the fornix is associated with less shortcuts. Essentially lower white matter integrity in fornix is associated with lower performance.

Hypothesis for mediation is that greater estradiol is driving the relationship in which greater integrity in the fornix for greater solution index. 


X= Mean diffusivity in fornix  
Y= greater SI on DSP task  
M= Estradiol  
<br>
<hr>
<br>

**Subject Numbers for DSP analyses**
Total SNAG numbers: 137  
    * 60 removed
Total participants with DSP: 77
Total participants with DSI scans: 73
Total participants used in analyses: 69


Shuyings numbers are as follows from her behavioral task, idk who she excluded:  
Women: 47  
MEn:28  
Total:75

Daniela's

Women: 45   
Men: 23  
Total: 68  

Subjects I excluded 
347 for Low quality outliar
424 for low quality outliar
372 for neurochistosomaisis
388 for cyst in cerebellum
352 for depression

These were excluded later from hippocampal analyses so i just excluded their behavior here as well. Adding these in gives me 77 which is still not the correct number of subjects. I'm not sure which one is the extra. For now I'll add them back in but it shouldn't affect much. 

# Results {.tabset .tabset-pills} 

Reading in and prepping our data 

<!-- Setting the path to our extracted diffusion data and grabbing our subject info -->
```{r reading in our CSVs, results='hide',message=FALSE}
##### Mac Desktop path
working_dir <- "/Users/danielacossio/Desktop/Scripts/Projects/SNAG/DSI_studio/DSP"

# Moving to save all figrues and output into a different folder bc it's too big for github

outputdir <- "/Users/danielacossio/Documents/Chrastil_Lab/Projects/SNAG/DSI/DSP"

# path to the subject sheets 
midlife_DSP_df <- read.csv(paste0(working_dir,"/Mid_DSP_DSI.csv"))

yng_DSP_df <-  read.csv(paste0(working_dir,"/DSP_yng_participant_info.csv"))

yng_DSP_scan_df <-  read.csv(paste0(working_dir,"/DSP_yng_participant_info.csv")) %>%  filter(Subject_ID != 84) %>% filter(Subject_ID != 80)


###### Laptop path

# 
# working_dir <- "/Users/danielacossio/Library/CloudStorage/GoogleDrive-dcossio1@uci.edu/Other computers/My iMac/Chrastil_Lab/Projects/SNAG/DSI/DSP"
# 
# behavior_sub_info <- read.csv("/Users/danielacossio/Library/CloudStorage/GoogleDrive-dcossio1@uci.edu/Other computers/My iMac/Chrastil_Lab/Projects/SNAG/sub_info_sheets/SNAG_Behavior.csv")
# 
# 
# DSP_DSI_DF <- read.csv("/Users/danielacossio/Library/CloudStorage/GoogleDrive-dcossio1@uci.edu/Other computers/My iMac/Chrastil_Lab/Projects/SNAG/sub_info_sheets/DSPDSI.csv") %>%  filter(!is.na(subject_id)) %>%  filter(subject_id != 352)


```

# Young Adult Summary Stats

Total number of young adults with DSP 
Mean = 0.27
SD = 0.15
```{r, sumamry stats for young adults with DSP}
yng_DSP_df %>% dplyr::summarise(count = n(), mean = mean(dsp_si_true_pct, na.rm = TRUE), sd = sd(dsp_si_true_pct, na.rm = TRUE), min(dsp_si_true_pct, na.rm = TRUE), max(dsp_si_true_pct, na.rm = TRUE))
```

<br>

Total number of young adults with DSP+good scan
Mean = 0.26
SD = 0.16

```{r, sumamry stats for young adults with DSP + good scan}
yng_DSP_scan_df %>% dplyr::summarise(count = n(), mean = mean(dsp_si_true_pct, na.rm = TRUE), sd = sd(dsp_si_true_pct, na.rm = TRUE), min(dsp_si_true_pct, na.rm = TRUE), max(dsp_si_true_pct, na.rm = TRUE))
```

<br>


# Midlife Adults Summary Stats

Total number of midlife adults
n = 68
Mean = 0.23
SD = 0.17
```{r, sum stats for midlife adults}
midlife_DSP_df %>% dplyr::summarise(count = n(), mean = mean(dsp_si_true_pct, na.rm = TRUE), sd = sd(dsp_si_true_pct, na.rm = TRUE), min(dsp_si_true_pct, na.rm = TRUE), max(dsp_si_true_pct, na.rm = TRUE))
```

<br>

Midlife stats grouped by sex  

men
  n = 23
  mean = 0.19
  SD = 0.15]
  
<br>
  
women
  n = 45
  mean = 0.25
  SD = 0.18
```{r, sum stats for midlife adults split by sex}
group_by(midlife_DSP_df, sex) %>% dplyr::summarise(count = n(), mean = mean(dsp_si_true_pct, na.rm = TRUE), sd = sd(dsp_si_true_pct, na.rm = TRUE), min(dsp_si_true_pct, na.rm = TRUE), max(dsp_si_true_pct, na.rm = TRUE))
```



Midlife stats grouped by REPO 

Pre 
  n = 18
  mean = 0.31
  SD = 0.17
  
Peri Post
  n = 27
  mean = 0.22
  SD = 0.18
  
```{r, sum stats for midlife adults split by repo status}
group_by(midlife_DSP_df, repo_status) %>% dplyr::summarise(count = n(), mean = mean(dsp_si_true_pct, na.rm = TRUE), sd = sd(dsp_si_true_pct, na.rm = TRUE), min(dsp_si_true_pct, na.rm = TRUE), max(dsp_si_true_pct, na.rm = TRUE))
```

```{r}
# combining peri and post into one group
midlife_DSP_df$repo_status[midlife_DSP_df$repo_status =="Peri"]<-c("Peri_Post")
midlife_DSP_df$repo_status[midlife_DSP_df$repo_status =="Post"]<-c("Peri_Post")


#Creating group DF
Mid_dsp_fem_df <- midlife_DSP_df %>% filter(sex == "Female")
Mid_dsp_male_df <- midlife_DSP_df %>% filter(sex == "Male")
Mid_dsp_pre_df <- midlife_DSP_df %>% filter(repo_status == "Pre")
Mid_dsp_peripost_df <- midlife_DSP_df %>% filter(repo_status != "Pre") %>% filter(repo_status != "Men")

```

# Group comparisons {.tabset .tabset-pills} 

## Midlife vs Young

**Check normality of group**
Not normal
```{r}
shapiro.test(midlife_DSP_df$dsp_si_true_pct)
```
<br>
is normal
```{r}
shapiro.test(yng_DSP_scan_df$dsp_si_true_pct)
```

<br>

Since one is not normal, I will use wilconox test
Young adults do not take more shortcuts than midlife adults, although we see it with shuyings data 


```{r}
wilcox.test(midlife_DSP_df$dsp_si_true_pct, yng_DSP_scan_df$dsp_si_true_pct)
```

**Creating Graph**

```{r, Creating a simple DF with young and midlife}

all_SI_df <- midlife_DSP_df %>% dplyr::select(c("subject_id","sex","age_group","age_scan_years","dsp_si_true_pct","dsp_success_pct"))

temp_yng_df <- yng_DSP_scan_df %>% dplyr::select(c("Subject_ID","sex","age_group","age_scan_years","dsp_si_true_pct","dsp_success_pct")) %>% `colnames<-`(c("subject_id","sex","age_group","age_scan_years","dsp_si_true_pct","dsp_success_pct"))

all_SI_df <- rbind(all_SI_df,temp_yng_df)

```

```{r, out.width="120%"}
dev.size()
all_SI_df %>% ggplot(aes(
  x = factor(age_group, levels = c("Young", "Midlife")),
  y = dsp_si_true_pct,
  fill = age_group
)) + geom_boxplot(width = 0.5,
                  fatten = 1,
                  outliers = FALSE) +
  geom_jitter(width = 0.3, size = 2) +
  #geom_point(size=2) +
  scale_fill_manual(values = c("#7d4c5a", "#6c6c6e")) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2)) +
  xlab("Age Group") +
  ylab("Solution Index (%)") +
  theme(
    axis.title.x = element_text(vjust = -3, size = 24, face = "bold"),
    axis.title.y = element_text(vjust = 4, size = 24,face = "bold"),
    axis.text.x = element_text(
      size = 18,
      color = "black",
      vjust = -2,
      face = "bold"
    ),
    axis.text.y = element_text(
      size = 18,
      color = "black",
      hjust = 2,
      face = "bold"
    ),
    axis.ticks.y = element_line(color = "black",
                                linewidth =1 ),
    #axis.ticks.x = element_blank(),
    axis.ticks.length = unit(0.25, "cm"),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black", linewidth = 1),
    legend.position = "none",
    plot.margin = margin(1,1 , 1, 1, "cm"),
  )
ggsave(paste0(outputdir,"/DSP_age_diff_si.tiff"))

```




<br>
<hr>

**DSP success**


```{r}
wilcox.test(midlife_DSP_df$dsp_success_pct, yng_DSP_scan_df$dsp_success_pct)
```


```{r  out.width="120%"}

dev.size()

all_SI_df %>% ggplot(aes(
  x = factor(age_group, levels = c("Young", "Midlife")),
  y = dsp_success_pct,
  fill = age_group
)) + geom_boxplot(width = 0.5,
                  fatten = 1,
                  outliers = FALSE) +
  geom_jitter(width = 0.3, size = 2) +
  #geom_point(size=2) +
  scale_fill_manual(values = c("#7d4c5a", "#6c6c6e")) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2)) +
  xlab("Age Group") +
  ylab("DSP Success") +
  theme(
    axis.title.x = element_text(vjust = -3, size = 24, face = "bold"),
    axis.title.y = element_text(vjust = 4, size = 24,face = "bold"),
    axis.text.x = element_text(
      size = 18,
      color = "black",
      vjust = -2,
      face = "bold"
    ),
    axis.text.y = element_text(
      size = 18,
      color = "black",
      hjust = 2,
      face = "bold"
    ),
    axis.ticks.y = element_line(color = "black",
                                linewidth =1 ),
    #axis.ticks.x = element_blank(),
    axis.ticks.length = unit(0.25, "cm"),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black", linewidth = 1),
    legend.position = "none",
    plot.margin = margin(1,1, 1, 1, "cm"),
  )
ggsave(paste0(outputdir,"/DSP_age_diff_success.tiff"))

```




## Midlife men vs women

Not sig different here either'
W = 653.5, p-value = 0.07849
```{r}
wilcox.test(Mid_dsp_fem_df$dsp_si_true_pct, Mid_dsp_male_df$dsp_si_true_pct)
```

```{r out.width="120%"}

dev.size()

midlife_DSP_df %>% ggplot(aes(
  x = factor(sex, levels = c("Male", "Female")),
  y = dsp_si_true_pct,
  fill = sex
)) + geom_boxplot(width = 0.5,
                  fatten = 1,
                  outliers = FALSE) +
  geom_jitter(width = 0.3, size = 2) +
  #geom_point(size=2) +
  scale_fill_manual(values = c("#7d4c5a", "#6c6c6e")) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2)) +
  xlab("Sex") +
  ylab("Solution Index (%)") +
  theme(
    axis.title.x = element_text(vjust = -3, size = 24, face = "bold"),
    axis.title.y = element_text(vjust = 4, size = 24,face = "bold"),
    axis.text.x = element_text(
      size = 18,
      color = "black",
      vjust = -2,
      face = "bold"
    ),
    axis.text.y = element_text(
      size = 18,
      color = "black",
      hjust = 2,
      face = "bold"
    ),
    axis.ticks.y = element_line(color = "black",
                                linewidth =1 ),
    #axis.ticks.x = element_blank(),
    axis.ticks.length = unit(0.25, "cm"),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black", linewidth = 1),
    legend.position = "none",
    plot.margin = margin(1,1, 1, 1, "cm"),
  )

ggsave(paste0(outputdir,"/DSP_sexDiff.tiff"))

```

## Midlife X Young X sex and age interaction

### Solution Index

Here we are using the "all_SI_df" variable which as mid and young adults 

**ANOVA**

No main effect of age or sex but an interaction
Relationship between SI and age is dependent on sex 0.0144
```{r, Check group compairsions between DSP}
DSP_SI_ANOVA <- aov(dsp_si_true_pct ~ age_scan_years * sex, data = all_SI_df)
#There is a marginal effect of REPO on performance 

summary(DSP_SI_ANOVA)

```

```{r  out.width="120%"}

dev.size()

all_SI_df %>% ggplot(aes(
  x = factor(age_group, levels = c("Young", "Midlife")),
  y = dsp_si_true_pct,
  fill = interaction(age_group,sex),
)) + geom_boxplot(width = 0.5,
                  fatten = 1,
                  outliers = FALSE,
                    color = "black") +
  geom_jitter(width = 0.3, size = 2) +
  #geom_point(size=2) +
  scale_fill_manual(values = c(Young.Male ="#2d2d2d", Young.Female ="#3e262d", Midlife.Female = "#7d4c5a", Midlife.Male = "#6c6c6e")) + 
  scale_y_continuous(breaks = seq(0, 1, by = 0.2)) +
  xlab("Age Group") +
  ylab("Solution Index") +
  theme(
    axis.title.x = element_text(vjust = -3, size = 24, face = "bold"),
    axis.title.y = element_text(vjust = 4, size = 24,face = "bold"),
    axis.text.x = element_text(
      size = 18,
      color = "black",
      vjust = -2,
      face = "bold"
    ),
    axis.text.y = element_text(
      size = 18,
      color = "black",
      hjust = 2,
      face = "bold"
    ),
    axis.ticks.y = element_line(color = "black",
                                linewidth =1 ),
    #axis.ticks.x = element_blank(),
    axis.ticks.length = unit(0.25, "cm"),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black", linewidth = 1),
    legend.position = "none",
    plot.margin = margin(1,1, 1, 1, "cm"),
  )
ggsave(paste0(outputdir,"/DSP_SI_age_sex_boxplot.tiff"))

# see code below to add a significance label
 #ggsignif::geom_signif(annotations ="*", y_position = c(1), xmin = c(2), xmax =c(3)) +
```

### Success
effect of age <0.0001
effect of sex = 0.0121

no interaction
```{r, Check group comparisons between Success}
DSP_success_ANOVA <- aov(dsp_success_pct ~ age_scan_years * sex, data = all_SI_df)
#There is a marginal effect of REPO on performance 

summary(DSP_success_ANOVA)

```

```{r  out.width="120%"}

dev.size()

all_SI_df %>% ggplot(aes(
  x = factor(age_group, levels = c("Young", "Midlife")),
  y = dsp_success_pct,
  fill = interaction(age_group,sex),
)) + geom_boxplot(width = 0.5,
                  fatten = 1,
                  outliers = FALSE,
                    color = "black") +
  geom_jitter(width = 0.3, size = 2) +
  ggsignif::geom_signif(annotations ="*", y_position = c(1.1), xmin = c(0.7), xmax =c(2.25)) +
  #geom_point(size=2) +
  scale_fill_manual(values = c(Young.Male ="#2d2d2d", Young.Female ="#3e262d", Midlife.Female = "#7d4c5a", Midlife.Male = "#6c6c6e")) + 
  scale_y_continuous(breaks = seq(0, 1, by = 0.2)) +
  xlab("Age Group") +
  ylab("Solution Index") +
  theme(
    axis.title.x = element_text(vjust = -3, size = 24, face = "bold"),
    axis.title.y = element_text(vjust = 4, size = 24,face = "bold"),
    axis.text.x = element_text(
      size = 18,
      color = "black",
      vjust = -2,
      face = "bold"
    ),
    axis.text.y = element_text(
      size = 18,
      color = "black",
      hjust = 2,
      face = "bold"
    ),
    axis.ticks.y = element_line(color = "black",
                                linewidth =1 ),
    #axis.ticks.x = element_blank(),
    axis.ticks.length = unit(0.25, "cm"),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black", linewidth = 1),
    legend.position = "none",
    plot.margin = margin(1,1, 1, 1, "cm"),
  )
ggsave(paste0(outputdir,"/DSP_success_age_s_boxplot.tiff"))

# see code below to add a significance label
 #+
```


## Midlife pre vs peri_post

### SI
These are significantly different  0.037
```{r}
wilcox.test(Mid_dsp_pre_df$dsp_si_true_pct, Mid_dsp_peripost_df$dsp_si_true_pct)
```

```{r}
all_menopause_df <- rbind(Mid_dsp_pre_df,Mid_dsp_peripost_df)
```

```{r out.width="120%"}

dev.size()

all_menopause_df %>% ggplot(aes(
  x = factor(repo_status, levels = c("Pre", "Peri_Post")),
  y = dsp_si_true_pct,
  fill = repo_status
)) + geom_boxplot(width = 0.5,
                  fatten = 1,
                  outliers = FALSE) +
  geom_jitter(width = 0.3, size = 2) +
  #geom_point(size=2) +
  scale_fill_manual(values = c("#7d4c5a", "#6c6c6e")) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2)) +
  xlab("REPO status") +
  ylab("Solution Index (%)") +
  theme(
    axis.title.x = element_text(vjust = -3, size = 24, face = "bold"),
    axis.title.y = element_text(vjust = 4, size = 24,face = "bold"),
    axis.text.x = element_text(
      size = 18,
      color = "black",
      vjust = -2,
      face = "bold"
    ),
    axis.text.y = element_text(
      size = 18,
      color = "black",
      hjust = 2,
      face = "bold"
    ),
    axis.ticks.y = element_line(color = "black",
                                linewidth =1 ),
    #axis.ticks.x = element_blank(),
    axis.ticks.length = unit(0.25, "cm"),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black", linewidth = 1),
    legend.position = "none",
    plot.margin = margin(1,1, 1, 1, "cm"),
  )

ggsave(paste0(outputdir,"/DSP_meno_diff_SI.tiff"))

```

### Success

not significantly different 0.3645
```{r}
wilcox.test(Mid_dsp_pre_df$dsp_success_pct, Mid_dsp_peripost_df$dsp_success_pct)
```


```{r out.width="120%"}

dev.size()

all_menopause_df %>% ggplot(aes(
  x = factor(repo_status, levels = c("Pre", "Peri_Post")),
  y = dsp_success_pct,
  fill = repo_status
)) + geom_boxplot(width = 0.5,
                  fatten = 1,
                  outliers = FALSE) +
  geom_jitter(width = 0.3, size = 2) +
  #geom_point(size=2) +
  scale_fill_manual(values = c("#7d4c5a", "#6c6c6e")) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2)) +
  xlab("REPO status") +
  ylab("Success (%)") +
  theme(
    axis.title.x = element_text(vjust = -3, size = 24, face = "bold"),
    axis.title.y = element_text(vjust = 4, size = 24,face = "bold"),
    axis.text.x = element_text(
      size = 18,
      color = "black",
      vjust = -2,
      face = "bold"
    ),
    axis.text.y = element_text(
      size = 18,
      color = "black",
      hjust = 2,
      face = "bold"
    ),
    axis.ticks.y = element_line(color = "black",
                                linewidth =1 ),
    #axis.ticks.x = element_blank(),
    axis.ticks.length = unit(0.25, "cm"),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black", linewidth = 1),
    legend.position = "none",
    plot.margin = margin(1,1, 1, 1, "cm"),
  )

ggsave(paste0(outputdir,"/DSP_meno_diff_success.tiff"))

```

## Group hormone comparisons

```{r, creating empty dataframe to keep pvalues in}

hormone_comparison <-  data.frame(matrix(ncol = 5, nrow = 0)) %>% `colnames<-`(c("hormone","statistic","p.value","method","alternative"))


```


## Estradiol 

### Comparing pre and peri post hormone levels between pre and peri_post

Significantly different P < 0.001
```{r}
est_wilx_test <- wilcox.test(Mid_dsp_pre_df$estradiol_spatial_pg_ml, Mid_dsp_peripost_df$estradiol_spatial_pg_ml) %>% broom::tidy() %>%  mutate(hormone = "Estradiol") %>% dplyr::select("hormone",everything())

hormone_comparison <- rbind(hormone_comparison, est_wilx_test)

Mid_dsp_pre_df %>% dplyr::summarise(count = n(), mean = mean(estradiol_spatial_pg_ml, na.rm = TRUE), sd = sd(estradiol_spatial_pg_ml, na.rm = TRUE))

Mid_dsp_peripost_df %>% dplyr::summarise(count = n(), mean = mean(estradiol_spatial_pg_ml, na.rm = TRUE), sd = sd(estradiol_spatial_pg_ml, na.rm = TRUE))

```

```{r, estradiol comparison boxplot, out.width="120%"}
# Extract 9 x 6 portrait

dev.size()

all_menopause_df %>% ggplot(aes(x = factor(repo_status, levels=c("Pre", "Peri_Post")), y = estradiol_spatial_pg_ml, fill= repo_status)) +
  geom_boxplot(width=0.5,fatten = 1, show.legend = FALSE) +
  geom_point(shape=16) +
  scale_fill_manual(values=c("#7d4c5a", "#CD8A9B"))+
  #scale_y_continuous(breaks = seq(0, 1, by = 0.2)) +
   xlab("Repo Status")+
   ylab("Estradiol") +
  theme(
    axis.title.x = element_text(vjust = -3, size = 24, face = "bold"),
    axis.title.y = element_text(vjust = 3, size = 24,face = "bold"),
    axis.text.x = element_text(
      size = 18,
      color = "black",
      vjust = -2,
      face = "bold"
    ),
    axis.text.y = element_text(
      size = 18,
      color = "black",
      hjust = 1,
      face = "bold"
    ),
    axis.ticks.y = element_line(color = "black",
                                linewidth =1 ),
    #axis.ticks.x = element_blank(),
    axis.ticks.length = unit(0.25, "cm"),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black", linewidth = 1),
    legend.position = "none",
    plot.margin = margin(1,1, 1, 1, "cm"),
  )

ggsave(paste0(outputdir,"/DSP_Est_boxplot.tiff"))

```

### Estradiol and SI 
**Partial correlations**
**One-tailed correlation controlling for AGE using all females**

Here we want to control for age. ]
Originally shuying did one tailed but we decided to go with two tailed.
**Estradiol is significantly associated with SI when controlling for age (n=45, r(43)=0.37, p=0.014).** 
```{r, warning=FALSE,"2 tailed Est and SI correlation controlling age us"}

pcor.test(Mid_dsp_fem_df$estradiol_spatial_pg_ml,
          Mid_dsp_fem_df$dsp_si_true_pct,
          Mid_dsp_fem_df$age_spatial_years, 
          method = "spearman")

```

**Estradiol is significantly associated with SI (n=45, r(43)=0.46, p=0.0016).** 
```{r, warning=FALSE, "2 tailed Est and SI correlation"}
cor.test(all_menopause_df$estradiol_spatial_pg_ml,
          all_menopause_df$dsp_si_true_pct,
          method = "spearman") 

```


SCatter plot
```{r, "Estradiol VS DSP scatter plot",out.width="120%" }

# Using 
#PDF 9 X 6

dev.size()

all_menopause_df %>% ggplot(aes(x = estradiol_spatial_pg_ml,y = dsp_si_true_pct, color=repo_status)) +
  geom_point(aes(color = factor(repo_status)), size=3) +
  scale_color_manual(values=c( "#7d4c5a","#CD8A9B")) + 
   stat_smooth(method = "lm",
              formula = y ~ x,
              geom = "smooth",
             color="Black",
             se=FALSE)+
  xlab("Estradiol (pg/mL)")+
  ylab("Solution Index (%)") +
  theme(
    axis.title.x = element_text(vjust = -4, size = 24, face = "bold"),
    axis.title.y = element_text(vjust = 4, size = 24,face = "bold"),
    axis.text.x = element_text(
      size = 18,
      color = "black",
      vjust = -2,
      face = "bold"
    ),
    axis.text.y = element_text(
      size = 18,
      color = "black",
      hjust = 1,
      face = "bold"
    ),
    axis.ticks.y = element_line(color = "black",
                                linewidth =1 ),
    #axis.ticks.x = element_blank(),
    axis.ticks.length = unit(0.25, "cm"),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black", linewidth = 1),
    legend.position = "none",
    plot.margin = margin(1,1, 1, 1, "cm"),
  )
  

ggsave(paste0(outputdir,"/DSP_Est_SI_scatterplot.tiff"))

```

### Estradiol and Success 
**Partial correlations**
Originally shuying did one tailed but we decided to go with two tailed.
**Estradiol is significantly associated with SI when controlling for age (n=45, r(43)=0.37, p=0.014).** 
```{r, warning=FALSE,"2 tailed Est and success correlation controlling age us"}

pcor.test(Mid_dsp_fem_df$estradiol_spatial_pg_ml,
          Mid_dsp_fem_df$dsp_success_pct,
          Mid_dsp_fem_df$age_spatial_years, 
          method = "spearman")

```

**Estradiol is significantly associated with SI (n=45, r(43)=0.46, p=0.0016).** 
```{r, warning=FALSE, "2 tailed Est and Success correlation"}
cor.test(all_menopause_df$estradiol_spatial_pg_ml,
          all_menopause_df$dsp_success_pct,
          method = "spearman") 

```

SCatter plot
```{r, "Estradiol VS DSP success scatter plot",out.width="120%" }

# Using 
#PDF 9 X 6

dev.size()

all_menopause_df %>% ggplot(aes(x = estradiol_spatial_pg_ml,y = dsp_success_pct, color=repo_status)) +
  geom_point(aes(color = factor(repo_status)),size=3,alpha = 0.7) +
  scale_color_manual(values=c( "#7d4c5a","#CD8A9B")) + 
   geom_line(stat = "smooth", method = "lm",
            formula = y ~ x,
             alpha = 0.7,
            color = "black",
            size = 1,
             se=FALSE) +
  xlab("Estradiol (pg/mL)")+
  ylab("Success") +
  theme(
    axis.title.x = element_text(vjust = -4, size = 24, face = "bold"),
    axis.title.y = element_text(vjust = 4, size = 24,face = "bold"),
    axis.text.x = element_text(
      size = 18,
      color = "black",
      vjust = -2,
      face = "bold"
    ),
    axis.text.y = element_text(
      size = 18,
      color = "black",
      hjust = 1,
      face = "bold"
    ),
    axis.ticks.y = element_line(color = "black",
                                linewidth =1 ),
    #axis.ticks.x = element_blank(),
    axis.ticks.length = unit(0.25, "cm"),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black", linewidth = 1),
    legend.position = "none",
    plot.margin = margin(1,1, 1, 1, "cm"),
  )
  

ggsave(paste0(outputdir,"/DSP_success_Est_scatterplot.tiff"))

```

### FSH + SI

**Partial correlations**
**One-tailed correlation controlling for AGE using all females**

Here we want to control for age. ]
Originally shuying did one tailed but we decided to go with two tailed.
**FSH is not significantly associated with SI when controlling for age (n=45, r(43)=-0.16, p=0.29).** 
```{r, warning=FALSE,"2 tailed FSH and SI correlation controlling age us"}

pcor.test(Mid_dsp_fem_df$fsh_spatial_miu_ml,
          Mid_dsp_fem_df$dsp_si_true_pct,
          Mid_dsp_fem_df$age_spatial_years, 
          method = "spearman")

```

**FSH is significantly associated with SI (n=45, r(43)=-0.32, p=0.03).** 
```{r, warning=FALSE, "2 tailed FSH and SI correlation"}
cor.test(all_menopause_df$fsh_spatial_miu_ml,
          all_menopause_df$dsp_si_true_pct,
          method = "spearman") 

```


SCatter plot
```{r, "FSH VS DSP scatter plot",out.width="120%" }

# Using 
#PDF 9 X 6

dev.size()

all_menopause_df %>% ggplot(aes(x = fsh_spatial_miu_ml,y = dsp_si_true_pct, color=repo_status)) +
  geom_point(aes(color = factor(repo_status)), size=3) +
  scale_color_manual(values=c( "#7d4c5a","#CD8A9B")) + 
   stat_smooth(method = "lm",
              formula = y ~ x,
              geom = "smooth",
             color="Black",
             se=FALSE)+
  xlab("FSH (pg/mL)")+
  ylab("Solution Index (%)") +
  theme(
    axis.title.x = element_text(vjust = -4, size = 24, face = "bold"),
    axis.title.y = element_text(vjust = 4, size = 24,face = "bold"),
    axis.text.x = element_text(
      size = 18,
      color = "black",
      vjust = -2,
      face = "bold"
    ),
    axis.text.y = element_text(
      size = 18,
      color = "black",
      hjust = 1,
      face = "bold"
    ),
    axis.ticks.y = element_line(color = "black",
                                linewidth =1 ),
    #axis.ticks.x = element_blank(),
    axis.ticks.length = unit(0.25, "cm"),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black", linewidth = 1),
    legend.position = "none",
    plot.margin = margin(1,1, 1, 1, "cm"),
  )
  

ggsave(paste0(outputdir,"/DSP_FSH_SI_scatterplot.tiff"))

```
### FSH + Success

**Partial correlations**
**One-tailed correlation controlling for AGE using all females**

Here we want to control for age. ]
Originally shuying did one tailed but we decided to go with two tailed.
**FSH is not significantly associated with SI when controlling for age (n=45, r(43)=0.002, p=0.99).** 
```{r, warning=FALSE,"2 tailed FSH and success correlation controlling age us"}

pcor.test(Mid_dsp_fem_df$fsh_spatial_miu_ml,
          Mid_dsp_fem_df$dsp_success_pct,
          Mid_dsp_fem_df$age_spatial_years, 
          method = "spearman")

```

**FSH is significantly associated with success (n=45, r(43)=-0.07, p=0.66).** 
```{r, warning=FALSE, "2 tailed FSH and success correlation"}
cor.test(all_menopause_df$fsh_spatial_miu_ml,
          all_menopause_df$dsp_success_pct,
          method = "spearman") 

```


SCatter plot
```{r, "FSH VS DSP success scatter plot",out.width="120%" }

# Using 
#PDF 9 X 6

dev.size()

all_menopause_df %>% ggplot(aes(x = fsh_spatial_miu_ml,y = dsp_success_pct, color=repo_status)) +
  geom_point(aes(color = factor(repo_status)),size=3,alpha = 0.7) +
  scale_color_manual(values=c( "#7d4c5a","#CD8A9B")) + 
   geom_line(stat = "smooth", method = "lm",
            formula = y ~ x,
             alpha = 0.7,
            color = "black",
            size = 1,
             se=FALSE)+
  xlab("FSH (pg/mL)")+
  ylab("Success (%)") +
  theme(
    axis.title.x = element_text(vjust = -4, size = 24, face = "bold"),
    axis.title.y = element_text(vjust = 4, size = 24,face = "bold"),
    axis.text.x = element_text(
      size = 18,
      color = "black",
      vjust = -2,
      face = "bold"
    ),
    axis.text.y = element_text(
      size = 18,
      color = "black",
      hjust = 1,
      face = "bold"
    ),
    axis.ticks.y = element_line(color = "black",
                                linewidth =1 ),
    #axis.ticks.x = element_blank(),
    axis.ticks.length = unit(0.25, "cm"),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black", linewidth = 1),
    legend.position = "none",
    plot.margin = margin(1,1, 1, 1, "cm"),
  )
  

ggsave(paste0(outputdir,"/DSP_FSH_success_scatterplot.tiff"))

```