---
title: "NODDI_2025"
author: "Daniela Cossio"
date: "8/15/2025"
output: html_document
---

```{css, echo=FALSE}
TOC {
  color: #F6B2DB;
  font-family: Times;
  font-size: "16px"; 
  border-color: #F6B2DB;
}

h1.title {
  color: black ;
  font-family: Times;
  font-size: "72px";
  padding: "10px 0";
  background-color: #F6B2DB ;
  text-align: center;
}

h4.date {
  color: black ;
  font-family: Times;
  font-size: "34px";
  text-align: center;
}

h4.author {
  color: black;
  font-size: "34px";
  font-family: Times;
  text-align: center;
}


h1,h2, h3, h4, h5 ,h6 {
  text-align: center;
  font-family: Times;
  
}

body, p, h2{
  color: black; 
  font-family: Times;
}

hr {
  height:5px;
  border-width:0;
  background-color: black ;
}



```

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 100)
```

```{r adding libraries,echo=FALSE, results='hide',message=FALSE}
library(ggplot2)
#(plyr)
library(tidyverse)
library(stringr)
library(kableExtra)
library(markdown)
```

```{r, Functions}


clean_noddi_csv <- function(atlas) {
  #' @description: Purpose of this function is to clean up the CSV that we are reading into here so that we have a nice and clean data frame to work with
  
  #' @input: atlas names such as : "HarvardCort50", "HarvardSub50", "ModelRois"
  
  #' @return: DF
  
  #
  # Inputs
  df <-
    data.frame(matrix(nrow = 0, ncol = 8)) %>% `colnames<-`(columns)
  temp_df <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)
  
  metrics <- c("ICVF", "OD", "ISOVF")
  
  tissues <- c("gm", "wm")
  
  # LEt's create an if statement for Harvard Cort
  
  if (atlas == "HarvardCort50") {
    atlas_dir <- paste0(main_dir, "Data/harvardcort50")
    
    # First we need to go thorugh each CSV
    for (M in metrics) {
      for (t in tissues) {
        CSV <- read_csv(paste0(atlas_dir, "/all_", M, "_", t, "NODDI.csv")) #REad in the correct CSV
        
        # Get number of rows and cols for later
          num_cols <- ncol(CSV)
          num_rows <- nrow(CSV)
        
        # Let's get rid of those subject numbers we actually don't need rn
          
        evenrows <- seq(2,num_rows,2)
        CSV_subnums_removed <- CSV[evenrows,] # also removing an empty row.. should be 78 subs
        
          
        for (col in 1:num_cols) {
          print(col)
          
          # Create new label for Brain area by cleaning column na,es
          colname_split <- colnames(CSV_subnums_removed[, col]) %>%  str_split( " ")
          newcolname <- paste0("harvardcort50_", colname_split[[1]][1])
          colnames(CSV_subnums_removed)[col] <- newcolname
          
          
          # Let's do some cleaning of the  voxel info out of there
          Rawvalue <- as.character(unlist(CSV_subnums_removed[, col]))
          x <- str_split(Rawvalue, " ")
          
          for (row in 1:nrow(CSV_subnums_removed)) {
            CSV_subnums_removed[row, col] <- x[[row]][1] 
            as.numeric(CSV[row, col])
          }
          
          temp_df$Brain_Area <- newcolname
          temp_df$Value <- CSV_subnums_removed[, col]
          temp_df$Metric <- M
          temp_df$Tissue <- t
          temp_df$SubjectID <- sub_info$SubjectID
          temp_df$Age <- sub_info$Age
          temp_df$Score <- sub_info$Score
          temp_df$Gender <- sub_info$Gender
          # Need to make sure subject info get's added here
          df <- rbind(temp_df, df)
        }
        
      }
      
      cleaned_df <- df %>% arrange(Brain_Area)
    }
    colnames(cleaned_df[2]) <- "Value"
    
    
    
    
  } else if (atlas == "HarvardSub50") {
    atlas_dir <- paste0(main_dir, "Data/harvardsub50")
    
    # First we need to go thorugh each CSV
    for (M in metrics) {
      for (t in tissues) {
        CSV <- read_csv(paste0(atlas_dir, "/all_", M, "_", t, "NODDI.csv"))
        
        num_cols <- ncol(CSV)
        num_rows <- nrow(CSV)
         
        # Let's get rid of those subject numbers we actually don't need rn
          
        evenrows <- seq(2,num_rows,2)
        CSV_subnums_removed <- CSV[evenrows,] %>% head(-1) # also removing an empty row.. should be 78 subs
                                   
        for (col in 1:num_cols) {
          print(col)
          
          # Create new label for Brain area by cleaning column na,es
          colname_split <- colnames(CSV_subnums_removed[, col]) %>%  str_split(" ")
          newcolname <- paste0("harvardsub50_", colname_split[[1]][1])
          colnames(CSV_subnums_removed)[col] <- newcolname
          
          
          # Let's do some cleaning of the  voxel info out of there
          Rawvalue <- as.character(unlist(CSV_subnums_removed[, col]))
          x <- str_split(Rawvalue, " ")
          
            for (row in 1:nrow(CSV_subnums_removed)) {
              CSV_subnums_removed[row, col] <- x[[row]][1] 
              as.numeric(CSV_subnums_removed[row, col])
            }
          
          temp_df$Brain_Area <- newcolname
          temp_df$Value <- CSV_subnums_removed[, col]
          temp_df$Metric <- M
          temp_df$Tissue <- t
           temp_df$SubjectID <- sub_info$SubjectID
          temp_df$Age <- sub_info$Age
          temp_df$Score <- sub_info$Score
          temp_df$Gender <- sub_info$Gender
          # Need to make sure subject info get's added here
          df <- rbind(temp_df, df)
        }
        
      }
      
      cleaned_df <- df %>% arrange(Brain_Area)
    }
    colnames(cleaned_df[2]) <- "Value"
    
    
  } else if (atlas == "ModelRois") {
    atlas_dir <- paste0(main_dir, "Data/modelROIs")
    # First we need to go thorugh each CSV
    for (M in metrics) {
      for (t in tissues) {
        CSV <- read_csv(paste0(atlas_dir, "/all_", M, "_", t, "NODDI.csv"))
        
        num_cols <- ncol(CSV)
        num_rows <- nrow(CSV)
        
          evenrows <- seq(2,num_rows,2)
        CSV_subnums_removed <- CSV[evenrows,] %>% head(-1) # also removing an empty row.. should be 78 subs
        
        for (col in 1:num_cols) {
          print(col)
          
          # Create new label for Brain area by cleaning column na,es
          colname_split <- colnames(CSV_subnums_removed[, col]) %>%  str_split(" ")
          newcolname <- paste0("ModelROIs", colname_split[[1]][1])
          colnames(CSV)[col] <- newcolname
          
          
          # Let's do some cleaning of the  voxel info out of there
          Rawvalue <- as.character(unlist(CSV_subnums_removed[, col]))
          x <- str_split(Rawvalue, " ")
          
            for (row in 1:nrow(CSV_subnums_removed)) {
              CSV_subnums_removed[row, col] <- x[[row]][1] 
              as.numeric(CSV[row, col])
            }
          
          
          temp_df$Brain_Area <- newcolname
          temp_df$Value <- CSV_subnums_removed[, col]
          temp_df$Metric <- M
          temp_df$Tissue <- t
          temp_df$SubjectID <- sub_info$SubjectID
          temp_df$Age <- sub_info$Age
          temp_df$Score <- sub_info$Score
          temp_df$Gender <- sub_info$Gender

          # Need to make sure subject info get's added here
          df <- rbind(temp_df, df)
        }
        
      }
      
      cleaned_df <- df %>% arrange(Brain_Area)
    }
    colnames(cleaned_df[2]) <- "Value"
  }
  
  return (cleaned_df)
}


  
```

# Methods {.tabset .tabset-dropdown} 
## Participants 

•	Liz's data shows that we have 79 subjects but my code has 78. I realized that subject 064 failed preproc
  - August 15: Trying to re preprocess abd reconstruct this subject 
  
## Preprocessing

•	All bids data is located here /mnt/chrastil/data/mlindiv
  - converted to bids using heudiconv. Thanks Mike. See scripts in bids folder
  
•	Preprocessing was run using qsiprep 0.16.1. via singularity container
    • For specific output info, see logs

Preproc data was output here          
  “/mnt/chrastil/users/cossio/MLINDIV_young/QSI/qsiprep”
  
•	The scripts to run are located here and contain all of the parameters
  /mnt/chrastil/lab/users/cossio/MLINDIV_young/QSI/
      o	AMICO_QSI_batch_slurm.sh 
      o	AMICO__sbatchscript

- Processing failed for subject 064 but i'm not sure why. Re processing on August 15th 


## Reconstruction
  •	 We used AMICO Noddi to reconstruct the data and extract noddi metrics
      o	First, I created a config file based on Hamsi’s advice to be able to             customize the diffusivity metrics from NODDI
            	File name here:  qsiprep_amico_wm_2025.json
            	Here, we wanted to change the parameter settings for noddi to custom settings
            	Original parameter settings had 1.7E for gray and white matter diffusivity.
            	New settings changed to 
                  •	GM: 1.3E-3
                  •	WM: 1.7E-3
      o	Then I created two separate scripts to be able to run things on Kirby
            	AMICO_QSI_batch_slurm_2025:  Has the recon commands
            	AMICO_sbatchscript: used to send things in batch processes 
      o	output path 
            	qsiprep output: /mnt/chrastil/lab/users/cossio/MLINDIV_young/QSI/qsiprep
            	qsirecon /mnt/chrastil/lab/users/cossio/MLINDIV_young/QSI/qsirecon


## Converting to same space

All of the noddi images and data need to be put into the same space as the atlases. I will be converting the NODDI files to match the atlas.
    1.	Based on my previous code, I assumed that my atlases were already in MNI space so then I just converted all the subjects’ images into the same space 
        a.  note that some more recent DSI studio puts things in MNi. my stuff was not.
        b.	Starting with Harvard Cort 50 
            i.	Code: Step1.Convert2HarvardCort50.sh
            ii.	Did this in a few batches via slurm processing
            iii.	It looks like it matches to the atlas on FSL 
        c.	Harvard sub 50
            i.	Code: Step1_B.Convert2HarvardSub50.sh
        d.	Model ROIs
            i.	Step1_C.Convert2ModelROIs
## Extracting the Data: I ran specific scripts that would go through and run AFNI asave mask to extract voxels
    - Harvard Cort
        2A.harvardcort_extract
        Created a script to go through the GM and WM values and extract using AFNI 3d mask
            
    - Harvard Sub
        2B.harvardcort_extract  
        
    - Model ROIS
        - 2C  
        - the current script is written so that it outputs the actual ROI name instead of just numerical label. We probably want the numerical label so may want to update that script later if you want one over the other. Just have the labels replicate the structure from the other scripts.
        - Note that this script is a bit different and because i didn't include the small bit which made sure to include subject numbers to be printed in the text file like the other two. This means the cleaning script below is different for Model ROIs.

## Data cleaning and wrangling before R
  Something I did for the harvard cort before putting in r is that i manually removed the subject numebrs from the columns that had only subject numbers
  
  




Things that failed below

1.	Let’s create the register brain     (https://dataportal.brainminds.jp/ants-tutorial)
        a.	Registering brain thing did not work. Couldn’t get this command to work. So ignore this
        
Aug 15: relized that I extracted some subjects that need to be excluded

REalized subjects 064 and 092 were not actually processed nor were they reconstructed.


# Reading in subject data

```{r}

#Using liz's old version of the noddi data set so that i also have a template for what i want.
#main_dir <- "/Users/danielacossio/Documents/Chrastil_Lab/Projects/NODDI_2025/"

main_dir <-"/Users/danielacossio/Library/CloudStorage/GoogleDrive-dcossio1@uci.edu/Other computers/My iMac/Chrastil_Lab/Projects/NODDI_2025/"


old_df <- read_csv(paste0(main_dir,"noddi_data.csv"))

columns <- c("Brain_Area","Value","SubjectID","Metric","Score","Age","Gender", "Tissue")    


clean_NODDI_DF <- data.frame(matrix(nrow = 0, ncol = 8)) %>% `colnames<-`(columns)

sub_info <- old_df %>% select("SubjectID","Age","Gender","Score") %>% unique() %>% filter(SubjectID != 64)
  
  
```


# Harvard Cort 50 
I have this as a function up top but it's such a big job that i'm splitting in case i need to re run things seprately 

## ICVF
```{r, harvard cortical 50 ICVF}

# First thing is to read in our first CSV

HC50_ICVF_gm <- read_csv(paste0(main_dir,"Data/harvardcort50/Raw/all_ICVF_gmNODDI.csv"))

HC50_ICVF_wm <- read_csv(paste0(main_dir,"Data/harvardcort50/Raw/all_ICVF_wmNODDI.csv"))

# Get number of rows and cols for later. Same for both so just using one
num_cols <- ncol(HC50_ICVF_gm)
num_rows <- nrow(HC50_ICVF_gm)

# Let's get rid of those subject numbers we actually don't need rn
evenrows <- seq(2,num_rows,2)

HC50_ICVF_gm_subsremoved <- HC50_ICVF_gm[evenrows,]
HC50_ICVF_wm_subsremoved <- HC50_ICVF_wm[evenrows,]

#Updated number of cols

num_cols <- ncol(HC50_ICVF_gm_subsremoved)
num_rows <- nrow(HC50_ICVF_gm_subsremoved)

HC50_ICVF_gm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = 8)) %>% `colnames<-`(columns)
HC50_ICVF_wm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = 8)) %>% `colnames<-`(columns)
temp_gm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)
temp_wm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)

 # Create new label for Brain area by cleaning column names. again same for each database so just using one 

for (col in 1:num_cols) {
  print(col)
  colname_split <- colnames(HC50_ICVF_gm_subsremoved[, col]) %>%  str_split( " ")
  newcolname <- paste0("harvardcort50_", colname_split[[1]][1])
  colnames(HC50_ICVF_gm_subsremoved)[col] <- newcolname
  colnames(HC50_ICVF_wm_subsremoved)[col] <- newcolname
  
  # Let's do some cleaning of the  voxel info out of there first with GM
  raw_value <- as.character(unlist(HC50_ICVF_gm_subsremoved[, col]))
  raw_value_split <- str_split(raw_value, " ")
          for (row in 1:num_rows) {
            HC50_ICVF_gm_subsremoved[row, col] <- raw_value_split[[row]][1] 
          }
  temp_gm$Brain_Area <- newcolname
  temp_gm$Value <- HC50_ICVF_gm_subsremoved[, col]
  temp_gm$Metric <- "ICVF"
  temp_gm$Tissue <- "gm"
  temp_gm$SubjectID <- sub_info$SubjectID
  temp_gm$Age <- sub_info$Age
  temp_gm$Score <- sub_info$Score
  temp_gm$Gender <- sub_info$Gender
  
  
  #now white matter
  raw_value <- as.character(unlist(HC50_ICVF_wm_subsremoved[, col]))
  raw_value_split <- str_split(raw_value, " ")
          for (row in 1:num_rows) {
            HC50_ICVF_wm_subsremoved[row, col] <- raw_value_split[[row]][1] 
          }
  temp_wm$Brain_Area <- newcolname
  temp_wm$Value <- HC50_ICVF_wm_subsremoved[, col]
  temp_wm$Metric <- "ICVF"
  temp_wm$Tissue <- "wm"
  temp_wm$SubjectID <- sub_info$SubjectID
  temp_wm$Age <- sub_info$Age
  temp_wm$Score <- sub_info$Score
  temp_wm$Gender <- sub_info$Gender
  
  # Let's bind everything together 
  HC50_ICVF_gm_CLEANED <- rbind(HC50_ICVF_gm_CLEANED,temp_gm)
  HC50_ICVF_wm_CLEANED <- rbind(HC50_ICVF_wm_CLEANED,temp_wm)
}

#Small cleaning things 

HC50_ICVF_gm_CLEANED$Value <- as.numeric(unlist(HC50_ICVF_gm_CLEANED$Value)) #make sure this is numeric
HC50_ICVF_gm_CLEANED <- HC50_ICVF_gm_CLEANED %>% arrange(Brain_Area) 
colnames(HC50_ICVF_gm_CLEANED[2]) <- "Value"

##WM

HC50_ICVF_wm_CLEANED$Value <- as.numeric(unlist(HC50_ICVF_wm_CLEANED$Value)) #make sure this is numeric
HC50_ICVF_wm_CLEANED <- HC50_ICVF_wm_CLEANED %>% arrange(Brain_Area) 
colnames(HC50_ICVF_wm_CLEANED[2]) <- "Value"

HC50_ICVF_allNODDI <- rbind(HC50_ICVF_wm_CLEANED,HC50_ICVF_gm_CLEANED)
# Export

write.csv(HC50_ICVF_allNODDI,paste0(main_dir,"Data/harvardcort50/Cleaned/HC50_ICVF_NODDI.csv"), row.names = FALSE)


```

## OD
```{r, harvard cortical OD}

# First thing is to read in our first CSV

HC50_OD_gm <- read_csv(paste0(main_dir,"Data/harvardcort50/Raw/all_OD_gmNODDI.csv"))

HC50_OD_wm <- read_csv(paste0(main_dir,"Data/harvardcort50/Raw/all_OD_wmNODDI.csv"))

# Get number of rows and cols for later. Same for both so just using one
num_cols <- ncol(HC50_OD_gm)
num_rows <- nrow(HC50_OD_gm)

# Let's get rid of those subject numbers we actually don't need rn
evenrows <- seq(2,num_rows,2)

HC50_OD_gm_subsremoved <- HC50_OD_gm[evenrows,]
HC50_OD_wm_subsremoved <- HC50_OD_wm[evenrows,]

#Updated number of cols

num_cols <- ncol(HC50_OD_gm_subsremoved)
num_rows <- nrow(HC50_OD_gm_subsremoved)

HC50_OD_gm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = 8)) %>% `colnames<-`(columns)
HC50_OD_wm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = 8)) %>% `colnames<-`(columns)
temp_gm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)
temp_wm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)

 # Create new label for Brain area by cleaning column names. again same for each database so just using one 

for (col in 1:num_cols) {
  print(col)
  colname_split <- colnames(HC50_OD_gm_subsremoved[, col]) %>%  str_split( " ")
  newcolname <- paste0("harvardcort50_", colname_split[[1]][1])
  colnames(HC50_OD_gm_subsremoved)[col] <- newcolname
  colnames(HC50_OD_wm_subsremoved)[col] <- newcolname
  
  # Let's do some cleaning of the  voxel info out of there first with GM
  raw_value <- as.character(unlist(HC50_OD_gm_subsremoved[, col]))
  raw_value_split <- str_split(raw_value, " ")
          for (row in 1:num_rows) {
            HC50_OD_gm_subsremoved[row, col] <- raw_value_split[[row]][1] 
          }
  temp_gm$Brain_Area <- newcolname
  temp_gm$Value <- HC50_OD_gm_subsremoved[, col]
  temp_gm$Metric <- "OD"
  temp_gm$Tissue <- "gm"
  temp_gm$SubjectID <- sub_info$SubjectID
  temp_gm$Age <- sub_info$Age
  temp_gm$Score <- sub_info$Score
  temp_gm$Gender <- sub_info$Gender
  
  
  #now white matter
  raw_value <- as.character(unlist(HC50_OD_wm_subsremoved[, col]))
  raw_value_split <- str_split(raw_value, " ")
          for (row in 1:num_rows) {
            HC50_OD_wm_subsremoved[row, col] <- raw_value_split[[row]][1] 
          }
  temp_wm$Brain_Area <- newcolname
  temp_wm$Value <- HC50_OD_wm_subsremoved[, col]
  temp_wm$Metric <- "OD"
  temp_wm$Tissue <- "wm"
  temp_wm$SubjectID <- sub_info$SubjectID
  temp_wm$Age <- sub_info$Age
  temp_wm$Score <- sub_info$Score
  temp_wm$Gender <- sub_info$Gender
  
  # Let's bind everything together 
  HC50_OD_gm_CLEANED <- rbind(HC50_OD_gm_CLEANED,temp_gm)
  HC50_OD_wm_CLEANED <- rbind(HC50_OD_wm_CLEANED,temp_wm)
}

#Small cleaning things 

HC50_OD_gm_CLEANED$Value <- as.numeric(unlist(HC50_OD_gm_CLEANED$Value)) #make sure this is numeric
HC50_OD_gm_CLEANED <- HC50_OD_gm_CLEANED %>% arrange(Brain_Area) 
colnames(HC50_OD_gm_CLEANED[2]) <- "Value"

##WM

HC50_OD_wm_CLEANED$Value <- as.numeric(unlist(HC50_OD_wm_CLEANED$Value)) #make sure this is numeric
HC50_OD_wm_CLEANED <- HC50_OD_wm_CLEANED %>% arrange(Brain_Area) 
colnames(HC50_OD_wm_CLEANED[2]) <- "Value"

HC50_OD_allNODDI <- rbind(HC50_OD_gm_CLEANED,HC50_OD_wm_CLEANED)
# Export

write.csv(HC50_OD_allNODDI,paste0(main_dir,"Data/harvardcort50/Cleaned/HC50_OD_NODDI.csv"), row.names = FALSE)


```

## ISOVF

```{r, harvard cortical ISOVF}

# First thing is to read in our first CSV

HC50_ISOVF_gm <- read_csv(paste0(main_dir,"Data/harvardsub50/Raw/all_ISOVF_gmNODDI.csv"))

HC50_ISOVF_wm <- read_csv(paste0(main_dir,"Data/harvardsub50/Raw/all_ISOVF_wmNODDI.csv"))

# Get number of rows and cols for later. Same for both so just using one
num_cols <- ncol(HC50_ISOVF_gm)
num_rows <- nrow(HC50_ISOVF_gm)

# Let's get rid of those subject numbers we actually don't need rn
evenrows <- seq(2,num_rows,2)

HC50_ISOVF_gm_subsremoved <- HC50_ISOVF_gm[evenrows,]
HC50_ISOVF_wm_subsremoved <- HC50_ISOVF_wm[evenrows,]

#Updated number of cols

num_cols <- ncol(HC50_ISOVF_gm_subsremoved)
num_rows <- nrow(HC50_ISOVF_gm_subsremoved)

HC50_ISOVF_gm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = 8)) %>% `colnames<-`(columns)
HC50_ISOVF_wm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = 8)) %>% `colnames<-`(columns)
temp_gm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)
temp_wm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)

 # Create new label for Brain area by cleaning column names. again same for each database so just using one 

for (col in 1:num_cols) {
  print(col)
  colname_split <- colnames(HC50_ISOVF_gm_subsremoved[, col]) %>%  str_split( " ")
  newcolname <- paste0("harvardcort50_", colname_split[[1]][1])
  colnames(HC50_ISOVF_gm_subsremoved)[col] <- newcolname
  colnames(HC50_ISOVF_wm_subsremoved)[col] <- newcolname
  
  # Let's do some cleaning of the  voxel info out of there first with GM
  raw_value <- as.character(unlist(HC50_ISOVF_gm_subsremoved[, col]))
  raw_value_split <- str_split(raw_value, " ")
          for (row in 1:num_rows) {
            HC50_ISOVF_gm_subsremoved[row, col] <- raw_value_split[[row]][1] 
          }
  temp_gm$Brain_Area <- newcolname
  temp_gm$Value <- HC50_ISOVF_gm_subsremoved[, col]
  temp_gm$Metric <- "ISOVF"
  temp_gm$Tissue <- "gm"
  temp_gm$SubjectID <- sub_info$SubjectID
  temp_gm$Age <- sub_info$Age
  temp_gm$Score <- sub_info$Score
  temp_gm$Gender <- sub_info$Gender
  
  
  #now white matter
  raw_value <- as.character(unlist(HC50_ISOVF_wm_subsremoved[, col]))
  raw_value_split <- str_split(raw_value, " ")
          for (row in 1:num_rows) {
            HC50_ISOVF_wm_subsremoved[row, col] <- raw_value_split[[row]][1] 
          }
  temp_wm$Brain_Area <- newcolname
  temp_wm$Value <- HC50_ISOVF_wm_subsremoved[, col]
  temp_wm$Metric <- "ISOVF"
  temp_wm$Tissue <- "wm"
  temp_wm$SubjectID <- sub_info$SubjectID
  temp_wm$Age <- sub_info$Age
  temp_wm$Score <- sub_info$Score
  temp_wm$Gender <- sub_info$Gender
  
  # Let's bind everything together 
  HC50_ISOVF_gm_CLEANED <- rbind(HC50_ISOVF_gm_CLEANED,temp_gm)
  HC50_ISOVF_wm_CLEANED <- rbind(HC50_ISOVF_wm_CLEANED,temp_wm)
}

#Small cleaning things 

HC50_ISOVF_gm_CLEANED$Value <- as.numeric(unlist(HC50_ISOVF_gm_CLEANED$Value)) #make sure this is numeric
HC50_ISOVF_gm_CLEANED <- HC50_ISOVF_gm_CLEANED %>% arrange(Brain_Area) 
colnames(HC50_ISOVF_gm_CLEANED[2]) <- "Value"

##WM

HC50_ISOVF_wm_CLEANED$Value <- as.numeric(unlist(HC50_ISOVF_wm_CLEANED$Value)) #make sure this is numeric
HC50_ISOVF_wm_CLEANED <- HC50_ISOVF_wm_CLEANED %>% arrange(Brain_Area) 
colnames(HC50_ISOVF_wm_CLEANED[2]) <- "Value"

HC50_ISOVF_allNODDI <- rbind(HC50_ISOVF_gm_CLEANED,HC50_ISOVF_wm_CLEANED)
# Export

write.csv(HC50_ISOVF_allNODDI,paste0(main_dir,"Data/harvardcort50/Cleaned/HC50_ISOVF_NODDI.csv"), row.names = FALSE)


```


```{r}

ModelROIs <- clean_noddi_csv("ModelRois")


```
```{r}


#trying to split cell

value <- as.character(unlist(CSV[,col]))
x <- str_split(value, " ")
x[[1]][1]

atlas_dir <- read_csv(paste0(main_dir, "Data/harvardcort50","/all_", M, "_", t, "NODDI.csv")) 

odd_rows <- CSV[seq_len(num_rows) %% 2,]

df <- seq(2,num_rows,2)
df1 <- CSV[df,] %>% head(-1)


dfclean <- CSV %>% filter(df) 


```



# Harvard sub

## ICVF
```{r}
# First thing is to read in our first CSV

HS50_ICVF_gm <- read_csv(paste0(main_dir,"Data/harvardsub50/Raw/all_ICVF_gmNODDI.csv"))

HS50_ICVF_wm <- read_csv(paste0(main_dir,"Data/harvardsub50/Raw/all_ICVF_wmNODDI.csv"))

# Get number of rows and cols for later. Same for both so just using one
num_cols <- ncol(HS50_ICVF_gm)
num_rows <- nrow(HS50_ICVF_gm)

# Let's get rid of those subject numbers we actually don't need rn
evenrows <- seq(2,num_rows,2)

HS50_ICVF_gm_subsremoved <- HS50_ICVF_gm[evenrows,]
HS50_ICVF_wm_subsremoved <- HS50_ICVF_wm[evenrows,]

#Updated number of cols

num_cols <- ncol(HS50_ICVF_gm_subsremoved)
num_rows <- nrow(HS50_ICVF_gm_subsremoved)

HS50_ICVF_gm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = 8)) %>% `colnames<-`(columns)
HS50_ICVF_wm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = 8)) %>% `colnames<-`(columns)
temp_gm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)
temp_wm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)

 # Create new label for Brain area by cleaning column names. again same for each database so just using one 

for (col in 1:num_cols) {
  print(col)
  colname_split <- colnames(HS50_ICVF_gm_subsremoved[, col]) %>%  str_split( " ")
  newcolname <- paste0("harvardsub50_", colname_split[[1]][1])
  colnames(HS50_ICVF_gm_subsremoved)[col] <- newcolname
  colnames(HS50_ICVF_wm_subsremoved)[col] <- newcolname
  
  # Let's do some cleaning of the  voxel info out of there first with GM
  raw_value <- as.character(unlist(HS50_ICVF_gm_subsremoved[, col]))
  raw_value_split <- str_split(raw_value, " ")
          for (row in 1:num_rows) {
            HS50_ICVF_gm_subsremoved[row, col] <- raw_value_split[[row]][1] 
          }
  temp_gm$Brain_Area <- newcolname
  temp_gm$Value <- HS50_ICVF_gm_subsremoved[, col]
  temp_gm$Metric <- "ICVF"
  temp_gm$Tissue <- "gm"
  temp_gm$SubjectID <- sub_info$SubjectID
  temp_gm$Age <- sub_info$Age
  temp_gm$Score <- sub_info$Score
  temp_gm$Gender <- sub_info$Gender
  
  
  #now white matter
  raw_value <- as.character(unlist(HS50_ICVF_wm_subsremoved[, col]))
  raw_value_split <- str_split(raw_value, " ")
          for (row in 1:num_rows) {
            HS50_ICVF_wm_subsremoved[row, col] <- raw_value_split[[row]][1] 
          }
  temp_wm$Brain_Area <- newcolname
  temp_wm$Value <- HS50_ICVF_wm_subsremoved[, col]
  temp_wm$Metric <- "ICVF"
  temp_wm$Tissue <- "wm"
  temp_wm$SubjectID <- sub_info$SubjectID
  temp_wm$Age <- sub_info$Age
  temp_wm$Score <- sub_info$Score
  temp_wm$Gender <- sub_info$Gender
  
  # Let's bind everything together 
  HS50_ICVF_gm_CLEANED <- rbind(HS50_ICVF_gm_CLEANED,temp_gm)
  HS50_ICVF_wm_CLEANED <- rbind(HS50_ICVF_wm_CLEANED,temp_wm)
}

#Small cleaning things 

HS50_ICVF_gm_CLEANED$Value <- as.numeric(unlist(HS50_ICVF_gm_CLEANED$Value)) #make sure this is numeric
HS50_ICVF_gm_CLEANED <- HS50_ICVF_gm_CLEANED %>% arrange(Brain_Area) 
colnames(HS50_ICVF_gm_CLEANED[2]) <- "Value"

##WM

HS50_ICVF_wm_CLEANED$Value <- as.numeric(unlist(HS50_ICVF_wm_CLEANED$Value)) #make sure this is numeric
HS50_ICVF_wm_CLEANED <- HS50_ICVF_wm_CLEANED %>% arrange(Brain_Area) 
colnames(HS50_ICVF_wm_CLEANED[2]) <- "Value"

HS50_ICVF_allNODDI <- rbind(HS50_ICVF_wm_CLEANED,HS50_ICVF_gm_CLEANED)
# Export

write.csv(HS50_ICVF_allNODDI,paste0(main_dir,"Data/harvardsub50/Clean/HS50_ICVF_NODDI.csv"), row.names = FALSE)


```

## OD

```{r, harvard cortical OD}

# First thing is to read in our first CSV

HS50_OD_gm <- read_csv(paste0(main_dir,"Data/harvardsub50/Raw/all_OD_gmNODDI.csv"))

HS50_OD_wm <- read_csv(paste0(main_dir,"Data/harvardsub50/Raw/all_OD_wmNODDI.csv"))

# Get number of rows and cols for later. Same for both so just using one
num_cols <- ncol(HS50_OD_gm)
num_rows <- nrow(HS50_OD_gm)

# Let's get rid of those subject numbers we actually don't need rn
evenrows <- seq(2,num_rows,2)

HS50_OD_gm_subsremoved <- HS50_OD_gm[evenrows,]
HS50_OD_wm_subsremoved <- HS50_OD_wm[evenrows,]

#Updated number of cols

num_cols <- ncol(HS50_OD_gm_subsremoved)
num_rows <- nrow(HS50_OD_gm_subsremoved)

HS50_OD_gm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = 8)) %>% `colnames<-`(columns)
HS50_OD_wm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = 8)) %>% `colnames<-`(columns)
temp_gm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)
temp_wm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)

 # Create new label for Brain area by cleaning column names. again same for each database so just using one 

for (col in 1:num_cols) {
  print(col)
  colname_split <- colnames(HS50_OD_gm_subsremoved[, col]) %>%  str_split( " ")
  newcolname <- paste0("harvardsub50_", colname_split[[1]][1])
  colnames(HS50_OD_gm_subsremoved)[col] <- newcolname
  colnames(HS50_OD_wm_subsremoved)[col] <- newcolname
  
  # Let's do some cleaning of the  voxel info out of there first with GM
  raw_value <- as.character(unlist(HS50_OD_gm_subsremoved[, col]))
  raw_value_split <- str_split(raw_value, " ")
          for (row in 1:num_rows) {
            HS50_OD_gm_subsremoved[row, col] <- raw_value_split[[row]][1] 
          }
  temp_gm$Brain_Area <- newcolname
  temp_gm$Value <- HS50_OD_gm_subsremoved[, col]
  temp_gm$Metric <- "OD"
  temp_gm$Tissue <- "gm"
  temp_gm$SubjectID <- sub_info$SubjectID
  temp_gm$Age <- sub_info$Age
  temp_gm$Score <- sub_info$Score
  temp_gm$Gender <- sub_info$Gender
  
  
  #now white matter
  raw_value <- as.character(unlist(HS50_OD_wm_subsremoved[, col]))
  raw_value_split <- str_split(raw_value, " ")
          for (row in 1:num_rows) {
            HS50_OD_wm_subsremoved[row, col] <- raw_value_split[[row]][1] 
          }
  temp_wm$Brain_Area <- newcolname
  temp_wm$Value <- HS50_OD_wm_subsremoved[, col]
  temp_wm$Metric <- "OD"
  temp_wm$Tissue <- "wm"
  temp_wm$SubjectID <- sub_info$SubjectID
  temp_wm$Age <- sub_info$Age
  temp_wm$Score <- sub_info$Score
  temp_wm$Gender <- sub_info$Gender
  
  # Let's bind everything together 
  HS50_OD_gm_CLEANED <- rbind(HS50_OD_gm_CLEANED,temp_gm)
  HS50_OD_wm_CLEANED <- rbind(HS50_OD_wm_CLEANED,temp_wm)
}

#Small cleaning things 

HS50_OD_gm_CLEANED$Value <- as.numeric(unlist(HS50_OD_gm_CLEANED$Value)) #make sure this is numeric
HS50_OD_gm_CLEANED <- HS50_OD_gm_CLEANED %>% arrange(Brain_Area) 
colnames(HS50_OD_gm_CLEANED[2]) <- "Value"

##WM

HS50_OD_wm_CLEANED$Value <- as.numeric(unlist(HS50_OD_wm_CLEANED$Value)) #make sure this is numeric
HS50_OD_wm_CLEANED <- HS50_OD_wm_CLEANED %>% arrange(Brain_Area) 
colnames(HS50_OD_wm_CLEANED[2]) <- "Value"

HS50_OD_allNODDI <- rbind(HS50_OD_gm_CLEANED,HS50_OD_wm_CLEANED)
# Export

write.csv(HS50_OD_allNODDI,paste0(main_dir,"Data/harvardsub50/Clean/HS50_OD_NODDI.csv"), row.names = FALSE)


```

## ISOVF

```{r, harvard cortical ISOVF}

# First thing is to read in our first CSV

HS50_ISOVF_gm <- read_csv(paste0(main_dir,"Data/harvardsub50/Raw/all_ISOVF_gmNODDI.csv"))

HS50_ISOVF_wm <- read_csv(paste0(main_dir,"Data/harvardsub50/Raw/all_ISOVF_wmNODDI.csv"))

# Get number of rows and cols for later. Same for both so just using one
num_cols <- ncol(HS50_ISOVF_gm)
num_rows <- nrow(HS50_ISOVF_gm)

# Let's get rid of those subject numbers we actually don't need rn
evenrows <- seq(2,num_rows,2)

HS50_ISOVF_gm_subsremoved <- HS50_ISOVF_gm[evenrows,]
HS50_ISOVF_wm_subsremoved <- HS50_ISOVF_wm[evenrows,]

#Updated number of cols

num_cols <- ncol(HS50_ISOVF_gm_subsremoved)
num_rows <- nrow(HS50_ISOVF_gm_subsremoved)

HS50_ISOVF_gm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = 8)) %>% `colnames<-`(columns)
HS50_ISOVF_wm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = 8)) %>% `colnames<-`(columns)
temp_gm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)
temp_wm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)

 # Create new label for Brain area by cleaning column names. again same for each database so just using one 

for (col in 1:num_cols) {
  print(col)
  colname_split <- colnames(HS50_ISOVF_gm_subsremoved[, col]) %>%  str_split( " ")
  newcolname <- paste0("harvardsub50_", colname_split[[1]][1])
  colnames(HS50_ISOVF_gm_subsremoved)[col] <- newcolname
  colnames(HS50_ISOVF_wm_subsremoved)[col] <- newcolname
  
  # Let's do some cleaning of the  voxel info out of there first with GM
  raw_value <- as.character(unlist(HS50_ISOVF_gm_subsremoved[, col]))
  raw_value_split <- str_split(raw_value, " ")
          for (row in 1:num_rows) {
            HS50_ISOVF_gm_subsremoved[row, col] <- raw_value_split[[row]][1] 
          }
  temp_gm$Brain_Area <- newcolname
  temp_gm$Value <- HS50_ISOVF_gm_subsremoved[, col]
  temp_gm$Metric <- "ISOVF"
  temp_gm$Tissue <- "gm"
  temp_gm$SubjectID <- sub_info$SubjectID
  temp_gm$Age <- sub_info$Age
  temp_gm$Score <- sub_info$Score
  temp_gm$Gender <- sub_info$Gender
  
  
  #now white matter
  raw_value <- as.character(unlist(HS50_ISOVF_wm_subsremoved[, col]))
  raw_value_split <- str_split(raw_value, " ")
          for (row in 1:num_rows) {
            HS50_ISOVF_wm_subsremoved[row, col] <- raw_value_split[[row]][1] 
          }
  temp_wm$Brain_Area <- newcolname
  temp_wm$Value <- HS50_ISOVF_wm_subsremoved[, col]
  temp_wm$Metric <- "ISOVF"
  temp_wm$Tissue <- "wm"
  temp_wm$SubjectID <- sub_info$SubjectID
  temp_wm$Age <- sub_info$Age
  temp_wm$Score <- sub_info$Score
  temp_wm$Gender <- sub_info$Gender
  
  # Let's bind everything together 
  HS50_ISOVF_gm_CLEANED <- rbind(HS50_ISOVF_gm_CLEANED,temp_gm)
  HS50_ISOVF_wm_CLEANED <- rbind(HS50_ISOVF_wm_CLEANED,temp_wm)
}

#Small cleaning things 

HS50_ISOVF_gm_CLEANED$Value <- as.numeric(unlist(HS50_ISOVF_gm_CLEANED$Value)) #make sure this is numeric
HS50_ISOVF_gm_CLEANED <- HS50_ISOVF_gm_CLEANED %>% arrange(Brain_Area) 
colnames(HS50_ISOVF_gm_CLEANED[2]) <- "Value"

##WM

HS50_ISOVF_wm_CLEANED$Value <- as.numeric(unlist(HS50_ISOVF_wm_CLEANED$Value)) #make sure this is numeric
HS50_ISOVF_wm_CLEANED <- HS50_ISOVF_wm_CLEANED %>% arrange(Brain_Area) 
colnames(HS50_ISOVF_wm_CLEANED[2]) <- "Value"

HS50_ISOVF_allNODDI <- rbind(HS50_ISOVF_gm_CLEANED,HS50_ISOVF_wm_CLEANED)
# Export

write.csv(HS50_ISOVF_allNODDI,paste0(main_dir,"Data/harvardsub50/Clean/HS50_ISOVF_NODDI.csv"), row.names = FALSE)


```

#  Model ROIS

forgot to print out subject number when running this one so we are cutting down on some Wrangle code code
## ICVF
```{r, modelROIs ICVF}

# LEt's get all of our labels and vars ready. I know i mispelled temporal but i'm dumb and mispelled it during the extraction so i'm leaving it here like this for now.
label_names <- c("hippocampus_whole","temproal-polar_PRC","PRC","ERC","PHC","DG_CA3","CA1","Subiculum")

# These are the labels i had when extracting but using the reordered ones above ot match the order of the columns bc i'm too lazy to reorder the actual columns 

# left_labels <- c(1,5,7,9,11,13,15,17)
# right_labels <- c(2,6,8,10,12,14,16,18)

# MODEL ROIS LABELS 
# Hippocampus whole : 1 and 2
# Temporal-polar_PRC : 5 and 6 
# PRC : 7 and 8
# ERC : 9 snd 10 
# PHC : 11 and 12 
# DG_CA3: 13 and 14 
# CA1 : 15 and 16
# Subiculum 17 and 18

##################     1      ######################

# First thing is to read in our first CSV. WE need to also make sure the columns are rordered 

ModelROIs_ICVF_gm <- read_csv("/Users/danielacossio/Desktop/Projects/Noddi/Noddi_modelROIs/all_ICVF_gmNODDI.csv")

ModelROIs_ICVF_wm <- read_csv("/Users/danielacossio/Desktop/Projects/Noddi/Noddi_modelROIs/all_ICVF_wmNODDI.csv")

##################     2      ######################
# LEt's set our  labels based on the order the columns are being read in  
# left_labels <- c(15,13,9,1,11,7,17,5)
# right_labels <- c(16,14,10,2,12,8,18,6)

ModelROISlabels <-c(1,5,7,9,11,13,15,17,2,6,8,10,12,14,16,18)

#Getting number of columns  
num_cols <- ncol(ModelROIs_ICVF_gm)
num_rows <- nrow(ModelROIs_ICVF_wm)

##################     3      ######################

 # creating an empty dataframe to put our stuff in later
ModelROIs_ICVF_gm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = length(ModelROISlabels))) %>% `colnames<-`(columns)

ModelROIs_ICVF_wm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = length(ModelROISlabels))) %>% `colnames<-`(columns)
temp_gm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)
temp_wm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)


##################     4      ######################

# need to get rid of the rows iwth subject numbers since we don't need this anymore. We should be left with just voxel rows.

evenrows <- seq(2,num_rows,2)
ModelROIs_ICVF_gm <- ModelROIs_ICVF_gm[evenrows,]
ModelROIs_ICVF_wm <- ModelROIs_ICVF_wm[evenrows,]


##################     5      ######################

 # Need to go ahead and create new column names for these databses and then combine them as well. Let's go back to ROI numbers

for (col in 1:num_cols) {
  print(col)
  
  # Splitting up the column names for each csv
  # colname_split_L_gm <-
  #   colnames(ModelROIs_L_ICVF_gm[, col]) %>%  str_split(" ")
  # colname_split_R_gm <-
  #   colnames(ModelROIs_R_ICVF_gm[, col]) %>%  str_split(" ")
  # colname_split_L_wm <-
  #   colnames(ModelROIs_L_ICVF_wm[, col]) %>%  str_split(" ")
  # colname_split_R_wm <-
  #   colnames(ModelROIs_R_ICVF_wm[, col]) %>%  str_split(" ")
  
    colname_split_gm <- colnames(ModelROIs_ICVF_gm[, col]) %>%  str_split(" ")
  colname_split_wm <-
    colnames(ModelROIs_ICVF_wm[, col]) %>%  str_split(" ")

  # Replacing the column names for each CSV
  # colnames(ModelROIs_L_ICVF_gm)[col] <-
  #   paste0("ModelROIs_", colname_split_L_gm[[1]][1], "_", left_labels[col])
  # colnames(ModelROIs_R_ICVF_gm)[col] <-
  #   paste0("ModelROIs_", colname_split_R_gm[[1]][1], "_", right_labels[col])
  # colnames(ModelROIs_L_ICVF_wm)[col] <-
  #   paste0("ModelROIs_", colname_split_L_wm[[1]][1], "_", left_labels[col])
  # colnames(ModelROIs_R_ICVF_wm)[col] <-
  #   paste0("ModelROIs_", colname_split_R_wm[[1]][1], "_", right_labels[col])
  
  colnames(ModelROIs_ICVF_gm)[col] <-
    paste0("ModelROIs_", colname_split_gm[[1]][1]) 
  colnames(ModelROIs_ICVF_wm)[col] <-
    paste0("ModelROIs_", colname_split_wm[[1]][1])
  
  # # Let's combine the columns now and also reorder
  # ModelROIs_ICVF_gm <-
  #   cbind(ModelROIs_L_ICVF_gm, ModelROIs_R_ICVF_gm)
  # ModelROIs_ICVF_wm <-
  #   cbind(ModelROIs_L_ICVF_wm, ModelROIs_R_ICVF_wm)
}

##################     6      ######################

# LEt's reorganize the columns so things are in order
  
  newColOrder <-
    c(
      "ModelROIs_1",
      "ModelROIs_2",
      "ModelROIs_5",
      "ModelROIs_6",
      "ModelROIs_7",
      "ModelROIs_8" ,
      "ModelROIs_9",
      "ModelROIs_10",
      "ModelROIs_11",
      "ModelROIs_12",
      "ModelROIs_13",
      "ModelROIs_14",
      "ModelROIs_15",
      "ModelROIs_16",
      "ModelROIs_17",
      "ModelROIs_18"
    )
  
  ModelROIs_ICVF_gm_reorganized <- ModelROIs_ICVF_gm[, newColOrder]
  ModelROIs_ICVF_wm_reorganized <- ModelROIs_ICVF_wm[, newColOrder]
    
##################     7       ######################

# Cleaning up ROI 1 and 2 

ModelROIs_ICVF_gm_reorganized$ModelROIs_1 <- NA
ModelROIs_ICVF_gm_reorganized$ModelROIs_2 <- NA
ModelROIs_ICVF_wm_reorganized$ModelROIs_1 <- NA
ModelROIs_ICVF_wm_reorganized$ModelROIs_2 <- NA


# overwriting previous number of cols and rows befor elooping and cleaning up our voxel information. Splitting cells so it's just the noddi score and not thenumber of voxels 
  
num_cols <- ncol(ModelROIs_ICVF_gm_reorganized)
num_rows <- nrow(ModelROIs_ICVF_gm_reorganized)

#
for (col in 1:num_cols) {
  print(col)
  
   # LEt's go back into that loop and fix our voxels
  # Let's do some cleaning of the  voxel info
  raw_value_gm <-
    as.character(unlist(ModelROIs_ICVF_gm_reorganized[, col])) #GM
  raw_value_wm <-
    as.character(unlist(ModelROIs_ICVF_wm_reorganized[, col])) #WM
  
  raw_value_gm_split <- str_split(raw_value_gm, " ")
  raw_value_wm_split <- str_split(raw_value_wm, " ")
  
  for (row in 1:num_rows) {
    ModelROIs_ICVF_gm_reorganized[row, col] <-
      raw_value_gm_split[[row]][1]
    ModelROIs_ICVF_wm_reorganized[row, col] <-
      raw_value_wm_split[[row]][1]
  }
  
  temp_gm$Brain_Area <- colnames(ModelROIs_ICVF_gm_reorganized[col])
  temp_gm$Value <- ModelROIs_ICVF_gm_reorganized[, col]
  temp_gm$Metric <- "ICVF"
  temp_gm$Tissue <- "gm"
  temp_gm$SubjectID <- sub_info$SubjectID
  temp_gm$Age <- sub_info$Age
  temp_gm$Score <- sub_info$Score
  temp_gm$Gender <- sub_info$Gender
  
  #now white matter
  
  temp_wm$Brain_Area <- colnames(ModelROIs_ICVF_wm_reorganized[col])
  temp_wm$Value <- ModelROIs_ICVF_wm_reorganized[, col]
  temp_wm$Metric <- "ICVF"
  temp_wm$Tissue <- "wm"
  temp_wm$SubjectID <- sub_info$SubjectID
  temp_wm$Age <- sub_info$Age
  temp_wm$Score <- sub_info$Score
  temp_wm$Gender <- sub_info$Gender
  
    # Let's bind everything together 
  ModelROIs_ICVF_gm_CLEANED <- rbind(ModelROIs_ICVF_gm_CLEANED,temp_gm)
  ModelROIs_ICVF_wm_CLEANED <- rbind(ModelROIs_ICVF_wm_CLEANED,temp_wm)
  
}  

##################     8       ######################


#Small cleaning things 

ModelROIs_ICVF_gm_CLEANED$Value <- as.numeric(unlist(ModelROIs_ICVF_gm_CLEANED$Value)) #make sure this is numeric
ModelROIs_ICVF_gm_CLEANED <- ModelROIs_ICVF_gm_CLEANED %>% arrange(Brain_Area) 


##WM

ModelROIs_ICVF_wm_CLEANED$Value <- as.numeric(unlist(ModelROIs_ICVF_wm_CLEANED$Value)) #make sure this is numeric
ModelROIs_ICVF_wm_CLEANED <- ModelROIs_ICVF_wm_CLEANED %>% arrange(Brain_Area) 

##################     9       ######################


ModelROIs_ICVF_allNODDI <- rbind(ModelROIs_ICVF_wm_CLEANED,ModelROIs_ICVF_gm_CLEANED)

# Export

write.csv(ModelROIs_ICVF_allNODDI,paste0(main_dir,"/Data/modelROIs/Clean/ModelROIs_ICVF_NODDI.csv"), row.names = FALSE)


```

## OD
```{r, modelROIs OD}

# LEt's get all of our labels and vars ready. I know i mispelled temporal but i'm dumb and mispelled it during the extraction so i'm leaving it here like this for now.
label_names <- c("hippocampus_whole","temproal-polar_PRC","PRC","ERC","PHC","DG_CA3","CA1","Subiculum")

# These are the labels i had when extracting but using the reordered ones above ot match the order of the columns bc i'm too lazy to reorder the actual columns 
# left_labels <- c(1,5,7,9,11,13,15,17)
# right_labels <- c(2,6,8,10,12,14,16,18)

# MODEL ROIS LABELS 
# Hippocampus whole : 1 and 2
# Temporal-polar_PRC : 5 and 6 
# PRC : 7 and 8
# ERC : 9 snd 10 
# PHC : 11 and 12 
# DG_CA3: 13 and 14 
# CA1 : 15 and 16
# Subiculum 17 and 18


##################     1      ######################

# First thing is to read in our first CSV. WE need to also make sure the columns are rordered 

ModelROIs_OD_gm <- read_csv("/Users/danielacossio/Desktop/Projects/Noddi/Noddi_modelROIs/all_OD_gmNODDI.csv")

ModelROIs_OD_wm <- read_csv("/Users/danielacossio/Desktop/Projects/Noddi/Noddi_modelROIs/all_OD_wmNODDI.csv")

##################     2      ######################
# LEt's set our  labels based on the order the columns are being read in  
# left_labels <- c(15,13,9,1,11,7,17,5)
# right_labels <- c(16,14,10,2,12,8,18,6)

ModelROISlabels <-c(1,5,7,9,11,13,15,17,2,6,8,10,12,14,16,18)

#Getting number of columns  
num_cols <- ncol(ModelROIs_OD_gm)
num_rows <- nrow(ModelROIs_OD_wm)

##################     3      ######################

 # creating an empty dataframe to put our stuff in later
ModelROIs_OD_gm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = length(ModelROISlabels))) %>% `colnames<-`(columns)

ModelROIs_OD_wm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = length(ModelROISlabels))) %>% `colnames<-`(columns)
temp_gm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)
temp_wm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)


##################     4      ######################

# need to get rid of the rows iwth subject numbers since we don't need this anymore. We should be left with just voxel rows.

evenrows <- seq(2,num_rows,2)
ModelROIs_OD_gm <- ModelROIs_OD_gm[evenrows,]
ModelROIs_OD_wm <- ModelROIs_OD_wm[evenrows,]

##################     5      ######################

 # Need to go ahead and create new column names for these databses and then combine them as well. Let's go back to ROI numbers

for (col in 1:num_cols) {
  print(col)
  
  # Splitting up the column names for each csv
    colname_split_gm <- colnames(ModelROIs_OD_gm[, col]) %>%  str_split(" ")
  colname_split_wm <-
    colnames(ModelROIs_OD_wm[, col]) %>%  str_split(" ")

  # Replacing the column names for each CSV
  #
  
  colnames(ModelROIs_OD_gm)[col] <-
    paste0("ModelROIs_", colname_split_gm[[1]][1]) 
  colnames(ModelROIs_OD_wm)[col] <-
    paste0("ModelROIs_", colname_split_wm[[1]][1])
  
  
}

##################     6      ######################

# LEt's reorganize the columns so things are in order
  
  newColOrder <-
    c(
      "ModelROIs_1",
      "ModelROIs_2",
      "ModelROIs_5",
      "ModelROIs_6",
      "ModelROIs_7",
      "ModelROIs_8" ,
      "ModelROIs_9",
      "ModelROIs_10",
      "ModelROIs_11",
      "ModelROIs_12",
      "ModelROIs_13",
      "ModelROIs_14",
      "ModelROIs_15",
      "ModelROIs_16",
      "ModelROIs_17",
      "ModelROIs_18"
    )
  
  ModelROIs_OD_gm_reorganized <- ModelROIs_OD_gm[, newColOrder]
  ModelROIs_OD_wm_reorganized <- ModelROIs_OD_wm[, newColOrder]
  
##################     7       ######################

# Cleaning up ROI 1 and 2 

ModelROIs_OD_gm_reorganized$ModelROIs_1 <- NA
ModelROIs_OD_gm_reorganized$ModelROIs_2 <- NA
ModelROIs_OD_wm_reorganized$ModelROIs_1 <- NA
ModelROIs_OD_wm_reorganized$ModelROIs_2 <- NA


# overwriting previous number of cols and rows befor elooping and cleaning up our voxel information. Splitting cells so it's just the noddi score and not thenumber of voxels 
  
num_cols <- ncol(ModelROIs_OD_gm_reorganized)
num_rows <- nrow(ModelROIs_OD_gm_reorganized)

#
for (col in 1:num_cols) {
  print(col)
  
   # LEt's go back into that loop and fix our voxels
  # Let's do some cleaning of the  voxel info
  raw_value_gm <-
    as.character(unlist(ModelROIs_OD_gm_reorganized[, col])) #GM
  raw_value_wm <-
    as.character(unlist(ModelROIs_OD_wm_reorganized[, col])) #WM
  
  raw_value_gm_split <- str_split(raw_value_gm, " ")
  raw_value_wm_split <- str_split(raw_value_wm, " ")
  
  for (row in 1:num_rows) {
    ModelROIs_OD_gm_reorganized[row, col] <-
      raw_value_gm_split[[row]][1]
    ModelROIs_OD_wm_reorganized[row, col] <-
      raw_value_wm_split[[row]][1]
  }
  
  temp_gm$Brain_Area <- colnames(ModelROIs_OD_gm_reorganized[col])
  temp_gm$Value <- ModelROIs_OD_gm_reorganized[, col]
  temp_gm$Metric <- "OD"
  temp_gm$Tissue <- "gm"
  temp_gm$SubjectID <- sub_info$SubjectID
  temp_gm$Age <- sub_info$Age
  temp_gm$Score <- sub_info$Score
  temp_gm$Gender <- sub_info$Gender
  
  #now white matter
  
  temp_wm$Brain_Area <- colnames(ModelROIs_OD_wm_reorganized[col])
  temp_wm$Value <- ModelROIs_OD_wm_reorganized[, col]
  temp_wm$Metric <- "OD"
  temp_wm$Tissue <- "wm"
  temp_wm$SubjectID <- sub_info$SubjectID
  temp_wm$Age <- sub_info$Age
  temp_wm$Score <- sub_info$Score
  temp_wm$Gender <- sub_info$Gender
  
    # Let's bind everything together 
  ModelROIs_OD_gm_CLEANED <- rbind(ModelROIs_OD_gm_CLEANED,temp_gm)
  ModelROIs_OD_wm_CLEANED <- rbind(ModelROIs_OD_wm_CLEANED,temp_wm)
  
}  

##################     8       ######################


#Small cleaning things 

ModelROIs_OD_gm_CLEANED$Value <- as.numeric(unlist(ModelROIs_OD_gm_CLEANED$Value)) #make sure this is numeric
ModelROIs_OD_gm_CLEANED <- ModelROIs_OD_gm_CLEANED %>% arrange(Brain_Area) 


##WM

ModelROIs_OD_wm_CLEANED$Value <- as.numeric(unlist(ModelROIs_OD_wm_CLEANED$Value)) #make sure this is numeric
ModelROIs_OD_wm_CLEANED <- ModelROIs_OD_wm_CLEANED %>% arrange(Brain_Area) 

##################     9       ######################


ModelROIs_OD_allNODDI <- rbind(ModelROIs_OD_wm_CLEANED,ModelROIs_OD_gm_CLEANED)

# Export

write.csv(ModelROIs_OD_allNODDI,paste0(main_dir,"/Data/modelROIs/Clean/ModelROIs_OD_NODDI.csv"), row.names = FALSE)
```

## ISOVF
```{r, modelROIs ISOVF}

# LEt's get all of our labels and vars ready. I know i mispelled temporal but i'm dumb and mispelled it during the extraction so i'm leaving it here like this for now.
label_names <- c("hippocampus_whole","temproal-polar_PRC","PRC","ERC","PHC","DG_CA3","CA1","Subiculum")

# These are the labels i had when extracting but using the reordered ones above ot match the order of the columns bc i'm too lazy to reorder the actual columns 
# left_labels <- c(1,5,7,9,11,13,15,17)
# right_labels <- c(2,6,8,10,12,14,16,18)

# MODEL ROIS LABELS 
# Hippocampus whole : 1 and 2
# Temporal-polar_PRC : 5 and 6 
# PRC : 7 and 8
# ERC : 9 snd 10 
# PHC : 11 and 12 
# DG_CA3: 13 and 14 
# CA1 : 15 and 16
# Subiculum 17 and 18


##################     1      ######################

# First thing is to read in our first CSV. WE need to also make sure the columns are rordered 

ModelROIs_ISOVF_gm <- read_csv("/Users/danielacossio/Desktop/Projects/Noddi/Noddi_modelROIs/all_ISOVF_gmNODDI.csv")

ModelROIs_ISOVF_wm <- read_csv("/Users/danielacossio/Desktop/Projects/Noddi/Noddi_modelROIs/all_ISOVF_wmNODDI.csv")

##################     2      ######################
# LEt's set our  labels based on the order the columns are being read in  
# left_labels <- c(15,13,9,1,11,7,17,5)
# right_labels <- c(16,14,10,2,12,8,18,6)

ModelROISlabels <-c(1,5,7,9,11,13,15,17,2,6,8,10,12,14,16,18)

#Getting number of columns  
num_cols <- ncol(ModelROIs_ISOVF_gm)
num_rows <- nrow(ModelROIs_ISOVF_wm)

##################     3      ######################

 # creating an empty dataframe to put our stuff in later
ModelROIs_ISOVF_gm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = length(ModelROISlabels))) %>% `colnames<-`(columns)

ModelROIs_ISOVF_wm_CLEANED <-
    data.frame(matrix(nrow = 0, ncol = length(ModelROISlabels))) %>% `colnames<-`(columns)
temp_gm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)
temp_wm <-
    data.frame(matrix(nrow = 78, ncol = 8)) %>% `colnames<-`(columns)


##################     4      ######################

# need to get rid of the rows iwth subject numbers since we don't need this anymore. We should be left with just voxel rows.

evenrows <- seq(2,num_rows,2)
ModelROIs_ISOVF_gm <- ModelROIs_ISOVF_gm[evenrows,]
ModelROIs_ISOVF_wm <- ModelROIs_ISOVF_wm[evenrows,]

##################     5      ######################

 # Need to go ahead and create new column names for these databses and then combine them as well. Let's go back to ROI numbers

for (col in 1:num_cols) {
  print(col)
  
  # Splitting up the column names for each csv
    colname_split_gm <- colnames(ModelROIs_ISOVF_gm[, col]) %>%  str_split(" ")
  colname_split_wm <-
    colnames(ModelROIs_ISOVF_wm[, col]) %>%  str_split(" ")

  # Replacing the column names for each CSV
  #
  
  colnames(ModelROIs_ISOVF_gm)[col] <-
    paste0("ModelROIs_", colname_split_gm[[1]][1]) 
  colnames(ModelROIs_ISOVF_wm)[col] <-
    paste0("ModelROIs_", colname_split_wm[[1]][1])
  
  
}

##################     6      ######################

# LEt's reorganize the columns so things are in order
  
  newColOrder <-
    c(
      "ModelROIs_1",
      "ModelROIs_2",
      "ModelROIs_5",
      "ModelROIs_6",
      "ModelROIs_7",
      "ModelROIs_8" ,
      "ModelROIs_9",
      "ModelROIs_10",
      "ModelROIs_11",
      "ModelROIs_12",
      "ModelROIs_13",
      "ModelROIs_14",
      "ModelROIs_15",
      "ModelROIs_16",
      "ModelROIs_17",
      "ModelROIs_18"
    )
  
  ModelROIs_ISOVF_gm_reorganized <- ModelROIs_ISOVF_gm[, newColOrder]
  ModelROIs_ISOVF_wm_reorganized <- ModelROIs_ISOVF_wm[, newColOrder]
  
##################     7       ######################

# Cleaning up ROI 1 and 2 

ModelROIs_ISOVF_gm_reorganized$ModelROIs_1 <- NA
ModelROIs_ISOVF_gm_reorganized$ModelROIs_2 <- NA
ModelROIs_ISOVF_wm_reorganized$ModelROIs_1 <- NA
ModelROIs_ISOVF_wm_reorganized$ModelROIs_2 <- NA


# overwriting previous number of cols and rows befor elooping and cleaning up our voxel information. Splitting cells so it's just the noddi score and not thenumber of voxels 
  
num_cols <- ncol(ModelROIs_ISOVF_gm_reorganized)
num_rows <- nrow(ModelROIs_ISOVF_gm_reorganized)

#
for (col in 1:num_cols) {
  print(col)
  
   # LEt's go back into that loop and fix our voxels
  # Let's do some cleaning of the  voxel info
  raw_value_gm <-
    as.character(unlist(ModelROIs_ISOVF_gm_reorganized[, col])) #GM
  raw_value_wm <-
    as.character(unlist(ModelROIs_ISOVF_wm_reorganized[, col])) #WM
  
  raw_value_gm_split <- str_split(raw_value_gm, " ")
  raw_value_wm_split <- str_split(raw_value_wm, " ")
  
  for (row in 1:num_rows) {
    ModelROIs_ISOVF_gm_reorganized[row, col] <-
      raw_value_gm_split[[row]][1]
    ModelROIs_ISOVF_wm_reorganized[row, col] <-
      raw_value_wm_split[[row]][1]
  }
  
  temp_gm$Brain_Area <- colnames(ModelROIs_ISOVF_gm_reorganized[col])
  temp_gm$Value <- ModelROIs_ISOVF_gm_reorganized[, col]
  temp_gm$Metric <- "ISOVF"
  temp_gm$Tissue <- "gm"
  temp_gm$SubjectID <- sub_info$SubjectID
  temp_gm$Age <- sub_info$Age
  temp_gm$Score <- sub_info$Score
  temp_gm$Gender <- sub_info$Gender
  
  #now white matter
  
  temp_wm$Brain_Area <- colnames(ModelROIs_ISOVF_wm_reorganized[col])
  temp_wm$Value <- ModelROIs_ISOVF_wm_reorganized[, col]
  temp_wm$Metric <- "ISOVF"
  temp_wm$Tissue <- "wm"
  temp_wm$SubjectID <- sub_info$SubjectID
  temp_wm$Age <- sub_info$Age
  temp_wm$Score <- sub_info$Score
  temp_wm$Gender <- sub_info$Gender
  
    # Let's bind everything together 
  ModelROIs_ISOVF_gm_CLEANED <- rbind(ModelROIs_ISOVF_gm_CLEANED,temp_gm)
  ModelROIs_ISOVF_wm_CLEANED <- rbind(ModelROIs_ISOVF_wm_CLEANED,temp_wm)
  
}  

##################     8       ######################


#Small cleaning things 

ModelROIs_ISOVF_gm_CLEANED$Value <- as.numeric(unlist(ModelROIs_ISOVF_gm_CLEANED$Value)) #make sure this is numeric
ModelROIs_ISOVF_gm_CLEANED <- ModelROIs_ISOVF_gm_CLEANED %>% arrange(Brain_Area) 


##WM

ModelROIs_ISOVF_wm_CLEANED$Value <- as.numeric(unlist(ModelROIs_ISOVF_wm_CLEANED$Value)) #make sure this is numeric
ModelROIs_ISOVF_wm_CLEANED <- ModelROIs_ISOVF_wm_CLEANED %>% arrange(Brain_Area) 

##################     9       ######################


ModelROIs_ISOVF_allNODDI <- rbind(ModelROIs_ISOVF_wm_CLEANED,ModelROIs_ISOVF_gm_CLEANED)

# Export

write.csv(ModelROIs_ISOVF_allNODDI,paste0(main_dir,"/Data/modelROIs/Clean/ModelROIs_ISOVF_NODDI.csv"), row.names = FALSE)

```