---
title: "Hippocampal subfield"
author: "Daniela Cossio"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    keep_tex: true
    
header-includes:
- \usepackage{booktabs}
- \usepackage{sectsty} \allsectionsfont{\centering\huge}
- \usepackage{sectsty} \subsectionfont{\centering\LARGE}
- \usepackage{sectsty} \subsubsectionfont{\centering\Large}
- \usepackage{sectsty} \paragraphfont{\large}
- \usepackage{sectsty} \subparagraphfont{\normalsize}
- \usepackage{titlesec}
- \usepackage{lipsum}
---

\newpage

```{r adding libraries,echo=FALSE, results='hide',message=FALSE}
library(ggplot2)
#(plyr)
library(tidyverse)
# library(dplyr)
# library(tidyr)
library(stringr)
library(kableExtra)
# library(data.table)
# library(network)
# library(tidygraph)
# library(ggraph)
# library(igraph)
# library(networkD3)
# library(CINNA)
# library(umap)
# library(plotly)
#library(factoextra)
#library(lsr)
# library(car)
library(ggpubr)
#library(entropy)
#library(ds4psy)
# library(pROC)
#library(devtools)
#library(BRRR)
#library(stats)
#library(afex)
library(knitr)
library(janitor)
library(car)
library(ggiraph)
library(ggiraphExtra)
library(moonBook)
library(nationalparkcolors)
library(gridExtra)
library(markdown)
library(patchwork)
```

```{r reading in our CSVs,echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


working_dir <-getwd()
  
# Laptop path

columns2grab <-
  c(
    "subject_id",
    "sex",
    "age_group",
    "age_spatial_years",
    "age_scan_years",
    "loop_pe_rad1_m",
    "loop_pe_rad2_m",
    "loop_pe_rad3_m",
    "loop_pe_avg_m",
    "loop_de_rad1_degree",
    "loop_de_rad2_degree",
    "loop_de_rad3_degree",
    "loop_de_avg_degree",
    "loop_ae_rad1_degree",
    "loop_ae_rad2_degree",
    "loop_ae_rad3_degree",
    "loop_ae_avg_degree",
    "t2hipp_vol_avg_ca1",
    "t2hipp_vol_avg_ca23",
    "t2hipp_vol_avg_dg",
    "t2hipp_vol_avg_erc",
    "t2hipp_vol_avg_phc",
    "t2hipp_vol_avg_prc",
    "t2hipp_vol_avg_sub",
    "t2hipp_vol_left_ca1",
    "t2hipp_vol_left_ca23",
    "t2hipp_vol_left_dg",
    "t2hipp_vol_left_erc",
    "t2hipp_vol_left_phc",
    "t2hipp_vol_left_prc",
    "t2hipp_vol_left_sub",
    "t2hipp_vol_right_ca1",
    "t2hipp_vol_right_ca23",
    "t2hipp_vol_right_dg",
    "t2hipp_vol_right_erc",
    "t2hipp_vol_right_phc",
    "t2hipp_vol_right_prc",
    "t2hipp_vol_right_sub",
    "estradiol_scan_pg_ml",
    "progesterone_scan_ng_ml",
    "fsh_scan_miu_ml",
    "shbg_scan_nmol_l",
    "dheas_scan_ug_dl",
    "testosterone_scan_ng_dl",
    "estradiol_spatial_pg_ml",
    "progesterone_spatial_ng_ml",
    "fsh_spatial_miu_ml",
    "shbg_spatial_nmol_l",
    "dheas_spatial_ug_dl",
    "testosterone_spatial_ng_dl"
  )

df <- read.csv("hippocampalsubs.csv") %>% select(columns2grab)
df <- filter(df, df$subject_id != 0)

 #Create T2 total hipp and MTL, averaged and L/R
df <-
  df %>%  mutate(
    avg_total_hipp = t2hipp_vol_avg_ca1 + t2hipp_vol_avg_ca23 + t2hipp_vol_avg_dg + t2hipp_vol_avg_sub,
    
    left_total_hipp = t2hipp_vol_left_ca1 + t2hipp_vol_left_ca23 + t2hipp_vol_left_dg + t2hipp_vol_left_sub,
    
    right_total_hipp = t2hipp_vol_right_ca1 + t2hipp_vol_right_ca23 + t2hipp_vol_right_dg + t2hipp_vol_right_sub,
    
    avg_mtl = t2hipp_vol_avg_ca1 + t2hipp_vol_avg_ca23 + t2hipp_vol_avg_dg + t2hipp_vol_avg_sub + t2hipp_vol_avg_erc + t2hipp_vol_avg_phc + t2hipp_vol_avg_prc,
    
    left_mtl = t2hipp_vol_left_ca1 + t2hipp_vol_left_ca23 + t2hipp_vol_left_dg + t2hipp_vol_left_sub + t2hipp_vol_left_erc + t2hipp_vol_left_phc + t2hipp_vol_left_prc , #note that shuyings original code had left sub in this twice 
    
    right_mtl = t2hipp_vol_right_ca1 + t2hipp_vol_right_ca23 + t2hipp_vol_right_dg + t2hipp_vol_right_sub + t2hipp_vol_right_erc + t2hipp_vol_right_phc + t2hipp_vol_right_prc
  )

df$sexbinary <- df$sex
df$sexbinary[df$sexbinary=="Male"] <- 1
df$sexbinary[df$sexbinary=="Female"] <- 0
df$sexbinary <- as.numeric(df$sexbinary)



# Let's make sure we have some split by sex too 
df_w <- df %>% filter(df$sex=="Female")

df_m <- df %>% filter(df$sex=="Male")


```


\section{Methods}



\vspace{1cm}
\vspace{1cm}



\section{Results}
\vspace{1cm}
\subsection{Angular Error}
\vspace{1cm}

\subsubsection{Average}
Total N= 27
F=16
M=11

\paragraph{CA1}
&nbsp;
There were no significant associations between CA1 and average angular error across men and women. ( Correlations are not controlled by sex.) All linear regressions run with a pearson 
\vspace{1cm}
```{r, Avg CA1 + avg angular error, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

c1 <- ggscatter(df, x = "t2hipp_vol_avg_ca1", y = "loop_ae_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged CA1 Subfield Volume", ylab = "Averaged \nAngular Error (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg CA1 + avg angular error split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


c1a <- ggscatter(df, x = "t2hipp_vol_avg_ca1", y = "loop_ae_avg_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged CA1 Subfield Volume", ylab = "Averaged \nPosition Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, fig.width=10, warning=FALSE,message=FALSE}
library(patchwork)
c1 + c1a
```

\vspace{1cm}

Running multiple linear regressions to see the effect of age and sex and then plotting results

```{r, Avg CA1 + avg angular error MLR, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

avgCA1_fit <- lm(loop_ae_avg_degree ~ t2hipp_vol_avg_ca1 + age_spatial_years + sex ,data= df )

summary(avgCA1_fit)

avgCA1_plot <- ggPredict(avgCA1_fit,terms ="t2hipp_vol_avg_ca1", se=TRUE,interactive=FALSE)

avgCA1_plot
```




\newpage
\paragraph{CA2/3}

\subparagraph{There were no significant associations between CA2/3 and average angular error across men and women. The lm was run using a pearson. When conducting the sex stratification, men were analyzed using a spearman and women with a pearson}

&nbsp;
\vspace{1cm}

```{r, Avg CA2 + avg angular error, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

c2 <- ggscatter(df, x = "t2hipp_vol_avg_ca23", y = "loop_ae_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged CA2 Subfield Volume", ylab = "Averaged \nAngular Error (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg CA2 + avg angular error split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

c2aw <- ggscatter(df_w, x = "t2hipp_vol_avg_ca23", y = "loop_ae_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged CA1 Subfield Volume", ylab = "Averaged \nAngular Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")

c2am <- ggscatter(df_m, x = "t2hipp_vol_avg_ca23", y = "loop_ae_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "spearman",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged CA2 Subfield Volume", ylab = "Averaged \nAngular Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
c2 + (c2aw/c2am)
```

\vspace{1cm}

Running multiple linear regressions to see the effect of age and sex and then plotting results

```{r, Avg CA2 + avg angular error MLR, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

avgCA23_fit <- lm(loop_ae_avg_degree ~ t2hipp_vol_avg_ca23 + age_spatial_years + sex ,data= df )

summary(avgCA23_fit)

avgCA23_plot <- ggPredict(avgCA23_fit, se=TRUE,interactive=FALSE)

avgCA23_plot
```


\paragraph{DG}
&nbsp;
\vspace{1cm}
```{r, Avg DG + avg angular error, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

dg1 <- ggscatter(df, x = "t2hipp_vol_avg_dg", y = "loop_ae_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged dg Subfield Volume", ylab = "Averaged \nAngular Error (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg dg + avg angular error split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


dg1a <- ggscatter(df, x = "t2hipp_vol_avg_dg", y = "loop_ae_avg_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged dg Subfield Volume", ylab = "Averaged \nPosition Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
dg1 + dg1a
```

\vspace{1cm}

Running multiple linear regressions to see the effect of age and sex and then plotting results

```{r, Avg DG + avg angular error MLR, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

avgDG_fit <- lm(loop_ae_avg_degree ~ t2hipp_vol_avg_dg + age_spatial_years + sex ,data= df )

summary(avgDG_fit)

avgDG_plot <- ggPredict(avgDG_fit,terms ="t2hipp_vol_avg_dg", se=TRUE,interactive=FALSE)

avgDG_plot
```

\newpage
\paragraph{PHC}
&nbsp;
\vspace{1cm}
```{r, Avg PHC + avg angular error, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

phc1 <- ggscatter(df, x = "t2hipp_vol_avg_phc", y = "loop_ae_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged phc Subfield Volume", ylab = "Averaged \nAngular Error (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg phc + avg angular error split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


phc1a <- ggscatter(df, x = "t2hipp_vol_avg_phc", y = "loop_ae_avg_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged phc Subfield Volume", ylab = "Averaged \nPosition Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
phc1 + phc1a
```

\vspace{1cm}

Running multiple linear regressions to see the effect of age and sex and then plotting results

```{r, Avg PHC + avg angular error MLR, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

avgPHC_fit <- lm(loop_ae_avg_degree ~ t2hipp_vol_avg_phc + age_spatial_years + sex ,data= df )

summary(avgPHC_fit)

avgPHC_plot <- ggPredict(avgPHC_fit,terms ="t2hipp_vol_avg_phc", se=TRUE,interactive=FALSE)

avgPHC_plot
```

\vspace{1cm}

\paragraph{PRC}
&nbsp;
\vspace{1cm}
```{r, Avg PRC + avg angular error, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

prc1 <- ggscatter(df, x = "t2hipp_vol_avg_prc", y = "loop_ae_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged PRC Subfield Volume", ylab = "Averaged \nAngular Error (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg PRC + avg angular error split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


prc1a <- ggscatter(df, x = "t2hipp_vol_avg_prc", y = "loop_ae_avg_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged PRC Subfield Volume", ylab = "Averaged \nPosition Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
prc1 + prc1a
```

\vspace{1cm}

Running multiple linear regressions to see the effect of age and sex and then plotting results

```{r, Avg PRC + avg angular error MLR, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

avgPRC_fit <- lm(loop_ae_avg_degree ~ t2hipp_vol_avg_prc + age_spatial_years + sex ,data= df )

summary(avgPRC_fit)

avgPRC_plot <- ggPredict(avgPRC_fit,terms ="t2hipp_vol_avg_prc", se=TRUE,interactive=FALSE)

avgPRC_plot
```
\vspace{1cm}


\newpage
\paragraph{ERC}
&nbsp;
\vspace{1cm}
```{r, Avg ERCC + avg angular error, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

ERC1 <- ggscatter(df, x = "t2hipp_vol_avg_erc", y = "loop_ae_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged ERC Subfield Volume", ylab = "Averaged \nAngular Error (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg ERC + avg angular error split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


ERC1a <- ggscatter(df, x = "t2hipp_vol_avg_erc", y = "loop_ae_avg_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged PRC Subfield Volume", ylab = "Averaged \nPosition Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
ERC1 + ERC1a
```

\vspace{1cm}

Running multiple linear regressions to see the effect of age and sex and then plotting results

```{r, Avg ERC + avg angular error MLR, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

avgERC_fit <- lm(loop_ae_avg_degree ~ t2hipp_vol_avg_erc + age_spatial_years + sex ,data= df )

summary(avgERC_fit)

avgERC_plot <- ggPredict(avgERC_fit,terms ="t2hipp_vol_avg_erc", se=TRUE,interactive=FALSE)

avgERC_plot
```
\vspace{1cm}

\paragraph{SUB}
&nbsp;
\vspace{1cm}
```{r, Avg sub + avg angular error, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

sub1 <- ggscatter(df, x = "t2hipp_vol_avg_sub", y = "loop_ae_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged sub Subfield Volume", ylab = "Averaged \nAngular Error (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg sub + avg angular error split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


sub1aw <- ggscatter(df_w, x = "t2hipp_vol_avg_sub", y = "loop_ae_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "spearman",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged sub Subfield Volume ", ylab = "Averaged \nAngular Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")

sub1am <- ggscatter(df_m, x = "t2hipp_vol_avg_sub", y = "loop_ae_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged sub Subfield Volume ", ylab = "Averaged \nAngular Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
sub1 + (sub1aw/sub1am)
```

\vspace{1cm}

Running multiple linear regressions to see the effect of age and sex and then plotting results

```{r, Avg SUB + avg angular error MLR, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

avgSUB_fit <- lm(loop_ae_avg_degree ~ t2hipp_vol_avg_sub + age_spatial_years + sex ,data= df )

summary(avgSUB_fit)

avgSUB_plot <- ggPredict(avgSUB_fit,terms ="t2hipp_vol_avg_sub", se=TRUE,interactive=FALSE)

avgSUB_plot
```
\vspace{1cm}

\newpage
\subsubsection{rad3}

\paragraph{CA1}
&nbsp;
\vspace{1cm}
```{r, Avg CA1 + rad3 angular error, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

c1_rad3 <- ggscatter(df, x = "t2hipp_vol_avg_ca1", y = "loop_ae_rad3_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged CA1 Subfield Volume", ylab = "Rad3 \nAngular Error (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg CA1 + rad3 angular error split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


c1a_rad3 <- ggscatter(df, x = "t2hipp_vol_avg_ca1", y = "loop_ae_rad3_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged CA1 Subfield Volume", ylab = "Rad3 \nPosition Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, fig.width=10, warning=FALSE,message=FALSE}
library(patchwork)
c1_rad3 + c1a_rad3
```

\vspace{1cm}

Running multiple linear regressions to see the effect of age and sex and then plotting results

```{r, Avg CA1 + rad3 angular errorMLR, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

rad3CA1_fit <- lm(loop_ae_rad3_degree ~ t2hipp_vol_avg_ca1 + age_spatial_years + sex ,data= df )

summary(rad3CA1_fit)

rad3CA1_plot <- ggPredict(rad3CA1_fit,terms ="t2hipp_vol_avg_ca1", se=TRUE,interactive=FALSE)

rad3CA1_plot
```
\vspace{1cm}

\paragraph{CA2/3}
&nbsp;
\vspace{1cm}
```{r, Avg CA2 + rad3 angular error, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

c23_rad3 <- ggscatter(df, x = "t2hipp_vol_avg_ca23", y = "loop_ae_rad3_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged CA2 Subfield Volume", ylab = "Rad3 \nAngular Error (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg CA2 + Rad3 angular error split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


c23a_rad3 <- ggscatter(df, x = "t2hipp_vol_avg_ca23", y = "loop_ae_rad3_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged CA1 Subfield Volume", ylab = "Rad3 \nPosition Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
c23_rad3 + c23a_rad3
```

\vspace{1cm}

Running multiple linear regressions to see the effect of age and sex and then plotting results

```{r, avg CA2/3 + rad3 angular errorMLR, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

rad3CA23_fit <- lm(loop_ae_rad3_degree ~ t2hipp_vol_avg_ca23 + age_spatial_years + sex ,data= df )

summary(rad3CA23_fit)

rad3CA23_plot <- ggPredict(rad3CA23_fit,terms ="t2hipp_vol_avg_ca23", se=TRUE,interactive=FALSE)

rad3CA23_plot
```
\vspace{1cm}


\newpage
\paragraph{DG}
&nbsp;
\vspace{1cm}
```{r, Avg DG + Rad3 angular error, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

dg1_rad3 <- ggscatter(df, x = "t2hipp_vol_avg_dg", y = "loop_ae_rad3_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged dg Subfield Volume", ylab = "Rad3 \nAngular Error (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg dg + Rad3 angular error split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


dg1a_rad3 <- ggscatter(df, x = "t2hipp_vol_avg_dg", y = "loop_ae_rad3_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged dg Subfield Volume", ylab = "Rad3 \nPosition Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
dg1_rad3 + dg1a_rad3
```


\vspace{1cm}

Running multiple linear regressions to see the effect of age and sex and then plotting results

```{r, AVG DG + rad3 angular errorMLR, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

rad3DG_fit <- lm(loop_ae_rad3_degree ~ t2hipp_vol_avg_dg + age_spatial_years + sex ,data= df )

summary(rad3DG_fit)

rad3DG_plot <- ggPredict(rad3DG_fit,terms ="t2hipp_vol_avg_dg", se=TRUE,interactive=FALSE)

rad3DG_plot
```
\vspace{1cm}


\paragraph{PHC}
&nbsp;
\vspace{1cm}
```{r, Avg PHC + rad3 angular error, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

phc1_rad3 <- ggscatter(df, x = "t2hipp_vol_avg_phc", y = "loop_ae_rad3_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged phc Subfield Volume", ylab = "Rad3 \nAngular Error (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg phc + Rad3 angular error split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


phc1a_rad3 <- ggscatter(df, x = "t2hipp_vol_avg_phc", y = "loop_ae_rad3_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged phc Subfield Volume", ylab = "Rad3 \nPosition Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
phc1_rad3 + phc1a_rad3
```

\vspace{1cm}

Running multiple linear regressions to see the effect of age and sex and then plotting results

```{r, Avg PHC + rad3 angular errorMLR, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

rad3PHC_fit <- lm(loop_ae_rad3_degree ~ t2hipp_vol_avg_phc + age_spatial_years + sex ,data= df )

summary(rad3PHC_fit)

rad3PHC_fit <- ggPredict(rad3PHC_fit,terms ="t2hipp_vol_avg_phc", se=TRUE,interactive=FALSE)

rad3PHC_fit
```
\vspace{1cm}

\newpage
\paragraph{PRC}
&nbsp;
\vspace{1cm}
```{r, Avg PRC + Rad3 angular error, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

prc1_rad3 <- ggscatter(df, x = "t2hipp_vol_avg_prc", y = "loop_ae_rad3_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged PRC Subfield Volume", ylab = "Rad3 \nAngular Error (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg PRC + Rad3 angular error split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


prc1a_rad3 <- ggscatter(df, x = "t2hipp_vol_avg_prc", y = "loop_ae_rad3_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged PRC Subfield Volume", ylab = "Rad3 \nPosition Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
prc1_rad3 + prc1a_rad3
```

\vspace{1cm}

Running multiple linear regressions to see the effect of age and sex and then plotting results

```{r, Avg PRC + rad3 angular errorMLR, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

rad3PRC_fit <- lm(loop_ae_rad3_degree ~ t2hipp_vol_avg_prc + age_spatial_years + sex ,data= df )

summary(rad3PRC_fit)

rad3PRC_plot <- ggPredict(rad3PRC_fit,terms ="t2hipp_vol_avg_phc", se=TRUE,interactive=FALSE)

rad3PRC_plot
```
\vspace{1cm}

\paragraph{ERC}
&nbsp;
\vspace{1cm}
```{r, Avg ERC + Rad3 angular error, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

ERC1_rad3 <- ggscatter(df, x = "t2hipp_vol_avg_erc", y = "loop_ae_rad3_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged ERC Subfield Volume", ylab = "Rad3 \nAngular Error (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg ERC + Rad3 angular error split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


ERC1a_rad3 <- ggscatter(df, x = "t2hipp_vol_avg_erc", y = "loop_ae_rad3_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged PRC Subfield Volume", ylab = "Rad3 \nPosition Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
ERC1_rad3 + ERC1a_rad3
```

\vspace{1cm}

Running multiple linear regressions to see the effect of age and sex and then plotting results

```{r, Avg ERC + rad3 angular errorMLR, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

rad3ERC_fit <- lm(loop_ae_rad3_degree ~ t2hipp_vol_avg_erc + age_spatial_years + sex ,data= df )

summary(rad3ERC_fit)

rad3ERC_plot <- ggPredict(rad3ERC_fit,terms ="t2hipp_vol_avg_phc", se=TRUE,interactive=FALSE)

rad3ERC_plot
```
\vspace{1cm}


\newpage
\paragraph{SUB}
&nbsp;
\vspace{1cm}
```{r, Avg sub + Rad3 angular error, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

sub1_rad3 <- ggscatter(df, x = "t2hipp_vol_avg_sub", y = "loop_ae_rad3_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged sub Subfield Volume", ylab = "Rad3 \nAngular Error (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg sub + Rad3 angular error split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


sub1a_rad3 <- ggscatter(df, x = "t2hipp_vol_avg_sub", y = "loop_ae_rad3_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged sub Subfield Volume", ylab = "Rad3 \nPosition Error (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
sub1_rad3 + sub1a_rad3
```


\vspace{1cm}

Running multiple linear regressions to see the effect of age and sex and then plotting results

```{r, Avg SUB + rad3 angular errorMLR, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

rad3SUB_fit <- lm(loop_ae_rad3_degree ~ t2hipp_vol_avg_sub + age_spatial_years + sex ,data= df )

summary(rad3SUB_fit)

rad3SUB_plot <- ggPredict(rad3SUB_fit,terms ="t2hipp_vol_avg_phc", se=TRUE,interactive=FALSE)

rad3SUB_plot
```
\vspace{1cm}

\newpage

\subsection{Degrees Traveled Error}
\vspace{1cm}

\subsubsection{Average}


\paragraph{CA1}
&nbsp;
\vspace{1cm}
```{r, Avg CA1 + AVG Degrees Traveled, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

DT_CA1 <- ggscatter(df, x = "t2hipp_vol_avg_ca1", y = "loop_de_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged CA1 Subfield Volume", ylab = "Avg \nDegrees Traveled (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg CA1 + AVG Degrees Traveled split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


DT_CA1a <- ggscatter(df, x = "t2hipp_vol_avg_ca1", y = "loop_de_avg_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged CA1 Subfield Volume", ylab = "Avg \nDegrees Traveled (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, fig.width=10, warning=FALSE,message=FALSE}
library(patchwork)
DT_CA1 + DT_CA1a
```


\vspace{1cm}

Running multiple linear regressions to see the effect of age and sex and then plotting results

```{r, Avg CA1 + AVG Degrees Traveled MLR, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

avgCA1_dt_fit <- lm(loop_de_avg_degree ~ t2hipp_vol_avg_ca1 + age_spatial_years + sex ,data= df )

summary(avgCA1_dt_fit)

avgCA1_dt_plot <- ggPredict(avgCA1_dt_fit,terms ="t2hipp_vol_avg_phc", se=TRUE,interactive=FALSE)

avgCA1_dt_plot
```
\vspace{1cm}


\paragraph{CA2/3}
&nbsp;
\vspace{1cm}
```{r, Avg CA2 + AVG Degrees Traveled, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

DT_CA23 <- ggscatter(df, x = "t2hipp_vol_avg_ca23", y = "loop_de_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged CA2 Subfield Volume", ylab = "Avg \nDegrees Traveled (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg CA2 + AVG Degrees Traveled split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


DT_CA23w <- ggscatter(df_w, x = "t2hipp_vol_avg_ca23", y = "loop_de_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged CA2 Subfield Volume", ylab = "Avg \nDegrees Traveled (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")

DT_CA23m <- ggscatter(df_m, x = "t2hipp_vol_avg_ca23", y = "loop_de_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "spearman",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged CA2 Subfield Volume", ylab = "Avg \nDegrees Traveled (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
DT_CA23 + (DT_CA23w / DT_CA23m)
```

\paragraph{DG}
&nbsp;
\vspace{1cm}
```{r, Avg DG + AVG Degrees Traveled, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

DT_DG <- ggscatter(df, x = "t2hipp_vol_avg_dg", y = "loop_de_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged DG Subfield Volume", ylab = "Avg \nDegrees Traveled (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg DG + AVG Degrees Traveled split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


DT_DGa <- ggscatter(df, x = "t2hipp_vol_avg_dg", y = "loop_de_avg_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged DG Subfield Volume", ylab = "Avg \nDegrees Traveled (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
DT_DG + DT_DGa
```

\paragraph{ERC}
&nbsp;
\vspace{1cm}
```{r, Avg ERC + AVG Degrees Traveled, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

DT_ERC <- ggscatter(df, x = "t2hipp_vol_avg_erc", y = "loop_de_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged ERC Subfield Volume", ylab = "Avg \nDegrees Traveled (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg ERC + AVG Degrees Traveled split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


DT_ERCa <- ggscatter(df, x = "t2hipp_vol_avg_erc", y = "loop_de_avg_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged ERC Subfield Volume", ylab = "Avg \nDegrees Traveled (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
DT_ERC + DT_ERCa
```

\paragraph{PHC}
&nbsp;
\vspace{1cm}
```{r, Avg PHC + AVG Degrees Traveled, echo=FALSE,message = FALSE,warning=FALSE, error=FALSE}

DT_PHC <- ggscatter(df, x = "t2hipp_vol_avg_phc", y = "loop_de_avg_degree",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged PHC Subfield Volume", ylab = "Avg \nDegrees Traveled (m)", ) +
    theme(legend.position = "top", legend.title=element_blank())


```

```{r, Avg PHC + AVG Degrees Traveled split by sex, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}


DT_PHCa <- ggscatter(df, x = "t2hipp_vol_avg_phc", y = "loop_de_avg_degree", color = "sex",
          add = "reg.line",
          add.params = list(color = "black", fill = "lightgray"), # Customize reg. line
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          conf.int = TRUE,
          cor.method = "pearson",
          cor.coeff.args = list(label.sep = "\n"),
          xlab = "Averaged PHC Subfield Volume", ylab = "Avg \nDegrees Traveled (m)") +
    facet_wrap(. ~ sex, scale = "free", ncol = 1) +
     theme_bw() +
     theme(legend.position = "none")


```

```{r, echo=FALSE, message=FALSE, fig.width=10, warning=FALSE}
library(patchwork)
DT_PHC + DT_PHCa
```

\subsubsection{Rad3}